### 2019-04-26 Manuscript.tex
first

\documentclass[review]{elsarticle}
\usepackage{amssymb}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{tikz}
%\usetikzlibrary{arrows,shapes}
%\usetikzlibrary{shapes.geometric}
%\usetikzlibrary{arrows.meta}
\usepackage{authblk}
\usepackage{graphics,graphicx}
\usepackage{mathrsfs}
\usepackage{amsmath,bm}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{setspace}
\graphicspath{{picture/}}
\graphicspath{{TikzFig/}}

%\journal{Journal of Computational Physics}
\bibliographystyle{elsarticle-num}

\begin{document}

\title{A multi-material HLLC Riemann solver with both elastic and plastic waves for 1D  elastic-plastic flows}
\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
%\cortext[mycorrespondingauthor]{
%Correspondence to: Junbo Cheng, Institute of Applied Physics and Computational Mathematics, Beijing 100094, China. E-mail: Cheng\_junbo@iapcm.ac.cn}

\maketitle

\address{$^1$  Institute of Applied Physics and Computational Mathematics, Beijing 100094, China }

\begin{abstract}
  A multi-material HLLC-type  approximate Riemann solver with both elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic flows with the  hypo-elastic model and the von Mises yielding condition. Although Cheng in 2016 introduced a HLLC Riemann solver with elastic waves(HLLCE) for 1D elastic-plastic flows, Cheng assumed that pressure is continuous across the contact wave. This assumption maybe lead to big errors, especially for multi-material elastic-plastic flows. In our MHLLCEP, this assumption is not used again, and correspondingly the errors introduced by the assumption are deleted, describing and evaluating the plastic waves are more accurate than that in the HLLCE. Moreover, if the non-linear waves in the Riemann problem are only shock waves, even with the plastic waves, our MHLLCEP is theoretically accurate. For  the multi-material system, in this paper, a ghost cell method is used to achieve a high-order spatial reconstruction across the interface without numerical oscillations. Based on the MHLLCEP, combining with the third-order WENO reconstruction method and the third-order Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic-plastic flows is built in this paper. A number of numerical experiments are carried out. Numerical results show  that the presented third-order scheme is convergent, robust, and essentially non-oscillatory. Moreover, for multi-material elastic-plastic flows, the scheme with  the MHLLCEP is more accurate and reasonable in resolving the multi-material interface than the scheme with the  HLLCE.
\end{abstract}

\begin{keyword}
  HLLC Riemann solver, high-order cell-centered Lagrangian scheme,  WENO scheme,  hypo-elastic model, elastic-plastic flows
\end{keyword}

%\end{frontmatter}

\section{Introduction}

In this paper, a multi-material elastic-plastic HLLC-type approximate Riemann solver(MHLLCEP) is developed, with the capability of resolving both elastic and plastic waves, to simulate one-dimensional  multi-material elastic-plastic solid problems with the isotropic elastic-plastic model \cite{wilkins1963calculation} and  the von Mises' yielding condition in the framework of the  high-order cell-centered Lagrangian scheme.

Generally, elastic-plastic flows can be mainly simulated in three ways, Eulerian methods \cite{trangenstein1991higher,miller2001high,barton2009exact}, staggered Lagrangian schemes \cite{wilkins1963calculation} and cell-centered Lagrangian schemes \cite{burton2013cell,kluth2010discretization,maire2013nominally,cheng2017third} that  is considered in this paper. Comparing with the staggered Lagrangian scheme, cell-centered Lagrangian  schemes  have many advantages. Firstly, it's no necessary to add  extra artificial viscosity  which  must be used in the staggered Lagrangian schemes; Secondly, it is easy to guarantee the total energy conservation; Besides, it can also be used to simulate the problems with both  hyper-elastic and hypo-elastic models  \cite{burton2013cell,kluth2010discretization,maire2013nominally,cheng2017third}  as a Lagrangian scheme.

%In the  Godunov-type method
For a cell-centered Lagrangian scheme, a core process is to move the node of grids with the speed of fluids
 % and to construct the conservative flux
 by solving a Riemann problem at each cell face. As the Riemann problem contains many physical structures, especially in elastic-plastic flows, such as elastic waves, plastic waves and contact waves
  %or interfaces between different materials
  , the property of the approximate Riemann solver is of great importance in the simulation. Recently, a lot of works have been done in
  this area. For example, Gavrilyuk et al. \cite{gavrilyuk2008modelling} analyzed the structure of the Riemann solution and construct a Riemann solver for the linear elastic system  of hyperbolic non-conservative models for transverse waves, wherein, an extra evolution equation was added in order to make the elastic transformations reversible in the absence of shock waves. Despres \cite{despres2007geometrical} built a shock solution to a non-conservations reversible system of hypo-elasticity models and found that a sonic point is necessary to construct  the compression solution that begins at a constrained compressed state.  Cheng et al.  \cite{cheng2015high} analyzed the wave structures of one-dimensional elastic-plastic flows and developed an effective two-rarefaction approximate Riemann solver with elastic waves (TRRSE) and built a  second-order and  a third-order cell-centered Lagrangian schemes based on the TRRSE, but the TRRSE is a little  expensive as  the iteration method is used.
In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves. In the HLLCE,  Cheng evaluated the deviatoric stresses from the following \emph{assumption: a pressure is continuous across the contact wave}. This assumption is valid for pure fluids, but  in  elastic-plastic flows, this assumption may lead to some errors. There are three cases we need  to consider.
\begin{enumerate}
  \item If states in the star regions on both sides of the contact wave are elastic, this assumption does not result in errors;
  \item If both states reach the elastic limit, there are two cases need  to be taken into account:
  \begin{enumerate}
    \item if both  materials in both sides of the interface are same, this assumption does not result in errors either.
    \item if  materials are different, this assumption will result in big errors because the yielding strengths of different materials are different;
  \end{enumerate}
  \item If one state in one side of the interface reaches the elastic limit, but another is  not,  this assumption will  also result in big errors.
\end{enumerate}

%For above considerations,
In this paper, in order to eliminate these errors,
 we want to construct a new HLLC-type Riemann solver for 1D multi-material elastic-plastic flows. In the new solver, both the elastic waves and plastic waves are correctly resolved and the assumption in \cite{cheng2016harten} that the pressure is continuous across the interface is deleted; Correspondingly, the errors introduced by the assumption will also be eliminated.

Based on the MHLLCEP, we develop a high-order elastic-plastic cell-centered Lagrangian scheme for one-dimensional multi-material elastic-plastic flows. If we directly use the WENO reconstruction method \cite{liu2018novel} for multi-material elastic-plastic problems,
%With a high-order reconstruction scheme,
the spacial stencil may cross the material interface
% and in a multi-material state, and  will cause oscillation
 and numerical oscillations may be caused near the interface. In order to delete the numerical oscillations neat the material interface, a ghost cell method is used
   %in the  multi-material system to obtain a stable high-order reconstruction.
   Combined with an improved third-order WENO scheme\cite{liu2018novel} and the third-order Runge-Kutta scheme, a high-order cell-centered Lagrangian scheme is given in this paper for one-dimensional multi-material elastic-plastic flows.

This paper is organized as follows. In section 2, we briefly introduce the governing equations to be studied. In section 3, the MHLLCEP method is constructed.  Then, high-order elastic-plastic cell-centered Lagrangian scheme is given in section 4. Some numerical examples are presented to validate the method.  Conclusions are shown in section 5.

\section{Governing equations}
In this paper, the elastic energy is not included in the total energy. The exclution of the elastic energy is usual for practical engineering problems \cite{maire2013nominally} and is different from that in Ref.\cite{gavrilyuk2008modelling}.

The governing equations system is given as 
 \begin{equation}\label{eq:1d}
   \left\{ \begin{aligned}
       & \partial _t \rho +\partial_x(\rho u)=0,\\
       & \partial _t (\rho u)+\partial_x(\rho u^2 + p -s_{xx})=0,\\
       &\partial _t (\rho E)+\partial_x\left[(\rho E + p -s_{xx})u\right]=0,\\
       &\partial _t s_{xx}+u\partial_xs_{xx}-\frac{4}{3}\partial_x u=0,\\
& |s_{xx}|\leq \frac{2}{3}Y_{0}, \\
        \end{aligned}
  \right.
\end{equation}
It contains the following parts.

\subsection{Conservation terms}
For  the  continuous one-dimensional solid, the conservation terms  in differential form can be  given as
\begin{equation*}
\partial_t \mathbf{{U}} + \partial _x \bm{F}(\mathbf{{U}}) = 0, \   x \in \   \Omega \subset \mathbf{R}, \  t>0,
\end{equation*}
where
\begin{equation}
  \mathbf{U} = \left[ \begin{array}{l}
      \rho \\
      \rho u \\
      \rho  E \\
    \end{array}
  \right],
  \hspace{0.3cm}
  \mathbf{F} = \left[ \begin{array}{l}
      \rho u \\
      \rho u^2 -\sigma\\
      (\rho E -\sigma)u\\
  \end{array} \right],
\end{equation}
$\rho$, $u$, $\sigma$ and $E$ are  the density, velocity in $x-$direction, Cauchy stress and total energy per unit volume, respectively, $E$ has the relation with specific internal energy $e$ as
\begin{equation}
  E = e+\frac{1}{2}u^2,
\end{equation}
\begin{equation}
  \sigma = -p +s_{xx},
\end{equation}
where $p$ and $s_{xx}$ denote hydrostatic pressure and deviatoric stress in the $x-$ direction, respectively.

\subsection{The equation of state (EOS)}

The relation of the pressure with  the density and the specific internal energy is gotten from the equation of state (EOS). In this paper, we consider the Mie-Gr\"uneisen EOS,
\begin{equation}\label{eq:mie}
  p(\rho,e) = \rho_0 a_0^2f(\eta)+ \rho_0 \Gamma_0 e,
\end{equation}
where $f(\eta) = \frac{(\eta-1)(\eta-\Gamma_0(\eta-1)/2)}{(\eta-s(\eta-1))^2}$, $\eta = \frac{\rho}{\rho_0}$, $\rho_0$, $a_0$, $s$ and $\Gamma_0$ are constant parameters of the Mie-Gr\"uneisen EOS.

\subsection{The constitutive relation}
Hooke's law is used here to describe the relationship between the deviatoric stress and the strain,
\begin{equation}\label{eq:sxx1}
\dot{s}_{xx} = 2\mu \left(\dot{\varepsilon}_x-\frac{1}{3}\frac{\dot{V}}{V}\right),
\end{equation}
where $\mu$ is the shear modulus, $V$ is the volume, and the dot means the material time derivative,
\begin{equation}\label{eq:mt}
  \dot{()} = \frac{\partial ()}{\partial t} + u \frac{\partial ()}{\partial t},
\end{equation}
and
\begin{equation}\label{eq:vare}
  \dot{\varepsilon}_x = \frac{\partial u}{\partial x}, \hspace{0.3cm} \frac{\dot{V}}{V} = \frac{\partial u}{\partial x}.
\end{equation}

By using Eq.(\ref{eq:vare}), Eq.(\ref{eq:sxx1}) can be rewritten as
\begin{equation}\label{eq:sxx}
  \frac{\partial s_{xx}}{\partial t} + u \frac{\partial s_{xx}}{\partial t} =\frac{4}{3}\mu \frac{\partial u}{\partial x}.
\end{equation}

\subsection{The yielding condition}
The Von Mises' yielding condition is used here to describe the elastic limit. In one spatial dimension, the von Mises' yielding criterion is given by
\begin{equation}
  |s_{xx}| \le \frac{2}{3}Y_0,
\end{equation}
where $Y_0$ is the yield strength of the material in simple tension.

\section{The Riemann problem}

The Riemann problem for the 1D time dependent elastic-plastic equations is given as follows:
 \begin{equation}\label{eq:1d}
   \left\{ \begin{aligned}
       & \partial _t \rho +\partial_x(\rho u)=0,\\
       & \partial _t (\rho u)+\partial_x(\rho u^2 + p -s_{xx})=0,\\
       &\partial _t (\rho E)+\partial_x\left[(\rho E + p -s_{xx})u\right]=0,\\
       &\partial _t s_{xx}+u\partial_xs_{xx}-\frac{4}{3}\partial_x u=0,\\
& |s_{xx}|\leq \frac{2}{3}Y_{0}, \\
       &Q(x,t = 0) = \left\{\begin{aligned}
           Q_L, \hspace{0.1cm} \text{if} \hspace{0.1cm} x<0, \\
           Q_R, \hspace{0.1cm} \text{if} \hspace{0.1cm} x\ge 0, \\
       \end{aligned}\right.
     \end{aligned}
  \right.
\end{equation}
where $Q = (\rho, \rho u, \rho E, s_{xx})^T$.

According to the yielding of the material, the euqations may have different Jacobian matrix and different sonic velocities. We will discuss them seprately.
\subsection{Jacobian matrix in  elastic regions} %and the eigenvalues and eigenvectors}
For the Mie-Gr\"uneisen EOS, if the material is not yielding and 
\begin{equation}
  |s_{xx}| < \frac{2}{3}Y_0,
\end{equation}
the system (\ref{eq:1d}) can be written as
\begin{equation}
 \partial_t \mathbf{Q} +\mathbf{J}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
\end{equation}
where $Q = (\rho, \rho u, \rho E, s_{xx})$, and the Jacobian matrix is 
\begin{equation}\label{eq:Jcb}
  J(Q) = \left[\begin{array}{llll}
      0 & 1 & 0 & 0 \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma & -1 \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u & -\Gamma u^2 -\frac{\sigma}{\rho}+\frac{u^2}{2} +e & (1+\Gamma)u& -u\\
    \frac{4}{3}\mu\frac{u}{\rho} & -\frac{4}{3}\mu\frac{1}{\rho}& 0 & u \\
\end{array}
\right],
\end{equation}
where $\Gamma = \frac{\Gamma_0\rho_0}{\rho} $.

The eigenvalues of the coefficient matrix $\mathbf{J}(\mathbf{Q})$ are given as
\begin{equation}
  \lambda_1 =\lambda_2 = u, \hspace{0.3cm} \lambda_3 = u-c, \hspace{0.3cm} \lambda_4 = u+c,
\end{equation}
where
\begin{equation}\label{eq:c_e}
  \left\{ \begin{aligned}
      & c = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}},\\
    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
      \end{aligned} \right.
    \end{equation}
The corresponding right eigenvectors are
\begin{equation}\label{eq:eiv}
  r_1 = \left[ \begin{array}{l}
      \frac{1}{b_1} \\
      \frac{u}{b_1} \\
      0 \\
      1 \\
    \end{array}
    \right], \hspace{0.2cm}
    r_2= \left[ \begin{array}{l}
        -\frac{\Gamma}{b_1} \\
        -\frac{\Gamma u}{b_1} \\
        1 \\
        0\\
      \end{array}
    \right], \hspace{0.2cm}
r_3 =   \frac{1}{\phi^2}\left[\begin{array}{l}
        1 \\
        u-c \\
        h -uc \\
        \phi^2
      \end{array}
    \right], \hspace{0.2cm}
r_4 = \frac{1}{\phi^2}\left[\begin{array}{l}
        1 \\
        u+c \\
        h +uc \\
        \phi^2
      \end{array}
    \right],
  \end{equation}
  where
  \begin{equation}
    b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho},
  \end{equation}
  and
  \begin{equation}
    \phi^2 = a^2 -\frac{\rho_0}{\rho^2} \Gamma_0 s_{xx}-c^2 = -\frac{4\mu}{3}\frac{1}{\rho}.
  \end{equation}
\subsection{Jacobian matrix in  plastic  regions}
When the material is yielding,
\begin{equation}
  |s_{xx}| = \frac{2}{3}Y_0,
\end{equation}
the equations will turn into a more simple system with only constitutive terms as
\begin{equation}
  \partial_t \mathbf{{U}} + \mathbf{J}_p(\mathbf{U})\partial_x \mathbf{{U}}= 0,
\end{equation}
where $\mathbf{U} = (\rho, \rho u, \rho E )$, and the Jacobian matrix is
\begin{equation}
\mathbf{J}_p(\mathbf{U}) = \left[\begin{array}{lll}
      0 & 1 & 0   \\
      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma \\
	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u +\frac{u^2}{2} & -\Gamma u^2 -\frac{\sigma}{\rho} +e & (1+\Gamma)u\\
\end{array}
\right].
\end{equation} 
The eigenvalues of 
The eigenvalues of the coefficient matrix $\mathbf{J}_p(\mathbf{Q})$ are given as
$$\lambda_1 = u,\quad \lambda_2 = u-c, \quad \lambda_3 = u+c,$$
where 
\begin{equation}\label{eq:c_p}
  \left\{ \begin{aligned}
	  & c = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}} ,\\
    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
      \end{aligned} \right.
    \end{equation}
The corresponding right eigenvectors are
\begin{equation}\label{eq:eivp}
  r_1 = \left[ \begin{array}{l}
	  1 \\
	  u \\
	  E-\frac{c^2}{\Gamma}-\frac{\sigma}{\rho}\\
  \end{array}\right], \quad
 r_2 = \left[ \begin{array}{l}
	  1 \\
	  u-c \\
	  E-uc-\frac{\sigma}{\rho}\\
  \end{array}\right], \quad
 r_3 = \left[ \begin{array}{l}
	  1 \\
	  u+c \\
	  E+uc-\frac{\sigma}{\rho}\\
  \end{array}\right].
\end{equation}
Take a comparason  of Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}), we notice that the sonic speed is not continuous between the states of elastic and plastic. This is very important and may cause wrong results if ignoring it.

\subsection{Formulations across the contact wave}\label{sec:contact}
  For  a  system without molecular diffusion, there is no materials convecting  across the contact wave or interface, so the velocities on two sides of  the discontinuity are always equal. % .
  This can also be verified by the eigenvectors  in Eq.(\ref{eq:eiv}) and  Eq.(\ref{eq:eivp}).

Using $\mathbf{W}_L^*$ and $\mathbf{W}_R^*$ to denote the two data states connected the contact wave, where $\mathbf{W}=\left(\rho,u,p,s_{xx}\right)$.

According to  the eigenvectors in  Eq.(\ref{eq:eiv}), for the $\lambda_{1}$-wave and $\lambda_{2}$ wave,  we
have
\begin{equation}   \label{e23a}
\frac{d \rho}{1} = \frac{d \rho u}{u}.
\end{equation}
From the above equations, we can easily deduce that
\begin{equation}   \label{e23b}
du = 0,
\end{equation}

Samilarly, using the eigenvectors in Eq.(\ref{eq:eivp}), for the $\lambda_{1}$-wave, we have 
\begin{equation}  
  \frac{d \rho}{1} = \frac{d \rho u}{u},
\end{equation}
we also can get 
\begin{equation}  
du = 0,
\end{equation}
 which means
\begin{equation}   \label{e23c}
  u_{L}^{\ast}=u_{R}^{\ast},
\end{equation}
For convenience, we define
\begin{equation}\label{eq:contact}
  s^* = u_L^* = u_R^*. % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
\end{equation}
where $s^*$ denotes the velocity of the contact wave.

Then using  the  conservation relations between the contact  wave
\begin{equation}\label{eq:RH11}
	\bm{F}_R^* = \bm{F}_L^*+s^*(\bm{U}_R^*-\bm{U}_L^*),
\end{equation}

From the momentum term in Eq.(\ref{eq:RH11}),
\begin{equation}
  \rho_R^* u_R^{*2}-\sigma^*_R=\rho_L^* u_L^{*2}-\sigma_L^*+s^*(\rho_R^* u_R^*-\rho_L^* u_L^*).
\end{equation}
and taking  $ s^* = u_L^* = u_R^*$ in, we can get the relation of Cauchy stress
\begin{equation} 
  \sigma^*_L = \sigma^*_R,
\end{equation}
is always satisfied.

\subsection{A relation between $\rho$ and $s_{xx}$ in 1D elastic-plastic  equation system}

Thanks to (\ref{eq:mt}), the equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
  \begin{equation}\label{eq:d1}
    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
  \end{equation}
  and
  \begin{equation}\label{eq:s1}
    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
  \end{equation}

  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
%  We can get a relation of density and deviatoric stress,
  \begin{equation}
    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
\end{equation}
Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
\begin{equation}\label{eq:rhosxx}
  s_{xx2}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_{2}}{\rho_{1}})+s_{xx1}.
\end{equation}
The subscripts $2$ and $1$ mean the states in front of and behind the wave, respectively.
This relation always hold if there is no yielding in the integration path.
\subsection{Relations across rarefaction waves}\label{sec:rarefaction}
A Rarefaction wave contains a continuous of waves with the speed of $u\pm c$. Now we consider a left-going rarefaction wave as shown in Fig.\ref{fig:Rare} as an example, the state in front of the wave is known as  $(\rho_1,u_1,p_1,s_{xx1})$ and after the wave the state changes to $(\rho_2,u_2,p_2,s_{xx2})$ which is unknown.

We random choose a particle point inside the expansion region with the state of $(\rho,u, p,s_{xx})$, after a little expansion with the wave speed of $u-c$, the state changes to$(\rho+d\rho, u+du, p+dp, s_{xx}+ds_{xx})$. According to the conservation relations we can get 
\begin{equation}
  \begin{aligned}
	& (\rho+ \text{d}\rho)(u+ \text{d}u) = \rho u +(u-c)\text{d}\rho\\
	& (\rho+\text{d}\rho)(u+\text{d}u)^2 -(\sigma+\text{d}\sigma)=   \rho u^2-\sigma\\
	&+(u-c)[(\rho+\text{d}\rho)(u+\text{d}u)-\rho u] \\
	& [(\rho+\text{d}\rho)(E+\text{d}E)-(\sigma+\text{d}\sigma)](u+\text{d}u) = \\
	&(\rho E-\sigma)u+(u-c)[(\rho+\text{d}\rho)(E+\text{d}E)-\rho E]\\
 \end{aligned}
\end{equation}
Ignoring high-order infinite small terms, we can get  
\begin{align}
  \label{eq:urho}
  & \text{d} u =-\frac{c}{\rho}\text{d}\rho,\\
\label{eq:sigmarho}
  & \text{d} \sigma = -c^2 d\rho,\\
 \label{eq:Erho}
  & \text{d} E = -\frac{\sigma+\rho u c}{\rho^2} d\rho.
\end{align}
Also we know the deviatoric stress is a function of the  density by Eq.(\ref{eq:rhosxx})   
\begin{equation}
  ds_{xx} = \left\{ \begin{aligned}
	  -\frac{4}{3}\frac{\mu}{\rho}d\rho \quad |s_{xx}| < \frac{2}{3}Y_0,\\
	  0  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
	\end{aligned}
  \right.
\end{equation}
And from Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}) we can get
\begin{equation}\label{eq:c_2rho}
  c^2 = \left\{ \begin{aligned}
	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho} \quad |s_{xx}| < \frac{2}{3}Y_0,\\
	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
	\end{aligned}
  \right.
\end{equation}
Then the differential of  pressure is  given  as 
\begin{equation}
  dp = ds_{xx} -d\sigma = ds_{xx}+c^2 d\rho = \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
\end{equation}
it can be written as a differential equation of $p(\rho)$
\begin{equation}
  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho), \quad p(\rho_1) = p_1,
\end{equation}
where 
\begin{equation}
  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
\end{equation}
The pressure can be solved out as
\begin{equation}\label{eq:p_rho}
  p(\rho) = p_1e^{\frac{\lambda_1}{\rho_1}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_1}^\rho f_2(x) e^{\frac{\lambda_1}{x}}dx.
\end{equation}

By the above equations of Eq.(\ref{eq:urho}-\ref{eq:Erho},\ref{eq:c_2rho},\ref{eq:p_rho}), we know that the state $(\rho, u, p, s_{xx})$ is only  a function of the density $\rho$ no matter within or  after the rarefaction wave.

\subsection{Relations across  shock waves}\label{sec:shock}
Now we consider a shock wave with a speed of $s$, suppose the state in front of the shock is known as $(\rho_1,u_1,p_1,s_{xx1})$ and the state after the shock is unknown as $(\rho_2,u_2,p_2,s_{xx2})$.

Then use the conservation relation across the wave, which is also known as the Rankine-Hugoniot relation for a shock

\begin{align}
  &\rho_2u_2 = \rho_1 u_1 +s(\rho_2 -\rho_1),\\
  &\rho_2u_2^2-\sigma_{2} = \rho_1u_1^2-\sigma_{1}+s(\rho_2u_2-\rho_1u_1), \\
  &(\rho_2E_2-\sigma_{2})u_2 = (\rho_1E_1-\sigma_{1})u_1+s(\rho_2E_2-\rho_1E_1),
\end{align}
also can be written as
\begin{align}
\label{eq:RH1}
  &\rho_2(u_2-s) = \rho_1(u_1-s), \\
\label{eq444}
  &\rho_2u_2(u_2-s) = \rho_1u_1(u_1-s)+\sigma_2-\sigma_1,\\
\label{eq:RH3}
  &\rho_2E_2(u_2-s) = \rho_1E_1(u_1-s)+\sigma_2 u_2-\sigma_1u_1,
\end{align}
substituting (\ref{eq:RH1}) into (\ref{eq444}) yields  
\begin{equation}\label{eq:222}
  \rho_1(u_2-u_1)(u_1-s) = \sigma_2-\sigma_1,
\end{equation}
also according to (\ref{eq:RH1}), we have 
\begin{equation}
  u_1-s = \frac{(u_1 - u_2)\rho_2}{\rho_2 -\rho_1},
\end{equation}
then subtituting it into (\ref{eq:222})
\begin{equation}\label{eq:u2u1}
  -t(u_2-u_1)^2 = \sigma_2-\sigma_1,
\end{equation}
where $ t=\frac{\rho_1 \rho_2}{\rho_2-\rho_1}$.

Simimar to (\ref{eq:222}), (\ref{eq:RH3}) can be changed into
\begin{equation}
  t(u_1-u_2)(E_2-E_1) =\sigma_2 u_2-\sigma_1u_1.
\end{equation}
Because of $E= e+\frac{1}{2}u^2$, we can get
\begin{equation}\label{eq:e2e1}
  e_2 - e_1 = - \frac{\sigma_1 +\sigma_2}{2t}.
\end{equation}
Using the EOS of Mie-Gr\"uneisen (\ref{eq:mie}), can get
\begin{equation}
  e = c_0p -c_1f(\rho/\rho_0),
\end{equation}
where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
Put above equation into (\ref{eq:e2e1}), we can solve the pressure $p_2$ out as a function of $\rho_2$. 
\begin{equation}\label{eq:shockp}
  p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1},
\end{equation}
The derivative stress $\sigma_{xx2}$ is also a function of $rho_2$ only. So we can solve the Cauchy stress out as
\begin{equation}
  \sigma_2 = -p_2 +s_{xx2}.
\end{equation}
Then we can use (\ref{eq:u2u1}) to solve the velocity after the shock
\begin{equation}\label{eq:shocku}
  u_2 = \left\{ \begin{aligned}
	 & u_1 - \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Left-going}, \\
	 & u_1 + \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Right-going}.
	\end{aligned}
	\right.
  \end{equation}
And the shock speed is given as 
\begin{equation}
  s = \frac{\rho_2u_2-\rho_1u_1}{\rho_2-\rho_1}.
\end{equation}

By the above deductions of the shock wave, we can get that, if the density after the shock is known, all the unknowns can be solved out.

\section{Exact Riemann solver}\label{sec:riemann}
%Althoughx HLLCE Riemann solver can simulate the elastic-plastic flow effectively and efficiently without iterations, but the plastic structure is not considered in and  there are some assumptions that are not so reasonable, especially in the interface between different materials. For example, the normal stresses $\sigma_x$ are  always equavalent across the interface, but the pressures are not always equal, and the consequent evaluation of $\widetilde{s}^*$ may   be of large error.

Now we consider the constructing details of the exact  Riemann  solver. For  the Riemann problem in Section \ref{sec:riemann}, there are  $6\times 6$ possible  cases in the Riemann solution with different wave structures. Now we consider the  left six cases as shown in Fig.\ref{fig:cases}.

\begin{figure}
  \centering
  \subfigure[Elastic rarefaction wave]{
	\label{fig:subfigure:a}
  \includegraphics[width=3.8cm]{Tikz-figure0.eps}}
  \subfigure[Plastic rarefaction wave]{
	\label{fig:subfigure:b}
  \includegraphics[width=3.8cm]{Tikz-figure1.eps}}
  \subfigure[Both elastic and plastic rarefaction waves]{
	\label{fig:subfigure:c}
  \includegraphics[width=3.8cm]{Tikz-figure2.eps}}
  \subfigure[ Elastic shock wave]{
	\label{fig:subfigure:d}
  \includegraphics[width=3.8cm]{Tikz-figure3.eps}}
  \subfigure[Plastic shock wave]{
	\label{fig:subfigure:e}
  \includegraphics[width=3.8cm]{Tikz-figure4.eps}}
  \subfigure[Both elastic and plastic shock waves]{
	\label{fig:subfigure:f}
	\includegraphics[width=3.8cm]{Tikz-figure5.eps}}
  \caption{The possible cases of Riemann solution structures in the left side.}
  \label{fig:cases}
\end{figure}

There are mainly three parts in the soluting process.

Firstly, a pre-evaluation need to  be done to detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases. This is done in Section (\ref{sec:eva}) with shock-contact-shock waves assumption.

Secondly, for the cases with two waves in one side (i.e.  case c and case f in Fig.\ref{fig:cases}),we need to  solve  the states in the region $\tilde{\mathbf{Q}}_L$ and $\tilde{\mathbf{Q}}_R$. This is done in Section \ref{sec:tilde}.

At last,   we know all  the states besides $Q^*_L$ and $Q^*_R$. According to the knowledge in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, if we  know the densities $\rho^*_L$ and $\rho^*_R$, we can solve all other unknowns out.
Also, by the informations in Section \ref{sec:contact}, the velocities and the Cauchy stresses  in the two sides of the contact must be equal. So there are two equations 
\begin{equation}\label{eq:fus}
  \begin{align}
	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
\end{align}
\end{equation}
and two unknowns $\rho_L^*$ and $\rho_R^*$. Equation (\ref{eq:fus}) is implicit, we have use a Newton iteration method to solve it, this process is given in Section \ref{sec:iteration}. The details of $f_u$ and $f_\sigma$ are listed in Section \ref{sec:fufs}.
\subsection{Pre-evaluation and case classfication}\label{sec:eva}
At first, we assume that there are only one shock wave in the left side and one shock in the right side as shown in Fig.\ref{fig:HLLC}. According to the conservation relations across the shocks, we have    
\begin{equation}
  \left\{
  \begin{align}
	\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
	\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), \\
  \end{align}
\right.
\end{equation}
and
\begin{equation}
  \left\{
  \begin{align}
	\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
	\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). \\
  \end{align}
\right.
\end{equation}

Using the relation across the interface,
\begin{equation}
  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
\end{equation}
the speed of contact wave can be evaluated as 
\begin{equation}
\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
\end{equation}
the density is solved as 
\begin{equation}
\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
\end{equation}
The devaitoric stress is ecaluated as 
\begin{equation}  \label{sxx1}
  \hat{s}_{xxL}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_L^*}{\rho_L})+s_{xxL}, \quad   \hat{s}_{xxR}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_R^*}{\rho_R})+s_{xxR}.
\end{equation}
Here we define the speeds of left and right going waves as
 \begin{equation}
      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
\end{equation}
By  the relation of $\hat{\rho}_{L(R)}$ and  $\hat{s}_{xxL(R)}$ we can classify every side into six cases, and conditions for the classfication are  shown in Table \ref{tab:cases}, the  subscripts $_L$ and  $_R$  are omitted for simplication.

\begin{table}
  \centering 
  \caption{The condition of  cases classification.}
  \begin{tabular}{c|ccc}
	\toprule
	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$&  other\\
  \midrule
  $\hat{\rho^*} <\rho$ & case a& case b& case c \\
  $\hat{\rho^*} >\rho$ & case d& case e& case f \\
  \bottomrule
\end{tabular}
\label{tab:cases}
\end{table}

\subsection{State in region $\tilde{\mathbf{Q}}_{L(R)}$}\label{sec:tilde}

For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, if we give a density $\rho_L^*$ in the region $\mathbf{Q}_L^*$, by the deductions in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, all the unknowns in region $\mathbf{Q}_L^*$ can be solved out.

For cases (c,f), the meterial periods a yielding process from elastic to plastic. There is one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists. In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit 
\begin{equation}
  \tilde{s}_{xxL(R)} = \left\{ \begin{align}
	  &\frac{2}{3}Y_0 \quad  &\text{Case c},\\
	  &-\frac{2}{3}Y_0 \quad &\text{Case f},\\
	\end{align}
  \right.
\end{equation}
By (\ref{eq:rhosxx}), we can solve the density out as 
\begin{equation}
  \tilde{\rho}_{L(R)}= \left\{ \begin{align}
	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case c}, \\ 
	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case f}. 
	\end{align}
  \right.
	\end{equation}
	As  the density in region $\mathbf{Q}^*_{L(R)}$ is known, all the pressure and velocity  can be solved by equations (\ref{eq:p_rho},\ref{eq:c_2rho},  \ref{eq:urho}) for a rarefaction wave  or by  equations (\ref{eq:shockp}, \ref{eq:shocku}) for a shock wave.

	\subsubsection{Elastic rarefaction wave in case c}
	For case c, the pressure within the elastic rarefaction wave is 
	\begin{equation}
	  p(\rho) = p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx, \quad  \tilde{\rho}_{L(R)} \le \rho \le \rho_{L(R)}.
	\end{equation}
The sonic speed is 
	\begin{equation}
	c(\rho) =  \sqrt{ a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}} \quad   \tilde{\rho}_{L(R)} \le \rho \le \rho_{L(R)}.
	\end{equation}
With the sonic speed, the velocity can be solved as
\begin{equation}
  u(\rho) = \left\{ \begin{aligned}
	u_L - \int_{\rho_L}^\rho \frac{c(x)}{x} dx,  \quad   \tilde{\rho}_L \le \rho \le \rho_{L} \\
	u_R + \int_{\rho_R}^\rho \frac{c(x)}{x} dx,  \quad   \tilde{\rho}_R \le \rho \le \rho_{R} \\
	\end{aligned}
  \right.
\end{equation}
So the pressure and velocity after the elastic wave are 
\begin{equation}
  \tilde{p}_{L(R)} = p(\tilde{\rho}_{L(R)}), \quad \tilde{u}_{L(R)} = u(\tilde{\rho}_{L(R)}).
\end{equation}

\subsubsection{Elastic shock wave in  case f}
For a shock wave (case f ), the pressure is 
\begin{equation}
  \tilde{p}_{L(R)}= \frac{2t(c_1f(\tilde{\rho}_{L(R)}/\rho_0)+e_L)-(\sigma_{L(R)}+\tilde{s}_{xxL(R)})}{2tc_0-1},
\end{equation}
where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$. 
And the velocity is 
\begin{equation}
  \tilde{u}_L = u_L -\sqrt{\frac{\sigma_L-\tilde{\sigma}_L}{t}},
\end{equation}
for the left, and 
\begin{equation}
  \tilde{u}_R = u_R +\sqrt{\frac{\sigma_R-\tilde{\sigma}_R}{t}},
\end{equation}
for the right-going wave.
	\subsection{Functions of velocity and Cauchy stress in region $\mathbf{Q}^*_{L(R)}$}\label{sec:fufs}
	The deductions of  velocity and Cauchy stress  for rarefaction waves and shocks are given in Section \ref{sec:rarefaction} and Section \ref{sec:shock}. For convenient, we list them in this section in  different cases. 
	\subsubsection{ $\mathbf{Q}^*_{L(R)}$ in  rarefaction wave cases }
	For rarefaction waves  in region
	The deviatoric stress is 
	\begin{equation}
	  s_{xxL(R)}^*= \left\{ \begin{aligned}
		  & s_{xxL(R)} \quad &\text{case (b, e)}, \\
		  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  &\text{case (a,d)},\\
		  & \frac{2}{3}Y_0 \quad  &\text{case (c)},\\
		  & -\frac{2}{3}Y_0 \quad &\text{case (f)}.\\
		\end{aligned}
	  \right.
	\end{equation}
The  pressure for case (a,b,c) is 
\begin{equation}
  p_{L(R)}^* = \left\{\begin{aligned}
	  &	p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho_{L(R)}^*}} +e^{-\frac{\lambda_1}{\rho_{L(R)}^*}}\int_{\rho_{L(R)}}^{\rho_{L(R)}^*} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad & \text{case (a,b)},\\
	  &	\tilde{p}_{L(R)}e^{\frac{\lambda_1}{\tilde{\rho}_{L(R)}}-\frac{\lambda_1}{\rho_{L(R)}^*}} +e^{-\frac{\lambda_1}{\rho_{L(R)}^*}}\int_{\tilde{\rho}_{L(R)}}^{\rho_{L(R)}^*} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad & \text{case (c)},
  \end{aligned}
\right.
\end{equation} 
after get the pressure we can give the sonic speed as
\begin{equation}
  c_{L(R)}^{*2} = \left\{ \begin{aligned}
	&  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p_{L(R)}^*}{\rho_{L(R)}^{*2}}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_{L(R)}^{*2}}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho_{L(R)}^*} \quad & \text{case a},\\
	&	a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho_{L(R)}^{*2}}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_{L(R)}^{*2}}\Gamma_0 s_{xxL(R)}^*  \quad  & \text{case (b,c)}.
	\end{aligned}
  \right.
\end{equation}
then the velocity can be solved as
\begin{equation}
  u_{L}^* =\left\{ \begin{aligned} 
	  &u_L - \int_{\rho_L}^{\rho_L^*} \frac{c}{\rho} d\rho \quad \text{case a,b}, \\
	  &\tilde{u}_L - \int_{\tilde{\rho}_L}^{\rho_L^*} \frac{c}{\rho} d\rho \quad \text{case c}, \\
	\end{aligned}
  \right.
 u_{R}^* =\left\{ \begin{aligned} 
	 &u_R + \int_{\rho_R}^{\rho_R^*} \frac{c}{\rho} d\rho \quad \text{case a,b}, \\
	 &\tilde{u}_R + \int_{\tilde{\rho}_R}^{\rho_R^*} \frac{c}{\rho} d\rho \quad \text{case c}. \\
	\end{aligned}
  \right.
\end{equation}

  \subsection{An iteration process of $\rho^*_L$ and $\rho^*_R$}\label{sec:iteration}

  As the states in regions $\mathbf{Q}_L$ and $\mathbf{Q}_R$ are known, for cases (c,f) with two waves in one side, regions $\hat{\mathbf{Q}}_L$  and $\hat{\mathbf{Q}}_L$ are also solved in the above section, by the relaions in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, if we know the densities $\rho_L^*$ and $\rho_R^*$, states in regions $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$ can be deduced out. Till then, the  whole Riemann problem is solved.

The Newton iteration to evaluate $\rho_L^*$ and $\rho_R^*$ is given as
\begin{equation}
\left[ \begin{array}{l}
 \rho _{L,(k+1)}^*\\
\rho_{R,(k+1)}^*\\
\end{array}
\right] = 
\left[ \begin{array}{l}
 \rho _{L,(k)}^*\\
\rho_{R,(k)}^*\\
\end{array}
\right]-
\left[ \begin{array}{ll}
\frac{\partial f_{u(k)}}{\partial \rho_L^*} & \frac{\partial f_{u(k)}}{\partial \rho_R^*}\\
\frac{\partial f_{\sigma(k)}}{\partial \rho_L^*} & \frac{\partial f_{\sigma(k)}}{\partial \rho_R^*}\\
\end{array}
\right]^{-1}
\left[ \begin{array}{l}
f_{u(k)}\\
f_{\sigma(k)}\\
\end{array}
\right]
\end{equation}

The initial of densities are given as the pre-evalation values,
\begin{equation}
  \rho_{L(0)}^* = \hat{\rho}_L \quad \rho_{R(0)}^* = \hat{\rho}_R.
\end{equation}
The  convergence is meassured by 
\begin{equation}
\text{CHA} = \text{max} \left[  
\frac{|\rho_{L(k+1)}^*- \rho_{L,(k)}^*|}{\frac{1}{2}|\rho_{L(k+1)}^*+\rho_{L(k)}^*|},   \frac{|\rho_{R(k+1)}^*- \rho_{R,(k)}^*|}{\frac{1}{2}|\rho_{R(k+1)}^*+\rho_{R(k)}^*|},|f_{u}|,|f_{\sigma}|\right].
\end{equation}
and the tolerance is taken as $\text{TOL} = 10^{-4}$. It usually takes 3-4 step to get a convergence result.

The derivatives of $f_{u}$ and $f_{\sigma}$ are given by
\begin{equation}
  \frac{\partial f_{u,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u,(k+1)}-f_{u,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},\quad
  \frac{\partial f_{\sigma,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma,(k+1)}-f_{\sigma,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},
\end{equation}
At the first step, we use a simple  numerical difference  method
\begin{equation}
  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
\end{equation}
where $\Delta \rho$ is a little quatity, we can choose it as
\begin{equation}
  \Delta \rho_{L(R)} = \frac{\rho_{L(R),(0)}^*}{100}.
\end{equation}

A flow chat of this process is shown in Fig.

\subsection{Summary of MHLLCEP}
Here, we present all the procedures of MHLLCEP in a more simple way.
\begin{enumerate}
  \item  Assume  that there are three  waves in the Riemann solver. Based on this assumption, we perform the following evaluations:
  \begin{enumerate}
    \item evaluate  $\hat{s}^*$
    \begin{equation*}
       \hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)}.
   \end{equation*}
    \item Evaluate  $\hat{\rho}_L^*$ and $\hat{\rho}_R^*$
    \begin{equation*}
       \hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{s^*-s_L}, \hspace{0.3cm}  \hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{s^*-s_R}.
    \end{equation*}
    \item Evaluate  the deviatoric stress
       \begin{equation*}
        \hat{s}_{xxL}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_L^*}{\rho_L})+s_{xxL},\hspace{0.2cm}  \hat{s}_{xxR}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_R^*}{\rho_R})+s_{xxR}.
      \end{equation*}
    \item Evaluate the pressure
  \end{enumerate}
  \item Decide whether the state reach the elastic limit or not
        \begin{enumerate}
          \item If $|s_{xxL}| < \frac{2}{3}Y_0 \le |\hat{s}_{xxL}^*| $, there are two waves exist in the left, we need to  evaluate the left yielding state.

          The deviatoric stress, density and pressure behind the left elastic  wave are given as
\begin{equation*}
  \widetilde{s}_{xxL} =\left\{ \begin{aligned}
      -\frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_L^* > \rho_L,\\
      \frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_L^* < \rho_L,\\
    \end{aligned}\right.
 \end{equation*}
 \begin{equation*}    
     \widetilde{\rho}_{L} = \left\{ \begin{aligned}
      & \rho_L \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL}}{4\mu}\right)  \hspace{0.5cm} \text{if} \hspace{0.3cm} \rho_L^* > \rho_L,\\
& \rho_L \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL}}{4\mu}\right)
\hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_L^* < \rho_L,\\
  \end{aligned}\right.
 \end{equation*}

\begin{equation*}
  \widetilde{p}_L= \frac{2t(c_1f(\widetilde{\rho}_L)+e_L)-(\sigma_L+\widetilde{s}_{xxL})}{2tc_0-1}, \hspace{0.3cm}
t=\frac{\rho_L \widetilde{\rho}_L}{\widetilde{\rho}_L-\rho_L},
\end{equation*}
and the Cauchy stress and velocity are
\begin{equation*}
\widetilde{\sigma}_L = -\widetilde{p}_L+\widetilde{s}_{xxL},
\end{equation*}
\begin{equation*}
  \widetilde{u}_L= \left\{
  \begin{aligned}
    u_L-\sqrt{\frac{\sigma_L-\widetilde{\sigma}_L}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_L^* >\rho_L,\\
    u_L+\sqrt{\frac{\sigma_L-\widetilde{\sigma}_L}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_L^* <\rho_L.\\
\end{aligned} \right.
\end{equation*}
If not,
\begin{equation*}
  \widetilde{\mathbf{Q}}_L = \mathbf{Q}_L.
\end{equation*}
          \item If $|s_{xxR}| < \frac{2}{3}Y_0 \le |\hat{s}_{xxR}^*| $, right  elastic and plastic wave exist, we need to  evaluate the right yielding state.

                           The deviatoric stress, density and pressure  behind the right elastic  wave are given as
\begin{equation*}
  \widetilde{s}_{xxR} =\left\{ \begin{aligned}
      -\frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_R^* > \rho_R,\\
      \frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_R^* < \rho_R,\\
    \end{aligned}\right.
    \hspace{0.2cm} \widetilde{\rho}_{R} = \left\{ \begin{aligned}
      & \rho_R \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxR}}{4\mu}\right)  \hspace{0.5cm} \text{if} \hspace{0.3cm} \rho_R^* > \rho_R,\\
& \rho_R \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxR}}{4\mu}\right)
\hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_R^* < \rho_R,\\
  \end{aligned}\right.
 \end{equation*}
\begin{equation*}
  \widetilde{p}_R= \frac{2t(c_1f(\widetilde{\rho}_R)+e_R)-(\sigma_R+\widetilde{s}_{xxR})}{2tc_0-1}, \hspace{0.3cm}
t=\frac{\rho_R \widetilde{\rho}_R}{\widetilde{\rho}_R-\rho_R},
\end{equation*}
and the Cauchy stress and velocity are
\begin{equation*}
\widetilde{\sigma}_R = -\widetilde{p}_R+\widetilde{s}_{xxR},
\end{equation*}
\begin{equation*}
  \widetilde{u}_R= \left\{
  \begin{aligned}
    u_R+\sqrt{\frac{\sigma_R-\widetilde{\sigma}_R}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_R^* >\rho_R,\\
    u_R-\sqrt{\frac{\sigma_R-\widetilde{\sigma}_R}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_R^* <\rho_R.\\
\end{aligned} \right.
\end{equation*}
If not,
\begin{equation*}
  \widetilde{\mathbf{Q}}_R = \mathbf{Q}_R.
\end{equation*}

        \end{enumerate}
  \item Re-evaluate the states in the star regions on both sides of the contact wave
  \begin{enumerate}
    \item Evaluate the wave speeds:
\begin{equation*}
  s_L = \text{min} (\widetilde{u}_L-\widetilde{c}_L, \widetilde{u}_R-\widetilde{c}_R,0), \hspace{0.3cm} s_R = \text{max}(\widetilde{u}_L+\widetilde{c}_L, \widetilde{u}_R+\widetilde{c}_R,0),
    \end{equation*}
    \begin{equation*}
      s^* = \frac{\widetilde{\sigma}_L-\widetilde{\sigma}_R+\widetilde{\rho}_L \widetilde{u}_L(s_L-\widetilde{u}_L)-\widetilde{\rho}_R \widetilde{u}_R(s_R-\widetilde{u}_R)}{\widetilde{\rho}_L(s_L-\widetilde{u}_L)-\widetilde{\rho}_R(s_R-\widetilde{u}_R)}.
\end{equation*}

    \item Evaluate the densities:
\begin{equation*}
  \rho_L^* = \frac{\widetilde{\rho}_L(\widetilde{u}_L-s_L)}{s^*-s_L}, \hspace{0.3cm}  \rho_R^* = \frac{\widetilde{\rho}_R(\widetilde{u}_R-s_R)}{s^*-s_R},
\end{equation*}

    \item Evaluate the deviatoric stresses:
 \begin{align*}
   \widetilde{s}_{xxL}^* = \left\{\begin{array}{cc}
                       \widetilde{s}_{xxL} & if \ |\hat{s}_{xxL}^{*}|\geq \frac{2}{3}Y_{0} \\
                        -\frac{4}{3}\mu \text{ln}\left( \frac{\rho_L^*}{\widetilde{\rho}_L}  \right)+\widetilde{s}_{xxL} & otherwise
                     \end{array}\right.
   ,\\
   \widetilde{s}_{xxR}^* =  \left\{\begin{array}{cc}
                       \widetilde{s}_{xxR} & if \ |\hat{s}_{xxR}^{*}| \geq \frac{2}{3}Y_{0} \\
                        -\frac{4}{3}\mu \text{ln}\left( \frac{\rho_R^*}{\widetilde{\rho}_R}  \right)+\widetilde{s}_{xxR} & otherwise
                     \end{array}\right.
    ,
\end{align*}
then using  the von Mises' yielding condition
\begin{equation*}
  s_{xxL}^* = \Upsilon(\widetilde{s}_{xxL}^*) , \hspace{0.3cm}  s_{xxR}^* = \Upsilon(\widetilde{s}_{xxR}^*).
\end{equation*}

    \item Solving the Cauchy stresses:
\begin{equation*}
  \sigma_L^*=\sigma_R^*=\widetilde{\sigma}_L -\widetilde{\rho_L} (s_L-\widetilde{u}_L)(s^*-\widetilde{u}_L).
\end{equation*}

     \item The pressure is given by $p =s_{xx}-\sigma$.
  \end{enumerate}
\end{enumerate}

\end{document}

### 2019-04-26 Process.tex
first

\documentclass[border=10pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta,arrows}
\usepackage{setspace}
\begin{document}
\begin{tikzpicture}
[auto,
decision/.style={diamond, draw=blue, thick,
text width=4.5em,align=flush center,
inner sep=1pt},
block/.style ={rectangle, draw=blue, thick, 
text width=10em,align=center, rounded corners,
minimum height=4em},
line/.style ={draw, thick, -latex',shorten >=2pt},
cloud/.style ={draw=red, thick, ellipse,
minimum height=2em}]
\matrix [column sep=5mm,row sep=7mm]
{
% row 1
& \node [block] (init) {Estimate}; &\\
% row 2
\node [block] (Left) {
Case = shock  $ f_L(\rho_L^*) = \sigma_L^*$ \\  Case = Rare $ g_L(\rho_L^*) = \sigma_L^*$ }; 
&  & \node [block] (Left) {Case = shock : \vspace{-0.3cm}  $$ f_L(\rho_L^*) = \sigma_L^*$$  Case = Rare  \vspace{-0.3cm} $$ g_L(\rho_L^*) = \sigma_L^*$$  }; 
   \\
% row 3
&\node [block] (update) {update model}; &\\
&\node [block] (evaluate) {evaluate candidate models}; & \\
% row 4
& \node [decision] (decide) {is best candidate}; & \\
% row 5
& \node [block] (stop) {stop}; & \\
};
%\begin{scope}[every path/.style=line]
%\path (init) -- (identify);
%\path (identify) -- (evaluate);
%\path (evaluate) -- (decide);
%\path (update) |- (identify);
%\path (decide) -| node [near start] {yes} (update);
%\path (decide) -- node [midway] {no} (stop);
%\path [dashed] (expert) -- (init);
%\path [dashed] (system) -- (init);
%\path [dashed] (system) |- (evaluate);
%\end{scope}
\end{tikzpicture}

\end{document} 
\end{figure}
 \end{document}

### 2019-04-26 TikzFig/Tikz.tex
first

\documentclass{article}
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz,mathpazo}
\usetikzlibrary{calc}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta}
\usepackage{graphics,graphicx}
\usetikzlibrary{external}
\tikzexternalize
\tikzset{external/system call={latex \tikzexternalcheckshellescape
  -halt-on-error -interaction=batchmode -jobname "\image" "\texsource";
  dvips -o "\image".eps "\image".dvi}}
  % pdflatex --shell-escape *.tex

\begin{document}

\begin{tikzpicture}
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
	\draw [line width =1pt] (-4,0) -- (0,0);
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
	\draw [double](0,0) -- ([turn]165:3.5)   node [above]{Contact};
	\draw  (0,0) node [below]{$O$} -- ([turn]135:3.5) node [above]{Right wave};
	\draw  (0,0) -- ([turn]132:3.5);
	\draw  (0,0) -- ([turn]-135:3.5) node [above]{Elastic Rarefaction};
	\draw  (0,0) -- ([turn]-133:3.5);
	\draw  (0,0) -- ([turn]-131:3.5);
	\draw  (0,0) -- ([turn]-129:3.5);
	\node at (-1.3,0.5) {$\mathbf{Q}_L$};
	\node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
	\node at (0.7,1.2) {$\mathbf{Q}_R^*$};
	\node at (1.3,0.5) {$\mathbf{Q}_R$};
\end{tikzpicture}
%
  \begin{tikzpicture}
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
	\draw [line width =1pt] (-4,0) -- (0,0);
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
	\draw [double](0,0) -- ([turn]165:3.5)   node [above]{Contact};
	\draw  (0,0) node [below]{$O$} -- ([turn]135:3.5) node [above]{Right wave};
	\draw  (0,0) -- ([turn]132:3.5);
	\draw [dashed] (0,0) -- ([turn]-135:3.5) node [above]{Plastic Rarefaction};
	\draw  [dashed](0,0) -- ([turn]-133:3.5);
	\draw  [dashed](0,0) -- ([turn]-131:3.5);
	\draw  [dashed](0,0) -- ([turn]-129:3.5);
	\node at (-1.3,0.5) {$\mathbf{Q}_L$};
	\node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
	\node at (0.7,1.2) {$\mathbf{Q}_R^*$};
	\node at (1.3,0.5) {$\mathbf{Q}_R$};
\end{tikzpicture}

\begin{tikzpicture}
    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
    \draw [line width =1pt] (-4,0) -- (0,0);
    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
    \draw (0,0) node [below]{$O$} -- ([turn]-110:3.5);
    \draw (0,0) -- ([turn]-109:3.5);
    \draw (0,0) -- ([turn]-108:3.5);
	\draw (0,0) -- ([turn]-107:3.5);
    \draw [double](0,0) -- ([turn]165:3.5)   node [above]{Contact};
    \draw  (0,0) -- ([turn]135:3.5) node [above]{Right wave};
    \draw  (0,0) -- ([turn]131:3.5);
    \draw  (0,0)[dashed] -- ([turn]-140:3.5) node [above]{Plastic rarefaction} ;
    \draw  (0,0)[dashed] -- ([turn]-139:3.5) ;
    \draw  (0,0)[dashed] -- ([turn]-138:3.5) ;
    \draw  (0,0)[dashed] -- ([turn]-137:3.5) ;
    \node at (-1.6,0.2) {$\mathbf{Q}_L$};
    \node at (-1.2,0.8) {$\widetilde{\mathbf{Q}}_L$};
    \node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
    \node at (0.7,1.2) {$\mathbf{Q}_R^*$};
    \node at (1.3,0.5) {$\mathbf{Q}_R$};
	\node at (-2.7,1.5) {Elastic rarefaction};
\end{tikzpicture}

  \begin{tikzpicture}
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
	\draw [line width =1pt] (-4,0) -- (0,0);
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
	\draw [double](0,0)  -- ([turn]165:3.5)   node [above]{Contact};
	\draw  (0,0) -- ([turn]135:3.5) node [above]{Right wave};
	\draw  (0,0) -- ([turn]132:3.5);
	\draw  (0,0) [line width = 0.8pt] node [below]{ $O$ }  -- ([turn]-135:3.5) node [above]{Elastic shock};
	\node at (-1.3,0.5) {$\mathbf{Q}_L$};
	\node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
	\node at (0.7,1.2) {$\mathbf{Q}_R^*$};
	\node at (1.3,0.5) {$\mathbf{Q}_R$};
\end{tikzpicture}

  \begin{tikzpicture}
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
	\draw [line width =1pt] (-4,0) -- (0,0);
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
	\draw [double](0,0)  -- ([turn]165:3.5)   node [above]{Contact};
	\draw  (0,0) -- ([turn]135:3.5) node [above]{Right wave};
	\draw  (0,0) -- ([turn]132:3.5);
	\draw  (0,0) [dashed, line width = 0.8pt] node [below]{ $O$ }  -- ([turn]-135:3.5) node [above]{Plastic shock};
	\node at (-1.3,0.5) {$\mathbf{Q}_L$};
	\node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
	\node at (0.7,1.2) {$\mathbf{Q}_R^*$};
	\node at (1.3,0.5) {$\mathbf{Q}_R$};
\end{tikzpicture}

\begin{tikzpicture}
    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
    \draw [line width =1pt] (-4,0) -- (0,0);
    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
	\draw (0,0) [line width =0.8pt] node [below]{$O$} -- ([turn]-110:3.5) node [above]{Elastic shock};
    \draw [double](0,0) -- ([turn]165:3.5)   node [above]{Contact};
	\draw  (0,0) node[below]{$O$} -- ([turn]135:3.5) node [above]{Right wave};
    \draw  (0,0) -- ([turn]131:3.5);
	\draw  (0,0)[dashed, line width =0.8pt] -- ([turn]-140:3.5) node [above]{Plastic shock} ;
    \node at (-1.6,0.2) {$\mathbf{Q}_L$};
    \node at (-1.2,0.8) {$\widetilde{\mathbf{Q}}_L$};
    \node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
    \node at (0.7,1.2) {$\mathbf{Q}_R^*$};
    \node at (1.3,0.5) {$\mathbf{Q}_R$};
\end{tikzpicture}

\tikzstyle{startstop} = [rectangle, rounded corners, minimum width = 2cm, minimum height=1cm,text centered, draw = black, fill = red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill = blue!40]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill = yellow!50]
\tikzstyle{decision} = [diamond, aspect = 3, text centered, draw=black, fill = green!30]
% 箭头形式
\tikzstyle{arrow} = [->,>=stealth]

\begin{tikzpicture}[node distance=2cm]
%定义流程图具体形状
\node (start1) [startstop] {$\rho_L^*$};
\node (start2) [startstop,right of=start1, xshift = 1cm] {$\rho_R^*$};
\node (pro1) [process, below of=start1, yshift=0.2cm, left of=start1, xshift=0.8cm] {$p_L^*,s_{xxL}^*,u_L^*$};
\node (pro2) [process, right of=pro1, xshift= 3.7cm] {$p_R^*,s_{xxR}^*,u_R^*$};
\node (dec1) [decision, below of=pro1, yshift= -0.5cm, xshift=3.0cm] {Convergence ?};
\node (stop) [startstop, below of=dec1] {Output with $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$};

%连接具体形状
\draw [arrow](start1) -- (pro1);
\draw [arrow](start2) -- (pro2);
\draw [arrow](pro1) -- (dec1);
\draw [arrow](pro2) -- (dec1);
\draw [arrow](dec1) -- ($(dec1.east) + (2.5,0)$) node[anchor=north] {NO}  |- node [anchor =south] {A new $\rho_R^*$} (start2);
\draw [arrow](dec1) -- ($(dec1.west) + (-2.8,0)$) node[anchor=north] {NO} |- node [anchor =south] {A new $\rho_L^*$}(start1);
%\draw [arrow](dec1) -- ($(dec1.east) + (1.5,0)$) node[anchor=north] {NO} |- (pro2);
\draw [arrow](dec1) -- node[anchor=west] {YES} (stop);
\end{tikzpicture}

 \end{document}

### 2019-04-27 Manuscript.tex
second

@@
 
-\subsection{State in region $\tilde{\mathbf{Q}}_{L(R)}$}\label{sec:tilde}
-
+\subsection{States for one wave cases (a,b, d,e)}
 For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, if we give a density $\rho_L^*$ in the region $\mathbf{Q}_L^*$, by the deductions in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, all the unknowns in region $\mathbf{Q}_L^*$ can be solved out.
 
+\subsubsection{Rarefaction  wave cases (a,b)}
+For Rarefaction wave, we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region.
+
+First we give the function of $s_{xx}$,
+\begin{equation}
+  s_{xx}(\rho) = \left\{\begin{aligned}
+	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  &\text{case (a)},\\
+	& \frac{2}{3}Y_0 &\text{case (b)}.
+  \end{aligned} \right.
+  \end{equation}
+Then we give the pressure,
+\begin{equation}
+  p(\rho)=p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad & \text{case (a,b)}.
+\end{equation}
+and sonic speed,
+\begin{equation}
+  c(\rho) = \left\{ \begin{aligned}
+	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case (a)},\\
+	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case (b)}.
+	\end{aligned}\right.
+\end{equation}
+Then we can get  the  function of  velocity
+\begin{equation}
+  u(\rho) =\left\{ \begin{aligned} 
+	&u_L - \int_{\rho_L}^{\rho} \frac{c}{\rho} d\rho \quad \text{case (a,b) Left} , \\
+	 &u_R + \int_{\rho_R}^{\rho} \frac{c}{\rho} d\rho \quad   \rho_R^* \le \rho \le \rho_R \quad \text{case (a,b) Right}, \\
+	\end{aligned}
+  \right.
+\end{equation}
+
+\subsubsection{Shock wave cases (d,e)}
+For shock waves, the function of deviatoric is given as 
+\begin{equation}
+  s_{xx}(\rho) = \left\{\begin{aligned}
+	& \begin{aligned}
+	  & s_{xxL(R)} \quad  &\rho = \rho_{L(R)}\\
+	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}\quad &  \rho =\rho_{L(R)}^* \end{aligned}
+	\quad  &\text{case (d)},\\
+	& \frac{2}{3}Y_0 &\text{case (e)}.
+  \end{aligned} \right.
+  \end{equation}
+And the pressure is given as
+\begin{equation}
+  p(\rho)= \left\{\begin{aligned} 
+	& p_{L(R)}   \quad  & \rho = \rho_{L(R)} \\
+	& \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2tc_0-1} \quad  &  \rho=\rho_{L(R)}^* 
+  \end{aligned}\right.
+  \text{ case (d,e)},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\rho_{L(R)}}$. 
+The velocity is given as
+\begin{equation}
+  u(\rho) = \left\{ \begin{aligned} u_{L(R)} \quad  &\rho =\rho_{L(R)}\\
+	u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t}} \quad &\rho = \rho_L^*\\ 
+	u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t}} \quad & \rho = \rho_R^*\\
+  \end{aligned}
+  \right.
+\end{equation}
+
+\subsection{States for two wave cases (c,f)}
+
 For cases (c,f), the meterial periods a yielding process from elastic to plastic.
-There is one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
-In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit
+There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
+In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
 \begin{equation}
@@
 \end{equation}
-By (\ref{eq:rhosxx}), we can solve the density out as 
+By (\ref{eq:rhosxx}),at state $\tilde{\mathbf{Q}}_{L(R)}$ we can solve the density out as 
 \begin{equation}
@@
 	\end{equation}
-	As  the density in region $\mathbf{Q}^*_{L(R)}$ is known, all the pressure and velocity  can be solved by equations (\ref{eq:p_rho},\ref{eq:c_2rho},  \ref{eq:urho}) for a rarefaction wave  or by  equations (\ref{eq:shockp}, \ref{eq:shocku}) for a shock wave.
-
-	\subsubsection{Elastic rarefaction wave in case c}
-	For case c, the pressure within the elastic rarefaction wave is 
+\subsubsection{Rarefaction wave case (c)}
+For rarefaction wave case,
+we give the function of $s_{xx}$ at first,
 \begin{equation}
-	  p(\rho) = p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx, \quad  \tilde{\rho}_{L(R)} \le \rho \le \rho_{L(R)}.
+  s_{xx}(\rho) = \left\{\begin{aligned}
+	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}  ,\\
+	& \frac{2}{3}Y_0 & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^* .
+  \end{aligned} \right. \quad \text{case (c)}.
   \end{equation}
-The sonic speed is 
+And sonic speed,
 \begin{equation}
-	c(\rho) =  \sqrt{ a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}} \quad   \tilde{\rho}_{L(R)} \le \rho \le \rho_{L(R)}.
+  c(\rho) = \left\{ \begin{aligned}
+	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}\\
+	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  &   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.
+  \end{aligned}\right. \quad \text{case (c)}.
 \end{equation}
-With the sonic speed, the velocity can be solved as
+Then we can get  the   function of  velocity
 \begin{equation}
-  u(\rho) = \left\{ \begin{aligned}
-	u_L - \int_{\rho_L}^\rho \frac{c(x)}{x} dx,  \quad   \tilde{\rho}_L \le \rho \le \rho_{L} \\
-	u_R + \int_{\rho_R}^\rho \frac{c(x)}{x} dx,  \quad   \tilde{\rho}_R \le \rho \le \rho_{R} \\
+  u(\rho) =\left\{ \begin{aligned} 
+	&u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge \rho_L^* , \\
+	&u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge  \rho_R^* , 
 	\end{aligned}
-  \right.
+  \right. \quad \text{case (c)}.
 \end{equation}
-So the pressure and velocity after the elastic wave are 
+\subsubsection{Shock wave case (f)}
+For shock waves the function of deviatoric is given as 
 \begin{equation}
-  \tilde{p}_{L(R)} = p(\tilde{\rho}_{L(R)}), \quad \tilde{u}_{L(R)} = u(\tilde{\rho}_{L(R)}).
+  s_{xx}(\rho) = \left\{\begin{aligned}
+  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}\quad &  \rho =\rho_{L(R)}, \tilde{\rho}_{L(R)},\\
+	& \frac{2}{3}Y_0 &\rho = \rho_{L(R)}^*,
+  \end{aligned} \right. \quad  \text{case (f)}.
   \end{equation}
 
-\subsubsection{Elastic shock wave in  case f}
-For a shock wave (case f ), the pressure is 
+And the pressure is given as
 \begin{equation}
-  \tilde{p}_{L(R)}= \frac{2t(c_1f(\tilde{\rho}_{L(R)}/\rho_0)+e_L)-(\sigma_{L(R)}+\tilde{s}_{xxL(R)})}{2tc_0-1},
+  p(\rho)= \left\{\begin{aligned} 
+	& p_{L(R)}   \quad  & \rho = \rho_{L(R)} \\
+	& \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2t_1c_0-1} \quad  &  \rho=\tilde{\rho}_{L(R)}\\ 
+	& \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_L)-(\tilde{\sigma}_{L(R)}+s_{xx}(\rho))}{2t_2c_0-1} \quad  &  \rho=\rho_{L(R)}^*\\ 
+  \end{aligned}\right.
+  \text{ case (f)},
 \end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$. 
-And the velocity is 
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t_2=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$, $ t_1=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$
+
+The velocity is given as
 \begin{equation}
-  \tilde{u}_L = u_L -\sqrt{\frac{\sigma_L-\tilde{\sigma}_L}{t}},
-\end{equation}
-for the left, and 
-\begin{equation}
-  \tilde{u}_R = u_R +\sqrt{\frac{\sigma_R-\tilde{\sigma}_R}{t}},
-\end{equation}
-for the right-going wave.
-	\subsection{Functions of velocity and Cauchy stress in region $\mathbf{Q}^*_{L(R)}$}\label{sec:fufs}
-	The deductions of  velocity and Cauchy stress  for rarefaction waves and shocks are given in Section \ref{sec:rarefaction} and Section \ref{sec:shock}.
-For convenient, we list them in this section in  different cases.
-	\subsubsection{ $\mathbf{Q}^*_{L(R)}$ in  rarefaction wave cases }
-	For rarefaction waves  in region
-	The deviatoric stress is 
-	\begin{equation}
-	  s_{xxL(R)}^*= \left\{ \begin{aligned}
-		  & s_{xxL(R)} \quad &\text{case (b, e)}, \\
-		  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  &\text{case (a,d)},\\
-		  & \frac{2}{3}Y_0 \quad  &\text{case (c)},\\
-		  & -\frac{2}{3}Y_0 \quad &\text{case (f)}.\\
-		\end{aligned}
-	  \right.
-	\end{equation}
-The  pressure for case (a,b,c) is 
-\begin{equation}
-  p_{L(R)}^* = \left\{\begin{aligned}
-	  &	p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho_{L(R)}^*}} +e^{-\frac{\lambda_1}{\rho_{L(R)}^*}}\int_{\rho_{L(R)}}^{\rho_{L(R)}^*} f_2(x) e^{\frac{\lambda_1}{x}}dx.
-\quad & \text{case (a,b)},\\
-	  &	\tilde{p}_{L(R)}e^{\frac{\lambda_1}{\tilde{\rho}_{L(R)}}-\frac{\lambda_1}{\rho_{L(R)}^*}} +e^{-\frac{\lambda_1}{\rho_{L(R)}^*}}\int_{\tilde{\rho}_{L(R)}}^{\rho_{L(R)}^*} f_2(x) e^{\frac{\lambda_1}{x}}dx.
-\quad & \text{case (c)},
-  \end{aligned}
-\right.
-\end{equation} 
-after get the pressure we can give the sonic speed as
-\begin{equation}
-  c_{L(R)}^{*2} = \left\{ \begin{aligned}
-	&  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p_{L(R)}^*}{\rho_{L(R)}^{*2}}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_{L(R)}^{*2}}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho_{L(R)}^*} \quad & \text{case a},\\
-	&	a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho_{L(R)}^{*2}}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_{L(R)}^{*2}}\Gamma_0 s_{xxL(R)}^*  \quad  & \text{case (b,c)}.
-	\end{aligned}
-  \right.
-\end{equation}
-then the velocity can be solved as
-\begin{equation}
-  u_{L}^* =\left\{ \begin{aligned} 
-	  &u_L - \int_{\rho_L}^{\rho_L^*} \frac{c}{\rho} d\rho \quad \text{case a,b}, \\
-	  &\tilde{u}_L - \int_{\tilde{\rho}_L}^{\rho_L^*} \frac{c}{\rho} d\rho \quad \text{case c}, \\
-	\end{aligned}
-  \right.
- u_{R}^* =\left\{ \begin{aligned} 
-	 &u_R + \int_{\rho_R}^{\rho_R^*} \frac{c}{\rho} d\rho \quad \text{case a,b}, \\
-	 &\tilde{u}_R + \int_{\tilde{\rho}_R}^{\rho_R^*} \frac{c}{\rho} d\rho \quad \text{case c}. \\
-	\end{aligned}
-  \right.
+  u(\rho) = \left\{ \begin{array}{ll}
+	u_{L(R)} \quad  & \rho =\rho_{L(R)}\\
+		u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t_1}} \quad &\rho = \tilde{\rho}_L\\ 
+		\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t_2}} \quad &\rho = \rho_L^*\\ 
+		u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t_1}} \quad &\rho = \tilde{\rho}_R\\ 
+  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t_2}} \quad &\rho = \rho_R^*\\ \end{array}
+  \right. \quad \text{case (f)}.
 \end{equation}

### 2019-04-30 Manuscript.tex
third

@@
 \section{Exact Riemann solver}\label{sec:riemann}
+
 %Althoughx HLLCE Riemann solver can simulate the elastic-plastic flow effectively and efficiently without iterations, but the plastic structure is not considered in and  there are some assumptions that are not so reasonable, especially in the interface between different materials.
@@
 
-Secondly, for the cases with two waves in one side (i.e.
-case c and case f in Fig.\ref{fig:cases}),we need to  solve  the states in the region $\tilde{\mathbf{Q}}_L$ and $\tilde{\mathbf{Q}}_R$.
-This is done in Section \ref{sec:tilde}.
+Secondly,  we solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ in cases (a,b,d,e) in Section \ref{sec:one} and in cases (c,f) in Section \ref{sec:two}.
 
-At last,   we know all  the states besides $Q^*_L$ and $Q^*_R$.
-According to the knowledge in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, if we  know the densities $\rho^*_L$ and $\rho^*_R$, we can solve all other unknowns out.
-Also, by the informations in Section \ref{sec:contact}, the velocities and the Cauchy stresses  in the two sides of the contact must be equal. So there are two equations 
+At last,  we use  the informations in Section \ref{sec:contact}, the velocities and the Cauchy stresses  in the two sides of the contact must be equal. So there are two equations 
 \begin{equation}\label{eq:fus}
@@
 \end{equation}
-and two unknowns $\rho_L^*$ and $\rho_R^*$.
-Equation (\ref{eq:fus}) is implicit, we have use a Newton iteration method to solve it, this process is given in Section \ref{sec:iteration}.
-The details of $f_u$ and $f_\sigma$ are listed in Section \ref{sec:fufs}.
+and two unknowns $\rho_L^*$ and $\rho_R^*$. Equation (\ref{eq:fus}) is implicit, we have to use a Newton iteration method to solve it, this process is given in Section \ref{sec:iteration}.
 \subsection{Pre-evaluation and case classfication}\label{sec:eva}
-At first, we assume that there are only one shock wave in the left side and one shock in the right side as shown in Fig.\ref{fig:HLLC}.
+At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}.
 According to the conservation relations across the shocks, we have
@@
 \end{equation}
-
+\begin{figure}
+  \centering
+  \includegraphics[width=8cm]{Tikz-figure7.eps}
+  \caption{Pre-evaluation with a three-waves structure.}
+\end{figure}
 Using the relation across the interface,
@@
 
-\subsection{States for one wave cases (a,b, d,e)}
+\subsection{States for one wave cases (a,b, d,e)}\label{sec:one}
 For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, if we give a density $\rho_L^*$ in the region $\mathbf{Q}_L^*$, by the deductions in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, all the unknowns in region $\mathbf{Q}_L^*$ can be solved out.
@@
   s_{xx}(\rho) = \left\{\begin{aligned}
-	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  &\text{case (a)},\\
-	& \frac{2}{3}Y_0 &\text{case (b)}.
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}, \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (a)},\\
+	  & \frac{2}{3}Y_0,  \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (b)}.
   \end{aligned} \right.
@@
 \end{equation}
+where 
+\begin{equation}
+  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+\end{equation}
+
 and sonic speed,
@@
   u(\rho) =\left\{ \begin{aligned} 
-	&u_L - \int_{\rho_L}^{\rho} \frac{c}{\rho} d\rho \quad \text{case (a,b) Left} , \\
-	 &u_R + \int_{\rho_R}^{\rho} \frac{c}{\rho} d\rho \quad   \rho_R^* \le \rho \le \rho_R \quad \text{case (a,b) Right}, \\
+	  &u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_L \ge \rho \ge \rho_L^*,   \quad &\text{case (a,b)} , \\
+	  &u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_R \ge \rho \ge \rho_R^*, \quad &\text{case (a,b)}, \\
 	\end{aligned}
@@
   s_{xx}(\rho) = \left\{\begin{aligned}
-	& \begin{aligned}
-	  & s_{xxL(R)} \quad  &\rho = \rho_{L(R)}\\
-	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}\quad &  \rho =\rho_{L(R)}^* \end{aligned}
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad   &\rho =\rho_{L(R)},\rho_{L(R)}^*,
 	\quad  &\text{case (d)},\\
-	& \frac{2}{3}Y_0 &\text{case (e)}.
+	& -\frac{2}{3}Y_0,   \quad & \rho =\rho_{L(R)},\rho_{L(R)}^*, \quad
+ &\text{case (e)}.
   \end{aligned} \right.
@@
 \begin{equation}
-  p(\rho)= \left\{\begin{aligned} 
-	& p_{L(R)}   \quad  & \rho = \rho_{L(R)} \\
-	& \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2tc_0-1} \quad  &  \rho=\rho_{L(R)}^* 
-  \end{aligned}\right.
+  p(\rho)= 
+  \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2tc_0-1}, \quad  \rho=\rho_{L(R)},\rho_{L(R)}^*, \quad 
   \text{ case (d,e)},
@@
 \begin{equation}
-  u(\rho) = \left\{ \begin{aligned} u_{L(R)} \quad  &\rho =\rho_{L(R)}\\
-	u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t}} \quad &\rho = \rho_L^*\\ 
-	u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t}} \quad & \rho = \rho_R^*\\
+  u(\rho) = \left\{ \begin{aligned}
+	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t}} \quad &\rho =\rho_L, \rho_L^*\\ 
+	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t}} \quad & \rho =\rho_R, \rho_R^*\\
   \end{aligned}
-  \right.
+\right. \quad \text{case (d,e)}
 \end{equation}
 
-\subsection{States for two wave cases (c,f)}
+\subsection{States for two wave cases (c,f)}\label{sec:two}
 
@@
  \tilde{s}_{xxL(R)} = \left\{ \begin{align}
-	  &\frac{2}{3}Y_0 \quad  &\text{Case c},\\
-	  &-\frac{2}{3}Y_0 \quad &\text{Case f},\\
+	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
+	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},\\
 	\end{align}
@@
   \tilde{\rho}_{L(R)}= \left\{ \begin{align}
-	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case c}, \\ 
-	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case f}. 
+	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
+	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
 	\end{align}
@@
 	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}  ,\\
-	& \frac{2}{3}Y_0 & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^* .
+	& \frac{2}{3}Y_0, & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.\\
   \end{aligned} \right. \quad \text{case (c)}.
   \end{equation}
+
+The pressure is given as 
+\begin{equation}
+  p(\rho)= \left\{ \begin{aligned}
+	  p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,\quad & \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},\\
+	  \tilde{p}_{L(R)}e^{\frac{\lambda_1}{\tilde{\rho}_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,  \quad & \tilde{\rho}_{L(R)}\ge \rho \ge \rho_{L(R)}^*,
+  \end{aligned} \right.
+  \text{case (c)},
+\end{equation}
+where 
+\begin{equation}
+  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+\end{equation}
+
 And sonic speed,
@@
   s_{xx}(\rho) = \left\{\begin{aligned}
-  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}\quad &  \rho =\rho_{L(R)}, \tilde{\rho}_{L(R)},\\
-	& \frac{2}{3}Y_0 &\rho = \rho_{L(R)}^*,
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad &  \rho =\rho_{L(R)},\tilde{\rho}_{L(R)},\\
+	  & -\frac{2}{3}Y_0, \quad  & \rho = \rho_{L(R)}^*,
   \end{aligned} \right. \quad  \text{case (f)}.
@@
   p(\rho)= \left\{\begin{aligned} 
-	& p_{L(R)}   \quad  & \rho = \rho_{L(R)} \\
-	& \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2t_1c_0-1} \quad  &  \rho=\tilde{\rho}_{L(R)}\\ 
-	& \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_L)-(\tilde{\sigma}_{L(R)}+s_{xx}(\rho))}{2t_2c_0-1} \quad  &  \rho=\rho_{L(R)}^*\\ 
+	  & \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2t_1c_0-1}, \quad  &  \rho=\rho_{L(R)},\tilde{\rho}_{L(R)},\\ 
+	  & \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_L)-(\tilde{\sigma}_{L(R)}+s_{xx}(\rho))}{2t_2c_0-1}, \quad  &  \rho=\rho_{L(R)}^*,\\ 
   \end{aligned}\right.
@@
 \end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t_2=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$, $ t_1=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t_1=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$, $ t_2=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$.
 
@@
   u(\rho) = \left\{ \begin{array}{ll}
-	u_{L(R)} \quad  & \rho =\rho_{L(R)}\\
-		u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t_1}} \quad &\rho = \tilde{\rho}_L\\ 
-		\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t_2}} \quad &\rho = \rho_L^*\\ 
-		u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t_1}} \quad &\rho = \tilde{\rho}_R\\ 
-  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t_2}} \quad &\rho = \rho_R^*\\ \end{array}
+	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_L,\tilde{\rho}_L,\\ 
+	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_L^*,\\ 
+	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_R, \tilde{\rho}_R, \\ 
+	\tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_R^*, \end{array}
   \right. \quad \text{case (f)}.
@@
 
-  As the states in regions $\mathbf{Q}_L$ and $\mathbf{Q}_R$ are known, for cases (c,f) with two waves in one side, regions $\hat{\mathbf{Q}}_L$  and $\hat{\mathbf{Q}}_L$ are also solved in the above section, by the relaions in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, if we know the densities $\rho_L^*$ and $\rho_R^*$, states in regions $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$ can be deduced out.
-Till then, the  whole Riemann problem is solved.
+For a given  $\rho_L^*$ and a given $\rho_R^*$,
+\begin{equation}
+  \begin{aligned}
+ & u_L^* = u(\rho_L^*),\quad u_R^*= u(\rho_R^*) ,\\
+ & \sigma_L^* = -p(\rho_L^*)+s_{xx}(\rho_L^*),\quad \sigma_R^*= -p(\rho_R^*)+s_{xx}(\rho_R^*) ,\\
+\end{aligned}
+\end{equation}
+ by relations of 
+\begin{equation}
+  \begin{aligned}
+	f_u(\rho_L^*,\rho_R^*)_=  u_L^* -u_R^* =0,\\ 
+	f_\sigma(\rho_L^*,\rho_R^*)_=  \sigma_L^* -\sigma_R^* =0,\\ 
+\end{aligned}
+\end{equation}
+and used a Newton iteration method, we can solve the densities $\rho_L^*$ and $\rho_R^*$ out.
+\begin{figure}
+  \centering
+  \includegraphics[width= 10cm] {Tikz-figure6.eps}
+  \caption{A flow chat of the Newton iteration process.}
+  \label{fig:newton}
+\end{figure}
 
@@
 
-A flow chat of this process is shown in Fig.
+A flow chat of this process is shown in Fig.\ref{fig:newton}.
+\section{Half Riemann problem and  solver}
+Some times we need to analyse a half Riemann problem with a given velocity or Cauchy stress in one side.
+Shown in Fig.\ref{fig:half} , in these cases, we only need to solve the states in another side.
+There are six possible cases just like them in Section \ref{sec:riemann}.
 
-\subsection{Summary of MHLLCEP}
-Here, we present all the procedures of MHLLCEP in a more simple way.
-\begin{enumerate}
-  \item  Assume  that there are three  waves in the Riemann solver. Based on this assumption, we perform the following evaluations:
-  \begin{enumerate}
-    \item evaluate  $\hat{s}^*$
-    \begin{equation*}
-       \hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)}.
-   \end{equation*}
-    \item Evaluate  $\hat{\rho}_L^*$ and $\hat{\rho}_R^*$
-    \begin{equation*}
-       \hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{s^*-s_L}, \hspace{0.3cm}  \hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{s^*-s_R}.
-    \end{equation*}
-    \item Evaluate  the deviatoric stress
-       \begin{equation*}
-        \hat{s}_{xxL}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_L^*}{\rho_L})+s_{xxL},\hspace{0.2cm}  \hat{s}_{xxR}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_R^*}{\rho_R})+s_{xxR}.
-      \end{equation*}
-    \item Evaluate the pressure
-  \end{enumerate}
-  \item Decide whether the state reach the elastic limit or not
-        \begin{enumerate}
-          \item If $|s_{xxL}| < \frac{2}{3}Y_0 \le |\hat{s}_{xxL}^*| $, there are two waves exist in the left, we need to  evaluate the left yielding state.
+\begin{figure}
+  \centering
+  \includegraphics[width= 10cm] {Tikz-figure8.eps}
+  \caption{Half Riemann problem  with a given left velocity or Cauchy stress..}
+  \label{fig:half}
+\end{figure}
 
-          The deviatoric stress, density and pressure behind the left elastic  wave are given as
-\begin{equation*}
-  \widetilde{s}_{xxL} =\left\{ \begin{aligned}
-      -\frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_L^* > \rho_L,\\
-      \frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_L^* < \rho_L,\\
-    \end{aligned}\right.
- \end{equation*}
- \begin{equation*}    
-     \widetilde{\rho}_{L} = \left\{ \begin{aligned}
-      & \rho_L \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL}}{4\mu}\right)  \hspace{0.5cm} \text{if} \hspace{0.3cm} \rho_L^* > \rho_L,\\
-& \rho_L \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL}}{4\mu}\right)
-\hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_L^* < \rho_L,\\
-  \end{aligned}\right.
- \end{equation*}
+The process of solving a half Riemann problem is in three step:
 
-\begin{equation*}
-  \widetilde{p}_L= \frac{2t(c_1f(\widetilde{\rho}_L)+e_L)-(\sigma_L+\widetilde{s}_{xxL})}{2tc_0-1}, \hspace{0.3cm}
-t=\frac{\rho_L \widetilde{\rho}_L}{\widetilde{\rho}_L-\rho_L},
-\end{equation*}
-and the Cauchy stress and velocity are
-\begin{equation*}
-\widetilde{\sigma}_L = -\widetilde{p}_L+\widetilde{s}_{xxL},
-\end{equation*}
-\begin{equation*}
-  \widetilde{u}_L= \left\{
-  \begin{aligned}
-    u_L-\sqrt{\frac{\sigma_L-\widetilde{\sigma}_L}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_L^* >\rho_L,\\
-    u_L+\sqrt{\frac{\sigma_L-\widetilde{\sigma}_L}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_L^* <\rho_L.\\
-\end{aligned} \right.
-\end{equation*}
-If not,
-\begin{equation*}
-  \widetilde{\mathbf{Q}}_L = \mathbf{Q}_L.
-\end{equation*}
-          \item If $|s_{xxR}| < \frac{2}{3}Y_0 \le |\hat{s}_{xxR}^*| $, right  elastic and plastic wave exist, we need to  evaluate the right yielding state.
+First we need evaluate the density in the star region $\mathbf{Q}^*$ with a  elastic shock assumption.
+Then using the relation of $\sigma(\rho^*) = \sigma^*$.
+We can solve the evaluated density $\hat{\rho}$ out.
+A  Newton iteration process will be used.
 
-                           The deviatoric stress, density and pressure  behind the right elastic  wave are given as
-\begin{equation*}
-  \widetilde{s}_{xxR} =\left\{ \begin{aligned}
-      -\frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_R^* > \rho_R,\\
-      \frac{2}{3}Y_0, \hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_R^* < \rho_R,\\
-    \end{aligned}\right.
-    \hspace{0.2cm} \widetilde{\rho}_{R} = \left\{ \begin{aligned}
-      & \rho_R \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxR}}{4\mu}\right)  \hspace{0.5cm} \text{if} \hspace{0.3cm} \rho_R^* > \rho_R,\\
-& \rho_R \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxR}}{4\mu}\right)
-\hspace{0.3cm} \text{if} \hspace{0.3cm} \rho_R^* < \rho_R,\\
-  \end{aligned}\right.
- \end{equation*}
-\begin{equation*}
-  \widetilde{p}_R= \frac{2t(c_1f(\widetilde{\rho}_R)+e_R)-(\sigma_R+\widetilde{s}_{xxR})}{2tc_0-1}, \hspace{0.3cm}
-t=\frac{\rho_R \widetilde{\rho}_R}{\widetilde{\rho}_R-\rho_R},
-\end{equation*}
-and the Cauchy stress and velocity are
-\begin{equation*}
-\widetilde{\sigma}_R = -\widetilde{p}_R+\widetilde{s}_{xxR},
-\end{equation*}
-\begin{equation*}
-  \widetilde{u}_R= \left\{
-  \begin{aligned}
-    u_R+\sqrt{\frac{\sigma_R-\widetilde{\sigma}_R}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_R^* >\rho_R,\\
-    u_R-\sqrt{\frac{\sigma_R-\widetilde{\sigma}_R}{t}} \hspace{0.2cm} \text{if} \hspace{0.2cm} \rho_R^* <\rho_R.\\
-\end{aligned} \right.
-\end{equation*}
-If not,
-\begin{equation*}
-  \widetilde{\mathbf{Q}}_R = \mathbf{Q}_R.
-\end{equation*}
+Second, we can determine the case by the same condition in Table \ref{tab:cases}.
 
-        \end{enumerate}
-  \item Re-evaluate the states in the star regions on both sides of the contact wave
-  \begin{enumerate}
-    \item Evaluate the wave speeds:
-\begin{equation*}
-  s_L = \text{min} (\widetilde{u}_L-\widetilde{c}_L, \widetilde{u}_R-\widetilde{c}_R,0), \hspace{0.3cm} s_R = \text{max}(\widetilde{u}_L+\widetilde{c}_L, \widetilde{u}_R+\widetilde{c}_R,0),
-    \end{equation*}
-    \begin{equation*}
-      s^* = \frac{\widetilde{\sigma}_L-\widetilde{\sigma}_R+\widetilde{\rho}_L \widetilde{u}_L(s_L-\widetilde{u}_L)-\widetilde{\rho}_R \widetilde{u}_R(s_R-\widetilde{u}_R)}{\widetilde{\rho}_L(s_L-\widetilde{u}_L)-\widetilde{\rho}_R(s_R-\widetilde{u}_R)}.
-\end{equation*}
+At last, as we know the type of the structures, we can use the  iteration process again to solve the real density in region $\mathbf{Q}^*$ out.
+With the density, the pressure and the devaitoric stress are also can be solved.
 
-    \item Evaluate the densities:
-\begin{equation*}
-  \rho_L^* = \frac{\widetilde{\rho}_L(\widetilde{u}_L-s_L)}{s^*-s_L}, \hspace{0.3cm}  \rho_R^* = \frac{\widetilde{\rho}_R(\widetilde{u}_R-s_R)}{s^*-s_R},
-\end{equation*}
-
-    \item Evaluate the deviatoric stresses:
- \begin{align*}
-   \widetilde{s}_{xxL}^* = \left\{\begin{array}{cc}
-                       \widetilde{s}_{xxL} & if \ |\hat{s}_{xxL}^{*}|\geq \frac{2}{3}Y_{0} \\
-                        -\frac{4}{3}\mu \text{ln}\left( \frac{\rho_L^*}{\widetilde{\rho}_L}  \right)+\widetilde{s}_{xxL} & otherwise
-                     \end{array}\right.
-   ,\\
-   \widetilde{s}_{xxR}^* =  \left\{\begin{array}{cc}
-                       \widetilde{s}_{xxR} & if \ |\hat{s}_{xxR}^{*}| \geq \frac{2}{3}Y_{0} \\
-                        -\frac{4}{3}\mu \text{ln}\left( \frac{\rho_R^*}{\widetilde{\rho}_R}  \right)+\widetilde{s}_{xxR} & otherwise
-                     \end{array}\right.
-    ,
-\end{align*}
-then using  the von Mises' yielding condition
-\begin{equation*}
-  s_{xxL}^* = \Upsilon(\widetilde{s}_{xxL}^*) , \hspace{0.3cm}  s_{xxR}^* = \Upsilon(\widetilde{s}_{xxR}^*).
-\end{equation*}
-
-    \item Solving the Cauchy stresses:
-\begin{equation*}
-  \sigma_L^*=\sigma_R^*=\widetilde{\sigma}_L -\widetilde{\rho_L} (s_L-\widetilde{u}_L)(s^*-\widetilde{u}_L).
-\end{equation*}
-
-     \item The pressure is given by $p =s_{xx}-\sigma$.
-  \end{enumerate}
-\end{enumerate}
-
+\subsection{}
 \end{document}

### 2019-05-17 Manuscript.tex
2

@@
 \graphicspath{{TikzFig/}}
+\usepackage{hyperref}
 
@@
 
-\title{A multi-material HLLC Riemann solver with both elastic and plastic waves for 1D  elastic-plastic flows}
+\title{An exact Riemann solver for  multi-material   elastic-plastic flows with Mie-Gr\"uneisen equation of state}
 \author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
@@
 
-In this paper, a multi-material elastic-plastic HLLC-type approximate Riemann solver(MHLLCEP) is developed, with the capability of resolving both elastic and plastic waves, to simulate one-dimensional  multi-material elastic-plastic solid problems with the isotropic elastic-plastic model \cite{wilkins1963calculation} and  the von Mises' yielding condition in the framework of the  high-order cell-centered Lagrangian scheme.
-
-Generally, elastic-plastic flows can be mainly simulated in three ways, Eulerian methods \cite{trangenstein1991higher,miller2001high,barton2009exact}, staggered Lagrangian schemes \cite{wilkins1963calculation} and cell-centered Lagrangian schemes \cite{burton2013cell,kluth2010discretization,maire2013nominally,cheng2017third} that  is considered in this paper.
-Comparing with the staggered Lagrangian scheme, cell-centered Lagrangian  schemes  have many advantages.
-Firstly, it's no necessary to add  extra artificial viscosity  which  must be used in the staggered Lagrangian schemes; Secondly, it is easy to guarantee the total energy conservation; Besides, it can also be used to simulate the problems with both  hyper-elastic and hypo-elastic models  \cite{burton2013cell,kluth2010discretization,maire2013nominally,cheng2017third}  as a Lagrangian scheme.
-
-%In the  Godunov-type method
-For a cell-centered Lagrangian scheme, a core process is to move the node of grids with the speed of fluids
- % and to construct the conservative flux
- by solving a Riemann problem at each cell face. As the Riemann problem contains many physical structures, especially in elastic-plastic flows, such as elastic waves, plastic waves and contact waves
-  %or interfaces between different materials
-  , the property of the approximate Riemann solver is of great importance in the simulation. Recently, a lot of works have been done in
-  this area.
+In this paper, an exact  Riemann solver is built with the consideration of both elastic and plastic waves, for one-dimensional  multi-material elastic-plastic materials with the Mie-Gr\"uneisen EOS, isotropic elastic-plastic model \cite{wilkins1963calculation} and  the von Mises' yielding condition.
+
+The  elastic-plastic flow  is  used to describe the deformation process of solid materials under strong dynamics loading, such as explosive or high-speed impact.
+The simulation of elastic-plastic flows has important application backgrounds, espially in the Implosion Dynamics weapon and Innertial Confine Fusion (ICF).
+The first try of simulating the elastic-plastic flows was given by  Wilkins \cite{wilkins1963calculation} in 1960s.
+
+Although the control equations of elastic-plastic flow is samilar to the equations in computational fluid dynamics (CFD).
+But there are mainly three difficulties  of constructing  Riemann solvers in elastic-plastic flows.
+Firstly, the constitutive models used in elastic-plastic flows are more complicated.
+Secondly, the EOS for solid materials are also with more characters.
+Finally, the yielding process of materials may lead to more wave structures.
+
+Recently, a lot of works have been done in constructing  approximate Riemann solvers for elastic-plastic flows with the considering of structures in the Riemann problem.
 For example, Gavrilyuk et al.
-\cite{gavrilyuk2008modelling} analyzed the structure of the Riemann solution and construct a Riemann solver for the linear elastic system  of hyperbolic non-conservative models for transverse waves, wherein, an extra evolution equation was added in order to make the elastic transformations reversible in the absence of shock waves.
-Despres \cite{despres2007geometrical} built a shock solution to a non-conservations reversible system of hypo-elasticity models and found that a sonic point is necessary to construct  the compression solution that begins at a constrained compressed state.
+\cite{gavrilyuk2008modelling} analyzed the structure of the Riemann solution and constructed a Riemann solver for the linear elastic system  of hyperbolic non-conservative models for transverse waves.
 Cheng et al.
-\cite{cheng2015high} analyzed the wave structures of one-dimensional elastic-plastic flows and developed an effective two-rarefaction approximate Riemann solver with elastic waves (TRRSE) and built a  second-order and  a third-order cell-centered Lagrangian schemes based on the TRRSE, but the TRRSE is a little  expensive as  the iteration method is used.
+\cite{cheng2015high} analyzed the wave structures of one-dimensional elastic-plastic flows and developed an effective two-rarefaction approximate Riemann solver with elastic waves (TRRSE).
 In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves.
-In the HLLCE,  Cheng evaluated the deviatoric stresses from the following \emph{assumption: a pressure is continuous across the contact wave}.
-This assumption is valid for pure fluids, but  in  elastic-plastic flows, this assumption may lead to some errors.
-There are three cases we need  to consider.
-\begin{enumerate}
-  \item If states in the star regions on both sides of the contact wave are elastic, this assumption does not result in errors;
-  \item If both states reach the elastic limit, there are two cases need  to be taken into account:
-  \begin{enumerate}
-    \item if both  materials in both sides of the interface are same, this assumption does not result in errors either.
-    \item if  materials are different, this assumption will result in big errors because the yielding strengths of different materials are different;
-  \end{enumerate}
-  \item If one state in one side of the interface reaches the elastic limit, but another is  not,  this assumption will  also result in big errors.
-\end{enumerate}
-
-%For above considerations,
-In this paper, in order to eliminate these errors,
- we want to construct a new HLLC-type Riemann solver for 1D multi-material elastic-plastic flows.
-In the new solver, both the elastic waves and plastic waves are correctly resolved and the assumption in \cite{cheng2016harten} that the pressure is continuous across the interface is deleted; Correspondingly, the errors introduced by the assumption will also be eliminated.
-
-Based on the MHLLCEP, we develop a high-order elastic-plastic cell-centered Lagrangian scheme for one-dimensional multi-material elastic-plastic flows.
-If we directly use the WENO reconstruction method \cite{liu2018novel} for multi-material elastic-plastic problems,
-%With a high-order reconstruction scheme,
-the spacial stencil may cross the material interface
-% and in a multi-material state, and  will cause oscillation
- and numerical oscillations may be caused near the interface. In order to delete the numerical oscillations neat the material interface, a ghost cell method is used
-   %in the  multi-material system to obtain a stable high-order reconstruction.
-   Combined with an improved third-order WENO scheme\cite{liu2018novel} and the third-order Runge-Kutta scheme, a high-order cell-centered Lagrangian scheme is given in this paper for one-dimensional multi-material elastic-plastic flows.
+Then in \cite{liumulti}, Liu et.al remove the unreasonable assumution in HLLCE  which may cause big error in solving  multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.
+
+As we know, in hydrodynamic  numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the development of approximate solvers.
+However, in the elastic-plastic flows, for its complexity, there are only a few works have been done in constructing the exact Riemann solver.
+For example,
+Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.
+Miller \cite{miller2004iterative} presented a generial iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
+Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states.
+As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works.
+However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state.
+This symplification can truely deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
+
+In this paper, we want to construct an exact Riemann solver for the elastic-plastic equations system with the  isotropic elastic-plastic model and the  von Mises' yielding condition.
+In this system, the Mie-Gr\"uneisen EOS is used for both the elastic state and plastic state of the material, which is an adequate approximation to a wide variety of materials of interest, includes some gaseous or solid explosives and solid metals under high pressure \ref{ shyue2001fluid}.
+According to both the theoretical analyzation and numerical tests \cite{xiao1996numerical}, in this system, there may be three to five waves, including one contact wave and elastic wave (shock or rarefaction wave) or plastic wave or both the elastic and plastic waves in each side of the contact wave.
+We will prove this, the elastic wave always faster than the pastic wave in one side, so varing with the initial condition, there are $6\times 6$ thirty-six possible cases of the structures in the solution.
+For a given case, we will obtain theoretical relations of all the states as functions of density.
+At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained.
+Also, the half Riemann problem and its exact solution are considered in this paper.
 
 This paper is organized as follows.
-In section 2, we briefly introduce the governing equations to be studied.
-In section 3, the MHLLCEP method is constructed.
-Then, high-order elastic-plastic cell-centered Lagrangian scheme is given in section 4.
-Some numerical examples are presented to validate the method.
-Conclusions are shown in section 5.
+In section 2, we introduce the governing equations to be studied.
+In section 3, the Riemann problem and the relations for every wave type (contact wave, shock wave and rarefaction wave) is derived.
+Then,  the exact Riemann solver  is given in section 4.
+The half Riemann problem and its solver is introduced in section 5.
+Some numerical examples are presented to validate the method in section 6.
+Conclusions are shown in section 7.
 
@@
 According to the yielding of the material, the euqations may have different Jacobian matrix and different sonic velocities. We will discuss them seprately.
-\subsection{Jacobian matrix in  elastic regions} %and the eigenvalues and eigenvectors}
+\subsection{Elastic state}
+\subsubsection{Jacobian matrix in elastic regions} %and the eigenvalues and eigenvectors}
 For the Mie-Gr\"uneisen EOS, if the material is not yielding and 
@@
   \left\{ \begin{aligned}
-      & c = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}},\\
+      & c_e = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho}},\\
     &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
@@
         1 \\
-        u-c \\
-        h -uc \\
+        u-c_e \\
+        h -uc_e \\
         \phi^2
@@
         1 \\
-        u+c \\
-        h +uc \\
+        u+c_e \\
+        h +uc_e \\
         \phi^2
@@
   \begin{equation}
-    \phi^2 = a^2 -\frac{\rho_0}{\rho^2} \Gamma_0 s_{xx}-c^2 = -\frac{4\mu}{3}\frac{1}{\rho}.
-  \end{equation}
-\subsection{Jacobian matrix in  plastic  regions}
-When the material is yielding,
-\begin{equation}
-  |s_{xx}| = \frac{2}{3}Y_0,
-\end{equation}
-the equations will turn into a more simple system with only constitutive terms as
-\begin{equation}
-  \partial_t \mathbf{{U}} + \mathbf{J}_p(\mathbf{U})\partial_x \mathbf{{U}}= 0,
-\end{equation}
-where $\mathbf{U} = (\rho, \rho u, \rho E )$, and the Jacobian matrix is
-\begin{equation}
-\mathbf{J}_p(\mathbf{U}) = \left[\begin{array}{lll}
-      0 & 1 & 0   \\
-      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma \\
-	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u +\frac{u^2}{2} & -\Gamma u^2 -\frac{\sigma}{\rho} +e & (1+\Gamma)u\\
-\end{array}
-\right].
-\end{equation} 
-The eigenvalues of 
-The eigenvalues of the coefficient matrix $\mathbf{J}_p(\mathbf{Q})$ are given as
-$$\lambda_1 = u,\quad \lambda_2 = u-c, \quad \lambda_3 = u+c,$$
-where 
-\begin{equation}\label{eq:c_p}
-  \left\{ \begin{aligned}
-	  & c = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}} ,\\
-    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
-      \end{aligned} \right.
-    \end{equation}
-The corresponding right eigenvectors are
-\begin{equation}\label{eq:eivp}
-  r_1 = \left[ \begin{array}{l}
-	  1 \\
-	  u \\
-	  E-\frac{c^2}{\Gamma}-\frac{\sigma}{\rho}\\
-  \end{array}\right], \quad
- r_2 = \left[ \begin{array}{l}
-	  1 \\
-	  u-c \\
-	  E-uc-\frac{\sigma}{\rho}\\
-  \end{array}\right], \quad
- r_3 = \left[ \begin{array}{l}
-	  1 \\
-	  u+c \\
-	  E+uc-\frac{\sigma}{\rho}\\
-  \end{array}\right].
-\end{equation}
-Take a comparason  of Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}), we notice that the sonic speed is not continuous between the states of elastic and plastic.
-This is very important and may cause wrong results if ignoring it.
-
-\subsection{Formulations across the contact wave}\label{sec:contact}
+    \phi^2 = a^2 -\frac{\rho_0}{\rho^2} \Gamma_0 s_{xx}-c_e^2 = -\frac{4\mu}{3}\frac{1}{\rho}.
+  \end{equation}
+
+\subsubsection{A relation between $\rho$ and $s_{xx}$ }
+
+Thanks to (\ref{eq:mt}), the equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
+  \begin{equation}\label{eq:d1}
+    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
+  \end{equation}
+  and
+  \begin{equation}\label{eq:s1}
+    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
+  \end{equation}
+
+  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
+%  We can get a relation of density and deviatoric stress,
+  \begin{equation}
+    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
+\end{equation}
+Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
+\begin{equation}\label{eq:rhosxx}
+  s_{xx}+\frac{4}{3}\mu\text{ln}(\rho) = \text{constant}
+\end{equation}
+This relation always hold in the elastic state.
+
+\subsubsection{Relations across the contact wave}\label{sec:contact}
   For  a  system without molecular diffusion, there is no materials convecting  across the contact wave or interface, so the velocities on two sides of  the discontinuity are always equal. % .
@@
 
-According to  the eigenvectors in  Eq.(\ref{eq:eiv}), for the $\lambda_{1}$-wave and $\lambda_{2}$ wave,  we
+Thanks to Eq.(\ref{eq:eiv}), for the $\lambda_{1}$-wave we
 have
 \begin{equation}   \label{e23a}
-\frac{d \rho}{1} = \frac{d \rho u}{u}.
+\frac{d \rho}{\frac{1}{b_{1}}} = \frac{d \rho u}{\frac{u
+}{b_{1}}}=\frac{d \rho E}{0} = \frac{d s_{xx}}{1}.
 \end{equation}
@@
 \begin{equation}   \label{e23b}
-du = 0,
-\end{equation}
-
-Samilarly, using the eigenvectors in Eq.(\ref{eq:eivp}), for the $\lambda_{1}$-wave, we have 
-\begin{equation}  
-  \frac{d \rho}{1} = \frac{d \rho u}{u},
-\end{equation}
-we also can get 
-\begin{equation}  
-du = 0,
+du = 0, \quad d(s_{xx}-p)=0,
 \end{equation}
@@
 \end{equation}
+and
+\begin{equation}   \label{e23d}
+\sigma_{x,L}^{\ast}=\sigma_{x,R}^{\ast},
+\end{equation}
+where $()_{L}^{\ast}$ and $()_{R}^{\ast}$ denote $()$ in the region
+of $\mathbf{W}_{L}^{\ast}$ and $\mathbf{W}_{R}^{\ast}$,
+respectively. Here we do not show the details of the derivation for a simple
+ presentation.
+
+Similarly, for the $\lambda_{2}$-wave one
+has
+\begin{equation}   \label{e24a}
+\frac{d \rho}{\frac{-\Gamma}{b_{1}}} = \frac{d \rho u}{\frac{-u
+\Gamma}{b_{1}}}=\frac{d \rho E}{1} = \frac{d s_{xx}}{0}.
+\end{equation}
+From the above equations, we can easily deduce  that
+\begin{equation}   \label{e24b}
+du = 0, \quad dp=0, \quad ds_{xx}=0,
+\end{equation}
+ which means
+\begin{equation}   \label{e24c}
+  u_{L}^{\ast}=u_{R}^{\ast},
+\end{equation}
+\begin{equation}   \label{e24d}
+p_{L}^{\ast}=p_{R}^{\ast}, \quad
+  s_{xx,L}^{\ast}=s_{xx,R}^{\ast}.
+\end{equation}
+
+%where $()_{L}^{\ast}$ and $()_{R}^{\ast}$ denote $()$ in the region
+%of $\mathbf{W}_{L}^{\ast}$ and $\mathbf{W}_{R}^{\ast}$,
+%respectively.
+
+From  Eq.(\ref{e24d}), we  get that
+\begin{equation}   \label{e27a}
+\sigma_{x,L} ^{\ast}=  \sigma_{x,R} ^{\ast}.
+\end{equation}
+
+At last, for the $\lambda_{1}$ and $\lambda_{2}$ waves, one can find
+that the following two relations always hold:
+\begin{equation}   \label{e28}
+u_{L}^{\ast}=u_{R}^{\ast}, \quad
+\sigma_{x,L}^{\ast}=\sigma_{x,R}^{\ast}.
+\end{equation}
 For convenience, we define
@@
 
-Then using  the  conservation relations between the contact  wave
-\begin{equation}\label{eq:RH11}
-	\bm{F}_R^* = \bm{F}_L^*+s^*(\bm{U}_R^*-\bm{U}_L^*),
-\end{equation}
-
-From the momentum term in Eq.(\ref{eq:RH11}),
-\begin{equation}
-  \rho_R^* u_R^{*2}-\sigma^*_R=\rho_L^* u_L^{*2}-\sigma_L^*+s^*(\rho_R^* u_R^*-\rho_L^* u_L^*).
-\end{equation}
-and taking  $ s^* = u_L^* = u_R^*$ in, we can get the relation of Cauchy stress
-\begin{equation} 
-  \sigma^*_L = \sigma^*_R,
-\end{equation}
-is always satisfied.
-
-\subsection{A relation between $\rho$ and $s_{xx}$ in 1D elastic-plastic  equation system}
-
-Thanks to (\ref{eq:mt}), the equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
-  \begin{equation}\label{eq:d1}
-    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
-  \end{equation}
-  and
-  \begin{equation}\label{eq:s1}
-    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
-  \end{equation}
-
-  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
-%  We can get a relation of density and deviatoric stress,
-  \begin{equation}
-    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
-\end{equation}
-Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
-\begin{equation}\label{eq:rhosxx}
-  s_{xx2}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_{2}}{\rho_{1}})+s_{xx1}.
-\end{equation}
-The subscripts $2$ and $1$ mean the states in front of and behind the wave, respectively.
-This relation always hold if there is no yielding in the integration path.
-\subsection{Relations across rarefaction waves}\label{sec:rarefaction}
-A Rarefaction wave contains a continuous of waves with the speed of $u\pm c$.
-Now we consider a left-going rarefaction wave as shown in Fig.\ref{fig:Rare} as an example, the state in front of the wave is known as  $(\rho_1,u_1,p_1,s_{xx1})$ and after the wave the state changes to $(\rho_2,u_2,p_2,s_{xx2})$ which is unknown.
-
-We random choose a particle point inside the expansion region with the state of $(\rho,u, p,s_{xx})$, after a little expansion with the wave speed of $u-c$, the state changes to$(\rho+d\rho, u+du, p+dp, s_{xx}+ds_{xx})$.
-According to the conservation relations we can get
-\begin{equation}
-  \begin{aligned}
-	& (\rho+ \text{d}\rho)(u+ \text{d}u) = \rho u +(u-c)\text{d}\rho\\
-	& (\rho+\text{d}\rho)(u+\text{d}u)^2 -(\sigma+\text{d}\sigma)=   \rho u^2-\sigma\\
-	&+(u-c)[(\rho+\text{d}\rho)(u+\text{d}u)-\rho u] \\
-	& [(\rho+\text{d}\rho)(E+\text{d}E)-(\sigma+\text{d}\sigma)](u+\text{d}u) = \\
-	&(\rho E-\sigma)u+(u-c)[(\rho+\text{d}\rho)(E+\text{d}E)-\rho E]\\
- \end{aligned}
-\end{equation}
-Ignoring high-order infinite small terms, we can get  
+\subsubsection{Relations across rarefaction waves}\label{sec:rarefaction}
+%as an example, the state in front of the wave is known as  $(\rho_1,u_1,p_1,s_{xx1})$ and after the wave the state changes to $(\rho_2,u_2,p_2,s_{xx2})$ which is unknown.
+
+\emph{\textbf{Left-going rarefaction wave} }
+Across the left wave associated with $\lambda_3$-wave, ($\lambda_3=u-c_e$), we have
+\begin{equation}
+  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_e} = \frac{d(\rho E)}{h-uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
+\end{equation}
+which lead to 
 \begin{align}
   \label{eq:urho}
-  & \text{d} u =-\frac{c}{\rho}\text{d}\rho,\\
-\label{eq:sigmarho}
-  & \text{d} \sigma = -c^2 d\rho,\\
+  & \text{d} u =-\frac{c_e}{\rho}\text{d}\rho,\\
  \label{eq:Erho}
-  & \text{d} E = -\frac{\sigma+\rho u c}{\rho^2} d\rho.
+  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
+\label{eq:sxxrho}
+& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
 \end{align}
-Also we know the deviatoric stress is a function of the  density by Eq.(\ref{eq:rhosxx})   
-\begin{equation}
-  ds_{xx} = \left\{ \begin{aligned}
-	  -\frac{4}{3}\frac{\mu}{\rho}d\rho \quad |s_{xx}| < \frac{2}{3}Y_0,\\
-	  0  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
-	\end{aligned}
-  \right.
-\end{equation}
-And from Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}) we can get
-\begin{equation}\label{eq:c_2rho}
-  c^2 = \left\{ \begin{aligned}
-	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho} \quad |s_{xx}| < \frac{2}{3}Y_0,\\
-	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
-	\end{aligned}
-  \right.
-\end{equation}
-Then the differential of  pressure is  given  as 
-\begin{equation}
-  dp = ds_{xx} -d\sigma = ds_{xx}+c^2 d\rho = \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
+Take the relation of EOS (\ref{eq:mie}) in, we can get the pressure  as
+\begin{equation}
+  dp =  \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
 \end{equation}
@@
 \begin{equation}
-  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho), \quad p(\rho_1) = p_1,
+  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho),
 \end{equation}
@@
 \begin{equation}\label{eq:p_rho}
-  p(\rho) = p_1e^{\frac{\lambda_1}{\rho_1}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_1}^\rho f_2(x) e^{\frac{\lambda_1}{x}}dx.
-\end{equation}
-
-By the above equations of Eq.(\ref{eq:urho}-\ref{eq:Erho},\ref{eq:c_2rho},\ref{eq:p_rho}), we know that the state $(\rho, u, p, s_{xx})$ is only  a function of the density $\rho$ no matter within or  after the rarefaction wave.
-
-\subsection{Relations across  shock waves}\label{sec:shock}
+  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+\end{equation}
+Then for a given density $\rho$, we can get  the sonic speed $c_e$  and velocity 
+\begin{equation}
+  u+\int\frac{c_e}{\rho} d\rho = \text{constant}.
+\end{equation}
+
+\emph{\textbf{Right-going rarefaction wave} }
+Across the right wave associated with $\lambda_4$-wave, ($\lambda_3=u+c_e$), we have
+\begin{equation}
+  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_e} = \frac{d(\rho E)}{h+uc_e} = \frac{ds_{xx}}{-\frac{4\mu}{3}\frac{1}{\rho}}.
+\end{equation}
+which lead to 
+\begin{align}
+  \label{eq:urho}
+  & \text{d} u =\frac{c_e}{\rho}\text{d}\rho,\\
+ \label{eq:Erho}
+  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
+\label{eq:sxxrho}
+& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
+\end{align}
+We can get  similar  relations  as the left-going wave as
+\begin{equation}
+  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+\end{equation}
+\begin{equation}
+  u-\int\frac{c_e}{\rho} d\rho = \text{constant}.
+\end{equation}
+
+\subsubsection{Relations across  shock waves}\label{sec:shock}
 Now we consider a shock wave with a speed of $s$, suppose the state in front of the shock is known as $(\rho_1,u_1,p_1,s_{xx1})$ and the state after the shock is unknown as $(\rho_2,u_2,p_2,s_{xx2})$.
@@
 \end{align}
-also can be written as
+above relations also can be written as
 \begin{align}
@@
 Put above equation into (\ref{eq:e2e1}), we can solve the pressure $p_2$ out as a function of $\rho_2$. 
-\begin{equation}\label{eq:shockp}
+\begin{equation}\label{eq:shocke}
   p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1},
 \end{equation}
-The derivative stress $\sigma_{xx2}$ is also a function of $rho_2$ only. So we can solve the Cauchy stress out as
+The derivative stress $\sigma_{xx2}$ also is  a function of $\rho_2$ only. So we can solve the Cauchy stress out as
 \begin{equation}
@@
 
-\section{Exact Riemann solver}\label{sec:riemann}
+\subsection{Plastic state}
+  \subsubsection{Jacobian matrix in  plastic  regions\footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}}
+When the material is yielding,
+\begin{equation}
+  |s_{xx}| = \frac{2}{3}Y_0,
+\end{equation}
+the equations will turn into a more simple system with only constitutive terms as
+\begin{equation}
+  \partial_t \mathbf{{U}} + \mathbf{J}_p(\mathbf{U})\partial_x \mathbf{{U}}= 0,
+\end{equation}
+where $\mathbf{U} = (\rho, \rho u, \rho E )$, and the Jacobian matrix is
+\begin{equation}
+\mathbf{J}_p(\mathbf{U}) = \left[\begin{array}{lll}
+      0 & 1 & 0   \\
+      -u^2 + \frac{\partial p}{\partial \rho} +\Gamma(\frac{u^2}{2}-e)& u(2-\Gamma)& \Gamma \\
+	  (\Gamma(\frac{u^2}{2}-e)-e-\frac{u^2}{2}+\frac{\sigma}{\rho}+\frac{\partial p}{\partial \rho})u +\frac{u^2}{2} & -\Gamma u^2 -\frac{\sigma}{\rho} +e & (1+\Gamma)u\\
+\end{array}
+\right].
+\end{equation} 
+The eigenvalues of 
+The eigenvalues of the coefficient matrix $\mathbf{J}_p(\mathbf{Q})$ are given as
+$$\lambda_1 = u,\quad \lambda_2 = u-c, \quad \lambda_3 = u+c,$$
+where 
+\begin{equation}\label{eq:c_p}
+  \left\{ \begin{aligned}
+	  & c_p = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}} ,\\
+    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
+      \end{aligned} \right.
+    \end{equation}
+The corresponding right eigenvectors are
+\begin{equation}\label{eq:eivp}
+  r_1 = \left[ \begin{array}{l}
+	  -\frac{\Gamma}{b_1} \\
+	  -\frac{\Gamma u}{b_1} \\
+	  1\\
+  \end{array}\right], \quad
+  r_2 = \frac{1}{h-uc_p} \left[  \begin{array}{l}
+	  1 \\
+	  u-c_p \\
+	  h-uc_p\\
+  \end{array}\right], \quad
+ r_3 = \frac{1}{h+uc_p}\left[ \begin{array}{l}
+	  1 \\
+	  u+c_p \\
+	  h+uc_p\\
+  \end{array}\right].
+\end{equation}
+where 
+ \begin{equation}
+    b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho}.
+  \end{equation}
+
+Take a comparason  of Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}), we notice that the sonic speed is not continuous between the states of elastic and plastic.
+As the shear modulus $\mu$ is always positive, so the elastic wave is always faster than the plastic wave.
+This is very important and may cause wrong results if ignoring it.
+
+\subsubsection{Relations across the contact wave}\label{sec:contact}
+
+According to  the eigenvectors in  Eq.(\ref{eq:eivp}), for the $\lambda_{1}$-wave ($\lambda_1 = u$), we
+have
+\begin{equation}   \label{e232a}
+  \frac{d \rho}{\frac{-\Gamma}{b_1}} = \frac{d (\rho u)}{\frac{-u\Gamma}{b_1}} = \frac{d (\rho E)}{1}.
+\end{equation}
+From the above equations, we can easily deduce that
+\begin{equation}  
+  du = 0, \quad dp = 0. 
+\end{equation}
+Samilar to that in  section \ref{sec:contact}, we can also get the relations
+\begin{equation} 
+  s^* = u_L^* = u_R^*, % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
+ \quad
+  \sigma^*_L = \sigma^*_R.
+\end{equation}
+
+\subsubsection{Relations across rarefaction waves}
+%as an example, the state in front of the wave is known as  $(\rho_1,u_1,p_1,s_{xx1})$ and after the wave the state changes to $(\rho_2,u_2,p_2,s_{xx2})$ which is unknown.
+
+\emph{\textbf{Left-going rarefaction wave} }
+Across the left wave associated with $\lambda_2$-wave, ($\lambda_2=u-c_p$), we have
+\begin{equation}
+  \frac{d\rho}{1} = \frac{d(\rho u)}{u-c_p} = \frac{d(\rho E)}{h-uc_p}.
+\end{equation}
+Samilar to section \ref{sec:rarefaction}, we can get the relations
+\begin{equation}\label{eq:p_rhop}
+  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+\end{equation}
+and
+\begin{equation}
+  u+\int\frac{c_p}{\rho} d\rho = \text{constant},
+\end{equation}
+where
+\begin{equation}
+  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+\end{equation}
+\emph{\textbf{Right-going rarefaction wave} }
+Across the right wave associated with $\lambda_3$-wave, ($\lambda_3=u+c_e$), we have
+\begin{equation}
+  \frac{d\rho}{1} = \frac{d(\rho u)}{u+c_p} = \frac{d(\rho E)}{h+uc_p}.
+\end{equation}
+We can get  similar  relations  as the left-going wave as
+\begin{equation}
+  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+\end{equation}
+\begin{equation}
+  u-\int\frac{c_p}{\rho} d\rho = \text{constant}.
+\end{equation}
+\subsubsection{Relations across  shock waves}\label{sec:shockp}
+By a same deducing process with Section \ref{sec:shock}, we can get the state after a shock as  
+\begin{equation}
+  s_{xx2} = s_{xx1},
+\end{equation}
+\begin{equation}\label{eq:shockp}
+  p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
+\begin{equation}
+  \sigma_2 = -p_2 +s_{xx2}.
+\end{equation}
+\begin{equation}\label{eq:shockup}
+  u_2 = \left\{ \begin{aligned}
+	 & u_1 - \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Left-going}, \\
+	 & u_1 + \sqrt{\frac{\sigma_1- \sigma_2}{t}} \quad \text{Right-going}.
+	\end{aligned}
+	\right.
+  \end{equation}
+And the shock speed is given as 
+\begin{equation}
+  s = \frac{\rho_2u_2-\rho_1u_1}{\rho_2-\rho_1}.
+\end{equation}
+
+\section{Exact Riemann solver \footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}} \label{sec:riemann}
 
@@
 
-There are mainly three parts in the soluting process.
-
-Firstly, a pre-evaluation need to  be done to detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases.
-This is done in Section (\ref{sec:eva}) with shock-contact-shock waves assumption.
-
-Secondly,  we solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ in cases (a,b,d,e) in Section \ref{sec:one} and in cases (c,f) in Section \ref{sec:two}.
-
-At last,  we use  the informations in Section \ref{sec:contact}, the velocities and the Cauchy stresses  in the two sides of the contact must be equal. So there are two equations 
+There are mainly five  steps in the soluting process. 
+\begin{enumerate}
+  \item In section (\ref{sec:eva}), a pre-evaluation is done with a shock-contact-shock waves assumption to give an initial values of $\rho^*_L$ and $\rho^*_R$.
+
+  \item  With  given $\rho^*_L$ and $\rho^*^_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
+
+  \item  We solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ for  different cases in section \ref{sec:one}.
+
+\item At last,   with  the informations in Section \ref{sec:contact},  
 \begin{equation}\label{eq:fus}
-  \begin{align}
+  \begin{aligned}
 	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
 	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
-\end{align}
-\end{equation}
-and two unknowns $\rho_L^*$ and $\rho_R^*$. Equation (\ref{eq:fus}) is implicit, we have to use a Newton iteration method to solve it, this process is given in Section \ref{sec:iteration}.
+\end{aligned}
+\end{equation}
+ use a Newton iteration method to  get new $\rho^*_L$ and $\rho^*_R$, then do steps 2-5 again until the result convergents. this process is given in Section \ref{sec:iteration}.
+\end{enumerate}
 \subsection{Pre-evaluation and case classfication}\label{sec:eva}
@@
   \left\{
-  \begin{align}
+  \begin{aligned}
 	\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
-	\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), \\
-  \end{align}
+	\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
+  \end{aligned}
 \right.
@@
   \left\{
-  \begin{align}
+  \begin{aligned}
 	\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
-	\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). \\
-  \end{align}
+	\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
+  \end{aligned}
 \right.
@@
   \caption{Pre-evaluation with a three-waves structure.}
+  \label{fig:HLLC}
 \end{figure}
+
 Using the relation across the interface,
@@
 \end{equation}
-The devaitoric stress is ecaluated as 
+\subsection{Determination of the  structure case}
+
+Using a given density $\rho^*_L$, we can distinguish the shock and rarefaction in the left side.  This is done easily by comparing $\rho^*_L$ with $\rho_L$,
+\begin{equation}
+  \left\{
+  \begin{aligned}
+  & \text{Rarefaction wave:} & \rho_L > \rho_L^*\\
+  & \text{Shock wave:} &  \rho_L < \rho_L^*\\
+\end{aligned}\right.
+\end{equation}
+
+To determine the number of waves, we need to know the yielding situation, we first evaluate 
+The devaitoric stress is evaluated as 
 \begin{equation}  \label{sxx1}
@@
 \begin{equation}
-  p(\rho)=p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad & \text{case (a,b)}.
+  p(\rho)=p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad  \text{case (a,b)}.
 \end{equation}
@@
 \begin{equation}
- \tilde{s}_{xxL(R)} = \left\{ \begin{align}
+ \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
 	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
-	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},\\
-	\end{align}
+	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
+	\end{aligned}
   \right.
@@
 \begin{equation}
-  \tilde{\rho}_{L(R)}= \left\{ \begin{align}
+  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
 	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
 	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
-	\end{align}
+	\end{aligned}
   \right.
@@
 
-First we need evaluate the density in the star region $\mathbf{Q}^*$ with a  elastic shock assumption.
+First we  evaluate the density in the star region $\mathbf{Q}^*$ with a  elastic shock assumption.
 Then using the relation of $\sigma(\rho^*) = \sigma^*$.
@@
 
-Second, we can determine the case by the same condition in Table \ref{tab:cases}.
+Second, we can determine the real structure  case by Table \ref{tab:cases}.
 
@@
 
-\subsection{}
+\subsection{Evaluate of the density $\hat{\rho}$ in region $\mathbf{Q}^*$ }
+As shown in Fig.\ref{fig:half:shock}, we  assume there is only one elastic shock wave between region $\mathbf{Q}$ and region $\mathbf{Q}^*$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width= 10cm] {Tikz-figure9.eps}
+  \caption{Pre-evaluation of the half Riemann problem  with a elastic shock assumeption.}
+  \label{fig:half}
+\end{figure}
+Then use the shock relation in Section \ref{sec:shock}, and  by the Newton   iteration process we can solve the density $\hat{\rho}$ out.
+
+If the Cauchy stress  in region $\mathbf{Q}^*$ is given, let
+\begin{equation}
+  f(\rho) = \sigma^*(\rho) -\sigma_R,
+\end{equation}
+if the velocity is given, let
+\begin{equation}
+  f(\rho) = u^*(\rho) -u_R.
+\end{equation}
+
+The  Newton iteration is given as
+\begin{equation}
+  \hat{\rho}_{(k+1)} = \hat{\rho}_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
+\end{equation}
+and the initial is given as 
+\begin{equation}
+  \hat{\rho}_{(0)} = \rho_R.
+\end{equation}
+The  congergence is meassured by
+\begin{equation}
+  \text{CHA} = \text{max} \left[\frac{|\hat{\rho}_{(k+1)}-\hat{\rho}_{(k)}|}{\frac{1}{2}|\hat{\rho}_{(k+1)}+\hat{\rho}_{(k)|}},|f_{(k+1)}|\right].
+\end{equation}
+\subsection{Resolve  the state in region $\mathbf{Q}^*$}
+After evaluate the density $\hat{\rho}$ in region $\mathbf{Q}^*$,   the deviatoric stress also can be evaluated by Eq \ref{eq:rhosxx}, and use Table  \ref{tab:cases}, the real structure case is known.
+By  an exact same iteration process in above
+\begin{equation}
+ \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
+\end{equation}
+with the initial condition of 
+\begin{equation}
+  \rho^*_{(0)} = \hat{\rho},
+\end{equation}
+we can solve the $\rho^*$ out.
+
+In the iteration process the Cauchy stress $\sigma^*(\rho)$ or the velocity $\sigma^*(\rho)$ is given by the relation in Section \ref{sec:one} or Section \ref{sec:two} for different cases.
+\section{Numerical }
+%
+\section*{Conclusions}
+In this paper,  the multi-material HLLC-type  approximate Riemann solver with both the elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic  flows with a hypo-elastic model and the von Mises yielding condition.
+During constructing the  MHLLCEP, we do not use the assumption in which the pressure is continuous across the contact wave and so describing and evaluating the plastic waves are  more accurate than that in the  HLLCE.
+Based on the MHLLCEP,
+combining with the third-order ghost-cell reconstruction method and the third-order TVD-Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic flows is built.
+Verified by the numerical experiments, both the plastic waves and elastic waves can be resolved correctly, our scheme appears to be convergent, stable, essentially non-oscillatory and can reach third-order accuracy for smooth problems.
+Especially for multi-material elastic-plastic flows, the results solved by the scheme with HLLCE are with large errors, but our new scheme can eliminate these errors and leads to the reasonable numerical results.
+
+%
+\section*{Acknowledgement}
+This work was supported by NSFC(Grant No. 11672047) and Science Challenge Project (Grant No. TZ2016002).
+
+We random choose a particle point inside the expansion region with the state of $(\rho,u, p,s_{xx})$, after a little expansion with the wave speed of $u-c$, the state changes to$(\rho+d\rho, u+du, p+dp, s_{xx}+ds_{xx})$.
+According to the conservation relations we can get
+\begin{equation}
+  \begin{aligned}
+	& (\rho+ \text{d}\rho)(u+ \text{d}u) = \rho u +(u-c)\text{d}\rho\\
+	& (\rho+\text{d}\rho)(u+\text{d}u)^2 -(\sigma+\text{d}\sigma)=   \rho u^2-\sigma\\
+	&+(u-c)[(\rho+\text{d}\rho)(u+\text{d}u)-\rho u] \\
+	& [(\rho+\text{d}\rho)(E+\text{d}E)-(\sigma+\text{d}\sigma)](u+\text{d}u) = \\
+	&(\rho E-\sigma)u+(u-c)[(\rho+\text{d}\rho)(E+\text{d}E)-\rho E]\\
+ \end{aligned}
+\end{equation}
+Ignoring high-order infinite small terms, we can get  
+\begin{align}
+  \label{eq:urho}
+  & \text{d} u =-\frac{c}{\rho}\text{d}\rho,\\
+\label{eq:sigmarho}
+  & \text{d} \sigma = -c^2 d\rho,\\
+ \label{eq:Erho}
+  & \text{d} E = -\frac{\sigma+\rho u c}{\rho^2} d\rho.
+\end{align}
+Also we know the deviatoric stress is a function of the  density by Eq.(\ref{eq:rhosxx})   
+\begin{equation}
+  ds_{xx} = \left\{ \begin{aligned}
+	  -\frac{4}{3}\frac{\mu}{\rho}d\rho \quad |s_{xx}| < \frac{2}{3}Y_0,\\
+	  0  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
+	\end{aligned}
+  \right.
+\end{equation}
+And from Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}) we can get
+\begin{equation}\label{eq:c_2rho}
+  c^2 = \left\{ \begin{aligned}
+	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho} \quad |s_{xx}| < \frac{2}{3}Y_0,\\
+	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
+	\end{aligned}
+  \right.
+\end{equation}
+Then the differential of  pressure is  given  as 
+\begin{equation}
+  dp = ds_{xx} -d\sigma = ds_{xx}+c^2 d\rho = \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
+\end{equation}
+it can be written as a differential equation of $p(\rho)$
+\begin{equation}
+  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho), \quad p(\rho_1) = p_1,
+\end{equation}
+where 
+\begin{equation}
+  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+\end{equation}
+The pressure can be solved out as
+\begin{equation}\label{eq:p_rho}
+  p(\rho) = p_1e^{\frac{\lambda_1}{\rho_1}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_1}^\rho f_2(x) e^{\frac{\lambda_1}{x}}dx.
+\end{equation}
+
+By the above equations of Eq.(\ref{eq:urho}-\ref{eq:Erho},\ref{eq:c_2rho},\ref{eq:p_rho}), we know that the state $(\rho, u, p, s_{xx})$ is only  a function of the density $\rho$ no matter within or  after the rarefaction wave.
+
+\section*{References}
+
+\bibliography{mybibfile}
+
+\newpage
+  \appendix
+  \renewcommand{\appendixname}{Appendix~}
+
 \end{document}

### 2019-05-31 Manuscript.tex
11111

@@
 \usepackage{setspace}
-\graphicspath{{picture/}}
-\graphicspath{{TikzFig/}}
+\graphicspath{{TikzFig/}{Picture/}}
 \usepackage{hyperref}
@@
 The  elastic-plastic flow  is  used to describe the deformation process of solid materials under strong dynamics loading, such as explosive or high-speed impact.
-The simulation of elastic-plastic flows has important application backgrounds, espially in the Implosion Dynamics weapon and Innertial Confine Fusion (ICF).
+The simulation of elastic-plastic flows has important application backgrounds, especially in the Implosion Dynamics weapon and Innertial Confine Fusion (ICF).
 The first try of simulating the elastic-plastic flows was given by  Wilkins \cite{wilkins1963calculation} in 1960s.
 
-Although the control equations of elastic-plastic flow is samilar to the equations in computational fluid dynamics (CFD).
+Although the control equations of elastic-plastic flow is similar to the equations in computational fluid dynamics (CFD).
 But there are mainly three difficulties  of constructing  Riemann solvers in elastic-plastic flows.
 Firstly, the constitutive models used in elastic-plastic flows are more complicated.
-Secondly, the EOS for solid materials are also with more characters.
+Secondly, the EOS for solid materials is also with more characters.
 Finally, the yielding process of materials may lead to more wave structures.
@@
 In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves.
-Then in \cite{liumulti}, Liu et.al remove the unreasonable assumution in HLLCE  which may cause big error in solving  multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.
-
-As we know, in hydrodynamic  numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the development of approximate solvers.
+Then in \cite{liumulti}, Liu et.al remove the unreasonable assumution in HLLCE  which may cause big errors in solving  multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.
+
+As we know, in hydrodynamic  numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the developing of approximate solvers.
 However, in the elastic-plastic flows, for its complexity, there are only a few works have been done in constructing the exact Riemann solver.
@@
 Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.
-Miller \cite{miller2004iterative} presented a generial iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
+Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
 Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states.
@@
 However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state.
-This symplification can truely deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
+This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
 
@@
 In this system, the Mie-Gr\"uneisen EOS is used for both the elastic state and plastic state of the material, which is an adequate approximation to a wide variety of materials of interest, includes some gaseous or solid explosives and solid metals under high pressure \ref{ shyue2001fluid}.
-According to both the theoretical analyzation and numerical tests \cite{xiao1996numerical}, in this system, there may be three to five waves, including one contact wave and elastic wave (shock or rarefaction wave) or plastic wave or both the elastic and plastic waves in each side of the contact wave.
-We will prove this, the elastic wave always faster than the pastic wave in one side, so varing with the initial condition, there are $6\times 6$ thirty-six possible cases of the structures in the solution.
+According to both the theoretical analysation and numerical tests \cite{xiao1996numerical}, in this system, there may be three to five waves, including one contact wave and elastic wave (shock or rarefaction wave) or plastic wave or both the elastic and plastic waves in each side of the contact wave.
+We will prove this, the elastic wave always faster than the plastic wave of  one side, so varying from the initial condition, there are $6\times 6$ thirty-six possible cases of the structures in the solution.
 For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 
-According to the yielding of the material, the euqations may have different Jacobian matrix and different sonic velocities. We will discuss them seprately.
+According to the yielding of the material, the equations may have different Jacobian matrix and different sonic velocity. We will discuss them separately.
 \subsection{Elastic state}
 \subsubsection{Jacobian matrix in elastic regions} %and the eigenvalues and eigenvectors}
-For the Mie-Gr\"uneisen EOS, if the material is not yielding and 
+For the Mie-Gr\"uneisen EOS, if the material is not yielding, 
 \begin{equation}
@@
 \subsection{Plastic state}
+When the material is yielding, the deviatoric stress is a constant
+\begin{equation}
+  |s_{xx}| = \frac{2}{3}Y_0.
+\end{equation}
+And the Riemann problem turns into 
+\begin{equation}\label{eq:1dp}
+   \left\{ \begin{aligned}
+       & \partial _t \rho +\partial_x(\rho u)=0,\\
+       & \partial _t (\rho u)+\partial_x(\rho u^2 + p -s_{xx})=0,\\
+       &\partial _t (\rho E)+\partial_x\left[(\rho E + p -s_{xx})u\right]=0,\\
+& |s_{xx}| = \frac{2}{3}Y_{0}, \\
+       &U(x,t = 0) = \left\{\begin{aligned}
+           U_L, \hspace{0.1cm} \text{if} \hspace{0.1cm} x<0, \\
+           U_R, \hspace{0.1cm} \text{if} \hspace{0.1cm} x\ge 0, \\
+       \end{aligned}\right.
+     \end{aligned}
+  \right.
+\end{equation}
+where $\mathbf{U} = (\rho, \rho u, \rho E )$.
   \subsubsection{Jacobian matrix in  plastic  regions\footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}}
-When the material is yielding,
-\begin{equation}
-  |s_{xx}| = \frac{2}{3}Y_0,
-\end{equation}
-the equations will turn into a more simple system with only constitutive terms as
+  The equations (\ref{eq:1dp}) can be written as
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{U} = (\rho, \rho u, \rho E )$, and the Jacobian matrix is
+ where the Jacobian matrix is
 \begin{equation}
@@
 
-  \item  With  given $\rho^*_L$ and $\rho^*^_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
+  \item  With  given $\rho^*_L$ and $\rho^*_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
 
@@
 \end{enumerate}
-\subsection{Pre-evaluation and case classfication}\label{sec:eva}
-At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}.
-According to the conservation relations across the shocks, we have
-\begin{equation}
-  \left\{
-  \begin{aligned}
-	\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
-	\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
-  \end{aligned}
-\right.
-\end{equation}
-and
-\begin{equation}
-  \left\{
-  \begin{aligned}
-	\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
-	\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
-  \end{aligned}
-\right.
-\end{equation}
-\begin{figure}
-  \centering
-  \includegraphics[width=8cm]{Tikz-figure7.eps}
-  \caption{Pre-evaluation with a three-waves structure.}
-  \label{fig:HLLC}
-\end{figure}
-
-Using the relation across the interface,
-\begin{equation}
-  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
-\end{equation}
-the speed of contact wave can be evaluated as 
-\begin{equation}
-\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
-\end{equation}
-the density is solved as 
-\begin{equation}
-\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
-\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
-\end{equation}
-\subsection{Determination of the  structure case}
-
-Using a given density $\rho^*_L$, we can distinguish the shock and rarefaction in the left side.  This is done easily by comparing $\rho^*_L$ with $\rho_L$,
-\begin{equation}
-  \left\{
-  \begin{aligned}
-  & \text{Rarefaction wave:} & \rho_L > \rho_L^*\\
-  & \text{Shock wave:} &  \rho_L < \rho_L^*\\
-\end{aligned}\right.
-\end{equation}
-
-To determine the number of waves, we need to know the yielding situation, we first evaluate 
-The devaitoric stress is evaluated as 
-\begin{equation}  \label{sxx1}
-  \hat{s}_{xxL}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_L^*}{\rho_L})+s_{xxL}, \quad   \hat{s}_{xxR}^*=-\frac{4}{3}\mu\text{ln}(\frac{\hat{\rho}_R^*}{\rho_R})+s_{xxR}.
-\end{equation}
-Here we define the speeds of left and right going waves as
- \begin{equation}
-      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
-\end{equation}
-By  the relation of $\hat{\rho}_{L(R)}$ and  $\hat{s}_{xxL(R)}$ we can classify every side into six cases, and conditions for the classfication are  shown in Table \ref{tab:cases}, the  subscripts $_L$ and  $_R$  are omitted for simplication.
-
-\begin{table}
-  \centering 
-  \caption{The condition of  cases classification.}
-  \begin{tabular}{c|ccc}
-	\toprule
-	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$&  other\\
-  \midrule
-  $\hat{\rho^*} <\rho$ & case a& case b& case c \\
-  $\hat{\rho^*} >\rho$ & case d& case e& case f \\
-  \bottomrule
-\end{tabular}
-\label{tab:cases}
-\end{table}
-
-\subsection{States for one wave cases (a,b, d,e)}\label{sec:one}
-For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, if we give a density $\rho_L^*$ in the region $\mathbf{Q}_L^*$, by the deductions in Section \ref{sec:rarefaction} and Section \ref{sec:shock}, all the unknowns in region $\mathbf{Q}_L^*$ can be solved out.
-
-\subsubsection{Rarefaction  wave cases (a,b)}
-For Rarefaction wave, we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region.
-
-First we give the function of $s_{xx}$,
-\begin{equation}
-  s_{xx}(\rho) = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}, \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (a)},\\
-	  & \frac{2}{3}Y_0,  \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (b)}.
-  \end{aligned} \right.
-  \end{equation}
-Then we give the pressure,
-\begin{equation}
-  p(\rho)=p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad  \text{case (a,b)}.
-\end{equation}
-where 
-\begin{equation}
-  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
-\end{equation}
-
-and sonic speed,
-\begin{equation}
-  c(\rho) = \left\{ \begin{aligned}
-	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case (a)},\\
-	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case (b)}.
-	\end{aligned}\right.
-\end{equation}
-Then we can get  the  function of  velocity
-\begin{equation}
-  u(\rho) =\left\{ \begin{aligned} 
-	  &u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_L \ge \rho \ge \rho_L^*,   \quad &\text{case (a,b)} , \\
-	  &u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_R \ge \rho \ge \rho_R^*, \quad &\text{case (a,b)}, \\
-	\end{aligned}
-  \right.
-\end{equation}
-
-\subsubsection{Shock wave cases (d,e)}
-For shock waves, the function of deviatoric is given as 
-\begin{equation}
-  s_{xx}(\rho) = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad   &\rho =\rho_{L(R)},\rho_{L(R)}^*,
-	\quad  &\text{case (d)},\\
-	& -\frac{2}{3}Y_0,   \quad & \rho =\rho_{L(R)},\rho_{L(R)}^*, \quad
- &\text{case (e)}.
-  \end{aligned} \right.
-  \end{equation}
-And the pressure is given as
-\begin{equation}
-  p(\rho)= 
-  \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2tc_0-1}, \quad  \rho=\rho_{L(R)},\rho_{L(R)}^*, \quad 
-  \text{ case (d,e)},
-\end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\rho_{L(R)}}$. 
-The velocity is given as
-\begin{equation}
-  u(\rho) = \left\{ \begin{aligned}
-	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t}} \quad &\rho =\rho_L, \rho_L^*\\ 
-	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t}} \quad & \rho =\rho_R, \rho_R^*\\
-  \end{aligned}
-\right. \quad \text{case (d,e)}
-\end{equation}
-
-\subsection{States for two wave cases (c,f)}\label{sec:two}
-
-For cases (c,f), the meterial periods a yielding process from elastic to plastic.
-There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
-In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
-\begin{equation}
- \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
-	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
-	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
-	\end{aligned}
-  \right.
-\end{equation}
-By (\ref{eq:rhosxx}),at state $\tilde{\mathbf{Q}}_{L(R)}$ we can solve the density out as 
-\begin{equation}
-  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
-	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
-	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
-	\end{aligned}
-  \right.
-	\end{equation}
-\subsubsection{Rarefaction wave case (c)}
-For rarefaction wave case,
-we give the function of $s_{xx}$ at first,
-\begin{equation}
-  s_{xx}(\rho) = \left\{\begin{aligned}
-	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}  ,\\
-	& \frac{2}{3}Y_0, & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.\\
-  \end{aligned} \right. \quad \text{case (c)}.
-  \end{equation}
-
-The pressure is given as 
-\begin{equation}
-  p(\rho)= \left\{ \begin{aligned}
-	  p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,\quad & \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},\\
-	  \tilde{p}_{L(R)}e^{\frac{\lambda_1}{\tilde{\rho}_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,  \quad & \tilde{\rho}_{L(R)}\ge \rho \ge \rho_{L(R)}^*,
-  \end{aligned} \right.
-  \text{case (c)},
-\end{equation}
-where 
-\begin{equation}
-  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
-\end{equation}
-
-And sonic speed,
-\begin{equation}
-  c(\rho) = \left\{ \begin{aligned}
-	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}\\
-	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  &   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.
-  \end{aligned}\right. \quad \text{case (c)}.
-\end{equation}
-Then we can get  the   function of  velocity
-\begin{equation}
-  u(\rho) =\left\{ \begin{aligned} 
-	&u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge \rho_L^* , \\
-	&u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge  \rho_R^* , 
-	\end{aligned}
-  \right. \quad \text{case (c)}.
-\end{equation}
-\subsubsection{Shock wave case (f)}
-For shock waves the function of deviatoric is given as 
-\begin{equation}
-  s_{xx}(\rho) = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad &  \rho =\rho_{L(R)},\tilde{\rho}_{L(R)},\\
-	  & -\frac{2}{3}Y_0, \quad  & \rho = \rho_{L(R)}^*,
-  \end{aligned} \right. \quad  \text{case (f)}.
-  \end{equation}
-
-And the pressure is given as
-\begin{equation}
-  p(\rho)= \left\{\begin{aligned} 
-	  & \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2t_1c_0-1}, \quad  &  \rho=\rho_{L(R)},\tilde{\rho}_{L(R)},\\ 
-	  & \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_L)-(\tilde{\sigma}_{L(R)}+s_{xx}(\rho))}{2t_2c_0-1}, \quad  &  \rho=\rho_{L(R)}^*,\\ 
-  \end{aligned}\right.
-  \text{ case (f)},
-\end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t_1=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$, $ t_2=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$.
-
-The velocity is given as
-\begin{equation}
-  u(\rho) = \left\{ \begin{array}{ll}
-	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_L,\tilde{\rho}_L,\\ 
-	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_L^*,\\ 
-	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_R, \tilde{\rho}_R, \\ 
-	\tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_R^*, \end{array}
-  \right. \quad \text{case (f)}.
-\end{equation}
 
@@
 For a given  $\rho_L^*$ and a given $\rho_R^*$,
-\begin{equation}
-  \begin{aligned}
- & u_L^* = u(\rho_L^*),\quad u_R^*= u(\rho_R^*) ,\\
- & \sigma_L^* = -p(\rho_L^*)+s_{xx}(\rho_L^*),\quad \sigma_R^*= -p(\rho_R^*)+s_{xx}(\rho_R^*) ,\\
-\end{aligned}
-\end{equation}
  by relations of 
@@
 A flow chat of this process is shown in Fig.\ref{fig:newton}.
-\section{Half Riemann problem and  solver}
+\subsection{Pre-evaluation of densities}\label{sec:eva}
+At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}.
+According to the conservation relations across the shocks, we have
+\begin{equation}
+  \left\{
+  \begin{aligned}
+	&\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
+	&\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
+  \end{aligned}
+\right.
+\end{equation}
+and
+\begin{equation}
+  \left\{
+  \begin{aligned}
+	&\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
+	&\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
+  \end{aligned}
+\right.
+\end{equation}
+\begin{figure}
+  \centering
+  \includegraphics[width=8cm]{Tikz-figure7.eps}
+  \caption{Pre-evaluation with a three-waves structure.}
+  \label{fig:HLLC}
+\end{figure}
+
+Using the relation across the interface,
+\begin{equation}
+  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
+\end{equation}
+the speed of contact wave can be evaluated as 
+\begin{equation}
+\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
+\end{equation}
+the density is solved as 
+\begin{equation}
+\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
+\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
+\end{equation}
+Here we define the speeds of left and right going waves as
+ \begin{equation}
+      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
+\end{equation}
+\subsection{Determining the case of structures} \label{sec:deter}
+
+Using a given density $\rho^*_L$, we can distinguish the shock and rarefaction in the left side.  This is done easily by comparing $\rho^*_L$ with $\rho_L$,
+\begin{equation}
+  \left\{
+  \begin{aligned}
+	& \text{Rarefaction wave:} & \rho_L > \rho_L^*,\\
+	& \text{Shock wave:} &  \rho_L < \rho_L^*.\\
+\end{aligned}\right.
+\end{equation}
+
+To determine the number of waves, we need to know the yielding situation,  
+the devaitoric stress can be evaluated as 
+\begin{equation}  \label{sxx1}
+  \hat{s}_{xxL}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_L^*}{\rho_L})+s_{xxL},
+\quad
+  \hat{s}_{xxR}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_R^*}{\rho_R})+s_{xxR}.
+\end{equation}
+  Then we can classify every side into six cases, and conditions for the classfication are  shown in Table \ref{tab:cases}, the  subscripts $_L$ and  $_R$  are omitted for simplication.
+
+\begin{table}
+  \centering 
+  \caption{The condition of  cases classification.}
+  \begin{tabular}{c|ccc}
+	\toprule
+	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$&  other\\
+  \midrule
+  $\hat{\rho^*} <\rho$ & case a& case b& case c \\
+  $\hat{\rho^*} >\rho$ & case d& case e& case f \\
+  \bottomrule
+\end{tabular}
+\label{tab:cases}
+\end{table}
+
+\subsection{Functions of the pressure, derivative stress and velocity}\label{sec:functions}
+\subsubsection{State in $\tilde{\mathbf{Q}}_{L(R)}$ in cases (c,f)}
+
+For cases (c,f), the meterial periods a yielding process from elastic to plastic.
+There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
+In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
+\begin{equation}
+ \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
+	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
+	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
+	\end{aligned}
+  \right.
+\end{equation}
+By (\ref{eq:rhosxx}),at state $\tilde{\mathbf{Q}}_{L(R)}$ we can solve the density out as 
+\begin{equation}
+  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
+	  & \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
+	  & \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
+	\end{aligned}
+  \right.
+	\end{equation}
+	\emph{\textbf{Rarefaction wave case (c)}}
+For rarefaction wave case,
+we give the function of $s_{xx}$ at first,
+\begin{equation}
+  s_{xx}(\rho) =
+	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
+  \end{equation}
+
+The pressure is given as 
+\begin{equation}
+  p(\rho)=
+	  p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
+\end{equation}
+where 
+\begin{equation}
+  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+\end{equation}
+
+And sonic speed,
+\begin{equation}
+  c_e(\rho) = 
+	  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad   \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
+\end{equation}
+Then we can get  the   function of  velocity
+\begin{equation}
+  u(\rho) =\left\{ \begin{aligned} 
+	&u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad & \rho_{L} \ge \rho \ge \tilde{\rho}_{L}
+ , \\
+ &u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_R\ge \rho\ge \tilde{\rho}_R , 
+	\end{aligned}
+  \right. \quad \text{case (c)}.
+\end{equation}
+The states in region $\tilde{\mathbf{Q}}_{L(R)}$ can be solved as 
+\begin{equation}
+  \tilde{s}_{xxL(R)} = s_{xx}(\rho_{L(R)}),\quad \tilde{p}_{L(R)} = p(\rho_{L(R)}), \quad \tilde{u}_{L(R)} = u(\rho_{L(R)}).
+\end{equation}
+
+\emph{\textbf{Shock wave case (f)}} For shock wave case, the deviatoric stress is given as 
+\begin{equation}
+  \tilde{ s}_{xxL(R)} =
+  -\frac{4}{3}\mu\text{ln}\left(\frac{\tilde{\rho}_{L(R)}}{\rho_{L(R)}}\right)+s_{xxL(R)}
+	\end{equation}
+	Then the pressure can be solved as 
+\begin{equation}
+  \tilde{p}_{L(R)}=
+  \frac{2t(c_1f(\tilde{\rho}_{L(R)}/\rho_0)+e_L)-(\sigma_{L(R)}+\tilde{s}_{xxL(R)})}{2tc_0-1},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$.
+
+At last the velocity is
+\begin{equation}
+ \left\{ \begin{array}{ll}
+   \tilde{u}_{L}= u_L -\sqrt{\frac{\sigma_L-\tilde{\sigma}_{L}}{t}},\\ 
+	   \tilde{u}_{R} =   u_R +\sqrt{\frac{\sigma_R-\tilde{\sigma}_{R}}{t}},  
+   \end{array}
+ \right.
+ \end{equation}
+ where 
+ \begin{equation}
+   \tilde{\sigma}_{L(R)} = -\tilde{p}_{L(R)} + \tilde{s}_{L(R)}.
+ \end{equation}
+
+ \subsubsection{State in $\mathbf{Q}_{L(R)}^*$}
+
+ For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$. For  expression conveience, we let    
+ \begin{equation}
+   (\tilde{\rho}_{L(R)},\tilde{u}_{L(R)},\tilde{p}_{L(R)},\tilde{s}_{xx}) =(\rho_{L(R)}, u_{L(R)},p_{L(R)},s_{xxL(R)}),
+\end{equation}
+in cases (a,b,d,e). Then we can solve the states in region $\mathbf{Q}_{L(R)}^*$ from region  $\tilde{\mathbf{Q}}_{L(R)}$ with a given $\rho^*_{L(R)}$.
+
+\emph{\textbf{Rarefaction wave cases (a,b,c)}} For rarefaction wave, 
+we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region.
+
+First we give the function of $s_{xx}$,
+\begin{equation}
+  s_{xx}(\rho) = \left\{\begin{aligned}
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+s_{xxL(R)}, \quad & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (a)},\\
+	  & \frac{2}{3}Y_0,  \quad & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (b,c)}.
+  \end{aligned} \right.
+  \end{equation}
+Then we give the pressure,
+\begin{equation}
+  p(\rho)=\tilde{p}_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx, \quad   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*
+\end{equation}
+where 
+\begin{equation}
+  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+\end{equation}
+And sonic speed,
+\begin{equation}
+  c(\rho) = \left\{ \begin{aligned}
+	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case (a)},\\
+	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case (b,c)}.
+	\end{aligned}\right.
+\end{equation}
+Then we can get  the  function of  velocity
+\begin{equation}
+  u(\rho) =\left\{ \begin{aligned} 
+	  &\tilde{u}_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad  & \tilde{\rho}_L \ge \rho \ge \rho_L^*,   \\
+	  &\tilde{u}_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad  & \tilde{\rho}_R \ge \rho \ge \rho_R^*, \\
+	\end{aligned}
+  \right.
+\end{equation}
+By now, we can get the state in star regions as
+\begin{equation}
+  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
+\end{equation}
+
+\emph{\textbf{Shock wave cases (d,e,f)}} 
+For shock waves, the  deviatoric stress is given as 
+\begin{equation}
+  s_{xxL(R)}^* = \left\{\begin{aligned}
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
+	\quad  &\text{case (d)},\\
+	& -\frac{2}{3}Y_0,   \quad
+	&\text{cases (e, f)}.
+  \end{aligned} \right.
+  \end{equation}
+And the pressure is given as
+\begin{equation}
+  p^*_{L(R)}= 
+  \frac{2t(c_1f(\rho^*_{L(R)}/\rho_0)+\tilde{e}_{L(R)})-(\tilde{\sigma}_{L(R)}+{s}_{xxL(R)}^*)}{2tc_0-1},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$. 
+And the velocity is given as
+\begin{equation}
+  u_{L(R)}^* = \left\{ \begin{array}{l}
+	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma_{L(R)}^*}{t}},\\ 
+	  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma_{L(R)}^*}{t}}.\\
+  \end{array}
+\right.
+\end{equation}
+
+%\subsubsection{Rarefaction  wave cases (a,b)}
+%For Rarefaction wave, we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region. 
+%
+%First we give the function of $s_{xx}$,
+%\begin{equation}
+%  s_{xx}(\rho) = \left\{\begin{aligned}
+%	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}, \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (a)},\\
+%	  & \frac{2}{3}Y_0,  \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (b)}.
+%  \end{aligned} \right.
+%  \end{equation}
+%Then we give the pressure,
+%\begin{equation}
+%  p(\rho)=p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad  \text{case (a,b)}.
+%\end{equation}
+%where 
+%\begin{equation}
+%  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+%\end{equation}
+%
+%and sonic speed,
+%\begin{equation}
+%  c(\rho) = \left\{ \begin{aligned}
+%	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case (a)},\\
+%	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case (b)}.
+%	\end{aligned}\right.
+%\end{equation}
+%Then we can get  the  function of  velocity
+%\begin{equation}
+%  u(\rho) =\left\{ \begin{aligned} 
+%	  &u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_L \ge \rho \ge \rho_L^*,   \quad &\text{case (a,b)} , \\
+%	  &u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_R \ge \rho \ge \rho_R^*, \quad &\text{case (a,b)}, \\
+%	\end{aligned}
+%  \right.
+%\end{equation}
+%
+%
+%\subsubsection{Shock wave cases (d,e)}
+%For shock waves, the function of deviatoric is given as 
+%\begin{equation}
+%  s_{xx}(\rho) = \left\{\begin{aligned}
+%	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad   &\rho =\rho_{L(R)},\rho_{L(R)}^*,
+%	\quad  &\text{case (d)},\\
+%	& -\frac{2}{3}Y_0,   \quad & \rho =\rho_{L(R)},\rho_{L(R)}^*, \quad
+% &\text{case (e)}.
+%  \end{aligned} \right.
+%  \end{equation}
+%And the pressure is given as
+%\begin{equation}
+%  p(\rho)= 
+%  \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2tc_0-1}, \quad  \rho=\rho_{L(R)},\rho_{L(R)}^*, \quad 
+%  \text{ case (d,e)},
+%\end{equation}
+%where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\rho_{L(R)}}$. 
+%The velocity is given as
+%\begin{equation}
+%  u(\rho) = \left\{ \begin{aligned}
+%	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t}} \quad &\rho =\rho_L, \rho_L^*\\ 
+%	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t}} \quad & \rho =\rho_R, \rho_R^*\\
+%  \end{aligned}
+%\right. \quad \text{case (d,e)}
+%\end{equation}
+%
+%\subsection{States for two wave cases (c,f)}\label{sec:two}
+%
+%For cases (c,f), the meterial periods a yielding process from elastic to plastic.
+There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
+In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
+%\begin{equation}
+% \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
+%	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
+%	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
+%	\end{aligned}
+%  \right.
+%\end{equation}
+%By (\ref{eq:rhosxx}),at state $\tilde{\mathbf{Q}}_{L(R)}$ we can solve the density out as 
+%\begin{equation}
+%  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
+%	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
+%	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
+%	\end{aligned}
+%  \right.
+%	\end{equation}
+%\subsubsection{Rarefaction wave case (c)}
+%For rarefaction wave case,
+%we give the function of $s_{xx}$ at first,
+%\begin{equation}
+%  s_{xx}(\rho) = \left\{\begin{aligned}
+%	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}  ,\\
+%	& \frac{2}{3}Y_0, & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.\\
+%  \end{aligned} \right. \quad \text{case (c)}.
+%  \end{equation}
+%
+%The pressure is given as 
+%\begin{equation}
+%  p(\rho)= \left\{ \begin{aligned}
+%	  p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,\quad & \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},\\
+%	  \tilde{p}_{L(R)}e^{\frac{\lambda_1}{\tilde{\rho}_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,  \quad & \tilde{\rho}_{L(R)}\ge \rho \ge \rho_{L(R)}^*,
+%  \end{aligned} \right.
+%  \text{case (c)},
+%\end{equation}
+%where 
+%\begin{equation}
+%  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+%\end{equation}
+%
+%And sonic speed,
+%\begin{equation}
+%  c(\rho) = \left\{ \begin{aligned}
+%	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}\\
+%	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  &   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.
+%  \end{aligned}\right. \quad \text{case (c)}.
+%\end{equation}
+%Then we can get  the   function of  velocity
+%\begin{equation}
+%  u(\rho) =\left\{ \begin{aligned} 
+%	&u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge \rho_L^* , \\
+%	&u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge  \rho_R^* , 
+%	\end{aligned}
+%  \right. \quad \text{case (c)}.
+%\end{equation}
+%\subsubsection{Shock wave case (f)}
+%For shock waves the function of deviatoric is given as 
+%\begin{equation}
+%  s_{xx}(\rho) = \left\{\begin{aligned}
+%	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad &  \rho =\rho_{L(R)},\tilde{\rho}_{L(R)},\\
+%	  & -\frac{2}{3}Y_0, \quad  & \rho = \rho_{L(R)}^*,
+%  \end{aligned} \right. \quad  \text{case (f)}.
+%  \end{equation}
+%
+%And the pressure is given as
+%\begin{equation}
+%  p(\rho)= \left\{\begin{aligned} 
+%	  & \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2t_1c_0-1}, \quad  &  \rho=\rho_{L(R)},\tilde{\rho}_{L(R)},\\ 
+%	  & \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_L)-(\tilde{\sigma}_{L(R)}+s_{xx}(\rho))}{2t_2c_0-1}, \quad  &  \rho=\rho_{L(R)}^*,\\ 
+%  \end{aligned}\right.
+%  \text{ case (f)},
+%\end{equation}
+%where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t_1=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$, $ t_2=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$.
+%
+%The velocity is given as
+%\begin{equation}
+%  u(\rho) = \left\{ \begin{array}{ll}
+%	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_L,\tilde{\rho}_L,\\ 
+%	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_L^*,\\ 
+%	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_R, \tilde{\rho}_R, \\ 
+%	\tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_R^*, \end{array}
+%  \right. \quad \text{case (f)}.
+%\end{equation}
+%
+%
+\section{Half Riemann problem and its solver}
 Some times we need to analyse a half Riemann problem with a given velocity or Cauchy stress in one side.
@@
 
-The process of solving a half Riemann problem is in three step:
-
-First we  evaluate the density in the star region $\mathbf{Q}^*$ with a  elastic shock assumption.
-Then using the relation of $\sigma(\rho^*) = \sigma^*$.
-We can solve the evaluated density $\hat{\rho}$ out.
-A  Newton iteration process will be used.
-
-Second, we can determine the real structure  case by Table \ref{tab:cases}.
-
-At last, as we know the type of the structures, we can use the  iteration process again to solve the real density in region $\mathbf{Q}^*$ out.
-With the density, the pressure and the devaitoric stress are also can be solved.
-
+The process of solving a half Riemann problem is also in five steps just like the full Riemann problem:
+
+\begin{enumerate}
+\item First we  evaluate the density in the star region $\mathbf{Q}^*$ with a  elastic shock assumption. 
+\item By the evaluated density $\rho^*$, we can determine the structures case.
+\item Solving the functions of $\sigma(\rho)$ or $u(\rho)$ according to the wave case.
+  \item 
+	Then using the function of $f_\sigma(\rho^*) = \sigma(\rho^*) - \sigma^*$ (or  $f_u(\rho^*)=u(\rho^*) - u^*$) to take a  convergent decision, if not,  using   the  Newton iteration process to get a new $\rho^*$ and then take the steps 2-5 again.
+  \end{enumerate}
 \subsection{Evaluate of the density $\hat{\rho}$ in region $\mathbf{Q}^*$ }
@@
   \caption{Pre-evaluation of the half Riemann problem  with a elastic shock assumeption.}
-  \label{fig:half}
+  \label{fig:half:shock}
 \end{figure}
-Then use the shock relation in Section \ref{sec:shock}, and  by the Newton   iteration process we can solve the density $\hat{\rho}$ out.
+Then use the shock relation in Section \ref{sec:shock}, we can get the functions of Cauchy stress as 
+\begin{equation}
+  \sigma(\rho) = -p(\rho) +s_{xx}(\rho),
+\end{equation}
+where 
+\begin{equation}
+  p(\rho)= \frac{2t(c_1f(\rho/\rho_0)+e_R)-(\sigma_R+s_{xx}(\rho))}{2tc_0-1},
+\end{equation}
+and $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$, and  $ t=\frac{\rho\rho_R}{\rho-\rho_R}$. And the derivative stress is 
+\begin{equation}
+  s_{xx}(\rho) = 
+	   -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{R}}\right)+s_{xxR},
+ \end{equation}
+ and the velocity is given as
+ \begin{equation}
+   u(\rho) = u_R+ \sqrt{\frac{\sigma_R- \sigma(\rho)}{t}}.
+ \end{equation}
 
@@
 \begin{equation}
-  f(\rho) = \sigma^*(\rho) -\sigma_R,
+  f(\rho) = \sigma(\rho) -\sigma_R,
 \end{equation}
@@
 \begin{equation}
-  f(\rho) = u^*(\rho) -u_R.
+  f(\rho) = u(\rho) -u_R.
 \end{equation}
@@
 \subsection{Resolve the state in region $\mathbf{Q}^*$}
-After evaluate the density $\hat{\rho}$ in region $\mathbf{Q}^*$,   the deviatoric stress also can be evaluated by Eq \ref{eq:rhosxx}, and use Table  \ref{tab:cases}, the real structure case is known.
+With a given density $\rho^*$ in region $\mathbf{Q}^*$, a same case determining process is taken as in Section \ref{sec:deter} to determining the structures case in Table \ref{tab:cases}.
 By  an exact same iteration process in above
@@
 
-In the iteration process the Cauchy stress $\sigma^*(\rho)$ or the velocity $\sigma^*(\rho)$ is given by the relation in Section \ref{sec:one} or Section \ref{sec:two} for different cases.
-\section{Numerical }
-%
-\section*{Conclusions}
-In this paper,  the multi-material HLLC-type  approximate Riemann solver with both the elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic  flows with a hypo-elastic model and the von Mises yielding condition.
+In the iteration process the Cauchy stress $\sigma^*(\rho)$ or the velocity $\sigma^*(\rho)$ is given by the relations in Section \ref{sec:functions} for different cases.
+\section{Numerical  tests }
+In this section, by choosing suitable initial conditions, we will solve the Riemann problem with several different structure cases in the solution.
+For simple  expression, in figures, we use same representations as those in \cite{gao2018complete}.
+``$|$'' means the contact wave, and capital letters ''S'' and ''R'' means the shock and rarefaction wave.
+Superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave.
+Numerical results by the method  in \cite{liumulti} is used to verified the correctness of the exact solution.
+In the following tests, the materials are taken as  aluminium and copper.
+The parameters for the EOS and constitutive model for aluminum and copper  are
+$ (\rho_0, a_0, \Gamma_0, s, \mu)_{\text{Al}} =(8930 \text{kg}/\text{m}^3, 3940 \text{m}/\text{s},2, 1.49, 2.76 ,2.76\times 10^{10} \text{Pa} )$ and   $(\rho_0, a_0, \Gamma_0, s, \mu)_{\text{copper}} =(2785 \text{kg}/\text{m}^3, 5328 \text{m}/\text{s},2, 1.338,4.5\times 10^{10}\text{Pa})$, respectively.
+The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.
+
+\subsection{Test 1}
+In this case, the material is yielding at both sides, so the solution structure has three wave with two plastic wave and one contact.  
+The initial condition is
+\begin{equation}
+ \left\{ \begin{aligned}
+&	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 20\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
+&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
+   \end{aligned}
+ \right.
+\end{equation}
+It can be seen that the exact solution matches the numerical results very well in Fig.\ref{fig:case1}.
+\begin{figure}
+  \centering
+
+  \includegraphics[width= 6cm] {case1rho.pdf}
+  \includegraphics[width= 6cm] {case1u.pdf}
+  \includegraphics[width= 6cm] {case1p.pdf}
+  \includegraphics[width= 6cm] {case1sigma.pdf}
+
+    \caption{Comparison resutls for Test 1 with the structrures of $S^P|S^P$.  }
+  \label{fig:case1}
+\end{figure}
+\subsection{Test 2}
+Next, we consider a case with yielding process at both sides, so the result has five waves. The initial condition 
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 800\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
+&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
+   \end{aligned}
+ \right.
+\end{equation}
+Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, besides the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
+\begin{figure}
+  \centering
+\includegraphics[width= 6cm] {case2rho.pdf}
+  \includegraphics[width= 6cm] {case2u.pdf}
+  \includegraphics[width= 6cm] {case2p.pdf}
+  \includegraphics[width= 6cm] {case2sxx.pdf}
+  \caption{Comparison resutls for Test 1 with the structrures of $S^ES^P|S^PS^E$.  }
+  \label{fig:case2}
+\end{figure}
+
+\subsection{Test 3}
+In this example, we test the elastic rarefaction waves case. In the structrues there  is one  elastic rarefaction wave on each side of the contace wave. The initial condition is given as
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -2.0\text{m}/\text{s}, \quad  p = 1.0\time 10^7\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
+	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 2.0\text{m}/\text{s}, \quad  p = 1.0\times 10^7 \text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
+   \end{aligned}
+ \right.
+\end{equation}
+We can see that the results of the exact solution match the numerical results very well.
+%
+%j\section*{Conclusions}
+\begin{figure}
+  \centering
+
+  \includegraphics[width= 6cm] {case4rho.pdf}
+  \includegraphics[width= 6cm] {case4u.pdf}
+  \includegraphics[width= 6cm] {case4p.pdf}
+  \includegraphics[width= 6cm] {case4sxx.pdf}
+
+    \caption{Comparison resutls for Test 3 with the structrures of $R^E|R^E$.  }
+  \label{fig:case3}
+\end{figure}
+\subsection{Test 4}
+Then we test another example with both elastic and plastic rarefaction  waves on both sides. The initial condition is
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -40\text{m}/\text{s}, \quad  p = 1.0\times 10^7 \text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
+	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 1.0\times 10^7\text{Pa}, \quad  s_{xx}=0.0 \text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+Results are shown in Fig.\ref{fig:case4},  the results of the exact solver matches the numerical results very well.
+
+\begin{figure}
+  \centering
+
+  \includegraphics[width= 6cm] {case3rho.pdf}
+  \includegraphics[width= 6cm] {case3u.pdf}
+  \includegraphics[width= 6cm] {case3p.pdf}
+  \includegraphics[width= 6cm] {case3sxx.pdf}
+
+    \caption{Comparison resutls for Test 4 with the structrures of $R^ER^P|R^PR^E$.  }
+  \label{fig:case4}
+\end{figure}
+\subsection{Test 5}
+All the above four tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
+\begin{equation}
+ \left\{ \begin{aligned}
+&	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 1.0\times 10^8\text{Pa}, \quad  s_{xx}=-2.0\times 10^8 \text{Pa},\\
+&	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -40\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+In the Fig.\ref{fig:case5} shown in both the numerical and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.
+
+\begin{figure}
+  \centering
+
+  \includegraphics[width= 6cm] {case5rho.pdf}
+  \includegraphics[width= 6cm] {case5u.pdf}
+  \includegraphics[width= 6cm] {case5p.pdf}
+  \includegraphics[width= 6cm] {case5sxx.pdf}
+
+    \caption{Comparison resutls for Test 5 with the structrures of $R^P|R^PR^E$.  }
+  \label{fig:case5}
+\end{figure}
+\subsection{Test 6}
+In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves producted into the higher pressure side and shock waves generated into the lower pressure side.
+The initial condition is given as
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10} \text{Pa}, \quad s_{xx}= 0.0 \text{Pa},\\
+	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0 \times 10^2 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side. 
+\begin{figure}
+  \centering
+
+  \includegraphics[width= 6cm] {case9rho.pdf}
+  \includegraphics[width= 6cm] {case9u.pdf}
+  \includegraphics[width= 6cm] {case9p.pdf}
+  \includegraphics[width= 6cm] {case9sxx.pdf}
+
+    \caption{Comparison resutls for Test 6 with the structrures of $R^ER^P|S^PS^E$.  }
+  \label{fig:case9}
+\end{figure}
+\subsection{Test 7}
+Now we will consider two multi-material tests with different materials on different sides.
+In this test, on the left side, a lighter material of aluminum with a velocity impacts to a heavier material of copper.
+The initial condition is given as
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 40\text{m}/\text{s}, \quad  p = 0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa},\\
+	 &	 \text{R: Copper,}\quad  \rho = 8930\text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p =0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+Show in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface.
+The exact Riemann solver can solve the Riemann problem with multi-materials very well comparing to the MHLLCEP approximate solver.
+
+\begin{figure}
+  \centering
+  \includegraphics[width= 6cm] {case6rho.pdf}
+  \includegraphics[width= 6cm] {case6u.pdf}
+  \includegraphics[width= 6cm] {case6p.pdf}
+  \includegraphics[width= 6cm] {case6sigma.pdf}
+
+    \caption{Comparison results for Test 7 with structrures of $R^ER^P|R^PR^E$.  }
+  \label{fig:case7}
+\end{figure}
+
+%In this paper,  the multi-material HLLC-type  approximate Riemann solver with both the elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic  flows with a hypo-elastic model and the von Mises yielding condition.
 During constructing the  MHLLCEP, we do not use the assumption in which the pressure is continuous across the contact wave and so describing and evaluating the plastic waves are  more accurate than that in the  HLLCE.
 Based on the MHLLCEP,
-combining with the third-order ghost-cell reconstruction method and the third-order TVD-Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic flows is built.
+%combining with the third-order ghost-cell reconstruction method and the third-order TVD-Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic flows is built.
 Verified by the numerical experiments, both the plastic waves and elastic waves can be resolved correctly, our scheme appears to be convergent, stable, essentially non-oscillatory and can reach third-order accuracy for smooth problems.
 Especially for multi-material elastic-plastic flows, the results solved by the scheme with HLLCE are with large errors, but our new scheme can eliminate these errors and leads to the reasonable numerical results.
-
-%
+%
+%
+\subsection{Test 8}
+At last, we test another multi-materials case, in this test the initial condtion is given as 
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Copper,}\quad  \rho = 8930 \text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p = 1.0\times 10^{10}\text{Pa}, \quad  s_{xx}=0.0 \text{Pa},\\
+	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 10.0 \text{Pa}, \quad  s_{xx}=0.0 \text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+Shown in Fig.\ref{fig:case8}, there are two rarefaction waves on the left side and two shocks on the right side, there is a discontinuity of pressure on the interface, and the Cauchy stress is continuous, which  meets with the theoretical analysis.
+\begin{figure}
+  \centering
+  \includegraphics[width= 6cm] {case8rho.pdf}
+  \includegraphics[width= 6cm] {case8u.pdf}
+  \includegraphics[width= 6cm] {case8p.pdf}
+  \includegraphics[width= 6cm] {case8sigma.pdf}
+
+    \caption{Comparison results for Test 8 with the structrures of $R^ER^P|S^ES^P$.  }
+  \label{fig:case8}
+\end{figure}
+\subsection{Test 9}
+Then we give two tests of  half Riemann problem, the first is with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
+\begin{equation}
+ \text{Copper,}\quad\rho = 8930\text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p =0.1\text{Pa}, \quad  s_{xx}=0.0\text{Pa}.
+\end{equation}
+In Fig.\ref{fig:case9}, comparason results are given by the exact half Riemann solver and the numerical method.
+We can see that the exact solver  can resolve both the elastic and plastic shock waves well.
+\begin{figure}
+  \centering
+  \includegraphics[width= 6cm] {case10rho.pdf}
+  \includegraphics[width= 6cm] {case10u.pdf}
+  \includegraphics[width= 6cm] {case10p.pdf}
+  \includegraphics[width= 6cm] {case10sxx.pdf}
+
+    \caption{Comparison results for Test 9 with the structrures of $S^ES^P$.  }
+  \label{fig:case9}
+\end{figure}
+\subsection{Test 10}
+The second half Riemann case is with  a given left Cauchy stress $\sigma^* = 0 \text{Pa}$, and the right initial condition is
+\begin{equation}
+  \text{Copper,}\quad\rho = 8930\text{kg}/\text{m}^3, \quad  u = 0.0\text{m}/\text{s}, \quad  p =1.0\times 10^9 \text{Pa}, \quad  s_{xx}=0.0\text{Pa}.
+\end{equation}
+In Fig.\ref{fig:case10}, we give the results computed by the exact Riemann solver and the numerical simulation, shown in it, the exact solver can resolve the elastic and plastic rarefaction waves well.
+\begin{figure}
+  \centering
+  \includegraphics[width= 6cm] {case11rho.pdf}
+  \includegraphics[width= 6cm] {case11u.pdf}
+  \includegraphics[width= 6cm] {case11p.pdf}
+  \includegraphics[width= 6cm] {case11sigma.pdf}
+    \caption{Comparison results for Test 10 with the structrures of $R^ER^P$.  }
+  \label{fig:case10}
+\end{figure}
 \section*{Acknowledgement}
@@
 
-We random choose a particle point inside the expansion region with the state of $(\rho,u, p,s_{xx})$, after a little expansion with the wave speed of $u-c$, the state changes to$(\rho+d\rho, u+du, p+dp, s_{xx}+ds_{xx})$.
+%
+%We random choose a particle point inside the expansion region with the state of $(\rho,u, p,s_{xx})$, after a little expansion with the wave speed of $u-c$, the state changes to$(\rho+d\rho, u+du, p+dp, s_{xx}+ds_{xx})$.
 According to the conservation relations we can get
-\begin{equation}
-  \begin{aligned}
-	& (\rho+ \text{d}\rho)(u+ \text{d}u) = \rho u +(u-c)\text{d}\rho\\
-	& (\rho+\text{d}\rho)(u+\text{d}u)^2 -(\sigma+\text{d}\sigma)=   \rho u^2-\sigma\\
-	&+(u-c)[(\rho+\text{d}\rho)(u+\text{d}u)-\rho u] \\
-	& [(\rho+\text{d}\rho)(E+\text{d}E)-(\sigma+\text{d}\sigma)](u+\text{d}u) = \\
-	&(\rho E-\sigma)u+(u-c)[(\rho+\text{d}\rho)(E+\text{d}E)-\rho E]\\
- \end{aligned}
-\end{equation}
-Ignoring high-order infinite small terms, we can get  
-\begin{align}
-  \label{eq:urho}
-  & \text{d} u =-\frac{c}{\rho}\text{d}\rho,\\
-\label{eq:sigmarho}
-  & \text{d} \sigma = -c^2 d\rho,\\
- \label{eq:Erho}
-  & \text{d} E = -\frac{\sigma+\rho u c}{\rho^2} d\rho.
-\end{align}
-Also we know the deviatoric stress is a function of the  density by Eq.(\ref{eq:rhosxx})   
-\begin{equation}
-  ds_{xx} = \left\{ \begin{aligned}
-	  -\frac{4}{3}\frac{\mu}{\rho}d\rho \quad |s_{xx}| < \frac{2}{3}Y_0,\\
-	  0  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
-	\end{aligned}
-  \right.
-\end{equation}
-And from Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}) we can get
-\begin{equation}\label{eq:c_2rho}
-  c^2 = \left\{ \begin{aligned}
-	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho} \quad |s_{xx}| < \frac{2}{3}Y_0,\\
-	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
-	\end{aligned}
-  \right.
-\end{equation}
-Then the differential of  pressure is  given  as 
-\begin{equation}
-  dp = ds_{xx} -d\sigma = ds_{xx}+c^2 d\rho = \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
-\end{equation}
-it can be written as a differential equation of $p(\rho)$
-\begin{equation}
-  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho), \quad p(\rho_1) = p_1,
-\end{equation}
-where 
-\begin{equation}
-  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
-\end{equation}
-The pressure can be solved out as
-\begin{equation}\label{eq:p_rho}
-  p(\rho) = p_1e^{\frac{\lambda_1}{\rho_1}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_1}^\rho f_2(x) e^{\frac{\lambda_1}{x}}dx.
-\end{equation}
-
-By the above equations of Eq.(\ref{eq:urho}-\ref{eq:Erho},\ref{eq:c_2rho},\ref{eq:p_rho}), we know that the state $(\rho, u, p, s_{xx})$ is only  a function of the density $\rho$ no matter within or  after the rarefaction wave.
-
-\section*{References}
+%\begin{equation}
+%  \begin{aligned}
+%	& (\rho+ \text{d}\rho)(u+ \text{d}u) = \rho u +(u-c)\text{d}\rho\\
+%	& (\rho+\text{d}\rho)(u+\text{d}u)^2 -(\sigma+\text{d}\sigma)=   \rho u^2-\sigma\\
+%	&+(u-c)[(\rho+\text{d}\rho)(u+\text{d}u)-\rho u] \\
+%	& [(\rho+\text{d}\rho)(E+\text{d}E)-(\sigma+\text{d}\sigma)](u+\text{d}u) = \\
+%	&(\rho E-\sigma)u+(u-c)[(\rho+\text{d}\rho)(E+\text{d}E)-\rho E]\\
+% \end{aligned}
+%\end{equation}
+%Ignoring high-order infinite small terms, we can get  
+%\begin{align}
+%  \label{eq:urho}
+%  & \text{d} u =-\frac{c}{\rho}\text{d}\rho,\\
+%\label{eq:sigmarho}
+%  & \text{d} \sigma = -c^2 d\rho,\\
+% \label{eq:Erho}
+%  & \text{d} E = -\frac{\sigma+\rho u c}{\rho^2} d\rho.
+%\end{align}
+%Also we know the deviatoric stress is a function of the  density by Eq.(\ref{eq:rhosxx})   
+%\begin{equation}
+%  ds_{xx} = \left\{ \begin{aligned}
+%	  -\frac{4}{3}\frac{\mu}{\rho}d\rho \quad |s_{xx}| < \frac{2}{3}Y_0,\\
+%	  0  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
+%	\end{aligned}
+%  \right.
+%\end{equation}
+%And from Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}) we can get
+%\begin{equation}\label{eq:c_2rho}
+%  c^2 = \left\{ \begin{aligned}
+%	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho} \quad |s_{xx}| < \frac{2}{3}Y_0,\\
+%	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
+%	\end{aligned}
+%  \right.
+%\end{equation}
+%Then the differential of  pressure is  given  as 
+%\begin{equation}
+%  dp = ds_{xx} -d\sigma = ds_{xx}+c^2 d\rho = \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
+%\end{equation}
+%it can be written as a differential equation of $p(\rho)$
+%\begin{equation}
+%  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho), \quad p(\rho_1) = p_1,
+%\end{equation}
+%where 
+%\begin{equation}
+%  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+%\end{equation}
+%The pressure can be solved out as
+%\begin{equation}\label{eq:p_rho}
+%  p(\rho) = p_1e^{\frac{\lambda_1}{\rho_1}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_1}^\rho f_2(x) e^{\frac{\lambda_1}{x}}dx.
+%\end{equation}
+%
+%By the above equations of Eq.(\ref{eq:urho}-\ref{eq:Erho},\ref{eq:c_2rho},\ref{eq:p_rho}), we know that the state $(\rho, u, p, s_{xx})$ is only  a function of the density $\rho$ no matter within or  after the rarefaction wave.
+%
 

### 2019-05-31 TikzFig/Tikz.tex
third
2
11111

@@
   \node (start1) [startstop] {$\rho_L^*$};
-\node (start2) [startstop,right of=start1, xshift = 1cm] {$\rho_R^*$};
-\node (pro1) [process, below of=start1, yshift=0.2cm, left of=start1, xshift=0.8cm] {$p_L^*,s_{xxL}^*,u_L^*$};
-\node (pro2) [process, right of=pro1, xshift= 3.7cm] {$p_R^*,s_{xxR}^*,u_R^*$};
-\node (dec1) [decision, below of=pro1, yshift= -0.5cm, xshift=3.0cm] {Convergence ?};
+\node (start2) [startstop,right of=start1,xshift=2cm] {$\rho_R^*$};
+\node (decL) [decision, below of=start1,xshift=-0.1cm] {\tiny Left case determined};
+\node (decR) [decision, below of =start2,xshift=0.1cm] {\tiny  Right case determined};
+\node (pro1) [process, below of=decL] {$p_L^*,s_{xxL}^*,u_L^*$};
+\node (pro2) [process, below of = decR]{$p_R^*,s_{xxR}^*,u_R^*$};
+\node (dec1) [decision, below of=pro1,xshift = 2.5cm] {Convergence ?};
 \node (stop) [startstop, below of=dec1] {Output with $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$};
@@
 %连接具体形状
-\draw [arrow](start1) -- (pro1);
-\draw [arrow](start2) -- (pro2);
+\draw [arrow](start1) -- (decL);
+\draw [arrow](decL) -- (pro1);
+\draw [arrow](decR) -- (pro2);
+\draw [arrow](start2) -- (decR);
 \draw [arrow](pro1) -- (dec1);
 \draw [arrow](pro2) -- (dec1);
-\draw [arrow](dec1) -- ($(dec1.east) + (2.5,0)$) node[anchor=north] {NO}  |- node [anchor =south] {A new $\rho_R^*$} (start2);
-\draw [arrow](dec1) -- ($(dec1.west) + (-2.8,0)$) node[anchor=north] {NO} |- node [anchor =south] {A new $\rho_L^*$}(start1);
+\draw [arrow](dec1) -- ($(dec1.east) + (1.8,0)$) node[anchor=north] {NO}  |- node [anchor =south] {A new $\rho_R^*$} (start2);
+\draw [arrow](dec1) -- ($(dec1.west) + (-2.5,0)$) node[anchor=north] {NO} |- node [anchor =south] {A new $\rho_L^*$}(start1);
 %\draw [arrow](dec1) -- ($(dec1.east) + (1.5,0)$) node[anchor=north] {NO} |- (pro2);
@@
 
+  \begin{tikzpicture}
+    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
+    \draw [line width =1pt] (-4,0) -- (0,0);
+    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
+    \draw [double](0,0) -- ([turn]165:3.5)   node [above]{Contact};
+	\draw  (0,0) node[below]{$O$} -- ([turn]135:3.5) node [above]{Right elastic};
+    \draw  (0,0) -- ([turn]-135:3.5) node [above]{Left elastic} ;
+    \node at (-1.3,0.5) {$\mathbf{Q}_L$};
+    \node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
+    \node at (0.7,1.2) {$\mathbf{Q}_R^*$};
+    \node at (1.3,0.5) {$\mathbf{Q}_R$};
+\end{tikzpicture}
+
+% Half Riemann solver
+
+  \begin{tikzpicture}
+	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
+	\draw [line width =1pt] (-4,0) -- (0,0);
+	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
+%	\draw [double](0,0)  -- ([turn]165:3.5)   node [above]{Contact};
+
+	\draw  (0,0) -- ([turn]152:3.5);
+	\draw  (0,0) [line width = 0.8pt] node [below]{ $O$ }  -- ([turn]155:3.5) node [above]{Right wave};
+	\node at (-1.7,1.2) {$\mathbf{Q}*$};
+	\node at (-1.7,2.2) {With a fixed $u^*$ or $\sigma^*$};
+	\node at (1.7,1.2) {$\mathbf{Q}_R$};
+\end{tikzpicture}
+
+  \begin{tikzpicture}
+	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
+	\draw [line width =1pt] (-4,0) -- (0,0);
+	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
+%	\draw [double](0,0)  -- ([turn]165:3.5)   node [above]{Contact};
+
+	\draw  (0,0) [line width = 0.8pt] node [below]{ $O$ }  -- ([turn]155:3.5) node [above]{Elastic shock};
+	\node at (-1.7,1.2) {$\mathbf{Q}*$};
+	\node at (-1.7,2.2) {With a fixed $u^*$ or $\sigma^*$};
+	\node at (1.7,1.2) {$\mathbf{Q}_R$};
+\end{tikzpicture}
+
  \end{document}

### 2019-06-02 Manuscript.tex
revise1

@@
 \usepackage{amsthm}
+\usepackage{enumerate}
 \usepackage{subfigure}
@@
 
-\section{The Riemann problem}
+\section{The Riemann problem}\label{sec:Riemann}
 
@@
 
-\subsubsection{Relations across the contact wave}\label{sec:contact}
+\subsubsection{Relations across the contact wave}\label{sec:contacte}
   For  a  system without molecular diffusion, there is no materials convecting  across the contact wave or interface, so the velocities on two sides of  the discontinuity are always equal. % .
@@
 
-\subsubsection{Relations across the contact wave}\label{sec:contact}
+\subsubsection{Relations across the contact wave}\label{sec:contactp}
 
@@
 For  the Riemann problem in Section \ref{sec:riemann}, there are  $6\times 6$ possible  cases in the Riemann solution with different wave structures.
-Now we consider the  left six cases as shown in Fig.\ref{fig:cases}.
+The left six cases are  shown in Fig.\ref{fig:cases}.
 
@@
 
-There are mainly five  steps in the soluting process. 
-\begin{enumerate}
-  \item In section (\ref{sec:eva}), a pre-evaluation is done with a shock-contact-shock waves assumption to give an initial values of $\rho^*_L$ and $\rho^*_R$.
-
-  \item  With  given $\rho^*_L$ and $\rho^*_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
-
-  \item  We solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ for  different cases in section \ref{sec:one}.
-
-\item At last,   with  the informations in Section \ref{sec:contact},  
-\begin{equation}\label{eq:fus}
-  \begin{aligned}
-	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
-	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
-\end{aligned}
-\end{equation}
- use a Newton iteration method to  get new $\rho^*_L$ and $\rho^*_R$, then do steps 2-5 again until the result convergents. this process is given in Section \ref{sec:iteration}.
-\end{enumerate}
-
-  \subsection{An iteration process of $\rho^*_L$ and $\rho^*_R$}\label{sec:iteration}
-
-For a given  $\rho_L^*$ and a given $\rho_R^*$,
- by relations of 
+%
+%There are mainly five  steps in the soluting process. 
+%\begin{enumerate}
+%  \item In section (\ref{sec:eva}), a pre-evaluation is done with a shock-contact-shock waves assumption to give an initial values of $\rho^*_L$ and $\rho^*_R$.  
+%
+%  \item  With  given $\rho^*_L$ and $\rho^*_R$, we need to  detect the left cases in Fig.\ref{fig:cases} and the corresponding right cases, this is done in section \ref{sec:eva}.
+%
+%  \item  We solve functions $s_{xx}(\rho)$, $p(\rho)$ and $u(\rho)$ for  different cases in section \ref{sec:one}.
+%
+%\item At last,   with  the informations in Section \ref{sec:contact},  
+%\begin{equation}\label{eq:fus}
+%  \begin{aligned}
+%	f_u(\rho^*_L,\rho^*_R) = u_L^* -u_R^* = 0,\\
+%	f_\sigma(\rho^*_L,\rho^*_R) = \sigma_L^* -\sigma_R^* = 0,
+%\end{aligned}
+%\end{equation}
+% use a Newton iteration method to  get new $\rho^*_L$ and $\rho^*_R$, then do steps 2-5 again until the result convergents. this process is given in Section \ref{sec:iteration}.
+%\end{enumerate}
+
+  \subsection{The solving process}\label{sec:iteration}
+  By the relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{R}^*_L$ and  $\mathbf{R}^*_R$ are known, the Riemann problem is solved.
+
+For given  $\rho_L^*$ and  $\rho_R^*$,
+ by the relation across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get  
 \begin{equation}
@@
 	f_u(\rho_L^*,\rho_R^*)_=  u_L^* -u_R^* =0,\\ 
-	f_\sigma(\rho_L^*,\rho_R^*)_=  \sigma_L^* -\sigma_R^* =0,\\ 
-\end{aligned}
-\end{equation}
-and used a Newton iteration method, we can solve the densities $\rho_L^*$ and $\rho_R^*$ out.
+	f_\sigma(\rho_L^*,\rho_R^*)_=  \sigma_L^* -\sigma_R^* =0.\\ 
+\end{aligned}
+\end{equation}
+Then using a  Newton iteration method, we can solve the densities $\rho_L^*$ and $\rho_R^*$ out.  The solving process is shown in Fig.\ref{fig:newton}, and the details are list in the following.
 \begin{figure}
@@
 
+	\textbf{Initial:}
+
+	The initial densities are given as 
+\begin{equation}
+  \rho_{L(0)}^* = \rho_L \quad \rho_{R(0)}^* = \rho_R.
+\end{equation}
+
+\item 
+\end{enumerate}
+
+\textbf{Iteration begin:}
+\begin{enumerate}[Step 1]
+  \item Case select
+	By a given  $\rho _{L,(k)}$ and a  $\rho _{R,(k)}$ in $k$ iteration step, we need to determine the case of the wave structures in the left and right.
+The determine process is done in Section \ref{sec:deter}.
+
+  \item After determining the structure case, we need solve the Cauchy stresses and the velocities in regions $\mathbf{R}^*_L$ and $\mathbf{R}^*_L$, this is given in Section \ref{sec:functions}.
+
+  \item  new 
 The Newton iteration to evaluate $\rho_L^*$ and $\rho_R^*$ is given as
@@
 
-The initial of densities are given as the pre-evalation values,
-\begin{equation}
-  \rho_{L(0)}^* = \hat{\rho}_L \quad \rho_{R(0)}^* = \hat{\rho}_R.
+The initial of densities are given as 
+\begin{equation}
+  \rho_{L(0)}^* = \rho_L \quad \rho_{R(0)}^* = \rho_R.
 \end{equation}

### 2019-06-03 Manuscript.tex
w2

@@
 \usepackage{authblk}
-\usepackage{graphics,graphicx}
+\usepackage{graphics}
 \usepackage{mathrsfs}
@@
 \usepackage{subfigure}
+\usepackage{caption,subcaption}
 \usepackage{booktabs}
@@
 \usepackage{enumerate}
-\usepackage{subfigure}
 \usepackage{listings}
@@
 \usepackage{hyperref}
-
+\usepackage{stackengine}
+\usepackage[demo]{graphicx}
 %\journal{Journal of Computational Physics}
@@
 \begin{equation}
-  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho),
+  p'(\rho) - \lambda \frac{p}{\rho^2} = f_2(\rho),
 \end{equation}
@@
 \begin{equation}
-  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
+  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
 \end{equation}
@@
 \begin{equation}\label{eq:p_rho}
-  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
 \end{equation}
@@
 \begin{equation}
-  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
 \end{equation}
@@
 \begin{equation}\label{eq:p_rhop}
-  p e^{\frac{\lambda_1}{\rho}} - \int f_2(\rho) e^{\frac{\lambda_1}{\rho}}d\rho = \text{constant}.
+  p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
 \end{equation}
@@
 \begin{figure}
+\captionsetup[subfigure]{labelformat=empty}
   \centering
-  \subfigure[Elastic rarefaction wave]{
+  \subfigure[Elastic rarefaction wave $R^E$]{
 	\label{fig:subfigure:a}
@@
 
-%
+%\begin{figure}
+%  \centering
+%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure0.eps}}{\tiny ($\!R^\!E\!$) Elastic rarefaction}%
+%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure1.eps}}{\tiny ($\!R^\!P\!$) Plastic rarefaction}
+%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure2.eps}}{\tiny ($\!R\!^E\!R\!^P\!$) Both elastic and plastic rarefactions}
+%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure3.eps}}{\tiny ($\!S^\!E$) Elastic shock}%
+%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure4.eps}}{\tiny ($\!S^\!P\!$) Plastic shock}
+%\stackunder{\includegraphics[width=3.6cm]{Tikz-figure5.eps}}{\tiny ($\!S\!^E\!S\!^P\!$) Both elastic and plastic shocks}
+%\caption{November to April}
+%\end{figure}
+
 %There are mainly five  steps in the soluting process. 
@@
   \subsection{The solving process}\label{sec:iteration}
-  By the relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{R}^*_L$ and  $\mathbf{R}^*_R$ are known, the Riemann problem is solved.
+  By the relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$ are known, the Riemann problem is solved.
 
@@
 
-	\textbf{Initial:}
+\noindent  \textbf{Initial:}
 
@@
 
-\item 
-\end{enumerate}
-
+\noindent
 \textbf{Iteration begin:}
 \begin{enumerate}[Step 1]
-  \item Case select
-	By a given  $\rho _{L,(k)}$ and a  $\rho _{R,(k)}$ in $k$ iteration step, we need to determine the case of the wave structures in the left and right.
-The determine process is done in Section \ref{sec:deter}.
-
-  \item After determining the structure case, we need solve the Cauchy stresses and the velocities in regions $\mathbf{R}^*_L$ and $\mathbf{R}^*_L$, this is given in Section \ref{sec:functions}.
-
-  \item  new 
-The Newton iteration to evaluate $\rho_L^*$ and $\rho_R^*$ is given as
+  \item Case select:
+	By a given  $\rho _{L,(k)}^*$ and a  $\rho _{R,(k)}^*$ in $k$ iteration step, we need to determine the case of the wave structures in the left and right.
+The determining  process is done in Section \ref{sec:deter}.
+
+  \item Solving $f_u$ and $f_\sigma$:  After determining the structure case, we need  to solve the Cauchy stresses and the velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
+
+  \item  Updating  $\rho_L^*$ and $\rho_R^*$:   By the Newton iteration equation, new densities can be updated, 
 \begin{equation}
@@
 \end{equation}
-
-The initial of densities are given as 
-\begin{equation}
-  \rho_{L(0)}^* = \rho_L \quad \rho_{R(0)}^* = \rho_R.
-\end{equation}
+The derivatives of $f_{u}$ and $f_{\sigma}$ are given by
+\begin{equation}
+  \frac{\partial f_{u,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u,(k+1)}-f_{u,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},\quad
+  \frac{\partial f_{\sigma,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma,(k+1)}-f_{\sigma,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},
+\end{equation}
+At the first step, we use a simple  numerical difference  method
+\begin{equation}
+  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
+  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
+\end{equation}
+where $\Delta \rho$ is a little quatity, we can choose it as
+\begin{equation}
+  \Delta \rho_{L(R)} = \frac{\rho_{L(R),(0)}^*}{100}.
+\end{equation}
+\item Convergence test:
 The  convergence is meassured by 
@@
 \end{equation}
-and the tolerance is taken as $\text{TOL} = 10^{-4}$. It usually takes 3-4 step to get a convergence result.
-
-The derivatives of $f_{u}$ and $f_{\sigma}$ are given by
-\begin{equation}
-  \frac{\partial f_{u,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u,(k+1)}-f_{u,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},\quad
-  \frac{\partial f_{\sigma,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma,(k+1)}-f_{\sigma,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},
-\end{equation}
-At the first step, we use a simple  numerical difference  method
-\begin{equation}
-  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
-  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
-\end{equation}
-where $\Delta \rho$ is a little quatity, we can choose it as
-\begin{equation}
-  \Delta \rho_{L(R)} = \frac{\rho_{L(R),(0)}^*}{100}.
-\end{equation}
-
-A flow chat of this process is shown in Fig.\ref{fig:newton}.
-\subsection{Pre-evaluation of densities}\label{sec:eva}
-At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}.
+and the tolerance is taken as $\text{TOL} = 10^{-4}$.
+
+If $ \text{CHA} \le \text{TOL} $, the iteration ends. 
+It usually takes 2-4 step to get a convergence result.
+\end{enumerate}
+
+\noindent
+\textbf{Iteration end}
+%\subsection{Pre-evaluation of densities}\label{sec:eva}
+%At first, we assume that there are only one elastic shock wave in the left side and another one  elastic shock in the right side as shown in Fig.\ref{fig:HLLC}.
 According to the conservation relations across the shocks, we have
-\begin{equation}
-  \left\{
-  \begin{aligned}
-	&\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
-	&\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
-  \end{aligned}
-\right.
-\end{equation}
-and
-\begin{equation}
-  \left\{
-  \begin{aligned}
-	&\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
-	&\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
-  \end{aligned}
-\right.
-\end{equation}
-\begin{figure}
-  \centering
-  \includegraphics[width=8cm]{Tikz-figure7.eps}
-  \caption{Pre-evaluation with a three-waves structure.}
-  \label{fig:HLLC}
-\end{figure}
-
-Using the relation across the interface,
-\begin{equation}
-  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
-\end{equation}
-the speed of contact wave can be evaluated as 
-\begin{equation}
-\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
-\end{equation}
-the density is solved as 
-\begin{equation}
-\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
-\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
-\end{equation}
-Here we define the speeds of left and right going waves as
- \begin{equation}
-      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
-\end{equation}
+%\begin{equation}
+%  \left\{
+%  \begin{aligned}
+%	&\hat{\rho}_L\hat{u}^*_L = \rho_L u_L +s_L(\hat{\rho}_L^*-\rho_L), \\
+%	&\hat{\rho}_L\hat{u}_L^{*2}-\sigma_L^* = \rho_L u_L^2 -\sigma_L +s_L(\hat{\rho}_L^* \hat{u}_L^*-\rho_L u_L), 
+%  \end{aligned}
+%\right.
+%\end{equation}
+%and
+%\begin{equation}
+%  \left\{
+%  \begin{aligned}
+%	&\hat{\rho}_R\hat{u}^*_R = \rho_R u_R +s_R(\hat{\rho}_R^*-\rho_R), \\
+%	&\hat{\rho}_R\hat{u}_R^{*2}-\sigma_R^* = \rho_R u_R^2 -\sigma_R +s_R(\hat{\rho}_R^* \hat{u}_R^*-\rho_R u_R). 
+%  \end{aligned}
+%\right.
+%\end{equation}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=8cm]{Tikz-figure7.eps}
+%  \caption{Pre-evaluation with a three-waves structure.}
+%  \label{fig:HLLC}
+%\end{figure}
+%
+%
+%Using the relation across the interface,
+%\begin{equation}
+%  \hat{u}_L^* = \hat{u}_R^* =\hat{s}^*,\quad \hat{\sigma}_L^* = \hat{\sigma}_R^*.
+%\end{equation}
+%the speed of contact wave can be evaluated as 
+%\begin{equation}
+%\hat{s}^* = \frac{\sigma_L-\sigma_R+\rho_L u_L(s_L-u_L)-\rho_R u_R(s_R-u_R)}{\rho_L(s_L-u_L)-\rho_R(s_R-u_R)},
+%\end{equation}
+%the density is solved as 
+%\begin{equation}
+%\hat{\rho}_L^* = \frac{\rho_L(u_L-s_L)}{\hat{s}^*-s_L}, \quad
+%\hat{\rho}_R^* = \frac{\rho_R(u_R-s_R)}{\hat{s}^*-s_R}.
+%\end{equation}
+%Here we define the speeds of left and right going waves as
+% \begin{equation}
+%      s_L = \text{min} (u_L-c_L, u_R-c_R, 0),  \quad s_R = \text{max}(u_L+c_L, u_R+c_R, 0).
+%\end{equation}
 \subsection{Determining the case of structures} \label{sec:deter}
@@
 
-\subsection{Functions of the pressure, derivative stress and velocity}\label{sec:functions}
-\subsubsection{State in $\tilde{\mathbf{Q}}_{L(R)}$ in cases (c,f)}
+\subsection{States in  regions $\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$}
+ For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$. For  expression conveience, we let    
+ \begin{equation}
+   (\tilde{\rho}_{L(R)},\tilde{u}_{L(R)},\tilde{p}_{L(R)},\tilde{s}_{xx}) =(\rho_{L(R)}, u_{L(R)},p_{L(R)},s_{xxL(R)}),
+\end{equation}
 
 For cases (c,f), the meterial periods a yielding process from elastic to plastic.
-There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
+There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exist.
 In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
@@
 \end{equation}
-By (\ref{eq:rhosxx}),at state $\tilde{\mathbf{Q}}_{L(R)}$ we can solve the density out as 
+By  the relation in (\ref{eq:rhosxx}),  we can solve the density out as 
 \begin{equation}
@@
   p(\rho)=
-	  p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
+	  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx,\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
 \end{equation}
@@
 
- \subsubsection{State in $\mathbf{Q}_{L(R)}^*$}
-
- For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$. For  expression conveience, we let    
- \begin{equation}
-   (\tilde{\rho}_{L(R)},\tilde{u}_{L(R)},\tilde{p}_{L(R)},\tilde{s}_{xx}) =(\rho_{L(R)}, u_{L(R)},p_{L(R)},s_{xxL(R)}),
-\end{equation}
-in cases (a,b,d,e). Then we can solve the states in region $\mathbf{Q}_{L(R)}^*$ from region  $\tilde{\mathbf{Q}}_{L(R)}$ with a given $\rho^*_{L(R)}$.
-
-\emph{\textbf{Rarefaction wave cases (a,b,c)}} For rarefaction wave, 
+ \subsection{States in regions $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$}\label{sec:functions}
+
+\emph{\textbf{Rarefaction wave}} For rarefaction wave, 
 we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region.
@@
 \begin{equation}
-  p(\rho)=\tilde{p}_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx, \quad   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*
+  p(\rho)=\tilde{p}_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx, \quad   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*
 \end{equation}
@@
 
-\emph{\textbf{Shock wave cases (d,e,f)}} 
+\emph{\textbf{Shock wave}} 
 For shock waves, the  deviatoric stress is given as 
 \begin{equation}
-  s_{xxL(R)}^* = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
+s_{xx}(\rho) = \left\{\begin{aligned}
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
 	\quad  &\text{case (d)},\\
@@
 \begin{equation}
-  p^*_{L(R)}= 
-  \frac{2t(c_1f(\rho^*_{L(R)}/\rho_0)+\tilde{e}_{L(R)})-(\tilde{\sigma}_{L(R)}+{s}_{xxL(R)}^*)}{2tc_0-1},
-\end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$. 
+  p(\rho)= 
+  \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_{L(R)})-(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho))}{2tc_0-1},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\tilde{\rho}_{L(R)} \rho}{\rho-\tilde{\rho}_{L(R)}}$. 
 And the velocity is given as
 \begin{equation}
-  u_{L(R)}^* = \left\{ \begin{array}{l}
-	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma_{L(R)}^*}{t}},\\ 
-	  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma_{L(R)}^*}{t}}.\\
+  u(\rho)= \left\{ \begin{array}{l}
+	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t}},\\ 
+	  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t}},\\
   \end{array}
 \right.
+\end{equation}
+where $\sigma(\rho) = -p(\rho)+s_{xx}(\rho)$. And the state in  the star region is given as
+\begin{equation}
+  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
 \end{equation}
@@
 \section{Half Riemann problem and its solver}
-Some times we need to analyse a half Riemann problem with a given velocity or Cauchy stress in one side.
-Shown in Fig.\ref{fig:half} , in these cases, we only need to solve the states in another side.
+Some time we need to analyse a half Riemann problem with a given velocity or Cauchy stress.
+Shown in Fig.\ref{fig:half} , in these cases, we only need to solve the states in one side.
 There are six possible cases just like them in Section \ref{sec:riemann}.
@@
 
-The process of solving a half Riemann problem is also in five steps just like the full Riemann problem:
-
-\begin{enumerate}
-\item First we  evaluate the density in the star region $\mathbf{Q}^*$ with a  elastic shock assumption. 
-\item By the evaluated density $\rho^*$, we can determine the structures case.
-\item Solving the functions of $\sigma(\rho)$ or $u(\rho)$ according to the wave case.
-  \item 
-	Then using the function of $f_\sigma(\rho^*) = \sigma(\rho^*) - \sigma^*$ (or  $f_u(\rho^*)=u(\rho^*) - u^*$) to take a  convergent decision, if not,  using   the  Newton iteration process to get a new $\rho^*$ and then take the steps 2-5 again.
+As we know the velocity $u^*$ or the Cauchy stress $\sigma ^*$, there is only one function need to be solved as  
+\begin{equation}
+  f(\rho^*) =u(\rho^*) - u^* = 0,
+\end{equation}
+or
+\begin{equation}
+  f(\rho^*) =\sigma(\rho^*) - \sigma^* = 0.
+\end{equation}
+
+\noindent  \textbf{Initial:}
+
+	The initial densitie is  given as 
+\begin{equation}
+\rho_{(0)}^* = \rho_R, 
+\end{equation}
+\textbf{Iteration begin:}
+\begin{enumerate}[Step 1]
+  \item Case select:
+	By a given  $\rho _{(k)}^*$ in $k$ iteration step, we need to determine the case of the wave structures in the left side. The determining  process is  also done in Section \ref{sec:deter}.
+
+  \item Solving $f$:  After determining the structure case, we need to solve the velocity ( or  the Cauchy stress )in region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
+
+  \item  Updating   $\rho^*$:   By the Newton iteration equation, a new density can be updated as
+
+\begin{equation}
+ \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
+\end{equation}
+The derivatives of $f$ is  given by
+\begin{equation}
+  \frac{\partial f_{(k+1)}}{\partial \rho^*} = \frac{f_{(k+1)}-f_{(k)}}{\rho_{(k+1)}^* - \rho^*_{(k)}},
+\end{equation}
+At the first step, we use a simple  numerical difference  method
+\begin{equation}
+  \frac{\partial f_{(1)}}{\partial \rho^*} = \frac{f(\rho^*+\Delta \rho)-f(\rho^*)}{\Delta \rho},
+\end{equation}
+where $\Delta \rho$ is a little quatity, we can choose it as
+\begin{equation}
+  \Delta \rho = \frac{\rho_{(0)}^*}{100}.
+\end{equation}
+\item Convergence test:
+The  convergence is meassured by 
+\begin{equation}
+\text{CHA} = \text{max} \left[  
+\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right].
+\end{equation}
+and the tolerance is taken as $\text{TOL} = 10^{-4}$.
+
+If $ \text{CHA} \le \text{TOL} $, the iteration ends. 
+It usually takes 2-4 step to get a convergence result.
 \end{enumerate}
-\subsection{Evaluate of the density $\hat{\rho}$ in region $\mathbf{Q}^*$ }
-As shown in Fig.\ref{fig:half:shock}, we  assume there is only one elastic shock wave between region $\mathbf{Q}$ and region $\mathbf{Q}^*$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width= 10cm] {Tikz-figure9.eps}
-  \caption{Pre-evaluation of the half Riemann problem  with a elastic shock assumeption.}
-  \label{fig:half:shock}
-\end{figure}
-Then use the shock relation in Section \ref{sec:shock}, we can get the functions of Cauchy stress as 
-\begin{equation}
-  \sigma(\rho) = -p(\rho) +s_{xx}(\rho),
-\end{equation}
-where 
-\begin{equation}
-  p(\rho)= \frac{2t(c_1f(\rho/\rho_0)+e_R)-(\sigma_R+s_{xx}(\rho))}{2tc_0-1},
-\end{equation}
-and $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$, and  $ t=\frac{\rho\rho_R}{\rho-\rho_R}$. And the derivative stress is 
-\begin{equation}
-  s_{xx}(\rho) = 
-	   -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{R}}\right)+s_{xxR},
- \end{equation}
- and the velocity is given as
- \begin{equation}
-   u(\rho) = u_R+ \sqrt{\frac{\sigma_R- \sigma(\rho)}{t}}.
- \end{equation}
-
-If the Cauchy stress  in region $\mathbf{Q}^*$ is given, let
-\begin{equation}
-  f(\rho) = \sigma(\rho) -\sigma_R,
-\end{equation}
-if the velocity is given, let
-\begin{equation}
-  f(\rho) = u(\rho) -u_R.
-\end{equation}
-
-The  Newton iteration is given as
-\begin{equation}
-  \hat{\rho}_{(k+1)} = \hat{\rho}_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
-\end{equation}
-and the initial is given as 
-\begin{equation}
-  \hat{\rho}_{(0)} = \rho_R.
-\end{equation}
-The  congergence is meassured by
-\begin{equation}
-  \text{CHA} = \text{max} \left[\frac{|\hat{\rho}_{(k+1)}-\hat{\rho}_{(k)}|}{\frac{1}{2}|\hat{\rho}_{(k+1)}+\hat{\rho}_{(k)|}},|f_{(k+1)}|\right].
-\end{equation}
-\subsection{Resolve the state in region $\mathbf{Q}^*$}
-With a given density $\rho^*$ in region $\mathbf{Q}^*$, a same case determining process is taken as in Section \ref{sec:deter} to determining the structures case in Table \ref{tab:cases}.
-By  an exact same iteration process in above
-\begin{equation}
- \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
-\end{equation}
-with the initial condition of 
-\begin{equation}
-  \rho^*_{(0)} = \hat{\rho},
-\end{equation}
-we can solve the $\rho^*$ out.
-
-In the iteration process the Cauchy stress $\sigma^*(\rho)$ or the velocity $\sigma^*(\rho)$ is given by the relations in Section \ref{sec:functions} for different cases.
+\textbf{Iteration end.}
 \section{Numerical  tests }

### 2019-06-04 Manuscript_revise.tex
abstract

--- 2019-06-03 Manuscript.tex
@@
-\documentclass[review]{elsarticle}
-\usepackage{amssymb}
-%\usepackage{graphicx}
-\usepackage{amsmath}
+\documentclass{article}
+%\documentclass[review]{elsarticle}
+\usepackage{amssymb,lineno}
+\modulolinenumbers[5]
 \usepackage{color}
-%\usepackage{tikz}
-%\usetikzlibrary{arrows,shapes}
-%\usetikzlibrary{shapes.geometric}
-%\usetikzlibrary{arrows.meta}
 \usepackage{authblk}
@@
 \usepackage[demo]{graphicx} 
-%\journal{Journal of Computational Physics}
+\usepackage[margin=2.5cm]{geometry}
+\intextsep=8pt plus 3pt minus 1pt
+\definecolor{ColorMark}{rgb}{1,1,1}
+\numberwithin{equation}{section}
+\numberwithin{table}{section}
 \bibliographystyle{elsarticle-num}
-
 \begin{document}
 
-\title{An exact Riemann solver for  multi-material   elastic-plastic flows with Mie-Gr\"uneisen equation of state}
+\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state}
 \author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
+%\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
 %\cortext[mycorrespondingauthor]{
@@
 
-\address{$^1$  Institute of Applied Physics and Computational Mathematics, Beijing 100094, China }
+%\address{$^1$  Institute of Applied Physics and Computational Mathematics, Beijing 100094, China }
 
 \begin{abstract} 
+  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model \cite{wilkins1963calculation} and  the von Mises' yielding condition is studied in this paper.
+Through a detailed analysis of the Jacobian and eigenvectors, and the exact relations across different waves, an exact solution is constructed with three-to-five waves and thirty-six possible structure cases.
+More over, some useful results are also obtained in the analysis, for example, the significant jump of the sonic speed
+
   A multi-material HLLC-type  approximate Riemann solver with both elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic flows with the  hypo-elastic model and the von Mises yielding condition.
@@
 
-\begin{keyword}
-  HLLC Riemann solver, high-order cell-centered Lagrangian scheme,  WENO scheme,  hypo-elastic model, elastic-plastic flows
-\end{keyword}
+%\begin{keyword}
+%  HLLC Riemann solver, high-order cell-centered Lagrangian scheme,  WENO scheme,  hypo-elastic model, elastic-plastic flows
+%\end{keyword}
 
@@
 
-In this paper, an exact  Riemann solver is built with the consideration of both elastic and plastic waves, for one-dimensional  multi-material elastic-plastic materials with the Mie-Gr\"uneisen EOS, isotropic elastic-plastic model \cite{wilkins1963calculation} and  the von Mises' yielding condition.
+In this paper, an exact Riemann solver is built for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model \cite{wilkins1963calculation} and  the von Mises' yielding condition.
 
 The  elastic-plastic flow  is  used to describe the deformation process of solid materials under strong dynamics loading, such as explosive or high-speed impact.
-The simulation of elastic-plastic flows has important application backgrounds, especially in the Implosion Dynamics weapon and Innertial Confine Fusion (ICF).
+The simulation of elastic-plastic flows has important application backgrounds, especially in the Implosion Dynamics weapon and Inertial Confine Fusion (ICF).
 The first try of simulating the elastic-plastic flows was given by  Wilkins \cite{wilkins1963calculation} in 1960s.
 
-Although the control equations of elastic-plastic flow is similar to the equations in computational fluid dynamics (CFD).
+In the development history of hydrodynamic numerical methods, the exact Riemann solver has played a very important role {\color{red}as} it not only can give a guide and reference to the construction of approximate Riemann solvers, but also can be used to determine {\color{red}the convergence and stability of numerical schemes}.
+However, building the exact Riemann solver for 1D elastic-plastic flows is not that easy.
+Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.
+The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may leads to more non-linear waves in the structure of Riemann solvers.
+Moreover, in a general way, the equation of state(EOS) for solid materials is more complex than that for pure fluids, which directly increases the difficulty in solving the Riemann problem.
+
+For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{red}have been developed recently.
+However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver, but the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.
+All these makes easily deduce the relation across a non-linear wave.
+Although there are many  cases considered in their works \cite{gao20171d,gao2018complete}, for every case, they can easily obtain the exact solution.
+But for many engineering problems, the EOS is more complex, and the energy equation has to be included during simulating.
+For these engineering solid problems with a complex constitutive and a complex EOS, such as the Mie-Gr\"uneisen EOS, up to now, there is no  exact Riemann solution.
+
+%Although the control equations of elastic-plastic flow is similar to the equations in computational fluid dynamics (CFD).
 But there are mainly three difficulties  of constructing  Riemann solvers in elastic-plastic flows.
@@
 
-Recently, a lot of works have been done in constructing  approximate Riemann solvers for elastic-plastic flows with the considering of structures in the Riemann problem.
+%Recently, a lot of works have been done in constructing  approximate Riemann solvers for elastic-plastic flows with the considering of structures in the Riemann problem.
 For example, Gavrilyuk et al.
@@
 In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves.
-Then in \cite{liumulti}, Liu et.al remove the unreasonable assumution in HLLCE  which may cause big errors in solving  multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.
-
-As we know, in hydrodynamic  numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the developing of approximate solvers.
+Then in \cite{liumulti}, Liu et.al remove the unreasonable assumption in HLLCE which may cause numerical errors in simulating multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.
+
+%As everyone knows, in hydrodynamic numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the developing of approximate solvers.
 However, in the elastic-plastic flows, for its complexity, there are only a few works have been done in constructing the exact Riemann solver.
-For example,
-Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.
+
+ %designed an exact Riemann solution of isotropic hyper-elastic material theoretically; Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
+% Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states.
+As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works.
+%However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state.
+This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
+But for the elastic-plastic flows with hypo-elastic constitutive model, von Mises yielding condition and the complex equation of system(EOS), there is no exact Riemann solver.
+Of course, for some
+
+%For example, Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.
 Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
@@
 
-In this paper, we want to construct an exact Riemann solver for the elastic-plastic equations system with the  isotropic elastic-plastic model and the  von Mises' yielding condition.
-In this system, the Mie-Gr\"uneisen EOS is used for both the elastic state and plastic state of the material, which is an adequate approximation to a wide variety of materials of interest, includes some gaseous or solid explosives and solid metals under high pressure \ref{ shyue2001fluid}.
+In this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition.
+As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely  in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave.
+Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves.
+These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves.
+Moreover, elastic wave runs always faster than the followed plastic wave.
+So there are thirty-six possible cases of the wave structures in the Riemann solver.
+%For a given case, we will obtain theoretical relations of all the states as functions of density.
+At last,  through an iteration process of densities at both sides of the contact wave, the  exact solution will be obtained.
+Also, the half Riemann problem and its exact solution are considered in this paper.
+
+%the Mie-Gr\"uneisen EOS is used for both the elastic state and plastic state of the material, which is an adequate approximation to a wide variety of materials of interest, includes some gaseous or solid explosives and solid metals under high pressure \ref{ shyue2001fluid}.
 According to both the theoretical analysation and numerical tests \cite{xiao1996numerical}, in this system, there may be three to five waves, including one contact wave and elastic wave (shock or rarefaction wave) or plastic wave or both the elastic and plastic waves in each side of the contact wave.
@@
 In section 2, we introduce the governing equations to be studied.
-In section 3, the Riemann problem and the relations for every wave type (contact wave, shock wave and rarefaction wave) is derived.
+In section 3, the Riemann problem and the relations for every wave type (contact wave, shock wave and rarefaction wave) are  derived.
 Then,  the exact Riemann solver  is given in section 4.
@@
 
-The governing equations system is given as 
- \begin{equation}\label{eq:1d}
-   \left\{ \begin{aligned}
-       & \partial _t \rho +\partial_x(\rho u)=0,\\
-       & \partial _t (\rho u)+\partial_x(\rho u^2 + p -s_{xx})=0,\\
-       &\partial _t (\rho E)+\partial_x\left[(\rho E + p -s_{xx})u\right]=0,\\
-       &\partial _t s_{xx}+u\partial_xs_{xx}-\frac{4}{3}\partial_x u=0,\\
-& |s_{xx}|\leq \frac{2}{3}Y_{0}, \\
-        \end{aligned}
-  \right.
-\end{equation}
-It contains the following parts.
-
-\subsection{Conservation terms}
-For  the  continuous one-dimensional solid, the conservation terms  in differential form can be  given as
+%%The governing equations system is given as
+%% \begin{equation}\label{eq:1d}
+%   \left\{ \begin{aligned}
+%       & \partial _t \rho +\partial_x(\rho u)=0,\\
+%       & \partial _t (\rho u)+\partial_x(\rho u^2 + p -s_{xx})=0,\\
+%       &\partial _t (\rho E)+\partial_x\left[(\rho E + p -s_{xx})u\right]=0,\\
+%       &\partial _t s_{xx}+u\partial_xs_{xx}-\frac{4}{3}\partial_x u=0,\\
+%& |s_{xx}|\leq \frac{2}{3}Y_{0}, \\
+%        \end{aligned}
+%  \right.
+%\end{equation}
+%It contains the following parts.   
+\subsection{Motion equations}
+For  a continuous one-dimensional homogeneous solid, the motion equations  in differential form are
 \begin{equation*}
@@
 $\rho$, $u$, $\sigma$ and $E$ are  the density, velocity in $x-$direction, Cauchy stress and total energy per unit volume, respectively, $E$ has the relation with specific internal energy $e$ as
-\begin{equation}
+\begin{equation} \label{te1}
   E = e+\frac{1}{2}u^2,
@@
 
-According to the yielding of the material, the equations may have different Jacobian matrix and different sonic velocity. We will discuss them separately.
+The above equations are just for the elastic status of the solid material.
+If the material are in the plastic state, the above equations can be simplified 
+and correspondingly the jacobian matrix and sonic velocity are different.
+We will discuss them separately.
 \subsection{Elastic state}
@@
 \begin{equation}
- \partial_t \mathbf{Q} +\mathbf{J}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
+ \partial_t \mathbf{Q} +\mathbf{J}_{e}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
 \end{equation}
@@
 \begin{equation}\label{eq:Jcb}
-  J(Q) = \left[\begin{array}{llll}
+  \mathbf{J}_{e}(Q) = \left[\begin{array}{llll}
       0 & 1 & 0 & 0 \\
@@
 
-The eigenvalues of the coefficient matrix $\mathbf{J}(\mathbf{Q})$ are given as
-\begin{equation}
-  \lambda_1 =\lambda_2 = u, \hspace{0.3cm} \lambda_3 = u-c, \hspace{0.3cm} \lambda_4 = u+c,
-\end{equation}
-where
+The eigenvalues of $\mathbf{J}_{e}(\mathbf{Q})$ are given as
+\begin{equation}
+  \lambda_1 =\lambda_2 = u, \hspace{0.3cm} \lambda_3 = u-c_{e}, \hspace{0.3cm} \lambda_4 = u+c_{e},
+\end{equation}
+where $c_e$ means the sonic speed of the solid in the elastic state, 
 \begin{equation}\label{eq:c_e}
@@
 
-Using $\mathbf{W}_L^*$ and $\mathbf{W}_R^*$ to denote the two data states connected the contact wave, where $\mathbf{W}=\left(\rho,u,p,s_{xx}\right)$.
+Using $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$ to denote the two data states connected the contact wave, where $\mathbf{Q}=\left(\rho,u,p,s_{xx}\right)$.
 
@@
 where $()_{L}^{\ast}$ and $()_{R}^{\ast}$ denote $()$ in the region
-of $\mathbf{W}_{L}^{\ast}$ and $\mathbf{W}_{R}^{\ast}$,
+of $\mathbf{Q}_{L}^{\ast}$ and $\mathbf{Q}_{R}^{\ast}$,
 respectively. Here we do not show the details of the derivation for a simple
@@
 \end{equation}
-which lead to 
+which leads to
 \begin{align}
@@
  \label{eq:Erho}
-  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
+  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho,\\
 \label{eq:sxxrho}
-& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
+& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho.
 \end{align}
-Take the relation of EOS (\ref{eq:mie}) in, we can get the pressure  as
-\begin{equation}
-  dp =  \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
-\end{equation}
-it can be written as a differential equation of $p(\rho)$
-\begin{equation}
+
+Using (\ref{eq:mie}), one can get
+\begin{equation}\label{te2}
+  dE=de+udu.
+\end{equation}
+
+Substituting (\ref{eq:urho}) and (\ref{eq:Erho}) into the above equation yields
+\begin{equation}\label{te2}
+  d e = -\frac{\sigma}{\rho^2} d\rho=\frac{p-s_{xx}}{\rho^2} d\rho.
+\end{equation}
+
+Thanks to (\ref{eq:mie}), one can get
+\begin{equation}\label{dp1}
+  dp =  \frac{\partial p}{\partial \rho}d \rho +  \frac{\partial p}{\partial e}d e= a_0^2 \frac{\partial f}{\partial \eta} d \rho + \rho_0 \Gamma_0 de,
+\end{equation}
+
+Substituting (\ref{te2}) into the above equation yields
+\begin{equation}
+  dp =  \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho.
+\end{equation}
+
+The above equation  can  be rewritten as a differential equation of $p(\rho)$
+\begin{equation} \label{dp2}
   p'(\rho) - \lambda \frac{p}{\rho^2} = f_2(\rho),
@@
 \end{equation}
-The pressure can be solved out as 
+By integrating (\ref{dp2}) across the left rarefaction wave, the pressure can be solved out as
 \begin{equation}\label{eq:p_rho}
@@
 \end{equation}
-Then for a given density $\rho$, we can get  the sonic speed $c_e$  and velocity 
+%Then for a given density $\rho$, we can get  the sonic speed $c_e$  and velocity
+Integrating  (\ref{eq:urho}) across the left rarefaction wave yields
 \begin{equation}
@@
 \emph{\textbf{Right-going rarefaction wave} }
+
 Across the right wave associated with $\lambda_4$-wave, ($\lambda_3=u+c_e$), we have
@@
 \end{equation}
-which lead to 
+which leads to
 \begin{align}
-  \label{eq:urho}
+  \label{eq:urhoR}
   & \text{d} u =\frac{c_e}{\rho}\text{d}\rho,\\
- \label{eq:Erho}
-  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho.\\
-\label{eq:sxxrho}
-& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho,
+ \label{eq:ErhoR}
+  & \text{d} E = -\frac{\sigma+\rho u c_e}{\rho^2} d\rho,\\
+\label{eq:sxxrhoR}
+& \text{d} s_{xx} = -\frac{4}{3}\frac{\mu}{\rho} d\rho.
 \end{align}
-We can get  similar  relations  as the left-going wave as
+
+By using the same method, one can get
 \begin{equation}
@@
 \subsubsection{Relations across  shock waves}\label{sec:shock}
-Now we consider a shock wave with a speed of $s$, suppose the state in front of the shock is known as $(\rho_1,u_1,p_1,s_{xx1})$ and the state after the shock is unknown as $(\rho_2,u_2,p_2,s_{xx2})$.
-
-Then use the conservation relation across the wave, which is also known as the Rankine-Hugoniot relation for a shock
-
-\begin{align}
-  &\rho_2u_2 = \rho_1 u_1 +s(\rho_2 -\rho_1),\\
-  &\rho_2u_2^2-\sigma_{2} = \rho_1u_1^2-\sigma_{1}+s(\rho_2u_2-\rho_1u_1), \\
-  &(\rho_2E_2-\sigma_{2})u_2 = (\rho_1E_1-\sigma_{1})u_1+s(\rho_2E_2-\rho_1E_1),
-\end{align}
-above relations also can be written as
+Now we consider a shock wave moving with the speed of $s$. The data in front of the shock is $(\rho_1,u_1,p_1,s_{xx1})$ and that after the shock is $(\rho_2,u_2,p_2,s_{xx2})$.
+
+%Then use the conservation relation across the wave, which is also known as the Rankine-Hugoniot relation for a shock
+%\begin{align}
+%  &\rho_2u_2 = \rho_1 u_1 +s(\rho_2 -\rho_1),\\
+%  &\rho_2u_2^2-\sigma_{2} = \rho_1u_1^2-\sigma_{1}+s(\rho_2u_2-\rho_1u_1), \\
+%  &(\rho_2E_2-\sigma_{2})u_2 = (\rho_1E_1-\sigma_{1})u_1+s(\rho_2E_2-\rho_1E_1),
+%\end{align}above relations also can be written as
+We transform the equations  to a frame of reference moving with the shock and the Rankine-Hugoniot Conditions give
 \begin{align}
@@
 \label{eq:RH3}
-  &\rho_2E_2(u_2-s) = \rho_1E_1(u_1-s)+\sigma_2 u_2-\sigma_1u_1,
+  &\rho_2E_2(u_2-s) = \rho_1E_1(u_1-s)+\sigma_2 u_2-\sigma_1u_1.
 \end{align}
-substituting (\ref{eq:RH1}) into (\ref{eq444}) yields  
+
+Substituting (\ref{eq:RH1}) into (\ref{eq444}) yields
 \begin{equation}\label{eq:222}
-  \rho_1(u_2-u_1)(u_1-s) = \sigma_2-\sigma_1,
-\end{equation}
-also according to (\ref{eq:RH1}), we have 
+  \rho_1(u_2-u_1)(u_1-s) = \sigma_2-\sigma_1.
+\end{equation}
+
+From (\ref{eq:RH1}), one has
 \begin{equation}
@@
 \end{equation}
-then subtituting it into (\ref{eq:222})
+then subtituting it into (\ref{eq:222}) yields
 \begin{equation}\label{eq:u2u1}
@@
 
-Simimar to (\ref{eq:222}), (\ref{eq:RH3}) can be changed into
+By using the same methods for (\ref{eq:RH3}), (\ref{eq:RH3}) can be written as
 \begin{equation}
@@
 where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
-Put above equation into (\ref{eq:e2e1}), we can solve the pressure $p_2$ out as a function of $\rho_2$. 
+Put the above equation into (\ref{eq:e2e1}), we can solve the pressure $p_2$ out as a function of $\rho_2$.
 \begin{equation}\label{eq:shocke}
-  p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1},
-\end{equation}
-The derivative stress $\sigma_{xx2}$ also is  a function of $\rho_2$ only. So we can solve the Cauchy stress out as
+  p_2= \frac{2t(c_1f(\rho_2/\rho_0)+e_1)-(\sigma_1+s_{xx2})}{2tc_0-1}.
+\end{equation}
+
+Thanks to (\ref{eq:rhosxx}), $s_{xx2}$ can be written as
+\begin{equation}
+ s_{xx2} = s_{xx1}-\frac{4}{3}\mu\text{ln}(\frac{\rho_{2}}{\rho_{1}}).
+\end{equation}
+
+Then, the Cauchy stress can be written as
 \begin{equation}
@@
 
-By the above deductions of the shock wave, we can get that, if the density after the shock is known, all the unknowns can be solved out.
+By the above deductions for the moving shock wave, we can find that, if the density after the shock is known, all the data after the shock can be solved out.
 
 \subsection{Plastic state}
-When the material is yielding, the deviatoric stress is a constant
-\begin{equation}
-  |s_{xx}| = \frac{2}{3}Y_0.
-\end{equation}
-And the Riemann problem turns into 
+
+When the material is yielding,
+\begin{equation}
+  |s_{xx}| = \frac{2}{3}Y_0,
+\end{equation}
+the equations of Riemann problem  will turn into a more simple system with only constitutive terms as
 \begin{equation}\label{eq:1dp}
@@
 \end{equation}
-The eigenvalues of 
+
 The eigenvalues of the coefficient matrix $\mathbf{J}_p(\mathbf{Q})$ are given as
@@
 \end{equation}
-Samilar to that in  section \ref{sec:contact}, we can also get the relations
+Samilar to that in  section \ref{sec:contacte}, we can also get the relations
 \begin{equation} 
@@
   \centering
-  \subfigure[Elastic rarefaction wave $R^E$]{
+  \subfigure[Elastic rarefaction wave]{
 	\label{fig:subfigure:a}
-  \includegraphics[width=3.8cm]{Tikz-figure0.eps}}
+  \includegraphics[width=5cm]{Tikz-figure0.eps}}
   \subfigure[Plastic rarefaction wave]{
 	\label{fig:subfigure:b}
-  \includegraphics[width=3.8cm]{Tikz-figure1.eps}}
+  \includegraphics[width=5cm]{Tikz-figure1.eps}}
   \subfigure[Both elastic and plastic rarefaction waves]{
 	\label{fig:subfigure:c}
-  \includegraphics[width=3.8cm]{Tikz-figure2.eps}}
+  \includegraphics[width=5cm]{Tikz-figure2.eps}}
   \subfigure[ Elastic shock wave]{
 	\label{fig:subfigure:d}
-  \includegraphics[width=3.8cm]{Tikz-figure3.eps}}
+  \includegraphics[width=5cm]{Tikz-figure3.eps}}
   \subfigure[Plastic shock wave]{
 	\label{fig:subfigure:e}
-  \includegraphics[width=3.8cm]{Tikz-figure4.eps}}
+  \includegraphics[width=5cm]{Tikz-figure4.eps}}
   \subfigure[Both elastic and plastic shock waves]{
 	\label{fig:subfigure:f}
-	\includegraphics[width=3.8cm]{Tikz-figure5.eps}}
+	\includegraphics[width=5cm]{Tikz-figure5.eps}}
   \caption{The possible cases of Riemann solution structures in the left side.}
@@
   \subsection{The solving process}\label{sec:iteration}
-  By the relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$ are known, the Riemann problem is solved.
-
-For given  $\rho_L^*$ and  $\rho_R^*$,
- by the relation across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get  
+  By those relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$ are known, the Riemann problem is solved.
+e
+For given values of  $\rho_L^*$ and   $\rho_R^*$,
+ by relations across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get  
 \begin{equation}
@@
   \item Case select:
-	By a given  $\rho _{L,(k)}^*$ and a  $\rho _{R,(k)}^*$ in $k$ iteration step, we need to determine the case of the wave structures in the left and right.
+	By a given  $\rho _{L,(k)}^*$ and a  $\rho _{R,(k)}^*$ in $k$ iteration step, we need to determine cases of  wave structures in the left and right.
 The determining  process is done in Section \ref{sec:deter}.
@@
 If $ \text{CHA} \le \text{TOL} $, the iteration ends. 
-It usually takes 2-4 step to get a convergence result.
+It usually takes 2-4 steps to get a convergence result.
 \end{enumerate}
@@
 
-Using a given density $\rho^*_L$, we can distinguish the shock and rarefaction in the left side.  This is done easily by comparing $\rho^*_L$ with $\rho_L$,
+Using a given density $\rho^*_{L(R)}$ we can distinguish the shock and rarefaction wave.
+This is done easily by comparing $\rho^*_{L(R)}$ with $\rho_{L(R)}$, the subscript $_{L(R)}$ means either both in the left side $_L$ and  right side $_R$.
 \begin{equation}
@@
   \begin{aligned}
-	& \text{Rarefaction wave:} & \rho_L > \rho_L^*,\\
-	& \text{Shock wave:} &  \rho_L < \rho_L^*.\\
+	& \text{Rarefaction wave:} & \rho_{L(R)} > \rho_{L(R)}^*,\\
+	& \text{Shock wave:} &  \rho_{L(R)} < \rho_{L(R)}^*.\\
 \end{aligned}\right.
@@
 \begin{equation}  \label{sxx1}
-  \hat{s}_{xxL}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_L^*}{\rho_L})+s_{xxL},
-\quad
-  \hat{s}_{xxR}=-\frac{4}{3}\mu\text{ln}(\frac{\rho_R^*}{\rho_R})+s_{xxR}.
+\hat{s}_{xxL(R)}=-\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\rho_{L(R)}}\right)+s_{xxL(R)},
 \end{equation}
@@
 \end{equation}
-The states in region $\tilde{\mathbf{Q}}_{L(R)}$ can be solved as 
+States in region $\tilde{\mathbf{Q}}_{L(R)}$ can be solved as 
 \begin{equation}
@@
 \emph{\textbf{Rarefaction wave}} For rarefaction wave, 
-we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region.
+we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know  states inside the expansion region.
 
@@
 Some time we need to analyse a half Riemann problem with a given velocity or Cauchy stress.
-Shown in Fig.\ref{fig:half} , in these cases, we only need to solve the states in one side.
+Shown in Fig.\ref{fig:half} , in these cases, we only need to solve states in one side.
 There are six possible cases just like them in Section \ref{sec:riemann}.
@@
 
+The solving process is list in the following.
+
 \noindent  \textbf{Initial:}
 
-	The initial densitie is  given as 
-\begin{equation}
-\rho_{(0)}^* = \rho_R, 
+	The initial density is  given as 
+\begin{equation}
+\rho_{(0)}^* = \rho_R. 
 \end{equation}
@@
 
-  \item Solving $f$:  After determining the structure case, we need to solve the velocity ( or  the Cauchy stress )in region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
+  \item Solving $f$:  After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
 
@@
 \subsection{Test 1}
-In this case, the material is yielding at both sides, so the solution structure has three wave with two plastic wave and one contact.  
+In this case, the material is yielding at both sides, so the solution structure has three wave with two plastic waves and one contact.  
 The initial condition is
@@
 
-  \includegraphics[width= 6cm] {case1rho.pdf}
-  \includegraphics[width= 6cm] {case1u.pdf}
-  \includegraphics[width= 6cm] {case1p.pdf}
-  \includegraphics[width= 6cm] {case1sigma.pdf}
+  \includegraphics[width= 8cm] {case1rho.pdf}
+  \includegraphics[width= 8cm] {case1u.pdf}
+  \includegraphics[width= 8cm] {case1p.pdf}
+  \includegraphics[width= 8cm] {case1sigma.pdf}
 
@@
 \subsection{Test 2}
-Next, we consider a case with yielding process at both sides, so the result has five waves. The initial condition 
+Next, we consider a case with yielding process at both sides, so the result has five waves. The initial condition is 
 \begin{equation}
@@
   \centering
-\includegraphics[width= 6cm] {case2rho.pdf}
-  \includegraphics[width= 6cm] {case2u.pdf}
-  \includegraphics[width= 6cm] {case2p.pdf}
-  \includegraphics[width= 6cm] {case2sxx.pdf}
+\includegraphics[width= 8cm] {case2rho.pdf}
+  \includegraphics[width= 8cm] {case2u.pdf}
+  \includegraphics[width= 8cm] {case2p.pdf}
+  \includegraphics[width= 8cm] {case2sxx.pdf}
   \caption{Comparison resutls for Test 1 with the structrures of $S^ES^P|S^PS^E$.  }
@@
 
-  \includegraphics[width= 6cm] {case4rho.pdf}
-  \includegraphics[width= 6cm] {case4u.pdf}
-  \includegraphics[width= 6cm] {case4p.pdf}
-  \includegraphics[width= 6cm] {case4sxx.pdf}
+  \includegraphics[width= 8cm] {case4rho.pdf}
+  \includegraphics[width= 8cm] {case4u.pdf}
+  \includegraphics[width= 8cm] {case4p.pdf}
+  \includegraphics[width= 8cm] {case4sxx.pdf}
 
@@
 
-  \includegraphics[width= 6cm] {case3rho.pdf}
-  \includegraphics[width= 6cm] {case3u.pdf}
-  \includegraphics[width= 6cm] {case3p.pdf}
-  \includegraphics[width= 6cm] {case3sxx.pdf}
+  \includegraphics[width= 8cm] {case3rho.pdf}
+  \includegraphics[width= 8cm] {case3u.pdf}
+  \includegraphics[width= 8cm] {case3p.pdf}
+  \includegraphics[width= 8cm] {case3sxx.pdf}
 
@@
 
-  \includegraphics[width= 6cm] {case5rho.pdf}
-  \includegraphics[width= 6cm] {case5u.pdf}
-  \includegraphics[width= 6cm] {case5p.pdf}
-  \includegraphics[width= 6cm] {case5sxx.pdf}
+  \includegraphics[width= 8cm] {case5rho.pdf}
+  \includegraphics[width= 8cm] {case5u.pdf}
+  \includegraphics[width= 8cm] {case5p.pdf}
+  \includegraphics[width= 8cm] {case5sxx.pdf}
 
@@
 
-  \includegraphics[width= 6cm] {case9rho.pdf}
-  \includegraphics[width= 6cm] {case9u.pdf}
-  \includegraphics[width= 6cm] {case9p.pdf}
-  \includegraphics[width= 6cm] {case9sxx.pdf}
+  \includegraphics[width= 8cm] {case9rho.pdf}
+  \includegraphics[width= 8cm] {case9u.pdf}
+  \includegraphics[width= 8cm] {case9p.pdf}
+  \includegraphics[width= 8cm] {case9sxx.pdf}
 
@@
   \centering
-  \includegraphics[width= 6cm] {case6rho.pdf}
-  \includegraphics[width= 6cm] {case6u.pdf}
-  \includegraphics[width= 6cm] {case6p.pdf}
-  \includegraphics[width= 6cm] {case6sigma.pdf}
+  \includegraphics[width= 8cm] {case6rho.pdf}
+  \includegraphics[width= 8cm] {case6u.pdf}
+  \includegraphics[width= 8cm] {case6p.pdf}
+  \includegraphics[width= 8cm] {case6sigma.pdf}
 
@@
   \centering
-  \includegraphics[width= 6cm] {case8rho.pdf}
-  \includegraphics[width= 6cm] {case8u.pdf}
-  \includegraphics[width= 6cm] {case8p.pdf}
-  \includegraphics[width= 6cm] {case8sigma.pdf}
+  \includegraphics[width= 8cm] {case8rho.pdf}
+  \includegraphics[width= 8cm] {case8u.pdf}
+  \includegraphics[width= 8cm] {case8p.pdf}
+  \includegraphics[width= 8cm] {case8sigma.pdf}
 
@@
   \centering
-  \includegraphics[width= 6cm] {case10rho.pdf}
-  \includegraphics[width= 6cm] {case10u.pdf}
-  \includegraphics[width= 6cm] {case10p.pdf}
-  \includegraphics[width= 6cm] {case10sxx.pdf}
+  \includegraphics[width= 8cm] {case10rho.pdf}
+  \includegraphics[width= 8cm] {case10u.pdf}
+  \includegraphics[width= 8cm] {case10p.pdf}
+  \includegraphics[width= 8cm] {case10sxx.pdf}
 
@@
   \centering
-  \includegraphics[width= 6cm] {case11rho.pdf}
-  \includegraphics[width= 6cm] {case11u.pdf}
-  \includegraphics[width= 6cm] {case11p.pdf}
-  \includegraphics[width= 6cm] {case11sigma.pdf}
+  \includegraphics[width= 8cm] {case11rho.pdf}
+  \includegraphics[width= 8cm] {case11u.pdf}
+  \includegraphics[width= 8cm] {case11p.pdf}
+  \includegraphics[width= 8cm] {case11sigma.pdf}
     \caption{Comparison results for Test 10 with the structrures of $R^ER^P$.  }
@@
 \end{figure}
+\section{Results}
+In this paper, we give a detailed analysis of the Riemann problem for one-dimensional  multi-material elastic-plastic flows with the  Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and the von Mises' yielding condition.
+Some useful results are found through the analysing:
+\begin{enumerate}
+	\item The sonic speed periods a significant jump when the material is yielding.
+	\item the plastic wave is always faster than the elastic wave for the reason of the sonic speed jump.
+
+	  \item There are only thirty-six possible cases of the structrues in the Riemann problem. 
+	\item All the variables after the wave can be written as functions of the density theoretically. 
+	\end{enumerate} 
+	  Then, based on the analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately, by an Newton iteration process.
+Tested by  a large number of examples, the exact Riemann solver is reasonable and matching  well with the numerical method for both the single material problem and multi-material Riemann problems.
+
 \section*{Acknowledgement}
@@
 
-%
-%We random choose a particle point inside the expansion region with the state of $(\rho,u, p,s_{xx})$, after a little expansion with the wave speed of $u-c$, the state changes to$(\rho+d\rho, u+du, p+dp, s_{xx}+ds_{xx})$.
-According to the conservation relations we can get
-%\begin{equation}
-%  \begin{aligned}
-%	& (\rho+ \text{d}\rho)(u+ \text{d}u) = \rho u +(u-c)\text{d}\rho\\
-%	& (\rho+\text{d}\rho)(u+\text{d}u)^2 -(\sigma+\text{d}\sigma)=   \rho u^2-\sigma\\
-%	&+(u-c)[(\rho+\text{d}\rho)(u+\text{d}u)-\rho u] \\
-%	& [(\rho+\text{d}\rho)(E+\text{d}E)-(\sigma+\text{d}\sigma)](u+\text{d}u) = \\
-%	&(\rho E-\sigma)u+(u-c)[(\rho+\text{d}\rho)(E+\text{d}E)-\rho E]\\
-% \end{aligned}
-%\end{equation}
-%Ignoring high-order infinite small terms, we can get  
-%\begin{align}
-%  \label{eq:urho}
-%  & \text{d} u =-\frac{c}{\rho}\text{d}\rho,\\
-%\label{eq:sigmarho}
-%  & \text{d} \sigma = -c^2 d\rho,\\
-% \label{eq:Erho}
-%  & \text{d} E = -\frac{\sigma+\rho u c}{\rho^2} d\rho.
-%\end{align}
-%Also we know the deviatoric stress is a function of the  density by Eq.(\ref{eq:rhosxx})   
-%\begin{equation}
-%  ds_{xx} = \left\{ \begin{aligned}
-%	  -\frac{4}{3}\frac{\mu}{\rho}d\rho \quad |s_{xx}| < \frac{2}{3}Y_0,\\
-%	  0  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
-%	\end{aligned}
-%  \right.
-%\end{equation}
-%And from Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}) we can get
-%\begin{equation}\label{eq:c_2rho}
-%  c^2 = \left\{ \begin{aligned}
-%	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx} +\frac{4}{3}\frac{\mu}{\rho} \quad |s_{xx}| < \frac{2}{3}Y_0,\\
-%	  a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}  \quad  |s_{xx}| \ge  \frac{2}{3}Y_0.
-%	\end{aligned}
-%  \right.
-%\end{equation}
-%Then the differential of  pressure is  given  as 
-%\begin{equation}
-%  dp = ds_{xx} -d\sigma = ds_{xx}+c^2 d\rho = \left( a_0^2 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}\right) d\rho,
-%\end{equation}
-%it can be written as a differential equation of $p(\rho)$
-%\begin{equation}
-%  p'(\rho) - \lambda_1 \frac{p}{\rho^2} = f_2(\rho), \quad p(\rho_1) = p_1,
-%\end{equation}
-%where 
-%\begin{equation}
-%  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
-%\end{equation}
-%The pressure can be solved out as
-%\begin{equation}\label{eq:p_rho}
-%  p(\rho) = p_1e^{\frac{\lambda_1}{\rho_1}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_1}^\rho f_2(x) e^{\frac{\lambda_1}{x}}dx.
-%\end{equation}
-%
-%By the above equations of Eq.(\ref{eq:urho}-\ref{eq:Erho},\ref{eq:c_2rho},\ref{eq:p_rho}), we know that the state $(\rho, u, p, s_{xx})$ is only  a function of the density $\rho$ no matter within or  after the rarefaction wave.
-%
-
 \bibliography{mybibfile}
-
-\newpage
   \appendix

### 2019-06-04 Manuscript_revise.tex
eee

@@
 \begin{abstract} 
-  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model \cite{wilkins1963calculation} and  the von Mises' yielding condition is studied in this paper.
-Through a detailed analysis of the Jacobian and eigenvectors, and the exact relations across different waves, an exact solution is constructed with three-to-five waves and thirty-six possible structure cases.
-More over, some useful results are also obtained in the analysis, for example, the significant jump of the sonic speed
-
-  A multi-material HLLC-type  approximate Riemann solver with both elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic flows with the  hypo-elastic model and the von Mises yielding condition.
-Although Cheng in 2016 introduced a HLLC Riemann solver with elastic waves(HLLCE) for 1D elastic-plastic flows, Cheng assumed that pressure is continuous across the contact wave.
-This assumption maybe lead to big errors, especially for multi-material elastic-plastic flows.
-In our MHLLCEP, this assumption is not used again, and correspondingly the errors introduced by the assumption are deleted, describing and evaluating the plastic waves are more accurate than that in the HLLCE.
-Moreover, if the non-linear waves in the Riemann problem are only shock waves, even with the plastic waves, our MHLLCEP is theoretically accurate.
-For  the multi-material system, in this paper, a ghost cell method is used to achieve a high-order spatial reconstruction across the interface without numerical oscillations.
-Based on the MHLLCEP, combining with the third-order WENO reconstruction method and the third-order Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic-plastic flows is built in this paper.
-A number of numerical experiments are carried out.
-Numerical results show  that the presented third-order scheme is convergent, robust, and essentially non-oscillatory.
-Moreover, for multi-material elastic-plastic flows, the scheme with  the MHLLCEP is more accurate and reasonable in resolving the multi-material interface than the scheme with the  HLLCE.
+  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and  the von Mises' yielding condition is studied in this paper.
+Through a detailed analysis of the Jacobian matrix and relations across different type of waves,  an exact Riemann solver is constructed with totally thirty-six possible cases of structure.
+Some useful results are also obtained in the analysing, for example, the sonic speed experiences a significant jump when the material is yielding and the plastic wave is always faster than the elastic wave.
+More over, an exact Riemann solver is also deduced for the half Riemann problem.
+A lot of examples show that, the results taken by the exact Riemann solver are in good agreement with those computed by the mumerical method.
+
 \end{abstract}

### 2019-06-13 Manuscript revise 20190612.tex
2

--- 2019-06-04 Manuscript_revise.tex
@@
 \usepackage{subfigure}
-\usepackage{caption,subcaption}
+%\usepackage{caption,subcaption}
 \usepackage{booktabs}
@@
 \usepackage{hyperref}
-\usepackage{stackengine}
+%\usepackage{stackengine}
 \usepackage[demo]{graphicx}
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{sigma1}
   \sigma = -p +s_{xx},
@@
 By integrating (\ref{dp2}) across the left rarefaction wave, the pressure can be solved out as
-\begin{equation}\label{eq:p_rho}
+\begin{equation}\label{eq:prhoEL}
   p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
@@
 Integrating  (\ref{eq:urho}) across the left rarefaction wave yields
-\begin{equation}
+\begin{equation}\label{eq:urhoEL}
   u+\int\frac{c_e}{\rho} d\rho = \text{constant}.
@@
 By using the same method, one can get
-\begin{equation}
+\begin{equation}\label{eq:prhoER}
   p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
 \end{equation}
-\begin{equation}
+\begin{equation}\label{eq:urhoER}
   u-\int\frac{c_e}{\rho} d\rho = \text{constant}.
@@
 \end{equation}
-the equations of Riemann problem  will turn into a more simple system with only constitutive terms as
+the equations of Riemann problem  can be written as
 \begin{equation}\label{eq:1dp}
@@
 where $\mathbf{U} = (\rho, \rho u, \rho E )$.
-  \subsubsection{Jacobian matrix in  plastic  regions\footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}}
- The equations (\ref{eq:1dp}) can be written as
+  \subsubsection{Jacobian matrix in  plastic  regions}
+  %\footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}}
+ The motion equations of (\ref{eq:1dp}) can be written as
 \begin{equation}
@@
 
-The eigenvalues of the coefficient matrix $\mathbf{J}_p(\mathbf{Q})$ are given as
-$$\lambda_1 = u,\quad \lambda_2 = u-c, \quad \lambda_3 = u+c,$$
+The eigenvalues of $\mathbf{J}_p(\mathbf{Q})$ are given as
+$$\lambda_1 = u,\quad \lambda_2 = u-c_p, \quad \lambda_3 = u+c_p,$$
 where
 \begin{equation}\label{eq:c_p}
-  \left\{ \begin{aligned}
-	  & c_p = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}} ,\\
-    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
-      \end{aligned} \right.
-    \end{equation}
+   c_p = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}}.
+\end{equation}
+%\begin{equation}\label{eq:c_p}
+%  \left\{ \begin{aligned}
+%	  & c_p = \sqrt{a^2-\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}} ,\\
+%    &   a^2 = \frac{\partial p}{\partial \rho} + \frac{p}{\rho^2}\frac{\partial p}{\partial e} = a^2_0 \frac{\partial f}{\partial \eta} + \frac{p}{\rho^2}\rho_0 \Gamma_0.
+%      \end{aligned} \right.
+%    \end{equation}
 The corresponding right eigenvectors are
@@
 \end{equation}
-where 
- \begin{equation}
-    b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho}.
-  \end{equation}
-
-Take a comparason  of Eq.(\ref{eq:c_e}) and Eq.(\ref{eq:c_p}), we notice that the sonic speed is not continuous between the states of elastic and plastic.
-As the shear modulus $\mu$ is always positive, so the elastic wave is always faster than the plastic wave.
-This is very important and may cause wrong results if ignoring it.
+%where
+% \begin{equation}
+%    b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho}.
+%  \end{equation}
+
+Comparing Eq.(\ref{eq:c_e}) with Eq.(\ref{eq:c_p}), we notice that the sonic speed is not continuous between the states of elastic and plastic.
+As the shear modulus $\mu$ is always positive, so the elastic wave runs always faster than the plastic wave.
+%This is very important and may cause wrong results if ignoring it.
 
@@
 \begin{equation}
-  du = 0, \quad dp = 0. 
-\end{equation}
-Samilar to that in  section \ref{sec:contacte}, we can also get the relations
-\begin{equation} 
-  s^* = u_L^* = u_R^*, % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
+  du = 0, \quad dp = 0,
+\end{equation}
+%Samilar to that in  section \ref{sec:contacte}, we can also get the relations
+which means that
+\begin{equation}
+u_L^* = u_R^*, % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
  \quad
+  p^*_L = p^*_R.
+\end{equation}
+Because $s^*_{xxL} = s^*_{xxR}$, thanks to (\ref{sigma1}), one can get
+\begin{equation}
   \sigma^*_L = \sigma^*_R.
+\end{equation}
+For convenience, we define
+\begin{equation}
+  s^* = u_L^* = u_R^*.
 \end{equation}
@@
 Samilar to section \ref{sec:rarefaction}, we can get the relations
-\begin{equation}\label{eq:p_rhop}
+\begin{equation}\label{eq:p_rhopL}
   p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
@@
 and
-\begin{equation}
-  u+\int\frac{c_p}{\rho} d\rho = \text{constant},
-\end{equation}
-where
-\begin{equation}
-  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
-\end{equation}
+\begin{equation}\label{eq:u_rhopL}
+  u+\int\frac{c_p}{\rho} d\rho = \text{constant}.
+\end{equation}
+%where
+%\begin{equation}
+%  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
+%\end{equation}
+
 \emph{\textbf{Right-going rarefaction wave} }
@@
 We can get  similar  relations  as the left-going wave as
-\begin{equation}
+\begin{equation}\label{eq:p_rhopR}
   p e^{\frac{\lambda}{\rho}} - \int f_2(\rho) e^{\frac{\lambda}{\rho}}d\rho = \text{constant}.
 \end{equation}
-\begin{equation}
+\begin{equation}\label{eq:u_rhopR}
   u-\int\frac{c_p}{\rho} d\rho = \text{constant}.
 \end{equation}
-\subsubsection{Relations across  shock waves}\label{sec:shockp}
-By a same deducing process with Section \ref{sec:shock}, we can get the state after a shock as  
+
+\subsubsection{Relations across  a shock wave}\label{sec:shockp}
+By using the same deducing process as Section \ref{sec:shock}, we can get the states after the shock wave as
 \begin{equation}
@@
 \end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
-\begin{equation}
-  \sigma_2 = -p_2 +s_{xx2}.
-\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$, $\sigma_2 = -p_2 +s_{xx2}$,
+%\begin{equation}
+%  \sigma_2 = -p_2 +s_{xx2},
+%\end{equation}
 \begin{equation}\label{eq:shockup}
@@
 
-\section{Exact Riemann solver \footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}} \label{sec:riemann}
+\section{Exact Riemann solver} %\footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}} \label{sec:riemann}
 
@@
 \begin{figure}
-\captionsetup[subfigure]{labelformat=empty}
+%\captionsetup[subfigure]{labelformat=empty}
   \centering
-  \subfigure[Elastic rarefaction wave]{
+  \subfigure[Elastic rarefaction wave ($R^{E}$)]{
 	\label{fig:subfigure:a}
   \includegraphics[width=5cm]{Tikz-figure0.eps}}
-  \subfigure[Plastic rarefaction wave]{
+  \subfigure[Plastic rarefaction wave ($R^{P}$)]{
 	\label{fig:subfigure:b}
   \includegraphics[width=5cm]{Tikz-figure1.eps}}
-  \subfigure[Both elastic and plastic rarefaction waves]{
+  \subfigure[Both elastic and plastic rarefaction waves ($R^{E}R^{P}$)] {
 	\label{fig:subfigure:c}
   \includegraphics[width=5cm]{Tikz-figure2.eps}}
-  \subfigure[ Elastic shock wave]{
+  \subfigure[ Elastic shock wave ($S^{E}$)]{
 	\label{fig:subfigure:d}
   \includegraphics[width=5cm]{Tikz-figure3.eps}}
-  \subfigure[Plastic shock wave]{
+  \subfigure[Plastic shock wave ($R^{P}$) ]{
 	\label{fig:subfigure:e}
   \includegraphics[width=5cm]{Tikz-figure4.eps}}
-  \subfigure[Both elastic and plastic shock waves]{
+  \subfigure[Both elastic and plastic shock waves ($S^{E}S^{P}$)]{
 	\label{fig:subfigure:f}
@@
   \subsection{The solving process}\label{sec:iteration}
-  By those relations in Section  \ref{sec:Riemann}, all  variables can be written as functions of  the density, so if  densities in regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$ are known, the Riemann problem is solved.
-e
-For given values of  $\rho_L^*$ and   $\rho_R^*$,
- by relations across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get  
-\begin{equation}
-  \begin{aligned}
-	f_u(\rho_L^*,\rho_R^*)_=  u_L^* -u_R^* =0,\\ 
-	f_\sigma(\rho_L^*,\rho_R^*)_=  \sigma_L^* -\sigma_R^* =0.\\ 
-\end{aligned}
-\end{equation}
-Then using a  Newton iteration method, we can solve the densities $\rho_L^*$ and $\rho_R^*$ out.  The solving process is shown in Fig.\ref{fig:newton}, and the details are list in the following.
+  %From those relations in Section  \ref{sec:Riemann}, all  variables can be formulated in terms of density.
+  %So, given densities in unknown regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$, the Riemann problem is solved.
+From Section  \ref{sec:Riemann}, we can find that all variables can be formulated in terms of density. So we define equations
+\begin{equation}
+\left\{
+\begin{array}{c}
+  f_u(\rho_L^*,\rho_R^*,\mathbf{Q}_{L},\mathbf{Q}_{R})_=  u_L^*(\rho_L^*,\mathbf{Q}_{L}) -u_R^*(\rho_R^*,\mathbf{Q}_{R}), \\
+  f_\sigma(\rho_L^*,\rho_R^*,\mathbf{Q}_{L},\mathbf{Q}_{R})_=  \sigma_L^*(\rho_L^*,\mathbf{Q}_{L}) -\sigma_R^*(\rho_R^*,\mathbf{Q}_{R}).
+\end{array}
+\right.
+\end{equation}
+By using the relations across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get
+\begin{equation} \label{exact1}
+\left\{
+\begin{array}{c}
+  f_u(\rho_L^*,\rho_R^*,\mathbf{Q}_{L},\mathbf{Q}_{R})_=  u_L^*(\rho_L^*,\mathbf{Q}_{L}) -u_R^*(\rho_R^*,\mathbf{Q}_{R})=0, \\
+  f_\sigma(\rho_L^*,\rho_R^*,\mathbf{Q}_{L},\mathbf{Q}_{R})_=  \sigma_L^*(\rho_L^*,\mathbf{Q}_{L}) -\sigma_R^*(\rho_R^*,\mathbf{Q}_{R})=0.
+\end{array}
+\right.
+\end{equation}
+
+Obviously, this system is uniquely solvable, but we can not get the analytical solution of (\ref{exact1}). We have to use an iteration procedure to solve (\ref{exact1}) and
+%, which is given in the following.
+%Given values of $\rho_L^*$ and  $\rho_R^*$,  by using relations across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get
+%\begin{equation}
+%  \begin{aligned}
+%	f_u(\rho_L^*,\rho_R^*)_=  u_L^* -u_R^* =0,\\
+%	f_\sigma(\rho_L^*,\rho_R^*)_=  \sigma_L^* -\sigma_R^* =0.\\
+%\end{aligned}
+%\end{equation}
+%Then using a  Newton iteration method, we can solve the densities $\rho_L^*$ and $\rho_R^*$ out.
+the solving process is shown in Fig.\ref{fig:newton}. The details are introduced in the following.
 \begin{figure}
@@
 \begin{equation}
-  \rho_{L(0)}^* = \rho_L \quad \rho_{R(0)}^* = \rho_R.
+  \rho_{L(1)}^* = \frac{\rho_L+\rho_R}{2} \quad \rho_{R(1)}^* = \frac{\rho_L+\rho_R}{2}.
 \end{equation}
@@
 \begin{enumerate}[Step 1]
-  \item Case select:
-	By a given  $\rho _{L,(k)}^*$ and a  $\rho _{R,(k)}^*$ in $k$ iteration step, we need to determine cases of  wave structures in the left and right.
-The determining  process is done in Section \ref{sec:deter}.
-
-  \item Solving $f_u$ and $f_\sigma$:  After determining the structure case, we need  to solve the Cauchy stresses and the velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
-
-  \item  Updating  $\rho_L^*$ and $\rho_R^*$:   By the Newton iteration equation, new densities can be updated, 
+  \item Determining the case of the wave structure:
+
+	Given $\rho _{L(k)}^*$ and a  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+In this procedure for solving this Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
+
+  \item Evaluating $f_{u(k)}$ and $f_{\sigma(k)}$:
+
+  After determining the structure case, we need  to solve the Cauchy stresses and the velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
+
+  \item Evaluating the derivatives of $f_{u(k)}$ and $f_{\sigma(k)}$.
+
+The derivatives of $f_{u(k)}$ and $f_{\sigma(k)}$ are given as
+\begin{equation}
+  \frac{\partial f_{u(k)}}{\partial \rho^*_{L(R)}} = \frac{f_{u(k)}-f_{u(k-1)}}{\rho_{L(R)(k)}^* - \rho_{L(R)(k-1)}},\quad
+  \frac{\partial f_{\sigma(k)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma(k)}-f_{\sigma(k-1)}}{\rho_{L(R)(k)}^* - \rho_{L(R)(k-1)}}.
+\end{equation}
+At the first step, we use a simple  numerical difference  method
+\begin{equation}
+  \frac{\partial f_{u(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
+  \frac{\partial f_{u(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
+\end{equation}
+where $\Delta \rho$ is a little quantity, we define
+\begin{equation}
+  \Delta \rho = \frac{\rho_{L(R)(1)}^*}{100}.
+\end{equation}
+
+  \item  Evaluating  $\rho_{L(k+1)}^*$ and $\rho_{R(k+1)}^*$:
 \begin{equation}
 \left[ \begin{array}{l}
- \rho _{L,(k+1)}^*\\
-\rho_{R,(k+1)}^*\\
+ \rho _{L(k+1)}^*\\
+\rho_{R(k+1)}^*\\
 \end{array}
@@
 \left[ \begin{array}{l}
- \rho _{L,(k)}^*\\
-\rho_{R,(k)}^*\\
+ \rho _{L(k)}^*\\
+\rho_{R(k)}^*\\
 \end{array}
@@
 \end{equation}
-The derivatives of $f_{u}$ and $f_{\sigma}$ are given by
-\begin{equation}
-  \frac{\partial f_{u,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u,(k+1)}-f_{u,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},\quad
-  \frac{\partial f_{\sigma,(k+1)}}{\partial \rho^*_{L(R)}} = \frac{f_{\sigma,(k+1)}-f_{\sigma,(k)}}{\rho_{L(R),(k+1)}^* - \rho_{L(R),(k)}},
-\end{equation}
-At the first step, we use a simple  numerical difference  method
-\begin{equation}
-  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},\quad
-  \frac{\partial f_{u,(1)}}{\partial \rho^*_{L(R)}} = \frac{f_{u}(\rho^*_{L(R)}+\Delta \rho)-f_{u}(\rho^*_{L(R)})}{\Delta \rho_{L(R)}},
-\end{equation}
-where $\Delta \rho$ is a little quatity, we can choose it as
-\begin{equation}
-  \Delta \rho_{L(R)} = \frac{\rho_{L(R),(0)}^*}{100}.
-\end{equation}
+
 \item Convergence test:
-The  convergence is meassured by 
+
+The iteration is convergent if
+\begin{equation}{\label{conv}}
+  \text{CHA} \le \text{TOL},
+\end{equation}
+where
+%The convergence is measured by
 \begin{equation}
 \text{CHA} = \text{max} \left[
-\frac{|\rho_{L(k+1)}^*- \rho_{L,(k)}^*|}{\frac{1}{2}|\rho_{L(k+1)}^*+\rho_{L(k)}^*|},   \frac{|\rho_{R(k+1)}^*- \rho_{R,(k)}^*|}{\frac{1}{2}|\rho_{R(k+1)}^*+\rho_{R(k)}^*|},|f_{u}|,|f_{\sigma}|\right].
-\end{equation}
-and the tolerance is taken as $\text{TOL} = 10^{-4}$.
-
-If $ \text{CHA} \le \text{TOL} $, the iteration ends. 
-It usually takes 2-4 steps to get a convergence result.
+\frac{|\rho_{L(k+1)}^*- \rho_{L,(k)}^*|}{\frac{1}{2}|\rho_{L(k+1)}^*+\rho_{L(k)}^*|},   \frac{|\rho_{R(k+1)}^*- \rho_{R,(k)}^*|}{\frac{1}{2}|\rho_{R(k+1)}^*+\rho_{R(k)}^*|},|f_{u}|,|f_{\sigma}|\right],
+\end{equation}
+$$\text{TOL} = 10^{-4}.$$
+%and the tolerance is taken as .
+If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv} ) is satisfied.
+%It usually takes 2-4 steps to get a convergence result.
 \end{enumerate}
@@
 
-Using a given density $\rho^*_{L(R)}$ we can distinguish the shock and rarefaction wave.
-This is done easily by comparing $\rho^*_{L(R)}$ with $\rho_{L(R)}$, the subscript $_{L(R)}$ means either both in the left side $_L$ and  right side $_R$.
-\begin{equation}
+Given the value of density $\rho^*_{L(R)}$, we can distinguish the non-linear wave is a shock or rarefaction wave.
+This is done easily by comparing $\rho^*_{L(R)}$ with $\rho_{L(R)}$, the subscript $_{L(R)}$ means in the left(right) side of the contact wave.
+\begin{equation}\label{shock1}
   \left\{
   \begin{aligned}
-	& \text{Rarefaction wave:} & \rho_{L(R)} > \rho_{L(R)}^*,\\
-	& \text{Shock wave:} &  \rho_{L(R)} < \rho_{L(R)}^*.\\
+	& \text{a rarefaction wave:} & \text{if} \ \rho_{L(R)} > \rho_{L(R)}^*,\\
+	& \text{a shock wave:} &   \text{if} \ \rho_{L(R)} < \rho_{L(R)}^*.\\
 \end{aligned}\right.
@@
 
-To determine the number of waves, we need to know the yielding situation,  
-the devaitoric stress can be evaluated as 
+Thanks to (\ref{eq:rhosxx}),
+%To determine the number of waves, we need to know the yielding situation,
+the deviatoric stress can be evaluated as
 \begin{equation}  \label{sxx1}
-\hat{s}_{xxL(R)}=-\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\rho_{L(R)}}\right)+s_{xxL(R)},
-\end{equation}
-  Then we can classify every side into six cases, and conditions for the classfication are  shown in Table \ref{tab:cases}, the  subscripts $_L$ and  $_R$  are omitted for simplication.
+\hat{s}_{xxL(R)}=-\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\rho_{L(R)}}\right)+s_{xxL(R)}.
+\end{equation}
+
+According to the values of initial and evaluated deviatoric stresses in (\ref{sxx1}) in one side of the contact wave, the non-linear wave in this side may be:
+
+\begin{equation} \label{yield1}
+  \left\{
+  \begin{aligned}
+	& \text{an elastic  rarefaction} & \text{if}  \ \hat{s}_{xxL(R)}<\frac{2}{3}Y^{0},\\
+	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y^{0},\\
+	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y^{0},\\
+	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y^{0},\\
+	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y^{0},\\
+	& \text{a elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y^{0}.
+\end{aligned}\right.
+\end{equation}
+
+Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any one side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ''S'' and ''R'' mean the shock and rarefaction wave, respectively; superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave, respectively.
+Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.
+
+%  Then we can classify every side into six cases, and conditions for the classfication are  shown in Table \ref{tab:cases}, the  subscripts $_L$ and  $_R$  are omitted for simplication.
 
@@
   \caption{The condition of  cases classification.}
-  \begin{tabular}{c|ccc}
+  \begin{tabular}{c|cccc}
 	\toprule
-	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$&  other\\
+	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$  and  $|\hat{s}_{xx}| \geq \frac{2}{3}Y_0$&  other\\
   \midrule
-  $\hat{\rho^*} <\rho$ & case a& case b& case c \\
-  $\hat{\rho^*} >\rho$ & case d& case e& case f \\
+  $\hat{\rho^*} <\rho$ & case a: $R^{E}$ & case b: $ R^{P}$ & case c: $R^{E}R^{P}$ \\
+  $\hat{\rho^*} >\rho$ & case d: $S^{E}$ & case e: $ S^{P}$ & case f: $S^{E}S^{P}$ \\
+  %\hline
   \bottomrule
@@
 
-\subsection{States in  regions $\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$}
- For cases (a,b,d,e) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$. For  expression conveience, we let    
+\subsection{States in  middle regions ($\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$) }
+
+\emph{\textbf{Cases ($R^{E}$, $R^{P}$, $S^{E}$ and $S^{P}$)}}
+
+ For cases ($R^{E}$, $R^{P}$, $S^{E}$ and $S^{P}$) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$.
+For  expression convenience, we let
  \begin{equation}
@@
 
-For cases (c,f), the meterial periods a yielding process from elastic to plastic.
-There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exist.
-In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
-\begin{equation}
- \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
-	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
-	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
+%For cases ($R^{E}R^{P}$, $S^{E}S^{P}$), the material will experience the process from the non-yielding condition to the yielding condition and so there are two non-linear waves in the one side of the wave structure and the middle state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
+In the middle state $\tilde{\mathbf{Q}}_{L(R)}$, the deviatoric stress achieves the elastic limit.
+%\begin{equation}
+% \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
+%	 &\frac{2}{3}Y_0 \quad  &\text{Case ($R^{E}R^{P}$)},\\
+%	 &-\frac{2}{3}Y_0 \quad &\text{Case ($S^{E}S^{P}$)}.
+%	\end{aligned}
+%  \right.
+%\end{equation}
+
+%Thanks to (\ref{eq:rhosxx}),  the density in $\tilde{\mathbf{Q}}_{L(R)}$ is given as
+%\begin{equation}
+%  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
+%	  & \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case ($R^{E}R^{P}$)}, \\
+%	  & \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case ($S^{E}S^{P}$)}.
+%	\end{aligned}
+%  \right.
+%	\end{equation}
+
+	\emph{\textbf{Case ($R^{E}R^{P}$)}}
+
+Using the methods introduced in  the Section (\ref{sec:rarefaction}), we can easily deduce the formulation of all unknown variables after the rarefaction wave.
+Here we do not show the details of deduction.
+
+%For rarefaction wave case, we give the function of $s_{xx}$ at first,
+%\begin{equation}
+%  s_{xx}(\rho) =	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
+%  \end{equation}
+
+For the case ($R^{E}R^{P}$),  after the elastic rarefaction wave, the deviatoric stress achieves the elastic limit. Thanks to (\ref{shock1}) and (\ref{yield1}), one can easily deduce that
+\begin{equation*}
+\tilde{s}_{xxL(R)} = \frac{2}{3}Y_0.
+\end{equation*}
+
+By using (\ref{eq:rhosxx}), the density in $\tilde{\mathbf{Q}}_{L(R)}$ is given as
+\begin{equation*}
+\tilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right).
+\end{equation*}
+
+From (\ref{eq:prhoEL}) and (\ref{eq:prhoER}), for the case ($R^{E}R^{P}$), the pressure is rearranged as
+\begin{equation}\label{rerpp}
+  p(\rho)=
+	  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx, %\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
+\end{equation}
+where
+\begin{equation}
+  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}, \ s_{xx}(\rho) =	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}.
+\end{equation}
+
+Thanks to (\ref{eq:urhoEL}) and (\ref{eq:urhoER}), for the rarefaction wave case ($R^{E}R^{P}$), the velocity is given as
+\begin{equation} \label{rerpu}
+  u(\rho) =\left\{ \begin{aligned}
+	&u_L - \int_{\rho_L}^{\rho} \frac{c_e(x)}{x} dx \quad  & \text{for the  left-going rarefaction wave}
+ , \\
+ &u_R + \int_{\rho_R}^{\rho} \frac{c_e(x)}{x} dx \quad &  \text{for the right-going rarefaction wave} ,
 	\end{aligned}
-  \right.
-\end{equation}
-By  the relation in (\ref{eq:rhosxx}),  we can solve the density out as 
-\begin{equation}
-  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
-	  & \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\ 
-	  & \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}. 
-	\end{aligned}
-  \right.
-	\end{equation}
-	\emph{\textbf{Rarefaction wave case (c)}}
-For rarefaction wave case,
-we give the function of $s_{xx}$ at first,
-\begin{equation}
-  s_{xx}(\rho) =
-	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
-  \end{equation}
-
-The pressure is given as 
-\begin{equation}
-  p(\rho)=
-	  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx,\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
-\end{equation}
-where 
-\begin{equation}
-  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
-\end{equation}
-
-And sonic speed,
+  \right. % \quad \text{case (c)}.
+\end{equation}
+where the sonic speed
 \begin{equation}
   c_e(\rho) =
-	  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad   \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
-\end{equation}
-Then we can get  the   function of  velocity
-\begin{equation}
-  u(\rho) =\left\{ \begin{aligned} 
-	&u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad & \rho_{L} \ge \rho \ge \tilde{\rho}_{L}
- , \\
- &u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_R\ge \rho\ge \tilde{\rho}_R , 
-	\end{aligned}
-  \right. \quad \text{case (c)}.
-\end{equation}
+	  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}}.
+% \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
+\end{equation}
+
 States in region $\tilde{\mathbf{Q}}_{L(R)}$ can be solved as
 \begin{equation}
-  \tilde{s}_{xxL(R)} = s_{xx}(\rho_{L(R)}),\quad \tilde{p}_{L(R)} = p(\rho_{L(R)}), \quad \tilde{u}_{L(R)} = u(\rho_{L(R)}).
-\end{equation}
-
-\emph{\textbf{Shock wave case (f)}} For shock wave case, the deviatoric stress is given as 
-\begin{equation}
-  \tilde{ s}_{xxL(R)} =
-  -\frac{4}{3}\mu\text{ln}\left(\frac{\tilde{\rho}_{L(R)}}{\rho_{L(R)}}\right)+s_{xxL(R)}
-	\end{equation}
-	Then the pressure can be solved as 
+  % \tilde{s}_{xxL(R)} = s_{xx}(\rho_{L(R)}),\quad
+  \tilde{p}_{L(R)} = p(\rho_{L(R)}), \quad \tilde{u}_{L(R)} = u(\rho_{L(R)}).
+\end{equation}
+
+\textbf{Remark}:  In (\ref{rerpp}) and (\ref{rerpu}), there are two integral terms.
+Obviously, because of the complexity of the EOS, we can not get the exact integral values.
+We have to use the numerical methods to approximate the two integral terms with high order of accuracy.
+The approximation methods are introduced in the Appendix 1.
+
+\emph{\textbf{Case ($S^{E}S^{P}$)}}
+
+Using the methods introduced in  the Section (\ref{sec:shock}), we can easily deduce the formulation of all unknown variables in $\tilde{\mathbf{Q}}_{L(R)}$.
+In order to shorten the length of our paper, we do not show the details of the deduction.
+
+For the case ($S^{E}S^{P}$), after the elastic shock wave, the deviatoric stress achieves the elastic limit. So, by using (\ref{shock1}) and (\ref{yield1}), one can easily deduce that
+\begin{equation*}
+\tilde{s}_{xxL(R)} = -\frac{2}{3}Y_0.
+\end{equation*}
+
+From (\ref{eq:rhosxx}), after the elastic shock wave, the density in $\tilde{\mathbf{Q}}_{L(R)}$ is given as
+\begin{equation*}
+\tilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right).
+\end{equation*}
+
+%For shock wave case, the deviatoric stress is given as
+%\begin{equation}
+%  \tilde{ s}_{xxL(R)} =
+%  -\frac{4}{3}\mu\text{ln}\left(\frac{\tilde{\rho}_{L(R)}}{\rho_{L(R)}}\right)+s_{xxL(R)}
+%	\end{equation}
+
+By using (\ref{eq:shocke}), the pressure can be solved as
 \begin{equation}
   \tilde{p}_{L(R)}=
-  \frac{2t(c_1f(\tilde{\rho}_{L(R)}/\rho_0)+e_L)-(\sigma_{L(R)}+\tilde{s}_{xxL(R)})}{2tc_0-1},
+  \frac{2t(c_1f(\tilde{\rho}_{L(R)}/\rho_0)+e_{L(R)})-(\sigma_{L(R)}+\tilde{s}_{xxL(R)})}{2tc_0-1},
 \end{equation}
@@
 
-At last the velocity is
+Thanks to (\ref{eq:shocku}), the velocity can be written as
 \begin{equation}
@@
  \begin{equation}
-   \tilde{\sigma}_{L(R)} = -\tilde{p}_{L(R)} + \tilde{s}_{L(R)}.
+   \tilde{\sigma}_{L(R)} = -\tilde{p}_{L(R)} + \tilde{s}_{xxL(R)}.
  \end{equation}
@@
 
-  \includegraphics[width= 8cm] {case1rho.pdf}
-  \includegraphics[width= 8cm] {case1u.pdf}
-  \includegraphics[width= 8cm] {case1p.pdf}
-  \includegraphics[width= 8cm] {case1sigma.pdf}
+  %\includegraphics[width= 8cm] {case1rho.pdf}
+  %\includegraphics[width= 8cm] {case1u.pdf}
+  %\includegraphics[width= 8cm] {case1p.pdf}
+  %\includegraphics[width= 8cm] {case1sigma.pdf}
 
@@
   \centering
-\includegraphics[width= 8cm] {case2rho.pdf}
-  \includegraphics[width= 8cm] {case2u.pdf}
-  \includegraphics[width= 8cm] {case2p.pdf}
-  \includegraphics[width= 8cm] {case2sxx.pdf}
+  %\includegraphics[width= 8cm] {case2rho.pdf}
+  %\includegraphics[width= 8cm] {case2u.pdf}
+  %\includegraphics[width= 8cm] {case2p.pdf}
+  %\includegraphics[width= 8cm] {case2sxx.pdf}
   \caption{Comparison resutls for Test 1 with the structrures of $S^ES^P|S^PS^E$.  }
@@
 
-  \includegraphics[width= 8cm] {case4rho.pdf}
-  \includegraphics[width= 8cm] {case4u.pdf}
-  \includegraphics[width= 8cm] {case4p.pdf}
-  \includegraphics[width= 8cm] {case4sxx.pdf}
+ % \includegraphics[width= 8cm] {case4rho.pdf}
+ % \includegraphics[width= 8cm] {case4u.pdf}
+ % \includegraphics[width= 8cm] {case4p.pdf}
+ % \includegraphics[width= 8cm] {case4sxx.pdf}
 
@@
 
-  \includegraphics[width= 8cm] {case3rho.pdf}
-  \includegraphics[width= 8cm] {case3u.pdf}
-  \includegraphics[width= 8cm] {case3p.pdf}
-  \includegraphics[width= 8cm] {case3sxx.pdf}
+%  \includegraphics[width= 8cm] {case3rho.pdf}
+%  \includegraphics[width= 8cm] {case3u.pdf}
+%  \includegraphics[width= 8cm] {case3p.pdf}
+%  \includegraphics[width= 8cm] {case3sxx.pdf}
 
@@
 
-  \includegraphics[width= 8cm] {case5rho.pdf}
-  \includegraphics[width= 8cm] {case5u.pdf}
-  \includegraphics[width= 8cm] {case5p.pdf}
-  \includegraphics[width= 8cm] {case5sxx.pdf}
+ % \includegraphics[width= 8cm] {case5rho.pdf}
+ % \includegraphics[width= 8cm] {case5u.pdf}
+ % \includegraphics[width= 8cm] {case5p.pdf}
+ % \includegraphics[width= 8cm] {case5sxx.pdf}
 
@@
 
-  \includegraphics[width= 8cm] {case9rho.pdf}
-  \includegraphics[width= 8cm] {case9u.pdf}
-  \includegraphics[width= 8cm] {case9p.pdf}
-  \includegraphics[width= 8cm] {case9sxx.pdf}
+ % \includegraphics[width= 8cm] {case9rho.pdf}
+ % \includegraphics[width= 8cm] {case9u.pdf}
+ % \includegraphics[width= 8cm] {case9p.pdf}
+ % \includegraphics[width= 8cm] {case9sxx.pdf}
 
@@
   \centering
-  \includegraphics[width= 8cm] {case6rho.pdf}
-  \includegraphics[width= 8cm] {case6u.pdf}
-  \includegraphics[width= 8cm] {case6p.pdf}
-  \includegraphics[width= 8cm] {case6sigma.pdf}
+ % \includegraphics[width= 8cm] {case6rho.pdf}
+ % \includegraphics[width= 8cm] {case6u.pdf}
+ % \includegraphics[width= 8cm] {case6p.pdf}
+ % \includegraphics[width= 8cm] {case6sigma.pdf}
 
@@
   \centering
-  \includegraphics[width= 8cm] {case8rho.pdf}
-  \includegraphics[width= 8cm] {case8u.pdf}
-  \includegraphics[width= 8cm] {case8p.pdf}
-  \includegraphics[width= 8cm] {case8sigma.pdf}
+ % \includegraphics[width= 8cm] {case8rho.pdf}
+ % \includegraphics[width= 8cm] {case8u.pdf}
+ % \includegraphics[width= 8cm] {case8p.pdf}
+ % \includegraphics[width= 8cm] {case8sigma.pdf}
 
@@
   \centering
-  \includegraphics[width= 8cm] {case10rho.pdf}
-  \includegraphics[width= 8cm] {case10u.pdf}
-  \includegraphics[width= 8cm] {case10p.pdf}
-  \includegraphics[width= 8cm] {case10sxx.pdf}
+ % \includegraphics[width= 8cm] {case10rho.pdf}
+ % \includegraphics[width= 8cm] {case10u.pdf}
+ % \includegraphics[width= 8cm] {case10p.pdf}
+ % \includegraphics[width= 8cm] {case10sxx.pdf}
 
@@
   \centering
-  \includegraphics[width= 8cm] {case11rho.pdf}
-  \includegraphics[width= 8cm] {case11u.pdf}
-  \includegraphics[width= 8cm] {case11p.pdf}
-  \includegraphics[width= 8cm] {case11sigma.pdf}
+%  \includegraphics[width= 8cm] {case11rho.pdf}
+%  \includegraphics[width= 8cm] {case11u.pdf}
+%  \includegraphics[width= 8cm] {case11p.pdf}
+%  \includegraphics[width= 8cm] {case11sigma.pdf}
     \caption{Comparison results for Test 10 with the structrures of $R^ER^P$.  }
@@
 	\end{enumerate}
-	  Then, based on the analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately, by an Newton iteration process.
-Tested by  a large number of examples, the exact Riemann solver is reasonable and matching  well with the numerical method for both the single material problem and multi-material Riemann problems.
+	  Then, based on the analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately.
+Tested by  a large number of examples, the exact Riemann solver is reasonable and matching  well with the numerical method for both  single material problems and multi-material Riemann problems.
 

### 2019-06-13 Manuscript revise 20190612.tex
3

@@
 	& \text{an elastic  rarefaction} & \text{if}  \ \hat{s}_{xxL(R)}<\frac{2}{3}Y^{0},\\
-	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y^{0},\\
-	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y^{0},\\
-	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y^{0},\\
-	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y^{0},\\
-	& \text{a elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y^{0}.
+	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
+	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
+	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y_{0},\\
+	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0},\\
+	& \text{an elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0}.
 \end{aligned}\right.
@@
 
-Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any one side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ''S'' and ''R'' mean the shock and rarefaction wave, respectively; superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave, respectively.
+Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ''S'' and ''R'' mean the shock and rarefaction wave, respectively; superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave, respectively.
 Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.

### 2019-06-14 Manuscript revise 20190612.tex
33

@@
 \usepackage{listings}
+\usepackage{appendix}
 \usepackage{setspace}
@@
 %\usepackage{stackengine}
+\usepackage{multirow}
 \usepackage[demo]{graphicx}
@@
   \caption{The condition of  cases classification.}
-  \begin{tabular}{c|cccc}
+  \begin{tabular}{c|ccc}
 	\toprule
-	Conditions & $|s_{xx}|<\frac{2}{3}Y_0$ and $|\hat{s}_{xx}|<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$  and  $|\hat{s}_{xx}| \geq \frac{2}{3}Y_0$&  other\\
-  \midrule
-  $\hat{\rho^*} <\rho$ & case a: $R^{E}$ & case b: $ R^{P}$ & case c: $R^{E}R^{P}$ \\
-  $\hat{\rho^*} >\rho$ & case d: $S^{E}$ & case e: $ S^{P}$ & case f: $S^{E}S^{P}$ \\
+	\multirow{2}{*}{  $\hat{\rho^*} <\rho$ }  &  $\hat{s}_{xx}<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$ and  $\hat{s}_{xx} \geq \frac{2}{3}Y_0$ &  other\\
+ & case a: $R^{E}$ & case b: $ R^{P}$ & case c: $R^{E}R^{P}$ \\
+ \hline
+ \multirow{2}{*}{  $\hat{\rho^*} >\rho$ } & $\hat{s}_{xx} > -\frac{2}{3}Y_0$ & $s_{xx}=-\frac{2}{3}Y_0$  and  $\hat{s}_{xx} \leq -\frac{2}{3}Y_0$&  other\\
+  & case d: $S^{E}$ & case e: $ S^{P}$ & case f: $S^{E}S^{P}$ \\
   %\hline
@@
 
-\section*{Acknowledgement}
+\section*{Acknowledgement}r
 This work was supported by NSFC(Grant No. 11672047) and Science Challenge Project (Grant No. TZ2016002).
@@
 
+  \section{Gauss-Legendre  quadrature}
+  In this paper, we use Gauss-Legendre quadrature to  take  numerical integrations. 
+For a function $f(x)$,  the intergration from $-1$ to $1$ is given as
+$$ 
+  \int_{-1}^1 f(x)dx \approx \sum_{i=0}^n \omega_i f(x_i)
+$$
+$\omega_i$ is the weight, and $x_i$ is the integrating point.
+For different orders they are listed in Table \ref{tab:coe}.
+
+\subsection{}
+\begin{table}\label{tab:coe}
+  \centering
+  \caption{Coefficiences for Guass-Legendere quadrature}
+  \begin{tabular}{cccc}
+	\toprule
+	Number of points, $n$ &  Order & Points, $x_i$ & Weights, $\omega_i$ \\
+	\midrule
+	1 & 1  & 0 & 2 \\
+	\hline
+	2 & 3  & $\pm \frac{1}{\sqrt{3}}$ & 1 \\
+	\hline
+	\multirow{4}{*}{3} &\multirow{4}{*}{3} & 0  & $\frac{8}{9}$ \\
+	\cline{3-4}
+	& & $\pm\sqrt{\frac{3}{5}}$ & $\frac{5}{9} $\\
+	\hline
+	\multirow{4}{*}{\makecell{4}} & \multirow{4}{*}{7}  & $\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18+\sqrt{30}}{36}$ \\
+	\cline{3-4}
+  &  &  $\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18-\sqrt{30}}{36}$ \\
+  \bottomrule
+\end{tabular}
+\end{table}
+
 \end{document}

### 2019-06-16 Manuscript revise 20190612.tex
2222

@@
 When the material is yielding,
-\begin{equation}
+\begin{equation}\label{eq:sxxp}
   |s_{xx}| = \frac{2}{3}Y_0,
@@
 
+{\color{red}
 \begin{equation} \label{yield1}
@@
 \end{equation}
+}
 
@@
 
+{\color{red}
 \begin{table}
@@
 	\multirow{2}{*}{  $\hat{\rho^*} <\rho$ }  &  $\hat{s}_{xx}<\frac{2}{3}Y_0$ & $s_{xx}=\frac{2}{3}Y_0$ and  $\hat{s}_{xx} \geq \frac{2}{3}Y_0$ &  other\\
+	\cline{2-4}
  & case a: $R^{E}$ & case b: $ R^{P}$ & case c: $R^{E}R^{P}$ \\
@@
  \multirow{2}{*}{  $\hat{\rho^*} >\rho$ } & $\hat{s}_{xx} > -\frac{2}{3}Y_0$ & $s_{xx}=-\frac{2}{3}Y_0$  and  $\hat{s}_{xx} \leq -\frac{2}{3}Y_0$&  other\\
+	\cline{2-4}
   & case d: $S^{E}$ & case e: $ S^{P}$ & case f: $S^{E}S^{P}$ \\
@@
 \end{table}
+}
 
@@
 
-\emph{\textbf{Rarefaction wave}} For rarefaction wave,
-we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know  states inside the expansion region.
-
-First we give the function of $s_{xx}$,
+\emph{\textbf{Case ($R^E$, $R^P$ and $R^ER^P$)}} For rarefaction wave case, by the equations of  (\ref{eq:rhosxx}) in elastic state  and  (\ref{eq:sxxp}) in plastic state, we can get
+the function of  deviatoric stress $s_{xx}$ as,
 \begin{equation}
   s_{xx}(\rho) = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+s_{xxL(R)}, \quad & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (a)},\\
-	  & \frac{2}{3}Y_0,  \quad & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (b,c)}.
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+s_{xxL(R)},  \quad &\text{case ($R^E$)},\\
+	  & \frac{2}{3}Y_0 ,  \quad &\text{case ($R^P$ and $R^ER^P$)}.
   \end{aligned} \right.
   \end{equation}
-Then we give the pressure,
+Just like the process in (\ref{rerpp}) the pressure is given as,
 \begin{equation}
@@
 \end{equation}
-where
-\begin{equation}
-  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}.
-\end{equation}
-And sonic speed,
+And the  sonic speed,
 \begin{equation}
   c(\rho) = \left\{ \begin{aligned}
-	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case (a)},\\
-	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case (b,c)}.
+	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case ($R^E$)},\\
+	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case ($R^P$ and  $R^ER^P$)}.
 	\end{aligned}\right.
 \end{equation}
-Then we can get  the  function of  velocity
+ By relations (\ref{eq:urhoEL}) and (\ref{eq:urhoER})
+ we can get  the  function of  velocity as
 \begin{equation}
   u(\rho) =\left\{ \begin{aligned}
-	  &\tilde{u}_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad  & \tilde{\rho}_L \ge \rho \ge \rho_L^*,   \\
-	  &\tilde{u}_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad  & \tilde{\rho}_R \ge \rho \ge \rho_R^*, \\
+	  &\tilde{u}_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx,  \\
+	  &\tilde{u}_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \\
 	\end{aligned}
@@
 
-\emph{\textbf{Shock wave}}
+\emph{\textbf{Shock wave cases ($S^E$, $S^P$ and $S^ES^P$}}
 For shock waves, the  deviatoric stress is given as
@@
 	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
-	\quad  &\text{case (d)},\\
+	\quad  &\text{case ($S^E$)},\\
 	& -\frac{2}{3}Y_0,   \quad
-	&\text{cases (e, f)}.
+	&\text{cases ( $S^P$ and $S^ES^P$)}.
   \end{aligned} \right.
   \end{equation}
-And the pressure is given as
+By the equation of (\ref{eq:shocke}), the pressure is given as
 \begin{equation}
@@
 \end{equation}
-where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\tilde{\rho}_{L(R)} \rho}{\rho-\tilde{\rho}_{L(R)}}$.
-And the velocity is given as
-\begin{equation}
-  u(\rho)= \left\{ \begin{array}{l}
-	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t}},\\
-	  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t}},\\
-  \end{array}
+And the velocity is
+\begin{equation}
+  u(\rho)= \left\{ \begin{aligned}
+	&	\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t}}, \quad \text{For the left-going shock wave},\\
+	&  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t}}, \quad \text{For the right-going shock wave}.\\
+  \end{aligned}
 \right.
@@
 Shown in Fig.\ref{fig:half} , in these cases, we only need to solve states in one side.
-There are six possible cases just like them in Section \ref{sec:riemann}.
+There are six possible cases just like them in Section \ref{sec:Riemann}.
 
@@
 As we know the velocity $u^*$ or the Cauchy stress $\sigma ^*$, there is only one function need to be solved as
-\begin{equation}
-  f(\rho^*) =u(\rho^*) - u^* = 0,
+\begin{equation}\label{eq:halfu}
+  f(\rho^*,\mathbf{Q}_R) =u(\rho^*,\mathbf{Q}_R) - u^* = 0,
 \end{equation}
 or
-\begin{equation}
-  f(\rho^*) =\sigma(\rho^*) - \sigma^* = 0.
-\end{equation}
-
-The solving process is list in the following.
+\begin{equation}\label{eq:halfs}
+  f(\rho^*,\mathbf{Q}_R) =\sigma(\rho^*,\mathbf{Q}_R) - \sigma^* = 0.
+\end{equation}
+Samilar to the process in Section (\ref{sec:iteration}), we have to use an iteration procedure to solve (\ref{exact1}) and
+the solving process is list in the following.
 
@@
 	\hline
-	\multirow{4}{*}{3} &\multirow{4}{*}{3} & 0  & $\frac{8}{9}$ \\
+	\multirow{2}{*}{3} &\multirow{2}{*}{3} & 0  & $\frac{8}{9}$ \\
 	\cline{3-4}
@@
 	\hline
-	\multirow{4}{*}{\makecell{4}} & \multirow{4}{*}{7}  & $\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18+\sqrt{30}}{36}$ \\
+	\multirow{2}{*}{\makecell{4}} & \multirow{2}{*}{7}  & $\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18+\sqrt{30}}{36}$ \\
 	\cline{3-4}

### 2019-06-17 Manuscript revise 20190612.tex
333

@@
 For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{red}have been developed recently.
-However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver, but the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.
-All these makes easily deduce the relation across a non-linear wave.
-Although there are many  cases considered in their works \cite{gao20171d,gao2018complete}, for every case, they can easily obtain the exact solution.
-But for many engineering problems, the EOS is more complex, and the energy equation has to be included during simulating.
-For these engineering solid problems with a complex constitutive and a complex EOS, such as the Mie-Gr\"uneisen EOS, up to now, there is no  exact Riemann solution.
+However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
+But there are three shotcomings in their works.
+{\color{red}Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.
+Secondly, the states of elastic and plastic is using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave.
+Thirdly, only the changing from  elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}
 
@@
 So there are thirty-six possible cases of the wave structures in the Riemann solver.
+{\color{red} Both the  changing from elastic to plastic and  the converse changing from plastic to elastic are considered.}
 %For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 \end{equation}
-where $\Delta \rho$ is a little quantity, we define
+where $\Delta \rho$ is a small quantity, we define
 \begin{equation}
@@
 	& \text{a plastic rarefaction} & \text{if} \ {s}_{xxL(R)} = \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
-	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
+	& \text{an elastic rarefaction  and a following plastic rarefaction} &  \text{if} \ {s}_{xxL(R)} < \frac{2}{3}Y_{0} \ \text{and} \ \hat{s}_{xxL(R)} \geq \frac{2}{3}Y_{0},\\
 	& \text{an elastic shock} & \text{if}  \ \hat{s}_{xxL(R)}> -\frac{2}{3}Y_{0},\\
-	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0},\\
-	& \text{an elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y^{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0}.
+	& \text{a plastic shock} & \text{if} \ {s}_{xxL(R)} = -\frac{2}{3}Y_{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0},\\
+	& \text{an elastic shock and a following plastic shock} &  \text{if} \ {s}_{xxL(R)} > -\frac{2}{3}Y_{0} \ \text{and} \ \hat{s}_{xxL(R)} \leq -\frac{2}{3}Y_{0}.
 \end{aligned}\right.
@@
 We have to use the numerical methods to approximate the two integral terms with high order of accuracy.
-The approximation methods are introduced in the Appendix 1.
+The approximation methods are introduced in the Appendix A.
 
@@
 \begin{equation}
-\rho_{(0)}^* = \rho_R.
+\rho_{(1)}^* = \rho_R.
 \end{equation}
@@
 \begin{enumerate}[Step 1]
-  \item Case select:
-	By a given  $\rho _{(k)}^*$ in $k$ iteration step, we need to determine the case of the wave structures in the left side. The determining  process is  also done in Section \ref{sec:deter}.
-
-  \item Solving $f$:  After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
-
-  \item  Updating   $\rho^*$:   By the Newton iteration equation, a new density can be updated as
+  \item Determining the case of the wave structure:
+	By a given  $\rho _{(k)}^*$ in the $k$-th iteration step, we can use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+In this procedure for solving this Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
+
+  \item Solving $f(\rho^*,\mathbf{Q}_R)$:
+
+	After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
+
+  \item Evaluating the derivative of  $f(\rho^*,\mathbf{Q}_R)$:
+
+The derivatives of $f$ is  given by
+\begin{equation}
+  \frac{\partial f_{(k+1)}}{\partial \rho^*} = \frac{f_{(k+1)}-f_{(k)}}{\rho_{(k+1)}^* - \rho^*_{(k)}},
+\end{equation}
+At the first step, we use a simple  numerical difference  method
+\begin{equation}
+  \frac{\partial f_{(1)}}{\partial \rho^*} = \frac{f(\rho^*+\Delta \rho)-f(\rho^*)}{\Delta \rho},
+\end{equation}
+where $\Delta \rho$ is a small quatity, we define
+\begin{equation}
+  \Delta \rho = \frac{\rho_{(1)}^*}{100}.
+\end{equation}
+  \item  Evaluating  $\rho^*_{(k+1)}$:
+
+	By the Newton iteration equation, a new density can be updated as
 
@@
 \end{equation}
-The derivatives of $f$ is  given by
-\begin{equation}
-  \frac{\partial f_{(k+1)}}{\partial \rho^*} = \frac{f_{(k+1)}-f_{(k)}}{\rho_{(k+1)}^* - \rho^*_{(k)}},
-\end{equation}
-At the first step, we use a simple  numerical difference  method
-\begin{equation}
-  \frac{\partial f_{(1)}}{\partial \rho^*} = \frac{f(\rho^*+\Delta \rho)-f(\rho^*)}{\Delta \rho},
-\end{equation}
-where $\Delta \rho$ is a little quatity, we can choose it as
-\begin{equation}
-  \Delta \rho = \frac{\rho_{(0)}^*}{100}.
-\end{equation}
+
 \item Convergence test:
+
+The iteration is convergent if
 The  convergence is meassured by
+\begin{equation}{\label{conv1}}
+  \text{CHA} \le \text{TOL},
+\end{equation}
+where
 \begin{equation}
@@
 
-If $ \text{CHA} \le \text{TOL} $, the iteration ends.
-It usually takes 2-4 step to get a convergence result.
+If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv1} ) is satisfied.
 \end{enumerate}
@@
 In this section, by choosing suitable initial conditions, we will solve the Riemann problem with several different structure cases in the solution.
-For simple  expression, in figures, we use same representations as those in \cite{gao2018complete}.
-``$|$'' means the contact wave, and capital letters ''S'' and ''R'' means the shock and rarefaction wave.
-Superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave.
 Numerical results by the method  in \cite{liumulti} is used to verified the correctness of the exact solution.
@@
 
-  %\includegraphics[width= 8cm] {case1rho.pdf}
-  %\includegraphics[width= 8cm] {case1u.pdf}
-  %\includegraphics[width= 8cm] {case1p.pdf}
-  %\includegraphics[width= 8cm] {case1sigma.pdf}
+\includegraphics[width= 8cm] {case1rho.pdf}
+\includegraphics[width= 8cm] {case1u.pdf}
+\includegraphics[width= 8cm] {case1p.pdf}
+\includegraphics[width= 8cm] {case1sigma.pdf}
 
@@
   \centering
-  %\includegraphics[width= 8cm] {case2rho.pdf}
-  %\includegraphics[width= 8cm] {case2u.pdf}
-  %\includegraphics[width= 8cm] {case2p.pdf}
-  %\includegraphics[width= 8cm] {case2sxx.pdf}
-  \caption{Comparison resutls for Test 1 with the structrures of $S^ES^P|S^PS^E$.  }
+  \includegraphics[width= 8cm] {case2rho.pdf}
+  \includegraphics[width= 8cm] {case2u.pdf}
+  \includegraphics[width= 8cm] {case2p.pdf}
+  \includegraphics[width= 8cm] {case2sxx.pdf}
+  \caption{Comparison resutls for Test 2 with the structrures of $S^ES^P|S^PS^E$.  }
   \label{fig:case2}
@@
 
- % \includegraphics[width= 8cm] {case4rho.pdf}
- % \includegraphics[width= 8cm] {case4u.pdf}
- % \includegraphics[width= 8cm] {case4p.pdf}
- % \includegraphics[width= 8cm] {case4sxx.pdf}
+  \includegraphics[width= 8cm] {case4rho.pdf}
+  \includegraphics[width= 8cm] {case4u.pdf}
+  \includegraphics[width= 8cm] {case4p.pdf}
+  \includegraphics[width= 8cm] {case4sxx.pdf}
 
@@
 
-%  \includegraphics[width= 8cm] {case3rho.pdf}
-%  \includegraphics[width= 8cm] {case3u.pdf}
-%  \includegraphics[width= 8cm] {case3p.pdf}
-%  \includegraphics[width= 8cm] {case3sxx.pdf}
+ \includegraphics[width= 8cm] {case3rho.pdf}
+  \includegraphics[width= 8cm] {case3u.pdf}
+  \includegraphics[width= 8cm] {case3p.pdf}
+  \includegraphics[width= 8cm] {case3sxx.pdf}
 
@@
 \subsection{Test 5}
-All the above four tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
+In Test 4, the material is  yielding from a elastic state to a plastic state through  an elastic rarefaction wave, just as we say in the introduction, 
+even when it is in the plastic state at the beginning, after a rarefaction wave, the material will return into an elastic state and then may change into the  plastic by an  expandation yielding process.
+This is shown in Fig.\ref{fig:case20} both by the numerical and theoretical results, the material truely change from plastic state to elastic then to plastic state again.
+The initial conditions are
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = -200\text{m}/\text{s}, \quad  p = 1.0 \text{Pa}, \quad  s_{xx}=-2.0\time 10^8 \text{Pa},\\
+	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}= -2.0 \time 10^8 \text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+\begin{figure}
+  \centering
+ \includegraphics[width= 8cm] {case20rho.pdf}
+  \includegraphics[width= 8cm] {case20u.pdf}
+  \includegraphics[width= 8cm] {case20p.pdf}
+  \includegraphics[width= 8cm] {case20sxx.pdf}
+    \caption{Comparison resutls for Test 5 with the structrures of $R^ER^P|R^PR^E$.  }
+  \label{fig:case20}
+\end{figure}
+\subsection{Test 6}
+All the above five tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
 \begin{equation}
@@
 
- % \includegraphics[width= 8cm] {case5rho.pdf}
- % \includegraphics[width= 8cm] {case5u.pdf}
- % \includegraphics[width= 8cm] {case5p.pdf}
- % \includegraphics[width= 8cm] {case5sxx.pdf}
-
-    \caption{Comparison resutls for Test 5 with the structrures of $R^P|R^PR^E$.  }
+  \includegraphics[width= 8cm] {case5rho.pdf}
+  \includegraphics[width= 8cm] {case5u.pdf}
+  \includegraphics[width= 8cm] {case5p.pdf}
+  \includegraphics[width= 8cm] {case5sxx.pdf}
+
+    \caption{Comparison resutls for Test 6 with the structrures of $R^P|R^PR^E$.  }
   \label{fig:case5}
 \end{figure}
-\subsection{Test 6}
+\subsection{Test 7}
 In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves producted into the higher pressure side and shock waves generated into the lower pressure side.
@@
 
- % \includegraphics[width= 8cm] {case9rho.pdf}
- % \includegraphics[width= 8cm] {case9u.pdf}
- % \includegraphics[width= 8cm] {case9p.pdf}
- % \includegraphics[width= 8cm] {case9sxx.pdf}
-
-    \caption{Comparison resutls for Test 6 with the structrures of $R^ER^P|S^PS^E$.  }
+  \includegraphics[width= 8cm] {case9rho.pdf}
+  \includegraphics[width= 8cm] {case9u.pdf}
+  \includegraphics[width= 8cm] {case9p.pdf}
+  \includegraphics[width= 8cm] {case9sxx.pdf}
+
+    \caption{Comparison resutls for Test 7 with the structrures of $R^ER^P|S^PS^E$.  }
   \label{fig:case9}
 \end{figure}
-\subsection{Test 7}
+\subsection{Test 8}
 Now we will consider two multi-material tests with different materials on different sides.
@@
   \centering
- % \includegraphics[width= 8cm] {case6rho.pdf}
- % \includegraphics[width= 8cm] {case6u.pdf}
- % \includegraphics[width= 8cm] {case6p.pdf}
- % \includegraphics[width= 8cm] {case6sigma.pdf}
-
-    \caption{Comparison results for Test 7 with structrures of $R^ER^P|R^PR^E$.  }
+  \includegraphics[width= 8cm] {case6rho.pdf}
+  \includegraphics[width= 8cm] {case6u.pdf}
+  \includegraphics[width= 8cm] {case6p.pdf}
+  \includegraphics[width= 8cm] {case6sigma.pdf}
+
+    \caption{Comparison results for Test 8 with structrures of $R^ER^P|R^PR^E$.  }
   \label{fig:case7}
@@
 %
-\subsection{Test 8}
+\subsection{Test 9}
 At last, we test another multi-materials case, in this test the initial condtion is given as
@@
   \centering
- % \includegraphics[width= 8cm] {case8rho.pdf}
- % \includegraphics[width= 8cm] {case8u.pdf}
- % \includegraphics[width= 8cm] {case8p.pdf}
- % \includegraphics[width= 8cm] {case8sigma.pdf}
-
-    \caption{Comparison results for Test 8 with the structrures of $R^ER^P|S^ES^P$.  }
+  \includegraphics[width= 8cm] {case8rho.pdf}
+  \includegraphics[width= 8cm] {case8u.pdf}
+  \includegraphics[width= 8cm] {case8p.pdf}
+  \includegraphics[width= 8cm] {case8sigma.pdf}
+
+    \caption{Comparison results for Test 9 with the structrures of $R^ER^P|S^ES^P$.  }
   \label{fig:case8}
 \end{figure}
-\subsection{Test 9}
+\subsection{Test 10}
 Then we give two tests of  half Riemann problem, the first is with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
@@
   \centering
- % \includegraphics[width= 8cm] {case10rho.pdf}
- % \includegraphics[width= 8cm] {case10u.pdf}
- % \includegraphics[width= 8cm] {case10p.pdf}
- % \includegraphics[width= 8cm] {case10sxx.pdf}
-
-    \caption{Comparison results for Test 9 with the structrures of $S^ES^P$.  }
+  \includegraphics[width= 8cm] {case10rho.pdf}
+  \includegraphics[width= 8cm] {case10u.pdf}
+  \includegraphics[width= 8cm] {case10p.pdf}
+  \includegraphics[width= 8cm] {case10sxx.pdf}
+
+    \caption{Comparison results for Test 10 with the structrures of $S^ES^P$.  }
   \label{fig:case9}
 \end{figure}
-\subsection{Test 10}
+\subsection{Test 11}
 The second half Riemann case is with  a given left Cauchy stress $\sigma^* = 0 \text{Pa}$, and the right initial condition is
@@
   \centering
-%  \includegraphics[width= 8cm] {case11rho.pdf}
-%  \includegraphics[width= 8cm] {case11u.pdf}
-%  \includegraphics[width= 8cm] {case11p.pdf}
-%  \includegraphics[width= 8cm] {case11sigma.pdf}
-    \caption{Comparison results for Test 10 with the structrures of $R^ER^P$.  }
+ \includegraphics[width= 8cm] {case11rho.pdf}
+  \includegraphics[width= 8cm] {case11u.pdf}
+  \includegraphics[width= 8cm] {case11p.pdf}
+  \includegraphics[width= 8cm] {case11sigma.pdf}
+    \caption{Comparison results for Test 11 with the structrures of $R^ER^P$.  }
   \label{fig:case10}
@@
 
-\section*{Acknowledgement}r
+\section*{Acknowledgement}
 This work was supported by NSFC(Grant No. 11672047) and Science Challenge Project (Grant No. TZ2016002).
@@
 \bibliography{mybibfile}
+
   \appendix
-  \renewcommand{\appendixname}{Appendix~}
+  \begin{appendices}
+
+  \renewcommand{\appendixname}{Appendix~\Alph{section}}
 
@@
 $$ 
-  \int_{-1}^1 f(x)dx \approx \sum_{i=0}^n \omega_i f(x_i)
+\int_{-1}^1 f(x)dx \approx \sum_{i=0}^n \omega_i f(x_i),
 $$
@@
 
-\subsection{}
-\begin{table}\label{tab:coe}
+\subsection{Change of interval}
+An integral over  $[x_0,x_1]$ must be changed into an integral over $[−1, 1]$ before applying the Gaussian quadrature rule. This change of interval can be done in the following way:
+$$ \int_{x_0}^{x_1}f(x) dx= \frac{x_1-x_0}{2}\int_{-1}^{1} f(\frac{x_1-x_0}{2}x+\frac{x_0+x_1}{2})dx.
+ $$
+ \begin{table}[htp]\label{tab:coe}
   \centering
@@
 \end{table}
-
+\end{appendices}
 \end{document}

### 2019-06-28 Manuscript revise 20190612.tex
222

@@
 However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
-But there are three shotcomings in their works.
+But there are three issues need to improve or overcome in their works.
 {\color{red}Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.
-Secondly, the states of elastic and plastic is using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave.
-Thirdly, only the changing from  elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}
+Secondly, the states of elastic and plastic is using with very different equations systems and parameters, the seperation  deduces to more possible non-physical wave-structure cases in which the plastic wave  may run faster than the elastic wave.
+Thirdly, only the changing from  elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material  can also change to elastic states.}
 
@@
 These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves.
-Moreover, elastic wave runs always faster than the followed plastic wave.
+Moreover, elastic wave always runs faster than the followed plastic wave.
 So there are thirty-six possible cases of the wave structures in the Riemann solver.
-{\color{red} Both the  changing from elastic to plastic and  the converse changing from plastic to elastic are considered.}
+{\color{red} Besides, both the changing from elastic to plastic and  the converse changing from plastic to elastic are considered in the Riemann problem.}
 %For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 \subsection{Motion equations}
-For  a continuous one-dimensional homogeneous solid, the motion equations  in differential form are
+For  a continuous one-dimensional homogeneous solid, the motion equations  in  the differential form are
 \begin{equation*}
@@
 \end{equation}
-$\rho$, $u$, $\sigma$ and $E$ are  the density, velocity in $x-$direction, Cauchy stress and total energy per unit volume, respectively, $E$ has the relation with specific internal energy $e$ as
+$\rho$, $u$, $\sigma$ and $E$ are  the density, velocity in $x-$direction, Cauchy stress and total energy per unit volume, respectively, $E$ has the relation with the  specific internal energy $e$ as
 \begin{equation} \label{te1}
@@
 \end{equation}
-where $p$ and $s_{xx}$ denote hydrostatic pressure and deviatoric stress in the $x-$ direction, respectively.
+where $p$ and $s_{xx}$ denote the  hydrostatic pressure and the deviatoric stress in the $x-$ direction, respectively.
 
@@
 \end{equation}
-where $Y_0$ is the yield strength of the material in simple tension.
+where $Y_0$ is the yield strength of the material in  simple tensions.
 
@@
 
-The Riemann problem for the 1D time dependent elastic-plastic equations is given as follows:
+The Riemann problem for 1D time dependent elastic-plastic equations is given as follows:
  \begin{equation}\label{eq:1d}
@@
 The above equations are just for the elastic status of the solid material.
-If the material are in the plastic state, the above equations can be simplified
-and correspondingly the jacobian matrix and sonic velocity are different.
+If the materials are in the plastic state, the above equations can be simplified
+and the jacobian matrix and sonic velocity are different,  correspondingly.
 We will discuss them separately.
@@
     \end{equation}
-The corresponding right eigenvectors are
+ Corresponding right eigenvectors are
 \begin{equation}\label{eq:eiv}
@@
 
-Thanks to (\ref{eq:mt}), the equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
+Thanks to (\ref{eq:mt}), equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
   \begin{equation}\label{eq:d1}
@@
 \end{equation}
-Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
+Integrating the above equation from the data in front of a wave to the data behind the wave and performing some simple algebraic manipulations, one can get
 \begin{equation}\label{eq:rhosxx}
@@
   For  a  system without molecular diffusion, there is no materials convecting  across the contact wave or interface, so the velocities on two sides of  the discontinuity are always equal. % .
-  This can also be verified by the eigenvectors  in Eq.(\ref{eq:eiv}) and  Eq.(\ref{eq:eivp}).
+  This can also be verified by eigenvectors in Eq.(\ref{eq:eiv}) and  Eq.(\ref{eq:eivp}).
 
@@
 \end{equation}
-From the above equations, we can easily deduce that
+From above equations, we can easily deduce that
 \begin{equation}   \label{e23b}
@@
 
-By using the same methods for (\ref{eq:RH3}), (\ref{eq:RH3}) can be written as
+By using the same methods for (\ref{eq:u2u1}), (\ref{eq:RH3}) can be written as
 \begin{equation}
@@
   %\footnote{\href{https://nbviewer.jupyter.org/github/bfly123/Exact-Elastic-plastic-Riemann-Solver-/blob/master/\%20CharacteristicForPlasticStateAfterYielding.ipynb\#}{Code site link}}}
- The motion equations of (\ref{eq:1dp}) can be written as
+ Motion equations of (\ref{eq:1dp}) can be written as
 \begin{equation}
@@
 
-The eigenvalues of $\mathbf{J}_p(\mathbf{Q})$ are given as
+Eigenvalues of $\mathbf{J}_p(\mathbf{Q})$ are given as
 $$\lambda_1 = u,\quad \lambda_2 = u-c_p, \quad \lambda_3 = u+c_p,$$
@@
 Now we consider the constructing details of the exact  Riemann  solver.
-For  the Riemann problem in Section \ref{sec:riemann}, there are  $6\times 6$ possible  cases in the Riemann solution with different wave structures.
+For  the Riemann problem in Section \ref{sec:Riemann}, there are  $6\times 6$ possible  cases in the Riemann solution with different wave structures.
 The left six cases are  shown in Fig.\ref{fig:cases}.
@@
   %So, given densities in unknown regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$, the Riemann problem is solved.
-From Section  \ref{sec:Riemann}, we can find that all variables can be formulated in terms of density. So we define equations
+From Section  \ref{sec:Riemann}, we can find that all variables can be formulated in terms of the  density. So we define equations
 \begin{equation}
@@
 
-	Given $\rho _{L(k)}^*$ and a  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
-In this procedure for solving this Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
+	Given $\rho _{L(k)}^*$ and  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the method introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+In the  procedure for solving the  Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
 
@@
 
-  After determining the structure case, we need  to solve the Cauchy stresses and the velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
+  After determining the structure case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
 
@@
 \end{equation}
-where $\Delta \rho$ is a small quantity, we define
+where $\Delta \rho$ is a small quantity, we define it as
 \begin{equation}
@@
 $ (\rho_0, a_0, \Gamma_0, s, \mu)_{\text{Al}} =(8930 \text{kg}/\text{m}^3, 3940 \text{m}/\text{s},2, 1.49, 2.76 ,2.76\times 10^{10} \text{Pa} )$ and   $(\rho_0, a_0, \Gamma_0, s, \mu)_{\text{copper}} =(2785 \text{kg}/\text{m}^3, 5328 \text{m}/\text{s},2, 1.338,4.5\times 10^{10}\text{Pa})$, respectively.
+The yielding strengths are $Y_{0,\text{Al}} = 3\times 10^8 \text{Pa}$ and   $Y_{0,\text{Copper}} = 9\times 10^7 \text{Pa}$.
 The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.
@@
 even when it is in the plastic state at the beginning, after a rarefaction wave, the material will return into an elastic state and then may change into the  plastic by an  expandation yielding process.
-This is shown in Fig.\ref{fig:case20} both by the numerical and theoretical results, the material truely change from plastic state to elastic then to plastic state again.
-The initial conditions are
+Considering an initial condition as
+
 \begin{equation}
@@
 \end{equation}
+
+The results show in Fig.\ref{fig:case20} both by the numerical and theoretical results, the material truely can  change from plastic state to elastic then to plastic state again.
+However, if we do not consider the plastic to elastic process, we will get a wrong result  as the red line shows.
 \begin{figure}
@@
 	\item the plastic wave is always faster than the elastic wave for the reason of the sonic speed jump.
-
+	\item Both the changing from elastic to plastic and the  converse changing from plastic to elastic may exist in the Riemann problem.
 	  \item There are only thirty-six possible cases of the structrues in the Riemann problem.
-	\item All the variables after the wave can be written as functions of the density theoretically.
 	\end{enumerate}
-	  Then, based on the analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately.
+	  Then, based on the analysis and the results above,  exact Riemann solvers are  constructed for both the Riemann problem  and the half Riemann problem, separately.
 Tested by  a large number of examples, the exact Riemann solver is reasonable and matching  well with the numerical method for both  single material problems and multi-material Riemann problems.
@@
 
-  \section{Gauss-Legendre  quadrature}
-  In this paper, we use Gauss-Legendre quadrature to  take  numerical integrations. 
-For a function $f(x)$,  the intergration from $-1$ to $1$ is given as
+  \section{Numerical intergration for the rarefaction wave}
+  There are two integrations in  functions $p(\rho)$ and $u(\rho)$ in the rarefaction wave, for example,  in the equations (\ref{rerpp}) and (\ref{rerpu}).
+In this paper, we use  a seventh-order (with 4 integrating points) Gauss-Legendre quadrature to  take  numerical integrations.
+For a function $g(x)$,  the Gauss-Legendre intergration from $-1$ to $1$ is given as
 $$ 
-\int_{-1}^1 f(x)dx \approx \sum_{i=0}^n \omega_i f(x_i),
+\int_{-1}^1 g(x)dx \approx \sum_{i=1}^n \omega_i g(x_i),
 $$
 $\omega_i$ is the weight, and $x_i$ is the integrating point.
-For different orders they are listed in Table \ref{tab:coe}.
-
-\subsection{Change of interval}
-An integral over  $[x_0,x_1]$ must be changed into an integral over $[−1, 1]$ before applying the Gaussian quadrature rule. This change of interval can be done in the following way:
-$$ \int_{x_0}^{x_1}f(x) dx= \frac{x_1-x_0}{2}\int_{-1}^{1} f(\frac{x_1-x_0}{2}x+\frac{x_0+x_1}{2})dx.
+For seventh-order,  integrating points  and  corresponding weights are
+
+$$x_1, \ x_2 =\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}} \quad (\omega_1, \  \omega_2 =\frac{18+\sqrt{30}}{36} ), $$
+$$x_3, \ x_4 =\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}} \quad (\omega_1, \  \omega_2 =\frac{18-\sqrt{30}}{36} ). $$
+
+Then for a function over $[\rho_0, \rho]$, this change of  interval can be done  in the following way:
+
+$$ \int_{\rho_0}^{\rho}g(x) dx= \frac{\rho-\rho_0}{2}\int_{-1}^{1} g(\frac{\rho-\rho_0}{2}x+\frac{\rho_0+\rho}{2})dx.
  $$
- \begin{table}[htp]\label{tab:coe}
-  \centering
-  \caption{Coefficiences for Guass-Legendere quadrature}
-  \begin{tabular}{cccc}
-	\toprule
-	Number of points, $n$ &  Order & Points, $x_i$ & Weights, $\omega_i$ \\
-	\midrule
-	1 & 1  & 0 & 2 \\
-	\hline
-	2 & 3  & $\pm \frac{1}{\sqrt{3}}$ & 1 \\
-	\hline
-	\multirow{2}{*}{3} &\multirow{2}{*}{3} & 0  & $\frac{8}{9}$ \\
-	\cline{3-4}
-	& & $\pm\sqrt{\frac{3}{5}}$ & $\frac{5}{9} $\\
-	\hline
-	\multirow{2}{*}{\makecell{4}} & \multirow{2}{*}{7}  & $\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18+\sqrt{30}}{36}$ \\
-	\cline{3-4}
-  &  &  $\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18-\sqrt{30}}{36}$ \\
-  \bottomrule
-\end{tabular}
-\end{table}
+
+ \emph{\textbf{Integrating of $p(\rho)$}}  Taking Equation (\ref{rerpp}) as an example, 
+ \begin{equation} \label{eq:app}
+  p(\rho) \approx
+  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}} \text{Intg}_1, %\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
+\end{equation}
+where
+$$\text{Intg}_1 = \frac{\rho - \rho_{L(R)}}{2} \sum_{n=1}^4 \omega_i f_2(\rho_i) e^{\lambda/\rho_i},$$
+
+and $\rho_i =  \frac{\rho-\rho_{L(R)}}{2}x_i+\frac{\rho_{L(R)}+\rho}{2} $.
+
+\emph{\textbf{Integrating of $u(\rho)$}}  Taking Equation (\ref{rerpu}) as an example, if the wave is on the left side
+
+$$u(\rho) = u_L - \int_{\rho_L}^{\rho} \frac{c_e(x)}{x} dx. $$
+
+The numerical intergration of $u(\rho)$ is given as
+\begin{equation}
+  u(\rho) \approx u_L - \text{Intg}_2
+\end{equation}
+where 
+$$\text{Intg}_2  =  \frac{\rho - \rho_{L(R)}}{2} \sum_{n=1}^4 \omega_i \frac{c_e(\rho_i)}{\rho_i}, $$
+
+Different from (\ref{eq:app}), the sonic speed $c_e(\rho_i)$ is dependent on $p(\rho_i)$ as
+
+\begin{equation}
+  c_e(\rho_i) =
+  \sqrt{a_0^2 \frac{\partial f}{\partial \eta}(\rho_i) + \frac{p(\rho_i)}{\rho_i^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_i^2}\Gamma_0 s_{xx}(\rho_i) +\frac{4}{3}\frac{\mu}{\rho_i}}.
+% \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
+\end{equation}
+And we can take an  integration of interval $[\rho_{L(R)}, \rho_i]$ by the same process of Equation (\ref{eq:app}) to solve $p(\rho_i)$.
+
 \end{appendices}

### 2019-07-07 Manuscript2.tex
222

--- 2019-06-17 Manuscript revise 20190612.tex
@@
 \graphicspath{{TikzFig/}{Picture/}}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 %\usepackage{stackengine}
@@
 \begin{abstract}
-  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and  the von Mises' yielding condition is studied in this paper.
-Through a detailed analysis of the Jacobian matrix and relations across different type of waves,  an exact Riemann solver is constructed with totally thirty-six possible cases of structure.
-Some useful results are also obtained in the analysing, for example, the sonic speed experiences a significant jump when the material is yielding and the plastic wave is always faster than the elastic wave.
-More over, an exact Riemann solver is also deduced for the half Riemann problem.
-A lot of examples show that, the results taken by the exact Riemann solver are in good agreement with those computed by the mumerical method.
-
+In this paper, we present exact Riemann solvers for the Riemann problem and the half Riemann problem for one-dimensional multi-material elastic-plastic flows with the Mie-Gr\"uneisen equation of state(EOS), hypo-elastic constitutive model and  the von Mises' yielding condition.
+We first analyze the Jacobian matrixes in elastic and plastic states respectively, and then build relations between different variables across different type of waves.
+Based on these formulations, an exact Riemann solver is constructed with totally thirty-six possible cases of wave structure.
+Although Gao and Liu also developed the exact Riemann solver for 1D elastic plastic flows, but the EOS they used is very simple.
+Moreover, the exact Riemann solver developed by them may result in wrong solutions when the initial material is in the plastic state, which has been proven in one of our tests.
+Comparing with the exact Riemann solver developed by Gao and Liu, our exact Riemann solver uses the more complex EOS and overcomes these mistakes.
+A large number of tests prove the rightness of our exact Riemann solver.
+Moreover, an exact Riemann solver is also deduced for the half Riemann problem.
+Two examples show our half Riemann solver is also right.
 \end{abstract}
@@
 Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.
-The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may leads to more non-linear waves in the structure of Riemann solvers.
+The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structure of Riemann solvers.
 Moreover, in a general way, the equation of state(EOS) for solid materials is more complex than that for pure fluids, which directly increases the difficulty in solving the Riemann problem.
 
-For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{red}have been developed recently.
-However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
-But there are three shotcomings in their works.
-{\color{red}Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.
-Secondly, the states of elastic and plastic is using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave.
-Thirdly, only the changing from  elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}
+For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{blue}have been developed recently.
+However, for the exact Riemann solver, the research is relatively few, and focuses mainly on the problem with relatively simple constitutive models and relatively simple EOSs.
+%them are only considered with  simple constitutive models and simple EOSs.
+} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
+But there are two shortcomings in their works.
+{\color{blue}Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary in the elastic state; in the plastic state,  a linear  "stiffened-gas" EOS was used.
+Secondly, Gao and Liu thought that the material is always in the plastic state if an initial material reaches the elastic limit.
+In fact this thought sometimes may lead to wrong solution, which has been proved in our $5$th numerical example.
+In our Test 5, although the initial material reaches the elastic limit, but in the Riemann solver, the state of this material changes from the plastic state to the elastic one and to the plastic state again.
+This changes result in the last plastic state is different from the initial plastic state.
+Analyzing the formulation about the deviatoric stress $s_{xx} $ in (\ref{sxx1}) in terms of the density $\rho$, one can find, $\frac{\partial s_{xx}}{\partial \rho}<0$.
+So, if the material is compressed and $\rho$ increases, $s_{xx}$ will decrease; if the material is expanded and $\rho$ decreases, $s_{xx}$ will increase.
+So, according to the initial deviatoric stress and the compressed or expanded process of the material, the material can be into the different state, even if the initial material is in the plastic state.
+Without considering the von Mises yielding condition, all cases are showed as follows:
+\begin{enumerate}
+  \item if $s_{xx}=\frac{2}{3}Y^{0}$, initial material reaches the elastic limit.
+If the material is compressed so that $\rho_{plastic}>\rho^{*}>\rho$, one can get $|s_{xx}^{*}|<\frac{2}{3}Y^{0}$, the compressed material jumps from the plastic state to the elastic state.
+Here $\rho$ and $s_{xx}$ mean the initial density and deviatoric stress, respectively, $\rho_{plastic} = \rho e^{\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xx}}{4\mu}\right)}$, $( )^{*}$ denotes the variable $( )$ of the compressed or expanded material.
+  \item if $s_{xx}=\frac{2}{3}Y^{0}$ and the material is compressed greatly so that  $\rho_{plastic}<\rho^{*}$, $s_{xx}^{*}\leq - \frac{2}{3}Y^{0}$, the compressed material will jump from the positive plastic state to the negative plastic state.
+Here the positive or negative plastic state means $s_{xx}=\frac{2}{3}Y^{0}$ or $s_{xx}=-\frac{2}{3}Y^{0}$, respectively.
+  \item if $s_{xx}=\frac{2}{3}Y^{0}$ and  the material is expanded, $s_{xx}^{*}>\frac{2}{3}Y^{0}$, the material is still in the positive plastic state.
+  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and the material is expanded so that $\rho_{plastic}<\rho^{*}<\rho$, one can get $|s_{xx}^{*}|<\frac{2}{3}Y^{0}$, the expanded material jumps from the plastic state to the elastic state.
+  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and the material is expanded greatly so that  $\rho_{plastic}>\rho^{*}$, $s_{xx}^{*}\geq  \frac{2}{3}Y^{0}$, the expanded material will jump from the negative plastic state to the  positive plastic state.
+  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and  the material is compressed, $s_{xx}^{*}<-\frac{2}{3}Y^{0}$, the material is still in the negative plastic state.
+\end{enumerate}
+
+ From the above analysis we can find that the material can not always be in the plastic state even if the initial material reaches the elastic limit.
+We need perform detailed analysis according to the initial deviatoric streses and the compressing or expanding process.}
+%in their paper, the states of elastic and plastic are using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave.Thirdly,
+%only the changing from elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}
 
@@
 So there are thirty-six possible cases of the wave structures in the Riemann solver.
-{\color{red} Both the  changing from elastic to plastic and  the converse changing from plastic to elastic are considered.}
+\textcolor[rgb]{0.00,0.00,1.00}{Of course, during determining the case of the wave structure, one important point is to consider the change of the elastic or plastic state even if the initial material is in the plastic state.}
+%{\color{red} Both the  changing from elastic to plastic and  the converse changing from plastic to elastic are considered.}
+
 %For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 	\label{fig:subfigure:a}
-  \includegraphics[width=5cm]{Tikz-figure0.eps}}
+ % \includegraphics[width=5cm]{Tikz-figure0.eps}
+ }
   \subfigure[Plastic rarefaction wave ($R^{P}$)]{
 	\label{fig:subfigure:b}
-  \includegraphics[width=5cm]{Tikz-figure1.eps}}
+%  \includegraphics[width=5cm]{Tikz-figure1.eps}
+}
   \subfigure[Both elastic and plastic rarefaction waves ($R^{E}R^{P}$)] {
 	\label{fig:subfigure:c}
-  \includegraphics[width=5cm]{Tikz-figure2.eps}}
+%  \includegraphics[width=5cm]{Tikz-figure2.eps}
+}
   \subfigure[ Elastic shock wave ($S^{E}$)]{
 	\label{fig:subfigure:d}
-  \includegraphics[width=5cm]{Tikz-figure3.eps}}
+%  \includegraphics[width=5cm]{Tikz-figure3.eps}
+}
   \subfigure[Plastic shock wave ($R^{P}$) ]{
 	\label{fig:subfigure:e}
-  \includegraphics[width=5cm]{Tikz-figure4.eps}}
+%  \includegraphics[width=5cm]{Tikz-figure4.eps}
+}
   \subfigure[Both elastic and plastic shock waves ($S^{E}S^{P}$)]{
 	\label{fig:subfigure:f}
-	\includegraphics[width=5cm]{Tikz-figure5.eps}}
+%	\includegraphics[width=5cm]{Tikz-figure5.eps}
+}
   \caption{The possible cases of Riemann solution structures in the left side.}
@@
   \centering
-  \includegraphics[width= 10cm] {Tikz-figure6.eps}
+%  \includegraphics[width= 10cm] {Tikz-figure6.eps}
   \caption{A flow chat of the Newton iteration process.}
@@
 
-\subsection{States in  middle regions ($\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$) }
+\subsection{Evaluating states in  middle regions ($\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$) }
 
@@
 \begin{equation}\label{rerpp}
-  p(\rho)=
-	  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx, %\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
+  \tilde{p}_{L(R)} =
+	  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\tilde{\rho}_{L(R)}}} +e^{-\frac{\lambda}{\tilde{\rho}_{L(R)}}}\int_{\rho_{L(R)}}^{\tilde{\rho}_{L(R)}} f_2(x) e^{\frac{\lambda}{x}}dx, %\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
 \end{equation}
 where
-\begin{equation}
+\begin{equation*}
   \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}, \ s_{xx}(\rho) =	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}.
-\end{equation}
+\end{equation*}
 
@@
 \begin{equation} \label{rerpu}
-  u(\rho) =\left\{ \begin{aligned}
-	&u_L - \int_{\rho_L}^{\rho} \frac{c_e(x)}{x} dx \quad  & \text{for the  left-going rarefaction wave}
+  \tilde{u}_{L(R)} =\left\{ \begin{aligned}
+	&u_L - \int_{\rho_L}^{\tilde{\rho}_{L(R)}} \frac{c_e(x)}{x} dx \quad  & \text{for the  left-going rarefaction wave}
  , \\
- &u_R + \int_{\rho_R}^{\rho} \frac{c_e(x)}{x} dx \quad &  \text{for the right-going rarefaction wave} ,
+ &u_R + \int_{\rho_R}^{\tilde{\rho}_{L(R)}} \frac{c_e(x)}{x} dx \quad &  \text{for the right-going rarefaction wave} ,
 	\end{aligned}
@@
 where the sonic speed
-\begin{equation}
+\begin{equation*}
   c_e(\rho) =
@@
 % \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
-\end{equation}
-
-States in region $\tilde{\mathbf{Q}}_{L(R)}$ can be solved as
-\begin{equation}
+\end{equation*}
+
+%States in region $\tilde{\mathbf{Q}}_{L(R)}$ can be solved as
+%\begin{equation}
   % \tilde{s}_{xxL(R)} = s_{xx}(\rho_{L(R)}),\quad
-  \tilde{p}_{L(R)} = p(\rho_{L(R)}), \quad \tilde{u}_{L(R)} = u(\rho_{L(R)}).
-\end{equation}
-
-\textbf{Remark}:  In (\ref{rerpp}) and (\ref{rerpu}), there are two integral terms.
+%  \tilde{p}_{L(R)} = p(\rho_{L(R)}), \quad \tilde{u}_{L(R)} = u(\rho_{L(R)}).
+%\end{equation}
+
+\textbf{Remark 1}:  In (\ref{rerpp}) and (\ref{rerpu}), there are two integral terms.
 Obviously, because of the complexity of the EOS, we can not get the exact integral values.
@@
 
- \subsection{States in regions $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$}\label{sec:functions}
-
-\emph{\textbf{Case ($R^E$, $R^P$ and $R^ER^P$)}} For rarefaction wave case, by the equations of  (\ref{eq:rhosxx}) in elastic state  and  (\ref{eq:sxxp}) in plastic state, we can get
-the function of  deviatoric stress $s_{xx}$ as,
-\begin{equation}
-  s_{xx}(\rho) = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+s_{xxL(R)},  \quad &\text{case ($R^E$)},\\
-	  & \frac{2}{3}Y_0 ,  \quad &\text{case ($R^P$ and $R^ER^P$)}.
+ \subsection{Evaluating states in regions $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$}\label{sec:functions}
+
+\emph{\textbf{Rarefaction wave cases ($R^E$, $R^P$ and $R^ER^P$)}}
+
+For the three rarefaction wave cases, thanks to (\ref{eq:rhosxx}) and  (\ref{eq:sxxp}), $s_{xx}$ in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are
+\begin{equation*}
+  s_{xxL(R)}^* = \left\{\begin{aligned}
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\tilde{\rho}_{L(R)}}\right)+s_{xxL(R)}  \quad &\text{for case ($R^E$)},\\
+	  & \frac{2}{3}Y_0   \quad &\text{for cases ($R^P$ and $R^ER^P$)}.
   \end{aligned} \right.
-  \end{equation}
-Just like the process in (\ref{rerpp}) the pressure is given as,
-\begin{equation}
-  p(\rho)=\tilde{p}_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda}{x}}dx, \quad   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*
-\end{equation}
-And the  sonic speed,
-\begin{equation}
-  c(\rho) = \left\{ \begin{aligned}
-	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case ($R^E$)},\\
-	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case ($R^P$ and  $R^ER^P$)}.
-	\end{aligned}\right.
-\end{equation}
- By relations (\ref{eq:urhoEL}) and (\ref{eq:urhoER})
- we can get  the  function of  velocity as
-\begin{equation}
-  u(\rho) =\left\{ \begin{aligned}
-	  &\tilde{u}_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx,  \\
-	  &\tilde{u}_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \\
+  \end{equation*}
+%Just like the process in (\ref{rerpp}), the pressure is given as
+From (\ref{rerpp}), the pressure in the star region is
+\begin{equation}\label{rerpp2}
+  p_{L(R)}^*=\tilde{p}_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho_{L(R)}^*}}\int_{\tilde{\rho}_{L(R)}}^{\rho_{L(R)}^*} f_2(x) e^{\frac{\lambda}{x}}dx,
+ % \quad   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*
+\end{equation}
+where
+\begin{equation*}
+  \lambda = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda\frac{s_{xx}(\rho)}{\rho^2}, \ s_{xx}(\rho) =	 -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}.
+\end{equation*}
+
+ By Equations (\ref{eq:urhoEL}) and (\ref{eq:urhoER})  the velocity in regions $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ can be written as
+\begin{equation} \label{rerpp1}
+  u^*_{L(R)} =\left\{ \begin{aligned}
+	  &\tilde{u}_L - \int_{\rho_L}^{\rho^*_{L(R)}} \frac{c(x)}{x} dx,  \\
+	  &\tilde{u}_R + \int_{\rho_R}^{\rho^*_{L(R)}} \frac{c(x)}{x} dx, \\
 	\end{aligned}
@@
 \end{equation}
-By now, we can get the state in star regions as
-\begin{equation}
-  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
-\end{equation}
-
-\emph{\textbf{Shock wave cases ($S^E$, $S^P$ and $S^ES^P$}}
-For shock waves, the  deviatoric stress is given as
-\begin{equation}
-s_{xx}(\rho) = \left\{\begin{aligned}
-	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
-	\quad  &\text{case ($S^E$)},\\
-	& -\frac{2}{3}Y_0,   \quad
-	&\text{cases ( $S^P$ and $S^ES^P$)}.
+where
+\begin{equation*}
+  c(\rho) = \left\{ \begin{aligned}
+	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{for case ($R^E$)},\\
+	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{for cases ($R^P$ and  $R^ER^P$)}.
+	\end{aligned}\right.
+\end{equation*}
+
+\textbf{Remark 2}:  Just like \textbf{Remark 1}, we have to use numerical integral methods introduced in the Appendix A to evaluate the integral terms in (\ref{rerpp2}) and (\ref{rerpp1}).
+%because we can not get the exact integral values of the two integral terms.
+
+%Now, we can get the states in star regions as
+%\begin{equation}
+%  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
+%\end{equation}
+
+\emph{\textbf{Shock wave cases ($S^E$, $S^P$ and $S^ES^P$)}}
+
+For shock waves cases, the  deviatoric stresses in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are given as
+\begin{equation}
+s_{xxL(R)}^* = \left\{\begin{aligned}
+	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho_{L(R)}^*}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)}
+	\quad  &\text{for case ($S^E$)},\\
+	& -\frac{2}{3}Y_0   \quad
+	&\text{for cases ( $S^P$ and $S^ES^P$)}.
   \end{aligned} \right.
   \end{equation}
-By the equation of (\ref{eq:shocke}), the pressure is given as
-\begin{equation}
-  p(\rho)=
-  \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_{L(R)})-(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho))}{2tc_0-1},
-\end{equation}
-And the velocity is
-\begin{equation}
-  u(\rho)= \left\{ \begin{aligned}
-	&	\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t}}, \quad \text{For the left-going shock wave},\\
-	&  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t}}, \quad \text{For the right-going shock wave}.\\
+(\ref{eq:shocke}) gives direct expressions for the
+the pressure in the star region as
+\begin{equation}
+  p_{L(R)}^*=
+  \frac{2t\left(c_1f(\rho_{L(R)}^*/\rho_0)+\tilde{e}_{L(R)}\right)-\left(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho_{L(R)}^*)\right)}{2tc_0-1},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho^*_{L(R)} \tilde{\rho}_{L(R)}}{\rho^*_{L(R)}- \tilde{\rho}_{L(R)}}$.
+
+Thanks to (\ref{eq:shocku}), the velocities in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are
+\begin{equation}
+  u_{L(R)}^*= \left\{ \begin{aligned}
+	&	\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma_{L(R)}^*}{t}} \quad \text{for the left-going shock wave},\\
+	&  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma_{L(R)}^*}{t}} \quad \text{for the right-going shock wave},\\
   \end{aligned}
@@
 \end{equation}
-where $\sigma(\rho) = -p(\rho)+s_{xx}(\rho)$. And the state in  the star region is given as
-\begin{equation}
-  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
-\end{equation}
+where $\sigma_{L(R)}^* = -p_{L(R)}^*+s_{xxL(R)}^*$.
+%And the state in  the star region is given as
+%\begin{equation}
+%  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
+%\end{equation}
 
@@
 \section{Half Riemann problem and its solver}
-Some time we need to analyse a half Riemann problem with a given velocity or Cauchy stress.
-Shown in Fig.\ref{fig:half} , in these cases, we only need to solve states in one side.
+Sometimes we need to analyse a half Riemann problem with a given velocity or Cauchy stress.
+Shown in Fig.\ref{fig:half}, in these cases, we only need to solve states in one side.
 There are six possible cases just like them in Section \ref{sec:Riemann}.
+Here we will use the example shown in Fig.\ref{fig:half} to show how to solve the half Riemann problem.
 
@@
   \centering
-  \includegraphics[width= 10cm] {Tikz-figure8.eps}
+%  \includegraphics[width= 10cm] {Tikz-figure8.eps}
   \caption{Half Riemann problem  with a given left velocity or Cauchy stress..}
@@
 
-As we know the velocity $u^*$ or the Cauchy stress $\sigma ^*$, there is only one function need to be solved as
+As we know the velocity $u^*$ or the Cauchy stress $\sigma ^*$ on the left, there is only one equation need to be solved:
 \begin{equation}\label{eq:halfu}
@@
 \end{equation}
-Samilar to the process in Section (\ref{sec:iteration}), we have to use an iteration procedure to solve (\ref{exact1}) and
+Similar to the process in Section (\ref{sec:iteration}), we have to use an iteration procedure to solve (\ref{eq:halfu}) or (\ref{eq:halfs}) and
 the solving process is list in the following.
@@
 \begin{enumerate}[Step 1]
-  \item Determining the case of the wave structure:
-	By a given  $\rho _{(k)}^*$ in the $k$-th iteration step, we can use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
-In this procedure for solving this Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
-
-  \item Solving $f(\rho^*,\mathbf{Q}_R)$:
-
-	After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
-
-  \item Evaluating the derivative of  $f(\rho^*,\mathbf{Q}_R)$:
+  \item Determine the case of the wave structure:
+
+	Given the value of  $\rho _{(k)}^*$ in the $k$-th iteration step, use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+Here the subscript $(k)$ means the variable in the $k$-th  iteration step.
+
+  \item Solve $f(\rho^*,\mathbf{Q}_R)$:
+
+	After determining the structure case, evaluate the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$ and the details are given in Section \ref{sec:functions}.
+
+  \item Evaluate the derivative of  $f(\rho^*,\mathbf{Q}_R)$:
 
@@
 \end{equation}
-where $\Delta \rho$ is a small quatity, we define
-\begin{equation}
-  \Delta \rho = \frac{\rho_{(1)}^*}{100}.
-\end{equation}
-  \item  Evaluating  $\rho^*_{(k+1)}$:
-
-	By the Newton iteration equation, a new density can be updated as
-
-\begin{equation}
- \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho},
+where $\Delta \rho$ is a small quantity, here we set $\Delta \rho = \frac{\rho_{(1)}^*}{100}$.
+%\begin{equation}
+%  \Delta \rho = \frac{\rho_{(1)}^*}{100}.
+%\end{equation}
+
+  \item  Evaluate  $\rho^*_{(k+1)}$:
+
+	% By the Newton iteration equation,
+A new density can be updated by
+
+\begin{equation}
+ \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho}.
 \end{equation}
@@
 The iteration is convergent if
-The  convergence is meassured by
 \begin{equation}{\label{conv1}}
@@
 where
-\begin{equation}
+\begin{equation*}
 \text{CHA} = \text{max} \left[
-\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right].
-\end{equation}
-and the tolerance is taken as $\text{TOL} = 10^{-4}$.
-
-If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv1} ) is satisfied.
+\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right], \quad \text{TOL} = 10^{-4}.
+\end{equation*}
+%and the tolerance is taken as $\text{TOL} = 10^{-4}$.
+
+If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv1}) is satisfied.
 \end{enumerate}
 \textbf{Iteration end.}
+
 \section{Numerical  tests }
-In this section, by choosing suitable initial conditions, we will solve the Riemann problem with several different structure cases in the solution.
-Numerical results by the method  in \cite{liumulti} is used to verified the correctness of the exact solution.
-In the following tests, the materials are taken as  aluminium and copper.
-The parameters for the EOS and constitutive model for aluminum and copper  are
+In this section, by choosing different initial conditions, we will solve different Riemann problems with several different wave structures in the solutions.
+In order to verify the correctness of our exact Riemann solver, we use a third-order numerical scheme for 1D elastic-plastic flows introduced in \cite{liumulti} to evaluate these Riemann problems and compare numerical results with our exact solution.
+
+In the following tests, the materials are taken as  aluminium and copper. The parameters for the EOS and constitutive model for aluminum and copper  are
 $ (\rho_0, a_0, \Gamma_0, s, \mu)_{\text{Al}} =(8930 \text{kg}/\text{m}^3, 3940 \text{m}/\text{s},2, 1.49, 2.76 ,2.76\times 10^{10} \text{Pa} )$ and   $(\rho_0, a_0, \Gamma_0, s, \mu)_{\text{copper}} =(2785 \text{kg}/\text{m}^3, 5328 \text{m}/\text{s},2, 1.338,4.5\times 10^{10}\text{Pa})$, respectively.
+The yielding strengths of the two materials are $Y_{0,\text{Al}} = 3\times 10^8 \text{Pa}$ and   $Y_{0,\text{Copper}} = 9\times 10^7 \text{Pa}$, respectively.
 The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.
+Otherwise, in the initial condition, "L" and "R" mean $x<0.5m$ and $x>0.5m$, respectively.
 
 \subsection{Test 1}
-In this case, the material is yielding at both sides, so the solution structure has three wave with two plastic waves and one contact.
+In this case, the material is yielding at both sides, so the solution structure has three wave with two plastic shock waves and one contact.
 The initial condition is
@@
 It can be seen that the exact solution matches the numerical results very well in Fig.\ref{fig:case1}.
-\begin{figure}
+\begin{figure}{ht}
   \centering
 
-\includegraphics[width= 8cm] {case1rho.pdf}
-\includegraphics[width= 8cm] {case1u.pdf}
-\includegraphics[width= 8cm] {case1p.pdf}
-\includegraphics[width= 8cm] {case1sigma.pdf}
-
-    \caption{Comparison resutls for Test 1 with the structrures of $S^P|S^P$.  }
+\includegraphics[width= 7cm] {case1rho.pdf}
+\includegraphics[width= 7cm] {case1u.pdf}
+\includegraphics[width= 7cm] {case1p.pdf}
+\includegraphics[width= 7cm] {case1sigma.pdf}
+
+    \caption{Comparison results for Test 1 with the structures of $S^P|S^P$.  }
   \label{fig:case1}
@@
 \subsection{Test 2}
-Next, we consider a case with yielding process at both sides, so the result has five waves. The initial condition is
+Here we consider a case with yielding process at both sides, so there are five waves in the wave structure of this Riemann problem. The initial condition is
 \begin{equation}
@@
 \end{equation}
-Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, besides the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
-\begin{figure}
+Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, except the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
+\begin{figure}{ht}
   \centering
-  \includegraphics[width= 8cm] {case2rho.pdf}
-  \includegraphics[width= 8cm] {case2u.pdf}
-  \includegraphics[width= 8cm] {case2p.pdf}
-  \includegraphics[width= 8cm] {case2sxx.pdf}
-  \caption{Comparison resutls for Test 2 with the structrures of $S^ES^P|S^PS^E$.  }
+  \includegraphics[width= 7cm] {case2rho.pdf}
+  \includegraphics[width= 7cm] {case2u.pdf}
+  \includegraphics[width= 7cm] {case2p.pdf}
+  \includegraphics[width= 7cm] {case2sxx.pdf}
+  \caption{Comparison results for Test 2 with the structures of $S^ES^P|S^PS^E$.  }
   \label{fig:case2}
@@
 \subsection{Test 3}
-In this example, we test the elastic rarefaction waves case. In the structrues there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
+In this example, we test the case with two elastic rarefaction waves. In the wave structure there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
 \begin{equation}
@@
 %j\section*{Conclusions}
-\begin{figure}
+\begin{figure}{ht}
   \centering
 
-  \includegraphics[width= 8cm] {case4rho.pdf}
-  \includegraphics[width= 8cm] {case4u.pdf}
-  \includegraphics[width= 8cm] {case4p.pdf}
-  \includegraphics[width= 8cm] {case4sxx.pdf}
-
-    \caption{Comparison resutls for Test 3 with the structrures of $R^E|R^E$.  }
+  \includegraphics[width= 7cm] {case4rho.pdf}
+  \includegraphics[width= 7cm] {case4u.pdf}
+  \includegraphics[width= 7cm] {case4p.pdf}
+  \includegraphics[width= 7cm] {case4sxx.pdf}
+
+    \caption{Comparison results for Test 3 with the wave structures of $R^E|R^E$.  }
   \label{fig:case3}
@@
 \subsection{Test 4}
-Then we test another example with both elastic and plastic rarefaction  waves on both sides. The initial condition is
+In this test we test the example with both elastic and plastic rarefaction waves on both sides of contact wave. The initial condition is
 \begin{equation}
@@
 
-\begin{figure}
+\begin{figure}{ht}
   \centering
 
- \includegraphics[width= 8cm] {case3rho.pdf}
-  \includegraphics[width= 8cm] {case3u.pdf}
-  \includegraphics[width= 8cm] {case3p.pdf}
-  \includegraphics[width= 8cm] {case3sxx.pdf}
-
-    \caption{Comparison resutls for Test 4 with the structrures of $R^ER^P|R^PR^E$.  }
+ \includegraphics[width= 7cm] {case3rho.pdf}
+  \includegraphics[width= 7cm] {case3u.pdf}
+  \includegraphics[width= 7cm] {case3p.pdf}
+  \includegraphics[width= 7cm] {case3sxx.pdf}
+
+    \caption{Comparison results for Test 4 with the wave structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case4}
 \end{figure}
+
 \subsection{Test 5}
-In Test 4, the material is  yielding from a elastic state to a plastic state through  an elastic rarefaction wave, just as we say in the introduction, 
-even when it is in the plastic state at the beginning, after a rarefaction wave, the material will return into an elastic state and then may change into the  plastic by an  expandation yielding process.
-This is shown in Fig.\ref{fig:case20} both by the numerical and theoretical results, the material truely change from plastic state to elastic then to plastic state again.
-The initial conditions are
+The initial condition of this Riemann problem is
 \begin{equation}
@@
 \end{equation}
-\begin{figure}
+From the initial condition, at the beginning, the material is in the negative plastic state (i.e.
+$s_{xxL(R)}=-\frac{2}{3}{Y}^{0}$).
+If using the thought introduced by Gao and Liu, the material will be always in the negative plastic state.
+Exact solutions based on this thought are denoted by blue solid lines in Fig.\ref{fig:case20}.
+Obviously, from Fig.\ref{fig:case20}, one can find that the exact solutions denoted by blue solid lines are wrong because they do not match the numerical results very seriously.
+On the contrary, according to the analysis introduced in Section "Introduction", we can get the right exact solutions which match the numerical solutions very well in Fig.\ref{fig:case20} .
+This shows our analysis in  Section "Introduction" is right.
+ %In the previous test, the material is  yielding from the elastic state to the plastic state through the elastic rarefaction wave.
+In this test, we will show, even if the material is in the negative plastic state at the beginning (i.e.
+$s_{xxL(R)}=-\frac{2}{3}{Y}^{0}$), after being expanded, the material can be into an elastic state or the positive plastic state, just as we analyze in the introduction.
+Solving this Rieman problem.
+This is proved in Fig.\ref{fig:case20} not only by the numerical and theoretical results, the material truly change from a plastic state to an elastic then to a plastic state again.
+However, if we do not consider the plastic to elastic process there maybe significant wrong in the numerical results as the red line shows.
+\begin{figure}{ht}
   \centering
- \includegraphics[width= 8cm] {case20rho.pdf}
-  \includegraphics[width= 8cm] {case20u.pdf}
-  \includegraphics[width= 8cm] {case20p.pdf}
-  \includegraphics[width= 8cm] {case20sxx.pdf}
-    \caption{Comparison resutls for Test 5 with the structrures of $R^ER^P|R^PR^E$.  }
+ %\includegraphics[width= 8cm] {case20rho.pdf}
+ % \includegraphics[width= 8cm] {case20u.pdf}
+ % \includegraphics[width= 8cm] {case20p.pdf}
+ % \includegraphics[width= 8cm] {case20sxx.pdf}
+    \caption{Comparison results for Test 5 with the structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case20}
 \end{figure}
+
 \subsection{Test 6}
-All the above five tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
+All the above five tests have symmetrical wave  structures, here we will test an example with different structures on two sides: one plastic shock on the left side and both the elastic and plastic shocks on the right of one contact wave.
+The initial condition is given as
 \begin{equation}
@@
 \end{equation}
-In the Fig.\ref{fig:case5} shown in both the numerical and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.
-
-\begin{figure}
+The solutions of this test are shown in Fig.\ref{fig:case5}. From this figure, we can find the exact solutions match numerical solutions very well.
+%and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.
+
+\begin{figure}{ht}
   \centering
 
-  \includegraphics[width= 8cm] {case5rho.pdf}
-  \includegraphics[width= 8cm] {case5u.pdf}
-  \includegraphics[width= 8cm] {case5p.pdf}
-  \includegraphics[width= 8cm] {case5sxx.pdf}
+  \includegraphics[width= 7cm] {case5rho.pdf}
+  \includegraphics[width= 7cm] {case5u.pdf}
+  \includegraphics[width= 7cm] {case5p.pdf}
+  \includegraphics[width= 7cm] {case5sxx.pdf}
 
@@
 \subsection{Test 7}
-In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves producted into the higher pressure side and shock waves generated into the lower pressure side.
+In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves produced into the higher pressure side and shock waves generated into the lower pressure side.
 The initial condition is given as
@@
 Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side.
-\begin{figure}
+\begin{figure}{ht}
   \centering
 
-  \includegraphics[width= 8cm] {case9rho.pdf}
-  \includegraphics[width= 8cm] {case9u.pdf}
-  \includegraphics[width= 8cm] {case9p.pdf}
-  \includegraphics[width= 8cm] {case9sxx.pdf}
+  \includegraphics[width= 7cm] {case9rho.pdf}
+  \includegraphics[width= 7cm] {case9u.pdf}
+  \includegraphics[width= 7cm] {case9p.pdf}
+  \includegraphics[width= 7cm] {case9sxx.pdf}
 
@@
 \subsection{Test 8}
-Now we will consider two multi-material tests with different materials on different sides.
-In this test, on the left side, a lighter material of aluminum with a velocity impacts to a heavier material of copper.
+Now we will consider two multi-material tests with different materials on both sides.
+In this test, on the left side, a lighter material of aluminum with a velocity impact to a heavier material of Copper.
 The initial condition is given as
@@
 Show in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface.
-The exact Riemann solver can solve the Riemann problem with multi-materials very well comparing to the MHLLCEP approximate solver.
-
-\begin{figure}
+Comparing to the numerical results of the scheme with MHLLCEP approximate solver, we can find that our exact Riemann solver can solve the Riemann problem with multi-materials very well.
+\begin{figure}{ht}
   \centering
-  \includegraphics[width= 8cm] {case6rho.pdf}
-  \includegraphics[width= 8cm] {case6u.pdf}
-  \includegraphics[width= 8cm] {case6p.pdf}
-  \includegraphics[width= 8cm] {case6sigma.pdf}
-
-    \caption{Comparison results for Test 8 with structrures of $R^ER^P|R^PR^E$.  }
+  \includegraphics[width= 7cm] {case6rho.pdf}
+  \includegraphics[width= 7cm] {case6u.pdf}
+  \includegraphics[width= 7cm] {case6p.pdf}
+  \includegraphics[width= 7cm] {case6sigma.pdf}
+
+    \caption{Comparison results for Test 8 with structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case7}
@@
 \subsection{Test 9}
-At last, we test another multi-materials case, in this test the initial condtion is given as
+Here we test another multi-materials case, in this test the initial condition is given as
 \begin{equation}
@@
 \end{equation}
-Shown in Fig.\ref{fig:case8}, there are two rarefaction waves on the left side and two shocks on the right side, there is a discontinuity of pressure on the interface, and the Cauchy stress is continuous, which  meets with the theoretical analysis.
-\begin{figure}
+Shown in Fig.\ref{fig:case8}, there are two rarefaction waves on the left side and two shocks on the right side, there is the discontinuity of pressure on the interface, and the Cauchy stress is continuous, which  satisfies the theoretical analysis.
+\begin{figure}{ht}
   \centering
-  \includegraphics[width= 8cm] {case8rho.pdf}
-  \includegraphics[width= 8cm] {case8u.pdf}
-  \includegraphics[width= 8cm] {case8p.pdf}
-  \includegraphics[width= 8cm] {case8sigma.pdf}
-
-    \caption{Comparison results for Test 9 with the structrures of $R^ER^P|S^ES^P$.  }
+  \includegraphics[width= 7cm] {case8rho.pdf}
+  \includegraphics[width= 7cm] {case8u.pdf}
+  \includegraphics[width= 7cm] {case8p.pdf}
+  \includegraphics[width= 7cm] {case8sigma.pdf}
+
+    \caption{Comparison results for Test 9 with the structures of $R^ER^P|S^ES^P$.  }
   \label{fig:case8}
 \end{figure}
+
 \subsection{Test 10}
-Then we give two tests of  half Riemann problem, the first is with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
+This test is a half Riemann problem with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
 \begin{equation}
@@
 \end{equation}
-In Fig.\ref{fig:case9}, comparason results are given by the exact half Riemann solver and the numerical method.
-We can see that the exact solver  can resolve both the elastic and plastic shock waves well.
-\begin{figure}
+In Fig.\ref{fig:case9}, comparison results are given by the exact half Riemann solver and the numerical method.
+We can see that the exact solver can resolve both the elastic and plastic shock waves very well.
+\begin{figure}{ht}
   \centering
-  \includegraphics[width= 8cm] {case10rho.pdf}
-  \includegraphics[width= 8cm] {case10u.pdf}
-  \includegraphics[width= 8cm] {case10p.pdf}
-  \includegraphics[width= 8cm] {case10sxx.pdf}
-
-    \caption{Comparison results for Test 10 with the structrures of $S^ES^P$.  }
+  \includegraphics[width= 7cm] {case10rho.pdf}
+  \includegraphics[width= 7cm] {case10u.pdf}
+  \includegraphics[width= 7cm] {case10p.pdf}
+  \includegraphics[width= 7cm] {case10sxx.pdf}
+
+    \caption{Comparison results for Test 10 with the structures of $S^ES^P$.  }
   \label{fig:case9}
 \end{figure}
+
 \subsection{Test 11}
@@
 \end{equation}
-In Fig.\ref{fig:case10}, we give the results computed by the exact Riemann solver and the numerical simulation, shown in it, the exact solver can resolve the elastic and plastic rarefaction waves well.
-\begin{figure}
+In Fig.\ref{fig:case10}, we give the results computed by the exact Riemann solver and the numerical simulation.
+From this figure one can see, the exact solver can resolve the elastic and plastic rarefaction waves well.
+\begin{figure}{ht}
   \centering
- \includegraphics[width= 8cm] {case11rho.pdf}
-  \includegraphics[width= 8cm] {case11u.pdf}
-  \includegraphics[width= 8cm] {case11p.pdf}
-  \includegraphics[width= 8cm] {case11sigma.pdf}
-    \caption{Comparison results for Test 11 with the structrures of $R^ER^P$.  }
+ \includegraphics[width= 7cm] {case11rho.pdf}
+  \includegraphics[width= 7cm] {case11u.pdf}
+  \includegraphics[width= 7cm] {case11p.pdf}
+  \includegraphics[width= 7cm] {case11sigma.pdf}
+    \caption{Comparison results for Test 11 with the structures of $R^ER^P$.  }
   \label{fig:case10}
 \end{figure}
+
 \section{Results}
@@
 	  \item There are only thirty-six possible cases of the structrues in the Riemann problem.
+
 	\item All the variables after the wave can be written as functions of the density theoretically.
+
+	\item if the initial material is in the negative plastic state, after being expanded, the material may be into the elastic state or the positive plastic state.
+
+	\item if the initial material is in the positive plastic state, after being compressed, the material may be into the elastic state or the negative plastic state.
 	\end{enumerate}
-	  Then, based on the analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately.
-Tested by  a large number of examples, the exact Riemann solver is reasonable and matching  well with the numerical method for both  single material problems and multi-material Riemann problems.
+	  Then, based on the above analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately.
+Tested by  a large number of examples, the exact Riemann solver is reasonable and  its solutions  are matching well with the numerical results for both  single material problems and multi-material Riemann problems.
 
@@
 
-  \renewcommand{\appendixname}{Appendix~\Alph{section}}
-
-  \section{Gauss-Legendre  quadrature}
-  In this paper, we use Gauss-Legendre quadrature to  take  numerical integrations. 
-For a function $f(x)$,  the intergration from $-1$ to $1$ is given as
+  \renewcommand{\appendixname}{Appendix\Alph{section}}
+
+  \section{Numerical intergration for the rarefaction wave}
+  There are two integrations in  functions $p(\rho)$ and $u(\rho)$ in the rarefaction wave, for example,  in the equations (\ref{rerpp}) and (\ref{rerpu}).
+In this paper, we use  a seventh-order (with 4 integrating points) Gaussian quadrature to make numerical integrations.
+For a function $g(x)$,  the Gaussian integration from $-1$ to $1$ is given as
 $$
-\int_{-1}^1 f(x)dx \approx \sum_{i=0}^n \omega_i f(x_i),
+\int_{-1}^1 g(x)dx \approx \sum_{i=1}^n \omega_i g(x_i),
 $$
 $\omega_i$ is the weight, and $x_i$ is the integrating point.
-For different orders they are listed in Table \ref{tab:coe}.
-
-\subsection{Change of interval}
-An integral over  $[x_0,x_1]$ must be changed into an integral over $[−1, 1]$ before applying the Gaussian quadrature rule. This change of interval can be done in the following way:
-$$ \int_{x_0}^{x_1}f(x) dx= \frac{x_1-x_0}{2}\int_{-1}^{1} f(\frac{x_1-x_0}{2}x+\frac{x_0+x_1}{2})dx.
+For seventh-order,  integrating points  and  corresponding weights are
+
+$$x_1, \ x_2 =\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}} \quad \left(\omega_1, \  \omega_2 =\frac{18+\sqrt{30}}{36} \right), $$
+$$x_3, \ x_4 =\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}} \quad \left(\omega_3, \  \omega_4 =\frac{18-\sqrt{30}}{36} \right). $$
+
+Then for a function over $[\rho_0, \rho]$, this change of  interval can be done  in the following way:
+
 $$
- \begin{table}[htp]\label{tab:coe}
-  \centering
-  \caption{Coefficiences for Guass-Legendere quadrature}
-  \begin{tabular}{cccc}
-	\toprule
-	Number of points, $n$ &  Order & Points, $x_i$ & Weights, $\omega_i$ \\
-	\midrule
-	1 & 1  & 0 & 2 \\
-	\hline
-	2 & 3  & $\pm \frac{1}{\sqrt{3}}$ & 1 \\
-	\hline
-	\multirow{2}{*}{3} &\multirow{2}{*}{3} & 0  & $\frac{8}{9}$ \\
-	\cline{3-4}
-	& & $\pm\sqrt{\frac{3}{5}}$ & $\frac{5}{9} $\\
-	\hline
-	\multirow{2}{*}{\makecell{4}} & \multirow{2}{*}{7}  & $\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18+\sqrt{30}}{36}$ \\
-	\cline{3-4}
-  &  &  $\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}}$  & $\frac{18-\sqrt{30}}{36}$ \\
-  \bottomrule
-\end{tabular}
-\end{table}
+\int_{\rho_0}^{\rho}g(x) dx= \frac{\rho-\rho_0}{2}\int_{-1}^{1} g\left(\frac{\rho-\rho_0}{2}x+\frac{\rho_0+\rho}{2}\right)dx .
+ $$
+
+At last, we can get
+\begin{equation}\label{int1}
+  \int_{\rho_0}^{\rho}g(x) dx \approx \frac{\rho-\rho_0}{2}\sum_{i=1}^n \omega_i g\left(\frac{\rho-\rho_0}{2}x_{i}+\frac{\rho_0+\rho}{2}\right).
+\end{equation}
+
+ \emph{\textbf{Integrating of $p(\rho)$}}
+
+ Taking Equation (\ref{rerpp}) as an example,
+ \begin{equation} \label{eq:app}
+  p(\rho) \approx
+  p_{L(R)}e^{\frac{\lambda}{\rho_{L(R)}}-\frac{\lambda}{\rho}} +e^{-\frac{\lambda}{\rho}} \text{Intg}_1, %\quad  \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},
+\end{equation}
+where
+$$\text{Intg}_1 = \frac{\rho - \rho_{L(R)}}{2} \sum_{n=1}^4 \omega_i f_2(\rho_i) e^{\lambda/\rho_i},$$
+
+and $\rho_i =  \frac{\rho-\rho_{L(R)}}{2}x_i+\frac{\rho_{L(R)}+\rho}{2} $.
+
+Obviously, we can use (\ref{eq:app}) to evaluate all the values of $p(\rho_{i})$ on all Gaussian quadrature points.
+
+\emph{\textbf{Integrating of $u(\rho)$}}
+
+Taking Equation (\ref{rerpu}) as an example, if the wave is on the left side
+
+$$u(\rho) = u_L - \int_{\rho_L}^{\rho} \frac{c_e(x)}{x} dx. $$
+
+The numerical intergration of $u(\rho)$ is given as
+\begin{equation}
+  u(\rho) \approx u_L - \text{Intg}_2
+\end{equation}
+where
+$$\text{Intg}_2  =  \frac{\rho - \rho_{L(R)}}{2} \sum_{n=1}^4 \omega_i \frac{c_e(\rho_i)}{\rho_i}, $$
+
+Different from (\ref{eq:app}), the sonic speed $c_e(\rho_i)$ is dependent on $p(\rho_i)$:
+
+\begin{equation}
+  c_e(\rho_i) =
+  \sqrt{a_0^2 \frac{\partial f}{\partial \eta}\left(\frac{\rho_i}{\rho_0}\right) + \frac{p(\rho_i)}{\rho_i^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_i^2}\Gamma_0 s_{xx}(\rho_i) +\frac{4}{3}\frac{\mu}{\rho_i}}.
+% \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
+\end{equation}
+After finishing the evaluation of  $p(\rho_{i})$, we can evaluate $c_e(\rho_i)$ by using the same process as (\ref{eq:app}).
+
+%And we can take an  integration of interval $[\rho_{L(R)}, \rho_i]$ by the same process of Equation (\ref{eq:app}) to solve $p(\rho_i)$.
+
 \end{appendices}

### 2019-07-07 Manuscript revise 20190612.tex
33

@@
 \title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state}
-\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
+\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$}
 %\author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$, Jiequan Li $^{1}$}
@@
 \begin{abstract}
-  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and  the von Mises' yielding condition is studied in this paper.
-Through a detailed analysis of the Jacobian matrix and relations across different type of waves,  an exact Riemann solver is constructed with totally thirty-six possible cases of structure.
-Some useful results are also obtained in the analysing, for example, the sonic speed experiences a significant jump when the material is yielding and the plastic wave is always faster than the elastic wave.
-More over, an exact Riemann solver is also deduced for the half Riemann problem.
-A lot of examples show that, the results taken by the exact Riemann solver are in good agreement with those computed by the mumerical method.
-
+  In this paper, we present exact Riemann solvers for the Riemann problem and the half Riemann problem, respectively,  for one-dimensional multi-material elastic-plastic flows with the Mie-Gr\"uneisen equation of state(EOS), hypo-elastic constitutive model and  the von Mises' yielding condition.
+We first analyze the Jacobian matrixes in  both elastic and plastic states, and then build relations between different variables across different type of waves.
+Based on these formulations, an exact Riemann solver is constructed with totally thirty-six possible cases of wave structures.
+Although Gao and Liu\cite{gao20171d} also developed the exact Riemann solver for 1D elastic plastic flows, but the EOS they used is very simple.
+Moreover, the exact Riemann solver developed by them may result in wrong solutions when the initial material is in the plastic state, which has been proven in one of our tests.
+Comparing with the exact Riemann solver developed by Gao and Liu, our exact Riemann solver uses a more complex EOS and overcomes these mistakes.
+A large number of tests prove the rightness of our exact Riemann solver.
+Moreover, an exact Riemann solver is also deduced for the half Riemann problem and  its validity is tested  by two examples.
 \end{abstract}
@@
 
-In the development history of hydrodynamic numerical methods, the exact Riemann solver has played a very important role {\color{red}as} it not only can give a guide and reference to the construction of approximate Riemann solvers, but also can be used to determine {\color{red}the convergence and stability of numerical schemes}.
+In the development history of hydrodynamic numerical methods, the exact Riemann solver has played a very important role as it not only can give a guide and reference to the construction of approximate Riemann solvers, but also can be used to determine the convergence and stability of numerical schemes.
 However, building the exact Riemann solver for 1D elastic-plastic flows is not that easy.
 Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.
-The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may leads to more non-linear waves in the structure of Riemann solvers.
+The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structure of Riemann solvers.
 Moreover, in a general way, the equation of state(EOS) for solid materials is more complex than that for pure fluids, which directly increases the difficulty in solving the Riemann problem.
 
-For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti}  {\color{red}have been developed recently.
-However, for the exact Riemann solver, the research is relatively few, and them are only considered with  simple constitutive models and simple EOSs.} For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
-But there are three issues need to improve or overcome in their works.
-{\color{red}Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary; in the plastic state,  a linear  "stiffened-gas" EOS was used.
-Secondly, the states of elastic and plastic is using with very different equations systems and parameters, the seperation  deduces to more possible non-physical wave-structure cases in which the plastic wave  may run faster than the elastic wave.
-Thirdly, only the changing from  elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material  can also change to elastic states.}
+For the elastic-plastic flow with the hypo-elastic constitutive model and  the von Mises' yielding condition,  some approximate Riemann solvers\cite{gavrilyuk2008modelling,cheng2015high,cheng2016harten,liumulti} have been developed recently.
+However, for the exact Riemann solver, the research is relatively few, and focuses mainly on the problem with relatively simple constitutive models and relatively simple EOSs.
+%them are only considered with  simple constitutive models and simple EOSs.
+For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
+But there are two shortcomings in their works.
+Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary in the elastic state; in the plastic state,  a linear  "stiffened-gas" EOS was used.
+{ \color{red} Secondly,  unloading (for example, an expanding process to a compressed yielding material) and reloading processes are not considered in the construction  of their Riemann solvers.
+This may leads to wrong solutions as the unloading and reloading are very common in the real computing cases, shown in our $5$th numerical example.
+}
+In fact, according to the relations in the governing equations, even if the initial material reaches the elastic limit and in a plastic state, after an unloading process, the material may change back to an elastic state and then may re-change to a plastic state by a reloading process.
+
+%in their paper, the states of elastic and plastic are using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave.Thirdly,
+%only the changing from elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}
 
@@
 So there are thirty-six possible cases of the wave structures in the Riemann solver.
-{\color{red} Besides, both the changing from elastic to plastic and  the converse changing from plastic to elastic are considered in the Riemann problem.}
+Besides, both the changing from elastic to plastic (loading or reloading) and  the converse changing from plastic to elastic(unloading)  are considered in the Riemann problem.
 %For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 %\end{align}above relations also can be written as
-We transform the equations  to a frame of reference moving with the shock and the Rankine-Hugoniot Conditions give
+We transform the equations  to a frame of reference moving with the shock and the Rankine-Hugoniot conditions give
 \begin{align}
@@
 \noindent
-\textbf{Iteration begin:}
+\textbf{Iterations begin:}
 \begin{enumerate}[Step 1]
@@
 \noindent
-\textbf{Iteration end}
+\textbf{Iterations end}
 %\subsection{Pre-evaluation of densities}\label{sec:eva}
@@
 
-{\color{red}
 \begin{equation} \label{yield1}
@@
 \end{equation}
-}
-
-Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ''S'' and ''R'' mean the shock and rarefaction wave, respectively; superscript letters ''E'' and  ''P'' indicate the elastic or plastic state of a wave, respectively.
+
+Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ``$S$'' and ``$R$'' mean the shock and rarefaction wave, respectively; superscript letters ``$E$'' and  ``$P$'' indicate the elastic or plastic state of a wave, respectively.
 Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.
@@
 
-{\color{red}
 \begin{table}
@@
 \end{table}
-}
-
-\subsection{States in  middle regions ($\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$) }
+
+\subsection{Evaluating states in  middle regions ($\tilde{\mathbf{Q}}_{L}$ and   $\tilde{\mathbf{Q}}_{R}$) }
 
@@
 Using the methods introduced in  the Section (\ref{sec:rarefaction}), we can easily deduce the formulation of all unknown variables after the rarefaction wave.
-Here we do not show the details of deduction.
+Here we do not show the details of the  deduction.
 
@@
 \end{equation}
-By now, we can get the state in star regions as
-\begin{equation}
-  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
-\end{equation}
-
-\emph{\textbf{Shock wave cases ($S^E$, $S^P$ and $S^ES^P$}}
-For shock waves, the  deviatoric stress is given as
+where
+\begin{equation*}
+  c(\rho) = \left\{ \begin{aligned}
+	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{for case ($R^E$)},\\
+	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{for cases ($R^P$ and  $R^ER^P$)}.
+	\end{aligned}\right.
+\end{equation*}
+
+\textbf{Remark 2}:  Just like \textbf{Remark 1}, we have to use numerical integral methods introduced in the Appendix A to evaluate the integral terms in (\ref{rerpp2}) and (\ref{rerpp1}).
+%because we can not get the exact integral values of the two integral terms.
+
+%Now, we can get the states in star regions as
+%\begin{equation}
+%  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
+%\end{equation}
+
+\emph{\textbf{Shock wave cases ($S^E$, $S^P$ and $S^ES^P$)}}
+
+For shock waves cases, the  deviatoric stresses in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are given as
 \begin{equation}
@@
   \end{equation}
+(\ref{eq:shocke}) gives direct expressions for the
 By the equation of (\ref{eq:shocke}), the pressure is given as
 \begin{equation}
-  p(\rho)=
-  \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_{L(R)})-(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho))}{2tc_0-1},
-\end{equation}
-And the velocity is
-\begin{equation}
-  u(\rho)= \left\{ \begin{aligned}
-	&	\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t}}, \quad \text{For the left-going shock wave},\\
-	&  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t}}, \quad \text{For the right-going shock wave}.\\
+  p_{L(R)}^*=
+  \frac{2t\left(c_1f(\rho_{L(R)}^*/\rho_0)+\tilde{e}_{L(R)}\right)-\left(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho_{L(R)}^*)\right)}{2tc_0-1},
+\end{equation}
+where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho^*_{L(R)} \tilde{\rho}_{L(R)}}{\rho^*_{L(R)}- \tilde{\rho}_{L(R)}}$.
+
+Thanks to (\ref{eq:shocku}), the velocities in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are
+\begin{equation}
+  u_{L(R)}^*= \left\{ \begin{aligned}
+	&	\tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma_{L(R)}^*}{t}} \quad \text{for the left-going shock wave},\\
+	&  \tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma_{L(R)}^*}{t}} \quad \text{for the right-going shock wave},\\
   \end{aligned}
@@
   \includegraphics[width= 10cm] {Tikz-figure8.eps}
-  \caption{Half Riemann problem  with a given left velocity or Cauchy stress..}
+  \caption{Half Riemann problem  with a given left velocity or Cauchy stress.}
   \label{fig:half}
@@
 \end{equation}
-\textbf{Iteration begin:}
+\textbf{Iterations begin:}
 \begin{enumerate}[Step 1]
-  \item Determining the case of the wave structure:
-	By a given  $\rho _{(k)}^*$ in the $k$-th iteration step, we can use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
-In this procedure for solving this Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
-
-  \item Solving $f(\rho^*,\mathbf{Q}_R)$:
-
-	After determining the structure case, we need to solve the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$, this is  given in Section \ref{sec:functions}.
-
-  \item Evaluating the derivative of  $f(\rho^*,\mathbf{Q}_R)$:
+  \item Determine the case of the wave structure:
+
+	Given the value of  $\rho _{(k)}^*$ in the $k$-th iteration step, use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+Here the subscript $(k)$ means the variable in the $k$-th  iteration step.
+
+  \item Solve $f(\rho^*,\mathbf{Q}_R)$:
+
+	After determining the structure case, evaluate the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$ and the details are given in Section \ref{sec:functions}.
+
+  \item Evaluate the derivative of  $f(\rho^*,\mathbf{Q}_R)$:
 
@@
 where
-\begin{equation}
+\begin{equation*}
 \text{CHA} = \text{max} \left[
-\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right].
-\end{equation}
-and the tolerance is taken as $\text{TOL} = 10^{-4}$.
-
-If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv1} ) is satisfied.
+\frac{|\rho_{(k+1)}^*- \rho_{(k)}^*|}{\frac{1}{2}|\rho_{(k+1)}^*+\rho_{(k)}^*|},|f|\right], \quad \text{TOL} = 10^{-4}.
+\end{equation*}
+%and the tolerance is taken as $\text{TOL} = 10^{-4}$.
+
+If not, go to Step 1 and continue the iteration procedure until convergent. Numerical examples show, after 2-4 iterations, the condition (\ref{conv1}) is satisfied.
 \end{enumerate}
-\textbf{Iteration end.}
+\textbf{Iterations end.}
+
 \section{Numerical  tests }
-In this section, by choosing suitable initial conditions, we will solve the Riemann problem with several different structure cases in the solution.
-Numerical results by the method  in \cite{liumulti} is used to verified the correctness of the exact solution.
-In the following tests, the materials are taken as  aluminium and copper.
-The parameters for the EOS and constitutive model for aluminum and copper  are
+In this section, by choosing different initial conditions, we will solve different Riemann problems with several different wave structures in the solutions.
+In order to verify the correctness of our exact Riemann solver, we use a third-order numerical scheme for 1D elastic-plastic flows introduced in \cite{liumulti} to evaluate these Riemann problems and compare numerical results with our exact solution.
+
+In the following tests, the materials are taken as  aluminium and copper. The parameters for the EOS and constitutive model for aluminum and copper  are
 $ (\rho_0, a_0, \Gamma_0, s, \mu)_{\text{Al}} =(8930 \text{kg}/\text{m}^3, 3940 \text{m}/\text{s},2, 1.49, 2.76 ,2.76\times 10^{10} \text{Pa} )$ and   $(\rho_0, a_0, \Gamma_0, s, \mu)_{\text{copper}} =(2785 \text{kg}/\text{m}^3, 5328 \text{m}/\text{s},2, 1.338,4.5\times 10^{10}\text{Pa})$, respectively.
-The yielding strengths are $Y_{0,\text{Al}} = 3\times 10^8 \text{Pa}$ and   $Y_{0,\text{Copper}} = 9\times 10^7 \text{Pa}$.
+The yielding strengths of the two materials are $Y_{0,\text{Al}} = 3\times 10^8 \text{Pa}$ and   $Y_{0,\text{Copper}} = 9\times 10^7 \text{Pa}$, respectively.
 The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.
+Otherwise, in the initial condition, "L" and "R" mean $x<0.5m$ and $x>0.5m$, respectively.
 
 \subsection{Test 1}
-In this case, the material is yielding at both sides, so the solution structure has three wave with two plastic waves and one contact.
+In this case, the material is yielding at both sides, so the solution structure has three waves with two plastic shock waves and one contact.
 The initial condition is
@@
 It can be seen that the exact solution matches the numerical results very well in Fig.\ref{fig:case1}.
-\begin{figure}
+\begin{figure}[ht]
   \centering
 
-\includegraphics[width= 8cm] {case1rho.pdf}
-\includegraphics[width= 8cm] {case1u.pdf}
-\includegraphics[width= 8cm] {case1p.pdf}
-\includegraphics[width= 8cm] {case1sigma.pdf}
-
-    \caption{Comparison resutls for Test 1 with the structrures of $S^P|S^P$.  }
+\includegraphics[width= 7cm] {case1rho.pdf}
+\includegraphics[width= 7cm] {case1u.pdf}
+\includegraphics[width= 7cm] {case1p.pdf}
+\includegraphics[width= 7cm] {case1sigma.pdf}
+
+    \caption{Comparison results for Test 1 with the structure of $S^P|S^P$.  }
   \label{fig:case1}
@@
 \end{equation}
-Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, besides the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
-\begin{figure}
+Shown in Fig.\ref{fig:case2}, the exact solution matches the numerical results well generally, except the under-cooling effect performed in the numerical results, but it is not considered in the designing of the exact Riemann solver.
+\begin{figure}[ht]
   \centering
-  \includegraphics[width= 8cm] {case2rho.pdf}
-  \includegraphics[width= 8cm] {case2u.pdf}
-  \includegraphics[width= 8cm] {case2p.pdf}
-  \includegraphics[width= 8cm] {case2sxx.pdf}
-  \caption{Comparison resutls for Test 2 with the structrures of $S^ES^P|S^PS^E$.  }
+  \includegraphics[width= 7cm] {case2rho.pdf}
+  \includegraphics[width= 7cm] {case2u.pdf}
+  \includegraphics[width= 7cm] {case2p.pdf}
+  \includegraphics[width= 7cm] {case2sxx.pdf}
+  \caption{Comparison results for Test 2 with the structure of $S^ES^P|S^PS^E$.  }
   \label{fig:case2}
@@
 
-\begin{figure}
+\begin{figure}[ht]
   \centering
 
- \includegraphics[width= 8cm] {case3rho.pdf}
-  \includegraphics[width= 8cm] {case3u.pdf}
-  \includegraphics[width= 8cm] {case3p.pdf}
-  \includegraphics[width= 8cm] {case3sxx.pdf}
-
-    \caption{Comparison resutls for Test 4 with the structrures of $R^ER^P|R^PR^E$.  }
+ \includegraphics[width= 7cm] {case3rho.pdf}
+  \includegraphics[width= 7cm] {case3u.pdf}
+  \includegraphics[width= 7cm] {case3p.pdf}
+  \includegraphics[width= 7cm] {case3sxx.pdf}
+
+    \caption{Comparison results for Test 4 with the wave structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case4}
 \end{figure}
+
 \subsection{Test 5}
-In Test 4, the material is  yielding from a elastic state to a plastic state through  an elastic rarefaction wave, just as we say in the introduction, 
-even when it is in the plastic state at the beginning, after a rarefaction wave, the material will return into an elastic state and then may change into the  plastic by an  expandation yielding process.
-Considering an initial condition as
-
+The initial condition of this Riemann problem is
 \begin{equation}
@@
 \end{equation}
-
-The results show in Fig.\ref{fig:case20} both by the numerical and theoretical results, the material truely can  change from plastic state to elastic then to plastic state again.
-However, if we do not consider the plastic to elastic process, we will get a wrong result  as the red line shows.
-\begin{figure}
+From the initial condition, at the beginning, the material is in the negative plastic state (i.e.
+$s_{xxL(R)}=-\frac{2}{3}{Y}^{0}$).
+If using the thought introduced by Gao and Liu, the material will be always in the negative plastic state.
+Exact solutions based on this thought are denoted by red dashed lines in Fig.\ref{fig:case20}.
+Obviously, from Fig.\ref{fig:case20}, one can find that the exact solutions denoted by red dashed lines are wrong because they do not match the numerical results very seriously.
+In fact, on the contrary, after an unloading process the material will turn back into a  elastic state, and will yielding again after a reloading process, we can get the right exact solutions which match the numerical solutions very well by the new Riemann solver in Fig.\ref{fig:case20}.
+ %In the previous test, the material is  yielding from the elastic state to the plastic state through the elastic rarefaction wave.
+In this test, we will show, even if the material is in the negative plastic state at the beginning (i.e.
+$s_{xxL(R)}=-\frac{2}{3}{Y}^{0}$), after being expanded, the material can be into an elastic state or the positive plastic state, just as we analyze in the introduction.
+Solving this Rieman problem.
+This is proved in Fig.\ref{fig:case20} not only by the numerical and theoretical results, the material truly change from a plastic state to an elastic then to a plastic state again.
+However, if we do not consider the plastic to elastic process there maybe significant wrong in the numerical results as the red line shows.
+\begin{figure}[ht]
   \centering
- \includegraphics[width= 8cm] {case20rho.pdf}
-  \includegraphics[width= 8cm] {case20u.pdf}
-  \includegraphics[width= 8cm] {case20p.pdf}
-  \includegraphics[width= 8cm] {case20sxx.pdf}
-    \caption{Comparison resutls for Test 5 with the structrures of $R^ER^P|R^PR^E$.  }
+ \includegraphics[width= 7cm] {case20rho.pdf}
+  \includegraphics[width= 7cm] {case20u.pdf}
+  \includegraphics[width= 7cm] {case20p.pdf}
+  \includegraphics[width= 7cm] {case20sxx.pdf}
+    \caption{Comparison results for Test 5 with the structure of $R^ER^P|R^PR^E$.  }
   \label{fig:case20}
 \end{figure}
+
 \subsection{Test 6}
-All the above five tests have symmetrical wave  structrues, next we will test an example with different structrues on different sides. The initial condition is given as
+All the above five tests have symmetrical wave  structures, here we will test an example with different structures on two sides: one plastic shock on the left side and both the elastic and plastic shocks on the right of one contact wave.
+The initial condition is given as
 \begin{equation}
@@
 \end{equation}
-In the Fig.\ref{fig:case5} shown in both the numerical and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.
-
-\begin{figure}
+The solutions of this test are shown in Fig.\ref{fig:case5}. From this figure, we can find the exact solutions match numerical solutions very well.
+%and exact solutions, there is one plastic shock on the left side and both the elastic and plastic shocks exist on the right.
+
+\begin{figure}[ht]
   \centering
 
-  \includegraphics[width= 8cm] {case5rho.pdf}
-  \includegraphics[width= 8cm] {case5u.pdf}
-  \includegraphics[width= 8cm] {case5p.pdf}
-  \includegraphics[width= 8cm] {case5sxx.pdf}
+  \includegraphics[width= 7cm] {case5rho.pdf}
+  \includegraphics[width= 7cm] {case5u.pdf}
+  \includegraphics[width= 7cm] {case5p.pdf}
+  \includegraphics[width= 7cm] {case5sxx.pdf}
 
@@
 Shown in Fig.\ref{fig:case9}, we can see there are two shocks in the right side and two rarefaction waves on the left side.
-\begin{figure}
+\begin{figure}[ht]
   \centering
 
-  \includegraphics[width= 8cm] {case9rho.pdf}
-  \includegraphics[width= 8cm] {case9u.pdf}
-  \includegraphics[width= 8cm] {case9p.pdf}
-  \includegraphics[width= 8cm] {case9sxx.pdf}
+  \includegraphics[width= 7cm] {case9rho.pdf}
+  \includegraphics[width= 7cm] {case9u.pdf}
+  \includegraphics[width= 7cm] {case9p.pdf}
+  \includegraphics[width= 7cm] {case9sxx.pdf}
 
@@
 Show in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface.
-The exact Riemann solver can solve the Riemann problem with multi-materials very well comparing to the MHLLCEP approximate solver.
-
-\begin{figure}
+Comparing to the numerical results of the scheme with MHLLCEP approximate solver, we can find that our exact Riemann solver can solve the Riemann problem with multi-materials very well.
+\begin{figure}[ht]
   \centering
-  \includegraphics[width= 8cm] {case6rho.pdf}
-  \includegraphics[width= 8cm] {case6u.pdf}
-  \includegraphics[width= 8cm] {case6p.pdf}
-  \includegraphics[width= 8cm] {case6sigma.pdf}
-
-    \caption{Comparison results for Test 8 with structrures of $R^ER^P|R^PR^E$.  }
+  \includegraphics[width= 7cm] {case6rho.pdf}
+  \includegraphics[width= 7cm] {case6u.pdf}
+  \includegraphics[width= 7cm] {case6p.pdf}
+  \includegraphics[width= 7cm] {case6sigma.pdf}
+
+    \caption{Comparison results for Test 8 with structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case7}
@@
 \end{equation}
-Shown in Fig.\ref{fig:case8}, there are two rarefaction waves on the left side and two shocks on the right side, there is a discontinuity of pressure on the interface, and the Cauchy stress is continuous, which  meets with the theoretical analysis.
-\begin{figure}
+Shown in Fig.\ref{fig:case8}, there are two rarefaction waves on the left side and two shocks on the right side, there is the discontinuity of pressure on the interface, and the Cauchy stress is continuous, which  satisfies the theoretical analysis.
+\begin{figure}[ht]
   \centering
-  \includegraphics[width= 8cm] {case8rho.pdf}
-  \includegraphics[width= 8cm] {case8u.pdf}
-  \includegraphics[width= 8cm] {case8p.pdf}
-  \includegraphics[width= 8cm] {case8sigma.pdf}
-
-    \caption{Comparison results for Test 9 with the structrures of $R^ER^P|S^ES^P$.  }
+  \includegraphics[width= 7cm] {case8rho.pdf}
+  \includegraphics[width= 7cm] {case8u.pdf}
+  \includegraphics[width= 7cm] {case8p.pdf}
+  \includegraphics[width= 7cm] {case8sigma.pdf}
+
+    \caption{Comparison results for Test 9 with the structure of $R^ER^P|S^ES^P$.  }
   \label{fig:case8}
 \end{figure}
+
 \subsection{Test 10}
-Then we give two tests of  half Riemann problem, the first is with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
+This test is a half Riemann problem with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
 \begin{equation}
@@
 \end{equation}
-In Fig.\ref{fig:case9}, comparason results are given by the exact half Riemann solver and the numerical method.
-We can see that the exact solver  can resolve both the elastic and plastic shock waves well.
-\begin{figure}
+In Fig.\ref{fig:case9}, comparison results are given by the exact half Riemann solver and the numerical method.
+We can see that the exact solver can resolve both the elastic and plastic shock waves very well.
+\begin{figure}[ht]
   \centering
-  \includegraphics[width= 8cm] {case10rho.pdf}
-  \includegraphics[width= 8cm] {case10u.pdf}
-  \includegraphics[width= 8cm] {case10p.pdf}
-  \includegraphics[width= 8cm] {case10sxx.pdf}
-
-    \caption{Comparison results for Test 10 with the structrures of $S^ES^P$.  }
+  \includegraphics[width= 7cm] {case10rho.pdf}
+  \includegraphics[width= 7cm] {case10u.pdf}
+  \includegraphics[width= 7cm] {case10p.pdf}
+  \includegraphics[width= 7cm] {case10sxx.pdf}
+
+    \caption{Comparison results for Test 10 with the structure of $S^ES^P$.  }
   \label{fig:case9}
 \end{figure}
+
 \subsection{Test 11}
@@
 \end{equation}
-In Fig.\ref{fig:case10}, we give the results computed by the exact Riemann solver and the numerical simulation, shown in it, the exact solver can resolve the elastic and plastic rarefaction waves well.
-\begin{figure}
+In Fig.\ref{fig:case10}, we give the results computed by the exact Riemann solver and the numerical simulation.
+From this figure one can see, the exact solver can resolve the elastic and plastic rarefaction waves well.
+\begin{figure}[ht]
   \centering
- \includegraphics[width= 8cm] {case11rho.pdf}
-  \includegraphics[width= 8cm] {case11u.pdf}
-  \includegraphics[width= 8cm] {case11p.pdf}
-  \includegraphics[width= 8cm] {case11sigma.pdf}
-    \caption{Comparison results for Test 11 with the structrures of $R^ER^P$.  }
+ \includegraphics[width= 7cm] {case11rho.pdf}
+  \includegraphics[width= 7cm] {case11u.pdf}
+  \includegraphics[width= 7cm] {case11p.pdf}
+  \includegraphics[width= 7cm] {case11sigma.pdf}
+    \caption{Comparison results for Test 11 with the structure of $R^ER^P$.  }
   \label{fig:case10}
 \end{figure}
+
 \section{Results}
@@
 	\item the plastic wave is always faster than the elastic wave for the reason of the sonic speed jump.
-	\item Both the changing from elastic to plastic and the  converse changing from plastic to elastic may exist in the Riemann problem.
+
 	  \item There are only thirty-six possible cases of the structrues in the Riemann problem.
+
+	\item All the variables after the wave can be written as functions of the density theoretically.
+
+	\item if the initial material is in the negative plastic state, after being expanded, the material may be into the elastic state or the positive plastic state.
+
+	\item if the initial material is in the positive plastic state, after being compressed, the material may be into the elastic state or the negative plastic state.
 	\end{enumerate}
-	  Then, based on the analysis and the results above,  exact Riemann solvers are  constructed for both the Riemann problem  and the half Riemann problem, separately.
-Tested by  a large number of examples, the exact Riemann solver is reasonable and matching  well with the numerical method for both  single material problems and multi-material Riemann problems.
+	  Then, based on the above analysis, we have constructed exact Riemann solvers for  both the Riemann problem  and the half Riemann problem, separately.
+Tested by  a large number of examples, the exact Riemann solver is reasonable and  its solutions  are matching well with the numerical results for both  single material problems and multi-material Riemann problems.
 
@@
 
-  \renewcommand{\appendixname}{Appendix~\Alph{section}}
+  \renewcommand{\appendixname}{Appendix\Alph{section}}
 
@@
   There are two integrations in  functions $p(\rho)$ and $u(\rho)$ in the rarefaction wave, for example,  in the equations (\ref{rerpp}) and (\ref{rerpu}).
-In this paper, we use  a seventh-order (with 4 integrating points) Gauss-Legendre quadrature to  take  numerical integrations.
-For a function $g(x)$,  the Gauss-Legendre intergration from $-1$ to $1$ is given as
+In this paper, we use  a seventh-order (with 4 integrating points) Gaussian quadrature to make numerical integrations.
+For a function $g(x)$,  the Gaussian integration from $-1$ to $1$ is given as
 $$
@@
 
-$$x_1, \ x_2 =\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}} \quad (\omega_1, \  \omega_2 =\frac{18+\sqrt{30}}{36} ), $$
-$$x_3, \ x_4 =\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}} \quad (\omega_1, \  \omega_2 =\frac{18-\sqrt{30}}{36} ). $$
+$$x_1, \ x_2 =\pm \sqrt{\frac{3}{7} -\frac{2}{7}\sqrt{\frac{6}{5}}} \quad \left(\omega_1, \  \omega_2 =\frac{18+\sqrt{30}}{36} \right), $$
+$$x_3, \ x_4 =\pm \sqrt{\frac{3}{7} +\frac{2}{7}\sqrt{\frac{6}{5}}} \quad \left(\omega_3, \  \omega_4 =\frac{18-\sqrt{30}}{36} \right). $$
 
@@
 
-$$ \int_{\rho_0}^{\rho}g(x) dx= \frac{\rho-\rho_0}{2}\int_{-1}^{1} g(\frac{\rho-\rho_0}{2}x+\frac{\rho_0+\rho}{2})dx.
 $$
-
- \emph{\textbf{Integrating of $p(\rho)$}}  Taking Equation (\ref{rerpp}) as an example, 
+\int_{\rho_0}^{\rho}g(x) dx= \frac{\rho-\rho_0}{2}\int_{-1}^{1} g\left(\frac{\rho-\rho_0}{2}x+\frac{\rho_0+\rho}{2}\right)dx .
+ $$
+
+At last, we can get
+\begin{equation}\label{int1}
+  \int_{\rho_0}^{\rho}g(x) dx \approx \frac{\rho-\rho_0}{2}\sum_{i=1}^n \omega_i g\left(\frac{\rho-\rho_0}{2}x_{i}+\frac{\rho_0+\rho}{2}\right).
+\end{equation}
+
+ \emph{\textbf{Integrating of $p(\rho)$}}
+
+ Taking Equation (\ref{rerpp}) as an example,
  \begin{equation} \label{eq:app}
@@
 
-\emph{\textbf{Integrating of $u(\rho)$}}  Taking Equation (\ref{rerpu}) as an example, if the wave is on the left side
+Obviously, we can use (\ref{eq:app}) to evaluate all the values of $p(\rho_{i})$ on all Gaussian quadrature points.
+
+\emph{\textbf{Integrating of $u(\rho)$}}
+
+Taking Equation (\ref{rerpu}) as an example, if the wave is on the left side
 
@@
 
-Different from (\ref{eq:app}), the sonic speed $c_e(\rho_i)$ is dependent on $p(\rho_i)$ as
+Different from (\ref{eq:app}), the sonic speed $c_e(\rho_i)$ is dependent on $p(\rho_i)$:
 
@@
   c_e(\rho_i) =
-  \sqrt{a_0^2 \frac{\partial f}{\partial \eta}(\rho_i) + \frac{p(\rho_i)}{\rho_i^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_i^2}\Gamma_0 s_{xx}(\rho_i) +\frac{4}{3}\frac{\mu}{\rho_i}}.
+  \sqrt{a_0^2 \frac{\partial f}{\partial \eta}\left(\frac{\rho_i}{\rho_0}\right) + \frac{p(\rho_i)}{\rho_i^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho_i^2}\Gamma_0 s_{xx}(\rho_i) +\frac{4}{3}\frac{\mu}{\rho_i}}.
 % \quad  \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}
 \end{equation}
-And we can take an  integration of interval $[\rho_{L(R)}, \rho_i]$ by the same process of Equation (\ref{eq:app}) to solve $p(\rho_i)$.
+After finishing the evaluation of  $p(\rho_{i})$, we can evaluate $c_e(\rho_i)$ by using the same process as (\ref{eq:app}).
+
+%And we can take an  integration of interval $[\rho_{L(R)}, \rho_i]$ by the same process of Equation (\ref{eq:app}) to solve $p(\rho_i)$.
 

### 2019-07-12 Manuscript20190712.tex
111

--- 2019-07-07 Manuscript revise 20190612.tex
@@
 
-\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state}
+\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state without vaccum}
 \author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$}
@@
 \begin{abstract}
+
   In this paper, we present exact Riemann solvers for the Riemann problem and the half Riemann problem, respectively,  for one-dimensional multi-material elastic-plastic flows with the Mie-Gr\"uneisen equation of state(EOS), hypo-elastic constitutive model and  the von Mises' yielding condition.
@@
 Based on these formulations, an exact Riemann solver is constructed with totally thirty-six possible cases of wave structures.
-Although Gao and Liu\cite{gao20171d} also developed the exact Riemann solver for 1D elastic plastic flows, but the EOS they used is very simple.
-Moreover, the exact Riemann solver developed by them may result in wrong solutions when the initial material is in the plastic state, which has been proven in one of our tests.
-Comparing with the exact Riemann solver developed by Gao and Liu, our exact Riemann solver uses a more complex EOS and overcomes these mistakes.
+{\color{red} In our work,  a four-equation Eulerian hyperbolic governing system is used and the elastic and plastic states are controlled by uniform equations and same EOS.
+The transformations of elastic and plastic states are  determined by the deviatoric stress spontaneously}.
 A large number of tests prove the rightness of our exact Riemann solver.
@@
 Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.
-The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structure of Riemann solvers.
+The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structures of Riemann solvers.
 Moreover, in a general way, the equation of state(EOS) for solid materials is more complex than that for pure fluids, which directly increases the difficulty in solving the Riemann problem.
@@
 For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
-But there are two shortcomings in their works.
-Firstly, the EOS used by them is very simple: in the elastic state, the material derivative of pressure is the linear function of the strain rate, which means the energy equation is not necessary in the elastic state; in the plastic state,  a linear  "stiffened-gas" EOS was used.
-{ \color{red} Secondly,  unloading (for example, an expanding process to a compressed yielding material) and reloading processes are not considered in the construction  of their Riemann solvers.
-This may leads to wrong solutions as the unloading and reloading are very common in the real computing cases, shown in our $5$th numerical example.
+{\color{red} In their works, a five-equation Eulerian governing system is constructed and a complete list of sixty-four cases of wave type is presented.
 }
-In fact, according to the relations in the governing equations, even if the initial material reaches the elastic limit and in a plastic state, after an unloading process, the material may change back to an elastic state and then may re-change to a plastic state by a reloading process.
 
@@
 This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
-
-In this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition.
+{\color{red}
+ Enlighen by but different from the works of Gao and Liu \cite{gao20171d,gao2018complete},
+ in this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition.
+Firstly, the elastic and plastic states are controlled by same equations but only different in the deviatoric stress, so there are  four equations in the governing system.
+Secondly, the same Mie-Gr\"uneisen EOS is used in both the elastic and plastic states.
 As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave.
@@
 These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves.
-Moreover, elastic wave always runs faster than the followed plastic wave.
+Moreover, elastic waves always runs faster than the followed plastic wave.
 So there are thirty-six possible cases of the wave structures in the Riemann solver.
-Besides, both the changing from elastic to plastic (loading or reloading) and  the converse changing from plastic to elastic(unloading)  are considered in the Riemann problem.
+Besides, both the changing from elastic to plastic and  the converse changing from plastic to elastic  are considered in the Riemann problem.}
 %For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 The above equations are just for the elastic status of the solid material.
-If the materials are in the plastic state, the above equations can be simplified
+If the material is in the plastic state, the above equations can be simplified
 and the jacobian matrix and sonic velocity are different,  correspondingly.
@@
 
-\subsubsection{A relation between $\rho$ and $s_{xx}$ }
-
-Thanks to (\ref{eq:mt}), equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
-  \begin{equation}\label{eq:d1}
-    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
-  \end{equation}
-  and
-  \begin{equation}\label{eq:s1}
-    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
-  \end{equation}
-
-  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
-%  We can get a relation of density and deviatoric stress,
-  \begin{equation}
-    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
-\end{equation}
-Integrating the above equation from the data in front of a wave to the data behind the wave and performing some simple algebraic manipulations, one can get
-\begin{equation}\label{eq:rhosxx}
-  s_{xx}+\frac{4}{3}\mu\text{ln}(\rho) = \text{constant}
-\end{equation}
-This relation always hold in the elastic state.
-
 \subsubsection{Relations across the contact wave}\label{sec:contacte}
@@
 \end{equation}
+
+\subsection{A relation between $\rho$ and $s_{xx}$ }\label{sec:relation}
+
+Thanks to (\ref{eq:mt}), the equations of the density and the deviatoric stress in Eq.(\ref{eq:1d}) can be written as
+  \begin{equation}\label{eq:d1}
+    \frac{\partial u}{\partial x} = -\frac{1}{\rho}\frac{d\rho}{dt},
+  \end{equation}
+  and
+  \begin{equation}\label{eq:s1}
+    \frac{ds_{xx}}{dt}=\frac{4}{3}\mu\frac{\partial u}{\partial x}.
+  \end{equation}
+
+  Substituting (\ref{eq:d1}) into (\ref{eq:s1}) yields
+%  We can get a relation of density and deviatoric stress,
+  \begin{equation}
+    \frac{ds_{xx}}{dt}=-\frac{4}{3}\mu \frac{1}{\rho}\frac{d\rho}{dt}.
+\end{equation}
+Integrate the above equation from the data in front of a wave to the data behind the wave and perform some simple algebraic manipulations, one can get
+\begin{equation}\label{eq:rhosxx}
+  s_{xx}+\frac{4}{3}\mu\text{ln}(\rho) = \text{constant}.
+\end{equation}
+
+Analyzing the formulation (\ref{eq:rhosxx}), one can find, $\frac{\partial s_{xx}}{\partial \rho}<0$.
+So, if the material is compressed and $\rho$ increases, $s_{xx}$ will decrease; if the material is expanded and $\rho$ decreases, $s_{xx}$ will increase.
+According to the compressed or expanded process of the material,  even if the initial material is in the plastic state, the material can be into a different state.
+With considering of the von Mises yielding condition, all cases are shown as follows:
+\begin{enumerate}
+  \item if $s_{xx}=\frac{2}{3}Y^{0}$, initial material reaches the elastic limit.
+If the material is compressed so that $\rho_{plastic}>\rho^{*}>\rho$, one can get $|s_{xx}^{*}|<\frac{2}{3}Y^{0}$, the compressed material jumps from the plastic state to the elastic state.
+Here $\rho$ and $s_{xx}$ mean the initial density and deviatoric stress, respectively, $\rho_{plastic} = \rho e^{\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xx}}{4\mu}\right)}$, $( )^{*}$ denotes the variable $( )$ of the compressed or expanded material.
+  \item if $s_{xx}=\frac{2}{3}Y^{0}$ and the material is compressed greatly so that  $\rho_{plastic}<\rho^{*}$, $s_{xx}^{*}\leq - \frac{2}{3}Y^{0}$, the compressed material will jump from the positive plastic state to the negative plastic state.
+Here the positive or negative plastic state means $s_{xx}=\frac{2}{3}Y^{0}$ or $s_{xx}=-\frac{2}{3}Y^{0}$, respectively.
+  \item if $s_{xx}=\frac{2}{3}Y^{0}$ and  the material is expanded, $s_{xx}^{*}>\frac{2}{3}Y^{0}$, the material is still in the positive plastic state.
+  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and the material is expanded so that $\rho_{plastic}<\rho^{*}<\rho$, one can get $|s_{xx}^{*}|<\frac{2}{3}Y^{0}$, the expanded material jumps from the plastic state to the elastic state.
+  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and the material is expanded greatly so that  $\rho_{plastic}>\rho^{*}$, $s_{xx}^{*}\geq  \frac{2}{3}Y^{0}$, the expanded material will jump from the negative plastic state to the  positive plastic state.
+  \item if $s_{xx}=-\frac{2}{3}Y^{0}$ and  the material is compressed, $s_{xx}^{*}<-\frac{2}{3}Y^{0}$, the material is still in the negative plastic state.
+\end{enumerate}
 
@@
 \begin{enumerate}[Step 1]
-  \item Determining the case of the wave structure:
-
-	Given $\rho _{L(k)}^*$ and  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the method introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+  \item Determining the case of the wave structures:
+
+	Given $\rho _{L(k)}^*$ and  $\rho _{R(k)}^*$ in the $k$-th  iteration step, we can use the method introduced in Section \ref{sec:deter} to determine the case of wave structures of this Riemann problem.
 In the  procedure for solving the  Riemann problem, the subscript $(k)$ means the variable in the $k$-th  iteration step.
@@
 
-  After determining the structure case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
+  After determining the structures case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
 
@@
 
-Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structure of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ``$S$'' and ``$R$'' mean the shock and rarefaction wave, respectively; superscript letters ``$E$'' and  ``$P$'' indicate the elastic or plastic state of a wave, respectively.
+Combining (\ref{shock1}) and (\ref{yield1}), we can find, in any side of the wave structures of this Riemann problem, there are six cases showed in Table \ref{tab:cases}, where capital letters ``$S$'' and ``$R$'' mean the shock and rarefaction wave, respectively; superscript letters ``$E$'' and  ``$P$'' indicate the elastic or plastic state of a wave, respectively.
 Otherwise, the  subscript $L$ or  $R$  are omitted for simplification.
@@
 	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\tilde{\rho}_{L(R)}}\right)+\tilde{s}_{xxL(R)},
-	\quad  &\text{case ($S^E$)},\\
+	\quad  &\text{for case ($S^E$)},\\
 	& -\frac{2}{3}Y_0,   \quad
-	&\text{cases ( $S^P$ and $S^ES^P$)}.
+	&\text{for cases ( $S^P$ and $S^ES^P$)}.
   \end{aligned} \right.
@@
 (\ref{eq:shocke}) gives direct expressions for the
-By the equation of (\ref{eq:shocke}), the pressure is given as
+the pressure in the star region as
 \begin{equation}
@@
 \begin{enumerate}[Step 1]
-  \item Determine the case of the wave structure:
-
-	Given the value of  $\rho _{(k)}^*$ in the $k$-th iteration step, use the methods introduced in Section \ref{sec:deter} to determine the case of wave structure of this Riemann problem.
+  \item Determine the case of the wave structures:
+
+	Given the value of  $\rho _{(k)}^*$ in the $k$-th iteration step, use the methods introduced in Section \ref{sec:deter} to determine the case of wave structures of this Riemann problem.
 Here the subscript $(k)$ means the variable in the $k$-th  iteration step.
@@
 
-	After determining the structure case, evaluate the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$ and the details are given in Section \ref{sec:functions}.
+	After determining the structures case, evaluate the velocity ( or  the Cauchy stress) in  the region $\mathbf{Q}^*$ and the details are given in Section \ref{sec:functions}.
 
@@
 \subsection{Test 1}
-In this case, the material is yielding at both sides, so the solution structure has three waves with two plastic shock waves and one contact.
+In this case, the material is yielding at both sides, so the solution structures has three waves with two plastic shock waves and one contact.
 The initial condition is
@@
 
-    \caption{Comparison results for Test 1 with the structure of $S^P|S^P$.  }
+    \caption{Comparison results for Test 1 with the structures of $S^P|S^P$.  }
   \label{fig:case1}
@@
 \subsection{Test 2}
-Here we consider a case with yielding process at both sides, so there are five waves in the wave structure of this Riemann problem. The initial condition is
+Here we consider a case with yielding process at both sides, so there are five waves in the wave structures of this Riemann problem. The initial condition is
 \begin{equation}
@@
   \includegraphics[width= 7cm] {case2sxx.pdf}
-  \caption{Comparison results for Test 2 with the structure of $S^ES^P|S^PS^E$.  }
+  \caption{Comparison results for Test 2 with the structures of $S^ES^P|S^PS^E$.  }
   \label{fig:case2}
@@
 \subsection{Test 3}
-In this example, we test the case with two elastic rarefaction waves. In the wave structure there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
+In this example, we test the case with two elastic rarefaction waves. In the wave structures there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
 \begin{equation}
@@
 %j\section*{Conclusions}
-\begin{figure}{ht}
+\begin{figure}[ht]
   \centering
@@
 $s_{xxL(R)}=-\frac{2}{3}{Y}^{0}$).
-If using the thought introduced by Gao and Liu, the material will be always in the negative plastic state.
-Exact solutions based on this thought are denoted by red dashed lines in Fig.\ref{fig:case20}.
-Obviously, from Fig.\ref{fig:case20}, one can find that the exact solutions denoted by red dashed lines are wrong because they do not match the numerical results very seriously.
-In fact, on the contrary, after an unloading process the material will turn back into a  elastic state, and will yielding again after a reloading process, we can get the right exact solutions which match the numerical solutions very well by the new Riemann solver in Fig.\ref{fig:case20}.
+According to the analysis introduced in  Section \ref{sec:relation}, after an expanding process the material will turn back into an elastic state and will yield again into a positive plastic state, we can get the right exact solutions which match the numerical solutions very well by the new Riemann solver in Fig.\ref{fig:case20}.
  %In the previous test, the material is  yielding from the elastic state to the plastic state through the elastic rarefaction wave.
@@
   \includegraphics[width= 7cm] {case20sxx.pdf}
-    \caption{Comparison results for Test 5 with the structure of $R^ER^P|R^PR^E$.  }
+    \caption{Comparison results for Test 5 with the structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case20}
@@
 \subsection{Test 6}
+The initial condition of this Riemann problem is
+\begin{equation}
+ \left\{ \begin{aligned}
+	 &	 \text{L: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 200\text{m}/\text{s}, \quad  p = 1.0 \text{Pa}, \quad  s_{xx}=2.0\time 10^8 \text{Pa},\\
+	 &	 \text{R: Al,}\quad  \rho = 2785 \text{kg}/\text{m}^3, \quad  u = 0\text{m}/\text{s}, \quad  p = 1.0\text{Pa}, \quad  s_{xx}= 2.0 \time 10^8 \text{Pa}.\\
+   \end{aligned}
+ \right.
+\end{equation}
+Different from Test 5, in  the initial condition, at the beginning, the material is in the positive  plastic state (i.e.
+$s_{xxL(R)}=\frac{2}{3}{Y}^{0}$).
+According to the analysis introduced in Section \ref{sec:relation}, after an compressing  process the material will turn back into an elastic state and will yield again into a negtive plastic state, we can get the exact  solutions match the numerical solutions very well by the new Riemann solver in Fig.\ref{fig:case21}.
+
+\begin{figure}[ht]
+  \centering
+ \includegraphics[width= 7cm] {case21rho.pdf}
+  \includegraphics[width= 7cm] {case21u.pdf}
+  \includegraphics[width= 7cm] {case21p.pdf}
+  \includegraphics[width= 7cm] {case21sxx.pdf}
+    \caption{Comparison results for Test 6 with the structures of $S^ES^P|S^PS^E$.  }
+  \label{fig:case21}
+\end{figure}
+
+\subsection{Test 7}
 All the above five tests have symmetrical wave  structures, here we will test an example with different structures on two sides: one plastic shock on the left side and both the elastic and plastic shocks on the right of one contact wave.
@@
 
-    \caption{Comparison resutls for Test 6 with the structrures of $R^P|R^PR^E$.  }
+    \caption{Comparison resutls for Test 7 with the structures of $R^P|R^PR^E$.  }
   \label{fig:case5}
 \end{figure}
-\subsection{Test 7}
+\subsection{Test 8}
 In this test, we consider an example with zero initial velocities on both sides, driving by the gradient of the pressure, there are rarefaction waves produced into the higher pressure side and shock waves generated into the lower pressure side.
@@
 
-    \caption{Comparison resutls for Test 7 with the structrures of $R^ER^P|S^PS^E$.  }
+    \caption{Comparison resutls for Test 8 with the structures of $R^ER^P|S^PS^E$.  }
   \label{fig:case9}
 \end{figure}
-\subsection{Test 8}
+\subsection{Test 9}
 Now we will consider two multi-material tests with different materials on both sides.
@@
 
-    \caption{Comparison results for Test 8 with structures of $R^ER^P|R^PR^E$.  }
+    \caption{Comparison results for Test 9 with the structures of $R^ER^P|R^PR^E$.  }
   \label{fig:case7}
@@
 %
-\subsection{Test 9}
+\subsection{Test 10}
 Here we test another multi-materials case, in this test the initial condition is given as
@@
 
-    \caption{Comparison results for Test 9 with the structure of $R^ER^P|S^ES^P$.  }
+    \caption{Comparison results for Test 10 with the structures of $R^ER^P|S^ES^P$.  }
   \label{fig:case8}
@@
 
-\subsection{Test 10}
+\subsection{Test 11}
 This test is a half Riemann problem with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
@@
 
-    \caption{Comparison results for Test 10 with the structure of $S^ES^P$.  }
+    \caption{Comparison results for Test 11 with the structures of $S^ES^P$.  }
   \label{fig:case9}
@@
 
-\subsection{Test 11}
+\subsection{Test 12}
 The second half Riemann case is with a given left Cauchy stress $\sigma^* = 0 \text{Pa}$, and the right initial condition is
@@
   \includegraphics[width= 7cm] {case11sigma.pdf}
-    \caption{Comparison results for Test 11 with the structure of $R^ER^P$.  }
-  \label{fig:case10}
+    \caption{Comparison results for Test 11 with the structures of $R^ER^P$.  }
+  \label{fig:case12}
 \end{figure}

### 2019-07-17 Manuscript20190714.tex
2

--- 2019-07-12 Manuscript20190712.tex
@@
 
-\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state without vaccum}
+\title{An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state without vacuum}
 \author{Li Liu$^1$, Jun-bo Cheng $^{1,*}$}
@@
   In this paper, we present exact Riemann solvers for the Riemann problem and the half Riemann problem, respectively,  for one-dimensional multi-material elastic-plastic flows with the Mie-Gr\"uneisen equation of state(EOS), hypo-elastic constitutive model and  the von Mises' yielding condition.
-We first  analyze the Jacobian matrixes in  both elastic and plastic states, and then build relations between different variables across different type of waves.
+We first  analyze the Jacobian matrices in  both elastic and plastic states, and then build relations between different variables across different type of waves.
 Based on these formulations, an exact Riemann solver is constructed with totally thirty-six possible cases of wave structures.
-{\color{red} In our work,  a four-equation Eulerian hyperbolic governing system is used and the elastic and plastic states are controlled by uniform equations and same EOS.
+  %{\color{red} In our work,  a four-equation Eulerian hyperbolic governing system is used and the elastic and plastic states are controlled by uniform equations and same EOS.
 The transformations of elastic and plastic states are  determined by the deviatoric stress spontaneously}.
-A large number of tests prove the rightness of our exact Riemann solver.
-Moreover, an exact Riemann solver is also deduced for the half Riemann problem and  its validity is tested  by two examples.
+  A large number of tests prove the rightness of our exact Riemann solver. Moreover, an exact Riemann solver is also deduced for the half Riemann problem and  its validity is tested  by two examples.
 \end{abstract}
@@
 In the development history of hydrodynamic numerical methods, the exact Riemann solver has played a very important role as it not only can give a guide and reference to the construction of approximate Riemann solvers, but also can be used to determine the convergence and stability of numerical schemes.
-However, building the exact Riemann solver for 1D elastic-plastic flows is not that easy.
-Comparing with the governing equations system of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.
+However, building the exact Riemann solver for 1D elastic-plastic flows is not easy.
+Comparing with the governing equations of 1D pure fluids, for 1D elastic-plastic flows, there are two more equations: a non-conservative constitutive equation and the von Mises yielding condition.
 The non-conservative character of the constitutive equation increases the difficulty in constructing  Riemann solvers, while the von Mises yielding condition may lead to more non-linear waves in the wave structures of Riemann solvers.
@@
 For example, Garaizar \cite{garaizar1991solution} and Miller \cite{miller2004iterative} introduced  an exact Riemann solver for elastic or hyper-elastic materials, Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding effect and developed an exact elastic-perfectly plastic solid Riemann solver.
-{\color{red} In their works, a five-equation Eulerian governing system is constructed and a complete list of sixty-four cases of wave type is presented.
+In their works, a five-equation Eulerian governing system is constructed, and a complete list of sixty-four cases of wave type is presented.
+{\color{blue} However, in their works, because the pressure is the function of strain rate in the elastic state, the energy equation is not considered in the elastic state.
+Moreover, the EOSs used in their system are relatively simple.
 }
 
-%in their paper, the states of elastic and plastic are using with very different equations systems and parameters, the seperation  deduces to more non-physical wave-structures cases in which the plastic wave  may be faster than the elastic wave.Thirdly,
-%only the changing from elastic to plastic is considered in their works, however, in fact  through an unloading and reloading process the plastic material also can change to elastic.}
-
-%Although the control equations of elastic-plastic flow is similar to the equations in computational fluid dynamics (CFD).
-But there are mainly three difficulties  of constructing  Riemann solvers in elastic-plastic flows.
-Firstly, the constitutive models used in elastic-plastic flows are more complicated.
-Secondly, the EOS for solid materials is also with more characters.
-Finally, the yielding process of materials may lead to more wave structures.
-
-%Recently, a lot of works have been done in constructing  approximate Riemann solvers for elastic-plastic flows with the considering of structures in the Riemann problem.
-For example, Gavrilyuk et al.
-\cite{gavrilyuk2008modelling} analyzed the structure of the Riemann solution and constructed a Riemann solver for the linear elastic system  of hyperbolic non-conservative models for transverse waves.
-Cheng et al.
-\cite{cheng2015high} analyzed the wave structures of one-dimensional elastic-plastic flows and developed an effective two-rarefaction approximate Riemann solver with elastic waves (TRRSE).
-In \cite{cheng2016harten}, for one-dimensional elastic-plastic flows, Cheng introduced a HLLCE Riemann solver, which is fast and efficient in resolving elastic waves and plastic waves.
-Then in \cite{liumulti}, Liu et.al remove the unreasonable assumption in HLLCE which may cause numerical errors in simulating multi-material problems and construct a multi-material HLLC elastic-plastic (MHLLCEP) solver.
-
-%As everyone knows, in hydrodynamic numerical system, the exact Riemann solver is developed before approximate Riemann solvers \cite{godunov1959difference}, and it gives a guide and reference to the developing of approximate solvers.
-However, in the elastic-plastic flows, for its complexity, there are only a few works have been done in constructing the exact Riemann solver.
-
- %designed an exact Riemann solution of isotropic hyper-elastic material theoretically; Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
-% Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states.
-As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works.
-%However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state.
-This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
-But for the elastic-plastic flows with hypo-elastic constitutive model, von Mises yielding condition and the complex equation of system(EOS), there is no exact Riemann solver.
-Of course, for some
-
-%For example, Garaizar \cite{garaizar1991solution} designed an exact Riemann solution of isotropic hyperelastic material theoretically.
-Miller \cite{miller2004iterative} presented a general iterative method for the solution of the Riemann problem for hyperbolic elastic systems.
-Gao and Liu \cite{gao20171d,gao2018complete} firstly considered the yielding condition in, and proposed an exact elastic-perfectly plastic solid Riemann solver with both elastic and plastic states.
-As many as thirty-six \cite{gao20171d} and sixty-four \cite{gao2018complete} different solution types are considered in their works.
-However, in their papers,  a linear  "stiffened-gas" EOS was used in the plastic state and a more simple linear relation of pressure and strain rate is used in the elastic state.
-This simplification can truly deduce to simple relations  across the shock wave and rarefaction wave, but we still need an exact Riemann solver with a uniform and more common used EOS and equations system for different elastic-plastic materials.
-{\color{red}
- Enlighen by but different from the works of Gao and Liu \cite{gao20171d,gao2018complete},
- in this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition.
-Firstly, the elastic and plastic states are controlled by same equations but only different in the deviatoric stress, so there are  four equations in the governing system.
-Secondly, the same Mie-Gr\"uneisen EOS is used in both the elastic and plastic states.
-As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows and so we have to use some special methods to resolve the rarefaction wave.
-Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves.
+{\color{blue}
+In this paper, we  plan to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition.
+Although Gao and Liu \cite{gao20171d,gao2018complete} have developed a comprehensive Riemann solver for 1D elastic-plastic flows, there are several notable differences and necessities of our works.
+%in this paper, we want to construct an exact Riemann solver for the system of 1D elastic-plastic flows with the Mie-Gr\"uneisen EOS, the hypo-elastic constitutive model and the von Mises' yielding condition.
+Firstly,  a four equations controlling system is considered in this paper, which is common used in the simulation of one-dimensional elastic and plastic flows \cite{ortega2014numerical,favrie2011dynamics}.
+In this equations system, the elastic and plastic states are treated as single material with same equations of masses, momentum and energy but only different in deviatoric stresses.
+While Gao and Liu \cite{gao20171d,gao2018complete} use a five equations system and treat elastic and plastic states by totally different equations.
+Secondly, the same Mie-Gr\"uneisen EOS is used in the elastic and plastic states, so the energy equation must be considered in both the elastic state and the plastic state, which is  very different from the works in \cite{gao20171d,gao2018complete}.
+Of course, the Mie-Gr\"uneisen EOS used in our work is more complex, for this reason, the process of resolving the rarefaction wave is also different and more difficult.}
+
+  %As every knows, the Mie-Gr\"uneisen EOS is complex and is used widely in many engineering problems, which makes the energy equation must be included in the system of elastic-plastic flows
+%  and so we have to use some special methods to resolve the rarefaction wave.}
+  % and so we have to use some special methods to resolve the rarefaction wave
+
+   %Otherwise, we analyse the Jacobian matrix and find, in the wave structures of Riemann solvers, there may be three to five waves, including one contact wave and other two to four non-linear waves.
 These nonlinear waves may be elastic shock waves, elastic rarefaction waves,  plastic shock waves or plastic rarefaction waves.
@@
 So there are thirty-six possible cases of the wave structures in the Riemann solver.
-Besides, both the changing from elastic to plastic and  the converse changing from plastic to elastic  are considered in the Riemann problem.}
+Besides, both the changing from elastic to plastic and  the converse changing from plastic to elastic  are considered in the Riemann problem.
 %For a given case, we will obtain theoretical relations of all the states as functions of density.
@@
 In section 3, the Riemann problem and the relations for every wave type (contact wave, shock wave and rarefaction wave) are  derived.
-Then,  the exact Riemann solver  is given in section 4.
-The half Riemann problem and its solver is introduced in section 5.
-Some numerical examples are presented to validate the method in section 6.
+Then  the exact Riemann solver  is given in section 4.
+The half Riemann problem and its solver is  discussed in section 5.
+Some numerical examples are presented to validate the new Riemann solvers in section 6.
 Conclusions are shown in section 7.
@@
 In this paper, the elastic energy is not included in the total energy.
-The exclution of the elastic energy is usual for practical engineering problems \cite{maire2013nominally} and is different from that in Ref.\cite{gavrilyuk2008modelling}.
+The exclusion of the elastic energy is usual for practical engineering problems \cite{maire2013nominally} and is different from that in Ref.\cite{gavrilyuk2008modelling}.
 
@@
 
-The above equations are just for the elastic status of the solid material.
-If the material is in the plastic state, the above equations can be simplified
-and the jacobian matrix and sonic velocity are different,  correspondingly.
-We will discuss them separately.
+%The above equations are just for the elastic status of the solid material. If the material is in the plastic state, the above equations can be simplified
+%and the jacobian matrix and sonic velocity are different,  correspondingly. We will discuss them separately.
+
+\textcolor[rgb]{0.00,0.00,1.00}{If the material is in the plastic state, the above forth and fifth equations can be simplified.
+Correspondingly, sonic velocity is different from that in the elastic state,
+which will be discussed in the following.}
+
 \subsection{Elastic state}
@@
 For the Mie-Gr\"uneisen EOS, if the material is not yielding,
-\begin{equation}
+\begin{equation*}
   |s_{xx}| < \frac{2}{3}Y_0,
-\end{equation}
+\end{equation*}
 the system (\ref{eq:1d}) can be written as
-\begin{equation}
+\begin{equation*}
  \partial_t \mathbf{Q} +\mathbf{J}_{e}(\mathbf{{Q}})\partial_x\mathbf{Q} = 0,
-\end{equation}
+\end{equation*}
 where $Q = (\rho, \rho u, \rho E, s_{xx})$, and the Jacobian matrix is
@@
 The eigenvalues of $\mathbf{J}_{e}(\mathbf{Q})$ are given as
-\begin{equation}
+\begin{equation*}
   \lambda_1 =\lambda_2 = u, \hspace{0.3cm} \lambda_3 = u-c_{e}, \hspace{0.3cm} \lambda_4 = u+c_{e},
-\end{equation}
+\end{equation*}
 where $c_e$ means the sonic speed of the solid in the elastic state,
@@
   where
-  \begin{equation}
+  \begin{equation*}
     b_1 = \frac{\partial p}{\partial \rho} - \Gamma E,  \quad h = E +\frac{p-s_{xx}}{\rho},
-  \end{equation}
+  \end{equation*}
   and
-  \begin{equation}
+  \begin{equation*}
     \phi^2 = a^2 -\frac{\rho_0}{\rho^2} \Gamma_0 s_{xx}-c_e^2 = -\frac{4\mu}{3}\frac{1}{\rho}.
-  \end{equation}
+  \end{equation*}
 
@@
 \emph{\textbf{Left-going rarefaction wave} }
+
 Across the left wave associated with $\lambda_3$-wave, ($\lambda_3=u-c_e$), we have
@@
 where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$.
-Put the above equation into (\ref{eq:e2e1}), we can solve the pressure $p_2$ out as a function of $\rho_2$.
+Put the above equation into (\ref{eq:e2e1}), we can formulate the pressure $p_2$ in terms of $\rho_2$.
 \begin{equation}\label{eq:shocke}
@@
 
-By the above deductions for the moving shock wave, we can find that, if the density after the shock is known, all the data after the shock can be solved out.
+%By the above deductions for the moving shock wave, we can find that, if the density after the shock is known, all the data after the shock can be solved out.
 
@@
 \end{equation}
-the equations of Riemann problem  can be written as
+the equations of Riemann problem  can be simplified as
 \begin{equation}\label{eq:1dp}
@@
  Motion equations of (\ref{eq:1dp}) can be written as
-\begin{equation}
+\begin{equation*}
   \partial_t \mathbf{{U}} + \mathbf{J}_p(\mathbf{U})\partial_x \mathbf{{U}}= 0,
-\end{equation}
+\end{equation*}
  where the Jacobian matrix is
-\begin{equation}
+\begin{equation*}
 \mathbf{J}_p(\mathbf{U}) = \left[\begin{array}{lll}
@@
 \right].
-\end{equation}
+\end{equation*}
 
@@
 $$\lambda_1 = u,\quad \lambda_2 = u-c_p, \quad \lambda_3 = u+c_p,$$
-where
+where $c_p$ shows the sonic speed in the plastic state,  
 \begin{equation}\label{eq:c_p}
@@
 From the above equations, we can easily deduce that
-\begin{equation}
+\begin{equation*}
   du = 0, \quad dp = 0,
-\end{equation}
+\end{equation*}
 %Samilar to that in  section \ref{sec:contacte}, we can also get the relations
 which means that
-\begin{equation}
+\begin{equation*}
 u_L^* = u_R^*, % \hspace{0.3cm} \sigma_L^* = \sigma_R^*,
@@
   p^*_L = p^*_R.
-\end{equation}
+\end{equation*}
 Because $s^*_{xxL} = s^*_{xxR}$, thanks to (\ref{sigma1}), one can get
-\begin{equation}
+\begin{equation*}
   \sigma^*_L = \sigma^*_R.
-\end{equation}
+\end{equation*}
 For convenience, we define
-\begin{equation}
+\begin{equation*}
   s^* = u_L^* = u_R^*.
-\end{equation}
+\end{equation*}
 
@@
 \emph{\textbf{Left-going rarefaction wave} }
+
 Across the left wave associated with $\lambda_2$-wave, ($\lambda_2=u-c_p$), we have
@@
 \end{equation}
-Samilar to section \ref{sec:rarefaction}, we can get the relations
+Similar to Section \ref{sec:rarefaction}, we can get the relations
 \begin{equation}\label{eq:p_rhopL}
@@
 \emph{\textbf{Right-going rarefaction wave} }
-Across the right wave associated with $\lambda_3$-wave, ($\lambda_3=u+c_e$), we have
+
+Across the right wave associated with $\lambda_3$-wave, ($\lambda_3=u+c_p$), we have
 \begin{equation}
@@
 \end{equation}
-We can get  similar  relations  as the left-going wave as
+Similarly, we can get %  similar  relations  as the left-going wave as
 \begin{equation}\label{eq:p_rhopR}
@@
 \subsubsection{Relations across  a shock wave}\label{sec:shockp}
-By using the same deducing process as Section \ref{sec:shock}, we can get the states after the shock wave as
+By using the same deducing process as Section \ref{sec:shock}, we can get the state after the shock wave:
 \begin{equation}
@@
 
-Analyzing the formulation (\ref{eq:rhosxx}), one can find, $\frac{\partial s_{xx}}{\partial \rho}<0$.
+Analyzing (\ref{eq:rhosxx}), one can find, $\frac{\partial s_{xx}}{\partial \rho}<0$.
 So, if the material is compressed and $\rho$ increases, $s_{xx}$ will decrease; if the material is expanded and $\rho$ decreases, $s_{xx}$ will increase.
@@
 The left six cases are  shown in Fig.\ref{fig:cases}.
+Here we remark that \emph{we do not consider vacuum in building our exact Riemann solver}.
 
 \begin{figure}
-%\captionsetup[subfigure]{labelformat=empty}
+\captionsetup[subfigure]{labelformat=empty}
   \centering
@@
   %So, given densities in unknown regions $\mathbf{Q}^*_L$ and  $\mathbf{Q}^*_R$, the Riemann problem is solved.
-From Section  \ref{sec:Riemann}, we can find that all variables can be formulated in terms of the  density. So we define equations
+From Section  \ref{sec:Riemann}, we can find that all variables can be formulated in terms of the  density. So we define functions $f_u$ and $f_\sigma$: 
 \begin{equation} 
@@
 Obviously, this system is uniquely solvable, but we can not get the analytical solution of (\ref{exact1}). We have to use an iteration procedure to solve (\ref{exact1}) and
-%, which is given in the following.
-%Given values of $\rho_L^*$ and  $\rho_R^*$,  by using relations across the contact wave in Section \ref{sec:contacte} and Section \ref{sec:contactp}, we can get
-%\begin{equation}
-%  \begin{aligned}
-%	f_u(\rho_L^*,\rho_R^*)_=  u_L^* -u_R^* =0,\\
-%	f_\sigma(\rho_L^*,\rho_R^*)_=  \sigma_L^* -\sigma_R^* =0.\\
-%\end{aligned}
-%\end{equation}
-%Then using a  Newton iteration method, we can solve the densities $\rho_L^*$ and $\rho_R^*$ out.
 the solving process is shown in Fig.\ref{fig:newton}. The details are introduced in the following.
@@
   \centering
-  \includegraphics[width= 10cm] {Tikz-figure6.eps}
+ % \includegraphics[width= 10cm] {Tikz-figure6.eps}
   \caption{A flow chat of the Newton iteration process.}
@@
 
-  After determining the structures case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$, those are given in Section \ref{sec:functions}.
+  After determining the structures case, we need  to solve  Cauchy stresses and velocities in regions $\mathbf{Q}^*_L$ and $\mathbf{Q}^*_R$ and the details are given in Section \ref{sec:functions}.
 
@@
 \end{equation}
-At the first step, we use a simple  numerical difference  method
+At the first step, we use a simple  numerical difference  method to evaluate
 \begin{equation}
@@
 \end{equation}
-where $\Delta \rho$ is a small quantity, we define it as
+where $\Delta \rho$ is a small quantity, here we define it as
 \begin{equation}
@@
 
- For cases ($R^{E}$, $R^{P}$, $S^{E}$ and $S^{P}$) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no midlle state $\tilde{\mathbf{Q}}_{L(R)}$.
+ For cases ($R^{E}$, $R^{P}$, $S^{E}$ and $S^{P}$) in Fig.\ref{fig:cases}, the material is totally yielding or totally not yielding, there is no middle state $\tilde{\mathbf{Q}}_{L(R)}$.
 For  expression convenience, we let
@@
 For shock waves cases, the  deviatoric stresses in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are given as
-\begin{equation}
+\begin{equation*}
 s_{xx}(\rho) = \left\{\begin{aligned}
@@
   \end{aligned} \right.
-  \end{equation}
-(\ref{eq:shocke}) gives direct expressions for the
-the pressure in the star region as
-\begin{equation}
+  \end{equation*}
+(\ref{eq:shocke}) gives direct expression for the pressure in the star region as
+\begin{equation*}
   p_{L(R)}^*=
   \frac{2t\left(c_1f(\rho_{L(R)}^*/\rho_0)+\tilde{e}_{L(R)}\right)-\left(\tilde{\sigma}_{L(R)}+{s}_{xx}(\rho_{L(R)}^*)\right)}{2tc_0-1},
-\end{equation}
+\end{equation*}
 where $c_0 = \frac{1}{\rho_0\Gamma_0}$, $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho^*_{L(R)} \tilde{\rho}_{L(R)}}{\rho^*_{L(R)}- \tilde{\rho}_{L(R)}}$.
@@
 Thanks to (\ref{eq:shocku}), the velocities in $\mathbf{Q}_{L}^*$  and  $\mathbf{Q}_{R}^*$ are
-\begin{equation}
+\begin{equation*}
   u_{L(R)}^*= \left\{ \begin{aligned}
@@
 \right.
-\end{equation}
+\end{equation*}
 where $\sigma_{L(R)}^* = -p_{L(R)}^*+s_{xxL(R)}^*$.
-%And the state in  the star region is given as
-%\begin{equation}
-%  p^*_{L(R)} = p(\rho_{L(R)}^*),\quad s_{xxL(R)}^* = s_{xx}(\rho_{L(R)}^*),\quad  u^*_{L(R)} = u(\rho_{L(R)}^*).
-%\end{equation}
-
-%\subsubsection{Rarefaction  wave cases (a,b)}
-%For Rarefaction wave, we not only  need to solve the state after the wave in region $\mathbf{Q}_{L(R)}^*$, but also  need to know the states inside the expansion region.
-%
-%First we give the function of $s_{xx}$,
-%\begin{equation}
-%  s_{xx}(\rho) = \left\{\begin{aligned}
-%	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)}, \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (a)},\\
-%	  & \frac{2}{3}Y_0,  \quad & \rho_{L(R)} \ge \rho \ge \rho_{L(R)}^*,  \quad &\text{case (b)}.
-%  \end{aligned} \right.
-%  \end{equation}
-%Then we give the pressure,
-%\begin{equation}
-%  p(\rho)=p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx. \quad  \text{case (a,b)}.
-%\end{equation}
-%where
-%\begin{equation}
-%  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
-%\end{equation}
-%
-%and sonic speed,
-%\begin{equation}
-%  c(\rho) = \left\{ \begin{aligned}
-%	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad & \text{case (a)},\\
-%	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  & \text{case (b)}.
-%	\end{aligned}\right.
-%\end{equation}
-%Then we can get  the  function of  velocity
-%\begin{equation}
-%  u(\rho) =\left\{ \begin{aligned}
-%	  &u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_L \ge \rho \ge \rho_L^*,   \quad &\text{case (a,b)} , \\
-%	  &u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad  & \rho_R \ge \rho \ge \rho_R^*, \quad &\text{case (a,b)}, \\
-%	\end{aligned}
-%  \right.
-%\end{equation}
-%
-%
-%\subsubsection{Shock wave cases (d,e)}
-%For shock waves, the function of deviatoric is given as
-%\begin{equation}
-%  s_{xx}(\rho) = \left\{\begin{aligned}
-%	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad   &\rho =\rho_{L(R)},\rho_{L(R)}^*,
-%	\quad  &\text{case (d)},\\
-%	& -\frac{2}{3}Y_0,   \quad & \rho =\rho_{L(R)},\rho_{L(R)}^*, \quad
-% &\text{case (e)}.
-%  \end{aligned} \right.
-%  \end{equation}
-%And the pressure is given as
-%\begin{equation}
-%  p(\rho)=
-%  \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2tc_0-1}, \quad  \rho=\rho_{L(R)},\rho_{L(R)}^*, \quad
-%  \text{ case (d,e)},
-%\end{equation}
-%where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t=\frac{\rho_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\rho_{L(R)}}$.
-%The velocity is given as
-%\begin{equation}
-%  u(\rho) = \left\{ \begin{aligned}
-%	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t}} \quad &\rho =\rho_L, \rho_L^*\\
-%	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t}} \quad & \rho =\rho_R, \rho_R^*\\
-%  \end{aligned}
-%\right. \quad \text{case (d,e)}
-%\end{equation}
-%
-%\subsection{States for two wave cases (c,f)}\label{sec:two}
-%
-%For cases (c,f), the meterial periods a yielding process from elastic to plastic.
-There are two waves and  one more state $\tilde{\mathbf{Q}}_{L(R)}$ exists.
-In state $\tilde{\mathbf{Q}}_{L(R)}$, the derivative stress achieves the elastic limit.
-%\begin{equation}
-% \tilde{s}_{xxL(R)} = \left\{ \begin{aligned}
-%	 &\frac{2}{3}Y_0 \quad  &\text{Case (c)},\\
-%	 &-\frac{2}{3}Y_0 \quad &\text{Case (f)},
-%	\end{aligned}
-%  \right.
-%\end{equation}
-%By (\ref{eq:rhosxx}),at state $\tilde{\mathbf{Q}}_{L(R)}$ we can solve the density out as
-%\begin{equation}
-%  \tilde{\rho}_{L(R)}= \left\{ \begin{aligned}
-%	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(-\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (c)}, \\
-%	  &\widetilde{\rho}_{L(R)} = \rho_{L(R)} \text{exp}\left(\frac{Y_0}{2\mu}+\frac{3 s_{xxL(R)}}{4\mu}\right), \quad  & \text{Case (f)}.
-%	\end{aligned}
-%  \right.
-%	\end{equation}
-%\subsubsection{Rarefaction wave case (c)}
-%For rarefaction wave case,
-%we give the function of $s_{xx}$ at first,
-%\begin{equation}
-%  s_{xx}(\rho) = \left\{\begin{aligned}
-%	& -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}  ,\\
-%	& \frac{2}{3}Y_0, & \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.\\
-%  \end{aligned} \right. \quad \text{case (c)}.
-%  \end{equation}
-%
-%The pressure is given as
-%\begin{equation}
-%  p(\rho)= \left\{ \begin{aligned}
-%	  p_{L(R)}e^{\frac{\lambda_1}{\rho_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\rho_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,\quad & \rho_{L(R)}\ge \rho \ge \tilde{\rho}_{L(R)},\\
-%	  \tilde{p}_{L(R)}e^{\frac{\lambda_1}{\tilde{\rho}_{L(R)}}-\frac{\lambda_1}{\rho}} +e^{-\frac{\lambda_1}{\rho}}\int_{\tilde{\rho}_{L(R)}}^{\rho} f_2(x) e^{\frac{\lambda_1}{x}}dx,  \quad & \tilde{\rho}_{L(R)}\ge \rho \ge \rho_{L(R)}^*,
-%  \end{aligned} \right.
-%  \text{case (c)},
-%\end{equation}
-%where
-%\begin{equation}
-%  \lambda_1 = \rho_0 \Gamma_0 \quad f_2(\rho) = a_0^2\frac{\partial f}{\partial \eta}- \lambda_1\frac{s_{xx}(\rho)}{\rho^2}.
-%\end{equation}
-%
-%And sonic speed,
-%\begin{equation}
-%  c(\rho) = \left\{ \begin{aligned}
-%	&  \sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho) +\frac{4}{3}\frac{\mu}{\rho}} \quad  & \rho_{L(R)} \ge \rho \ge \tilde{\rho}_{L(R)}\\
-%	&	\sqrt{a_0^2 \frac{\partial f}{\partial \eta} + \frac{p(\rho)}{\rho^2}\rho_0\Gamma_0 -\frac{\rho_0}{\rho^2}\Gamma_0 s_{xx}(\rho)}  \quad  &   \tilde{\rho}_{L(R)} \ge \rho \ge \rho_{L(R)}^*.
-%  \end{aligned}\right. \quad \text{case (c)}.
-%\end{equation}
-%Then we can get  the   function of  velocity
-%\begin{equation}
-%  u(\rho) =\left\{ \begin{aligned}
-%	&u_L - \int_{\rho_L}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge \rho_L^* , \\
-%	&u_R + \int_{\rho_R}^{\rho} \frac{c(x)}{x} dx, \quad &  \rho_L\ge \rho\ge  \rho_R^* ,
-%	\end{aligned}
-%  \right. \quad \text{case (c)}.
-%\end{equation}
-%\subsubsection{Shock wave case (f)}
-%For shock waves the function of deviatoric is given as
-%\begin{equation}
-%  s_{xx}(\rho) = \left\{\begin{aligned}
-%	  & -\frac{4}{3}\mu\text{ln}\left(\frac{\rho}{\rho_{L(R)}}\right)+s_{xxL(R)},\quad &  \rho =\rho_{L(R)},\tilde{\rho}_{L(R)},\\
-%	  & -\frac{2}{3}Y_0, \quad  & \rho = \rho_{L(R)}^*,
-%  \end{aligned} \right. \quad  \text{case (f)}.
-%  \end{equation}
-%
-%And the pressure is given as
-%\begin{equation}
-%  p(\rho)= \left\{\begin{aligned}
-%	  & \frac{2t(c_1f(\rho/\rho_0)+e_L)-(\sigma_{L(R)}+s_{xx}(\rho))}{2t_1c_0-1}, \quad  &  \rho=\rho_{L(R)},\tilde{\rho}_{L(R)},\\
-%	  & \frac{2t(c_1f(\rho/\rho_0)+\tilde{e}_L)-(\tilde{\sigma}_{L(R)}+s_{xx}(\rho))}{2t_2c_0-1}, \quad  &  \rho=\rho_{L(R)}^*,\\
-%  \end{aligned}\right.
-%  \text{ case (f)},
-%\end{equation}
-%where $c_0 = \frac{1}{\rho_0\Gamma_0}$ and $c_1 = \frac{a_0^2}{\Gamma_0}$ and $ t_1=\frac{\rho_{L(R)} \tilde{\rho}_{L(R)}}{\tilde{\rho}_{L(R)}-\rho_{L(R)}}$, $ t_2=\frac{\tilde{\rho}_{L(R)} \rho_{L(R)}^*}{\rho_{L(R)}^*-\tilde{\rho}_{L(R)}}$.
-%
-%The velocity is given as
-%\begin{equation}
-%  u(\rho) = \left\{ \begin{array}{ll}
-%	  u_L -\sqrt{\frac{\sigma_L-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_L,\tilde{\rho}_L,\\
-%	  \tilde{u}_L -\sqrt{\frac{\tilde{\sigma}_L-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_L^*,\\
-%	  u_R +\sqrt{\frac{\sigma_R-\sigma(\rho)}{t_1}}, \quad &\rho = \rho_R, \tilde{\rho}_R, \\
-%	\tilde{u}_R +\sqrt{\frac{\tilde{\sigma}_R-\sigma(\rho)}{t_2}}, \quad &\rho = \rho_R^*, \end{array}
-%  \right. \quad \text{case (f)}.
-%\end{equation}
 %
@@
 Shown in Fig.\ref{fig:half}, in these cases, we only need to solve states in one side.
-There are six possible cases just like them in Section \ref{sec:Riemann}.
+There are six possible cases which are introduced in Section \ref{sec:Riemann}.
 Here we will use the example shown in Fig.\ref{fig:half} to show how to solve the half Riemann problem.
@@
   \centering
-  \includegraphics[width= 10cm] {Tikz-figure8.eps}
+ % \includegraphics[width= 10cm] {Tikz-figure8.eps}
   \caption{Half Riemann problem  with a given left velocity or Cauchy stress.}
@@
 The derivatives of $f$ is  given by
-\begin{equation}
-  \frac{\partial f_{(k+1)}}{\partial \rho^*} = \frac{f_{(k+1)}-f_{(k)}}{\rho_{(k+1)}^* - \rho^*_{(k)}},
-\end{equation}
-At the first step, we use a simple  numerical difference  method
-\begin{equation}
+\begin{equation*}
+  \frac{\partial f_{(k)}}{\partial \rho^*} = \frac{f_{(k)}-f_{(k-1)}}{\rho_{(k)}^* - \rho^*_{(k-1)}}, \ \text{for} \ k>1
+\end{equation*}
+At the first step, %we use a simple  numerical difference  method
+\begin{equation*}
   \frac{\partial f_{(1)}}{\partial \rho^*} = \frac{f(\rho^*+\Delta \rho)-f(\rho^*)}{\Delta \rho},
-\end{equation}
+\end{equation*}
 where $\Delta \rho$ is a small quantity, here we set $\Delta \rho = \frac{\rho_{(1)}^*}{100}$.
@@
 
-\begin{equation}
+\begin{equation*}
  \rho^*_{(k+1)} = \rho^*_{(k)}- f/\frac{\partial f_{(k)}}{\partial \rho}.
-\end{equation}
+\end{equation*}
 
@@
 The yielding strengths of the two materials are $Y_{0,\text{Al}} = 3\times 10^8 \text{Pa}$ and   $Y_{0,\text{Copper}} = 9\times 10^7 \text{Pa}$, respectively.
-The computational domain is set to be $[0,1m]$ with 800 cell points and the intial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.
+The computational domain is set to be $[0,1m]$ with 800 cell points and the initial interface is located at $0.5m$, the terminal time is $t=5\times 10^{-5}s$.
 Otherwise, in the initial condition, "L" and "R" mean $x<0.5m$ and $x>0.5m$, respectively.
@@
 \subsection{Test 1}
-In this case, the material is yielding at both sides, so the solution structures has three waves with two plastic shock waves and one contact.
+In this case, the material is yielding at both sides, so there are three waves with two plastic shock waves and one contact.
 The initial condition is
@@
 
-    \caption{Comparison results for Test 1 with the structures of $S^P|S^P$.  }
+    \caption{Comparison for Test 1 with the structure of $S^P|S^P$.  }
   \label{fig:case1}
@@
   \includegraphics[width= 7cm] {case2sxx.pdf}
-  \caption{Comparison results for Test 2 with the structures of $S^ES^P|S^PS^E$.  }
+  \caption{Comparison for Test 2 with the structure of $S^ES^P|S^PS^E$.  }
   \label{fig:case2}
@@
 \subsection{Test 3}
-In this example, we test the case with two elastic rarefaction waves. In the wave structures there is one elastic rarefaction wave on each side of the contace wave. The initial condition is given as
+In this example, we test the case with two elastic rarefaction waves. In the wave structure there is one elastic rarefaction wave on each side of the contact wave. The initial condition is given as
 \begin{equation}
@@
 \end{equation}
-Results are shown in Fig.\ref{fig:case4},  the results of the exact solver matches the numerical results very well.
+Results are shown in Fig.\ref{fig:case4},  the results of the exact solver match the numerical results very well.
 
@@
 
-    \caption{Comparison results for Test 4 with the wave structures of $R^ER^P|R^PR^E$.  }
+    \caption{Comparison for Test 4 with the wave structure of $R^ER^P|R^PR^E$.  }
   \label{fig:case4}
@@
   \includegraphics[width= 7cm] {case20sxx.pdf}
-    \caption{Comparison results for Test 5 with the structures of $R^ER^P|R^PR^E$.  }
+    \caption{Comparison results for Test 5 with the structure of $R^ER^P|R^PR^E$.  }
   \label{fig:case20}
@@
 $s_{xxL(R)}=\frac{2}{3}{Y}^{0}$).
-According to the analysis introduced in Section \ref{sec:relation}, after an compressing  process the material will turn back into an elastic state and will yield again into a negtive plastic state, we can get the exact  solutions match the numerical solutions very well by the new Riemann solver in Fig.\ref{fig:case21}.
+According to the analysis introduced in Section \ref{sec:relation}, after an compressing  process the material will turn back into an elastic state and will yield again into a negative plastic state.
+We can get the exact  solutions which match the numerical solutions very well in Fig.\ref{fig:case21}.
 
@@
   \includegraphics[width= 7cm] {case21sxx.pdf}
-    \caption{Comparison results for Test 6 with the structures of $S^ES^P|S^PS^E$.  }
+    \caption{Comparison results for Test 6 with the structure of $S^ES^P|S^PS^E$.  }
   \label{fig:case21}
@@
 
-    \caption{Comparison resutls for Test 7 with the structures of $R^P|R^PR^E$.  }
+    \caption{Comparison results for Test 7 with the structure of $R^P|R^PR^E$.  }
   \label{fig:case5}
@@
 
-    \caption{Comparison resutls for Test 8 with the structures of $R^ER^P|S^PS^E$.  }
+    \caption{Comparison results for Test 8 with the structure of $R^ER^P|S^PS^E$.  }
   \label{fig:case9}
@@
 Now we will consider two multi-material tests with different materials on both sides.
-In this test, on the left side, a lighter material of aluminum with a velocity impact to a heavier material of Copper.
+In this test, on the left side, the lighter material of aluminum impacts the heavier material of Copper.
 The initial condition is given as
@@
 \end{equation}
-Show in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface.
+Shown in the Fig.\ref{fig:case7}, there is a large jump of density at the material interface and  both elastic shock and plastic shock exist in each side of the interface.
 Comparing to the numerical results of the scheme with MHLLCEP approximate solver, we can find that our exact Riemann solver can solve the Riemann problem with multi-materials very well.
@@
 
-    \caption{Comparison results for Test 9 with the structures of $R^ER^P|R^PR^E$.  }
+    \caption{Comparison results for Test 9 with the structure of $R^ER^P|R^PR^E$.  }
   \label{fig:case7}
@@
 
-    \caption{Comparison results for Test 10 with the structures of $R^ER^P|S^ES^P$.  }
+    \caption{Comparison results for Test 10 with the structure of $R^ER^P|S^ES^P$.  }
   \label{fig:case8}
@@
 \subsection{Test 11}
-This test is a half Riemann problem with a given left velocity $u^* = -20\text{m/s}$, and the right initial condition is
+This test is the half Riemann problem with a given velocity $u^* = -20\text{m/s}$ on the left, and the right initial condition is
 \begin{equation}
@@
 
-    \caption{Comparison results for Test 11 with the structures of $S^ES^P$.  }
+    \caption{Comparison results for Test 11 with the structure of $S^ES^P$.  }
   \label{fig:case9}
@@
 \subsection{Test 12}
-The second half Riemann case is with a given left Cauchy stress $\sigma^* = 0 \text{Pa}$, and the right initial condition is
+The second half Riemann case is with a given Cauchy stress $\sigma^* = 0 \text{Pa}$ on the left, and the right initial condition is
 \begin{equation}
@@
   \includegraphics[width= 7cm] {case11sigma.pdf}
-    \caption{Comparison results for Test 11 with the structures of $R^ER^P$.  }
-  \label{fig:case12}
+    \caption{Comparison results for Test 11 with the structure of $R^ER^P$.  }
+  \label{fig:case10}
 \end{figure}
@@
 \section{Results}
-In this paper, we give a detailed analysis of the Riemann problem for one-dimensional  multi-material elastic-plastic flows with the  Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and the von Mises' yielding condition.
-Some useful results are found through the analysing:
+In this paper, we have analyzed in detail the Riemann problem for one-dimensional  multi-material elastic-plastic flows with the  Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and the von Mises' yielding condition and found %some useful results are found through the analysing:
 \begin{enumerate}
 	\item The sonic speed periods a significant jump when the material is yielding.
+
 	\item the plastic wave is always faster than the elastic wave for the reason of the sonic speed jump.
 
-	  \item There are only thirty-six possible cases of the structrues in the Riemann problem.
-
-	\item All the variables after the wave can be written as functions of the density theoretically.
+	  \item There are only thirty-six possible cases of the wave structure in the Riemann problem.
+
+	 \item All the variables after the non-linear waves can be written as functions of the density theoretically.
 
@@
 
-  \section{Numerical intergration for the rarefaction wave}
+  \section{Numerical integration for the rarefaction wave}
   There are two integrations in  functions $p(\rho)$ and $u(\rho)$ in the rarefaction wave, for example,  in the equations (\ref{rerpp}) and (\ref{rerpu}).
@@
 $$\text{Intg}_1 = \frac{\rho - \rho_{L(R)}}{2} \sum_{n=1}^4 \omega_i f_2(\rho_i) e^{\lambda/\rho_i},$$
-
 and $\rho_i =  \frac{\rho-\rho_{L(R)}}{2}x_i+\frac{\rho_{L(R)}+\rho}{2} $.
@@
 
-The numerical intergration of $u(\rho)$ is given as
+The numerical integration of $u(\rho)$ is given as
 \begin{equation}
